### 2021-04-10 notes/erf_setup/erf_cartesian_setup.tex
adds erf setup notes into the repo

\documentclass[12pt,preprint]{article}
\usepackage{natbib}
\bibliographystyle{plain}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}

\usepackage{pb-diagram}

\parindent = 0.0 in
\parskip = 0.15 in

\newcommand\Beq{\begin{align}} 
\newcommand\Eeq{\end{align}}

\newcommand\Bfig{\begin{figure}} 
\newcommand\Efig{\end{figure}}

\newcommand\Ra{\mathrm{Ra}}
\newcommand\Pran{\mathrm{Pr}}
\newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
\newcommand\Ek{\mathrm{Ek}}
\newcommand\Ro{\mathrm{Ro}}
\newcommand\Nu{\mathrm{Nu}}
\newcommand\Sc{\mathrm{Sc}}

\newcommand\eps{\varepsilon}
\renewcommand\L {\mathcal{L}}

\newcommand{\n}{\\ \nonumber \\ }
\newcommand{\nn}{\nonumber}
\newcommand{\nnn}{\\ \nonumber \\ \nonumber}

\newcommand\ie{\textit{i.e.},~}
\newcommand\eg{\textit{e.g.},~}
\newcommand{\omicron}{o}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

\newcommand{\sump}[2]{\sideset{}{'}\sum_{{#1}=0}^{#2}}

\newcommand{\eq}[1]{eq.~(\ref{#1})}
\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\Eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\figs}[2]{Figs.~(\ref{#1})~\&~(\ref{#2})}

\newcommand{\tbl}[1]{Table~(#1)}

\begin{document}

\section{Nondimensional equations}
The nondimensional system of equations we solve is
\begin{align}
&\grad\dot\vec{u} = 0 \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \rm{Re}_0^{-1}\grad^2 \vec{u} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = \rm{Pe}_0^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
\end{align}
These are just the Boussinesq equations of motion, with some slight tweaks:
\begin{enumerate}
\item There is a nonzero adiabatic temperature gradient, $\partial_z T_{\rm{ad}} = -\grad_{\rm{ad}}$.
We choose this sign convention ($\grad_{\rm{ad}}$ and similarly $\grad_{\rm{rad}}$ will be positive) to align better with the stellar structure community's intuition.
$|\grad T_0|$ and $\grad_{\rm{ad}}$ may be much larger in magnitude than the convective fluctuations.
The background temperature field $T_0$ does not enter into the momentum equation, as it is automatically canceled by a background $\grad \varpi$.
\item Convection is driven by internal heating, $Q$.
I've confirmed with some simple tests that $|u|^2 \approx Q$, and therefore the convective frequency is $f_{\rm{conv}}^2 \approx Q$.
\item The control freefall P\'{e}clet number, $\rm{Pe}_0$, and the diffusivity associated with it, only acts on fluctuations, not on the $k_x = 0$ mode.
For the $k_x = 0$ mode, we model the radiative flux as $F_{\rm{rad}} = -k \grad \overline{T}$, where $k$ is a nonconstant coefficient, $k(z)$.
$k$ may be a larger or smaller diffusivity than $\rm{Pe}_0^{-1}$, and its magnitude is set by $\int Q\, dz \approx -k \grad\overline{T}$.
\end{enumerate}

\section{Model Setup}
We will study a two-layer model in $z = [0, L_z]$ in which the conductivity, $k(z)$ is a step function such that
\begin{equation}
k(z) = \begin{cases}
k_b & z < 1 \\
k_t & z \geq 1
\end{cases}
\end{equation}
where subscript ``t'' refers to the top layer and ``b'' refers to the bottom.
(These won't be true discontinuities, but will be smooth step-like functions achieved with erfs.)

There will be two important input parameters in this system:
\begin{enumerate}
\item The stiffness, 
\begin{equation}
\mathcal{S} = \frac{N_{t}^2}{f_{\mathrm{conv}}^2},
\end{equation}
which is the ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
\item $\mathcal{P}$, a parameter which determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
We will define $\mathcal{P} = -F_{\rm{conv, rz}}/F_{\rm{conv}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \ll 1$ and none when $\mathcal{P} \gg 1$.
\end{enumerate}
In addition to these parameters, the magnitude of the heating, $Q$ and the vertical extent of the heating layer, $\delta_H$, must be specified as they set $F_{\rm{conv}} = Q \delta_H$.
We will choose $Q = 1$ and $\delta_H = 0.2$ so that $F_{\rm{conv}} = 0.2$; we will furthermore choose and $F_{\rm{bot}} = \zeta F_{\rm{conv}}$, where $\zeta$ is some arbitrary scalar that sets how much smaller $k$ is in the cz than the RZ; we'll set $\zeta = 10^{-3}$ for now.

Under these choices, the system is determined by five equations,
\begin{enumerate}
\item At some point, the adiabatic gradient is equal to the radiative gradient,
\begin{equation}
k_{\rm{ad}}\grad_{\rm{ad}} = F_{\rm{tot}}.
\end{equation}
\item at $z = 0$, the base of the CZ, the adiabatic temperature gradient is the radiative gradient, $\grad_{\rm{ad}} = \grad_{\rm{rad}}$, and carries $F_{\rm{bot}}$,
\begin{equation}
k_b \grad_{\rm{ad}} = F_{\rm{bot}}
\end{equation}
\item The radiative gradient can carry the flux in the RZ,
\begin{equation}
k_{t} \grad_{\rm{rad,t}} = F_{\rm{tot}}
\end{equation}
\item Assuming $\grad T = -\grad_{\rm{ad}}$ everywhere, the convective flux in the top layer is $F_{\rm{conv,t}} = F_{\rm{conv}} - \Delta k \grad_{\rm{ad}}$, where $F_{\rm{conv}} = Q \delta_H$ and $\Delta k = k_t - k_b$.
Thus, definitionally,
\begin{equation}
\mathcal{P} = -\frac{F_{\rm{conv,t}}}{F_{\rm{conv}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right).
\end{equation}
\item Defining $f_{\rm{conv}}^2 \approx Q$ and $N^2 \approx -(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})$, the stiffness gives
\begin{equation}
\mathcal{S} = \frac{N^2}{f_{\mathrm{conv}}^2} = \frac{-(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})}{Q}
= \frac{F_{\mathrm{tot}}}{Q}(k_{\rm{ad}}^{-1} - k_t^{-1})
\end{equation}
\end{enumerate}

Solving this system of equations gives
\begin{align}
k_t = \frac{\delta_H \mathcal{P}}{\mathcal{S}},\qquad
k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}},\qquad
k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}},\\
\grad_{\rm{ad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta + \mathcal{P}),\qquad
\grad_{\rm{rad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta).
\end{align}

Just to be safe, I'm going to offset the internal heating from the bottom boundary.
We wouldn't need to do this if we didn't have a bottom, impenetrable boundary condition with a viscous boundary layer.
But, since $w \rightarrow 0$ at the bottom boundary, I don't want to inject heating into the domain somewhere where it must be carried by a superadiabatic temperature gradient (I explicitly don't want to study boundary-driven convection).
So
\begin{equation}
Q(z) = \begin{cases}
0 & z < 0.1 \\
Q & 0.1 \leq z < 0.1 + \delta_H, \\
0 & \text{elsewhere}
\end{cases}.
\end{equation}

We then choose $T_0$ to satisfy
\begin{equation}
\partial_z T_0 =
-\begin{cases}
\grad_{\mathrm{ad}} & z \leq 1 \\
\grad_{\mathrm{rad}} & z > 1
\end{cases}
\end{equation}
(again, perhaps not perfectly this, but with smooth transitions).
And we're off to the races.

\bibliography{biblio.bib}
\end{document}

### 2021-04-16 dedalus_code/erf_step.py
initial mapping of P -> 1/P

@@ -6,7 +6,7 @@ The lower part of the domain is stable; the domain is Schwarzschild stable above
 There are 6 control parameters:
     Re      - The approximate reynolds number = (u / diffusivity) of the evolved flows
     Pr      - The Prandtl number = (viscous diffusivity / thermal diffusivity)
-    P       - The penetration parameter; When P << 1 there is lots of convective penetration (of order 1/P); when P -> infty there is none.
+    P       - The penetration parameter; When P >> 1 there is lots of convective penetration (of order P); when P -> 0 there is none.
     S       - The stiffness: the characteristic ratio of N^2 (above the penetration region) compared to the square convective frequency.
     zeta    - The fraction of the convective flux carried by the adiabatic gradient at z = 0 (below the heating layer)
     Lz      - The height of the box
@@ -19,7 +19,7 @@ Usage:
 Options:
     --Re=<Reynolds>            Freefall reynolds number [default: 1e2]
     --Pr=<Prandtl>             Prandtl number = nu/kappa [default: 0.5]
-    --P=<penetration>          ratio of RZ convective flux / CZ convective flux [default: 1]
+    --P=<penetration>          ratio of CZ convective flux / RZ convective flux [default: 1]
     --S=<stiffness>            The stiffness [default: 1e2]
     --zeta=<frac>              Fbot = zeta * F_conv [default: 1e-3]
     --Lz=<L>                   Depth of domain [default: 2]
@@ -257,6 +257,7 @@ def run_cartesian_instability(args):
     S  = float(args['--S'])
     Pr = float(args['--Pr'])
     P = float(args['--P'])
+    invP = 1/P
 
     Pe0   = Pr*Re0
     Lz    = float(args['--Lz'])
@@ -269,12 +270,12 @@ def run_cartesian_instability(args):
     Fbot = zeta*Fconv
 
     #Model values
-    k_rz = dH * P / S 
-    k_cz = k_rz * ( zeta / (1 + zeta + P) )
-    k_ad = k_rz * ( (1 + zeta) / (1 + zeta + P) )
+    k_rz = dH * invP / S 
+    k_cz = k_rz * ( zeta / (1 + zeta + invP) )
+    k_ad = k_rz * ( (1 + zeta) / (1 + zeta + invP) )
     delta_k = k_rz - k_cz
[…]

### 2021-04-16 dedalus_code/plotting/full_post_process.sh
aligns pleiades job scripts with new inverted P formulation

@@ -10,7 +10,7 @@ NCORE=""
 while getopts ":d:n:h?:" opt; do
     case "$opt" in
     h|\?)
-        echo "secify dir with -d and core number with -n" 
+        echo "specify dir with -d and core number with -n" 
         exit 0
         ;;
     d)  DIR=$OPTARG

### 2021-04-16 dedalus_code/erf_step.py
adds flag that determines the location of the conductivity erf

@@ -24,6 +24,7 @@ Options:
     --zeta=<frac>              Fbot = zeta * F_conv [default: 1e-3]
     --Lz=<L>                   Depth of domain [default: 2]
     --aspect=<aspect>          Aspect ratio of domain [default: 2]
+    --L_cz=<L>                 Height of cz-rz erf step [default: 1]
 
     --nz=<nz>                  Vertical resolution   [default: 256]
     --nx=<nx>                  Horizontal resolution [default: 64]
@@ -235,7 +236,7 @@ def run_cartesian_instability(args):
     #############################################################################################
     ### 1. Read in command-line args, set up data directory
     data_dir = args['--root_dir'] + '/' + sys.argv[0].split('.py')[0]
-    data_dir += "_Re{}_P{}_zeta{}_S{}_Lz{}_Pr{}_a{}_{}x{}".format(args['--Re'], args['--P'], args['--zeta'], args['--S'], args['--Lz'], args['--Pr'], args['--aspect'], args['--nx'], args['--nz'])
+    data_dir += "_Re{}_P{}_zeta{}_S{}_Lz{}_Lcz{}_Pr{}_a{}_{}x{}".format(args['--Re'], args['--P'], args['--zeta'], args['--S'], args['--Lz'], args['--L_cz'], args['--Pr'], args['--aspect'], args['--nx'], args['--nz'])
     if args['--predictive']:
         data_dir += '_predictive'
     if args['--adiabatic_IC']:
@@ -260,6 +261,7 @@ def run_cartesian_instability(args):
     invP = 1/P
 
     Pe0   = Pr*Re0
+    L_cz  = float(args['--L_cz'])
     Lz    = float(args['--Lz'])
     Lx    = aspect * Lz
 
@@ -317,10 +319,10 @@ def run_cartesian_instability(args):
     for f in [T_ad_z, k0]:
         f.meta['x']['constant'] = True
 
-    cz_mask['g'] = zero_to_one(z_de, 0.2, width=0.05)*one_to_zero(z_de, 1, width=0.05)
+    cz_mask['g'] = zero_to_one(z_de, 0.2, width=0.05)*one_to_zero(z_de, L_cz, width=0.05)
 
     delta = 0.02
-    k_shape = lambda z: zero_to_one(z, 1, width=0.075)
[…]

### 2021-04-16 mesa_model/solar_model.py
updates to mesa profile plotting from adam

@@ -33,41 +33,42 @@ mass, r = mass.cgs, r.cgs
 rho = 10**p.logRho[::-1] * u.g / u.cm**3
 P = 10**p.logP[::-1] * u.g / u.cm / u.s**2
 T = 10**p.logT[::-1] * u.K
+g = p.grav[::-1] * (u.cm / u.s**2)
 opacity = p.opacity[::-1] * (u.cm**2 / u.g)
 Luminosity = p.luminosity[::-1] * u.L_sun
 Luminosity = Luminosity.cgs
 mlt_conv_vel = p.conv_vel * u.cm / u.s
-g = constants.G.cgs*mass/r**2
-
 conv_lum = p.conv_L_div_L[::-1] * Luminosity
+rad_lum = 10**(p.log_Lrad[::-1])* u.L_sun
+rad_lum = rad_lum.cgs
 
-grad_rad = p.gradr[::-1]
+
+#Get the gradients => grad = dlnT/dlnP
+#grad = dlnT/dlnP = (dlnT/dr)*(dr/dlnP) = (P/T)*(dT/dr)*(dr/dP)
+grad_rad = 3*opacity*P*Luminosity / (16 * constants.sigma_sb.cgs * g * T**4 * 4 * np.pi * r**2)
+grad_actual = p.gradT[::-1]
 grad_ad  = (p.gradr_div_grada[::-1])**(-1) * grad_rad
 
-
+#Radiative conductivity
 rad_cond = 16 * constants.sigma_sb.cgs * T**3 / (3 * rho * opacity) # = rho * cp * rad_diffusivity
 rad_cond = rad_cond.cgs
 
+#Calculate temperature gradients
+grad_T_rad = -(T/P)*rho*g*grad_rad
+grad_T_ad  = -(T/P)*rho*g*grad_ad
+grad_T_actual  = -(T/P)*rho*g*grad_actual
 
-
-#grad = dlnT/dlnP = (dlnT/dr)*(dr/dlnP) = (P/T)*(dT/dr)*(dr/dP)
-my_grad_rad = 3*opacity*P*Luminosity / (16 * constants.sigma_sb.cgs * g * T**4 * 4 * np.pi * r**2)
-
-
+#Find bottom of CZ
 bot_cz = sop.brentq(interp1d(r, grad_rad - grad_ad), (0.6*u.R_sun).cgs.value, (0.8*u.R_sun).cgs.value)
[…]

### 2021-04-16 notes/erf_setup/erf_cartesian_setup.tex
updates model setup pdf with P -> 1/P change

@@
 k(z) = \begin{cases}
-k_b & z < 1 \\
-k_t & z \geq 1
+k_b & z < L_{\rm{cz}} \\
+k_t & z \geq L_{\rm{cz}}
 \end{cases}
@@
 where subscript ``t'' refers to the top layer and ``b'' refers to the bottom.
+Generally, we will set $L_{\rm{cz}} = 1$.
 (These won't be true discontinuities, but will be smooth step-like functions achieved with erfs.)
@@
 which is the ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
-\item $\mathcal{P}$, a parameter which determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
-We will define $\mathcal{P} = -F_{\rm{conv, rz}}/F_{\rm{conv}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \ll 1$ and none when $\mathcal{P} \gg 1$.
+\item $\mathcal{P}$, a parameter which sets the penetration depth.
+$\mathcal{P}$ determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
+We will define $\mathcal{P} = -F_{\rm{conv}}/F_{\rm{conv, rz}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \gg 1$ and none when $\mathcal{P} \ll 1$.
 \end{enumerate}
@@
 \begin{equation}
-\mathcal{P} = -\frac{F_{\rm{conv,t}}}{F_{\rm{conv}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right).
+\mathcal{P} = -\frac{F_{\rm{conv}}}{F_{\rm{conv,t}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right)^{-1}.
 \end{equation}
@@
 \begin{align}
-k_t = \frac{\delta_H \mathcal{P}}{\mathcal{S}},\qquad
-k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}},\qquad
-k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}},\\
-\grad_{\rm{ad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta + \mathcal{P}),\qquad
-\grad_{\rm{rad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta).
+k_t = \frac{\delta_H}{\mathcal{S} \mathcal{P}},\qquad
+k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}^{-1}},\qquad
+k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}^{-1}},\\
+\grad_{\rm{ad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta + \mathcal{P}^{-1}),\qquad
+\grad_{\rm{rad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta).
 \end{align}

### 2021-04-16 dedalus_code/erf_step.py
improves readability of P and invP in erf_step.py

@@ -272,12 +272,12 @@ def run_cartesian_instability(args):
     Fbot = zeta*Fconv
 
     #Model values
-    k_rz = dH * invP / S 
+    k_rz = dH / (P * S) 
     k_cz = k_rz * ( zeta / (1 + zeta + invP) )
     k_ad = k_rz * ( (1 + zeta) / (1 + zeta + invP) )
     delta_k = k_rz - k_cz
-    grad_ad = (Qmag * S / invP) * (1 + zeta + invP)
-    grad_rad_top = (Qmag * S / invP) * (1 + zeta)
+    grad_ad = (Qmag * S * P) * (1 + zeta + invP)
+    grad_rad_top = (Qmag * S * P) * (1 + zeta)
 
     #Adjust to account for expected velocities. and larger m = 0 diffusivities.
     Pe0 /= (np.sqrt(Qmag))

### 2021-04-24 dedalus_code/erf_step.py
adds AE and predictive-IC to 2D script

@@ -40,7 +40,8 @@ Options:
     --root_dir=<dir>           Root directory for output [default: ./]
 
     --adiabatic_IC             If flagged, set the background profile as a pure adiabat (not thermal equilibrium in RZ)
-    --predictive               If flagged, predict the evolved state using a 1D model.
+    --predictive=<delta>       A guess for delta_P the penetration depth. The initial state grad(T) will be an erf from grad(T_ad) to grad(T_rad) centered at L_cz + delta_P
+    --T_iters=<N>              Number of times to iterate background profile before pure timestepping [default: 10]
     --plot_model               If flagged, create and plt.show() some plots of the 1D atmospheric structure.
 
 """
@@ -236,9 +237,9 @@ def run_cartesian_instability(args):
     #############################################################################################
     ### 1. Read in command-line args, set up data directory
     data_dir = args['--root_dir'] + '/' + sys.argv[0].split('.py')[0]
-    data_dir += "_Re{}_P{}_zeta{}_S{}_Lz{}_Lcz{}_Pr{}_a{}_{}x{}".format(args['--Re'], args['--P'], args['--zeta'], args['--S'], args['--Lz'], args['--L_cz'], args['--Pr'], args['--aspect'], args['--nx'], args['--nz'])
-    if args['--predictive']:
-        data_dir += '_predictive'
+    data_dir += "_Re{}_P{}_zeta{}_S{}_Lz{}_Lcz{}_Pr{}_a{}_Titer{}_{}x{}".format(args['--Re'], args['--P'], args['--zeta'], args['--S'], args['--Lz'], args['--L_cz'], args['--Pr'], args['--aspect'], args['--T_iters'], args['--nx'], args['--nz'])
+    if args['--predictive'] is not None:
+        data_dir += '_predictive{}'.format(args['--predictive'])
     if args['--adiabatic_IC']:
         data_dir += '_adiabaticIC'
     if args['--label'] is not None:
@@ -278,6 +279,7 @@ def run_cartesian_instability(args):
     delta_k = k_rz - k_cz
     grad_ad = (Qmag * S * P) * (1 + zeta + invP)
     grad_rad_top = (Qmag * S * P) * (1 + zeta)
+    delta_grad = grad_ad - grad_rad_top
 
     #Adjust to account for expected velocities. and larger m = 0 diffusivities.
     Pe0 /= (np.sqrt(Qmag))
[…]

### 2021-04-24 notes/penetration_argument/penetration_argument.tex
adds zeroth order penetration argument doc

\documentclass[12pt,preprint]{article}
\usepackage{natbib}
\bibliographystyle{plain}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}

\usepackage{pb-diagram}

\parindent = 0.0 in
\parskip = 0.15 in

\newcommand\Beq{\begin{align}} 
\newcommand\Eeq{\end{align}}

\newcommand\Bfig{\begin{figure}} 
\newcommand\Efig{\end{figure}}

\newcommand\Ra{\mathrm{Ra}}
\newcommand\Pran{\mathrm{Pr}}
\newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
\newcommand\Ek{\mathrm{Ek}}
\newcommand\Ro{\mathrm{Ro}}
\newcommand\Nu{\mathrm{Nu}}
\newcommand\Sc{\mathrm{Sc}}

\newcommand\eps{\varepsilon}
\renewcommand\L {\mathcal{L}}

\newcommand{\n}{\\ \nonumber \\ }
\newcommand{\nn}{\nonumber}
\newcommand{\nnn}{\\ \nonumber \\ \nonumber}

\newcommand\ie{\textit{i.e.},~}
\newcommand\eg{\textit{e.g.},~}
\newcommand{\omicron}{o}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

\newcommand{\sump}[2]{\sideset{}{'}\sum_{{#1}=0}^{#2}}

\newcommand{\eq}[1]{eq.~(\ref{#1})}
\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\Eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\figs}[2]{Figs.~(\ref{#1})~\&~(\ref{#2})}

\newcommand{\tbl}[1]{Table~(#1)}

\begin{document}

%\section{Nondimensional equations}
%The nondimensional system of equations we solve is
%\begin{align}
%&\grad\dot\vec{u} = 0 \\
%&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \rm{Re}_0^{-1}\grad^2 \vec{u} \\
%&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = \rm{Pe}_0^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
%\end{align}

\section{Convective Penetration argument}
First some definitions:
\begin{enumerate}
\item $z=L_s$ is the the top of the convection zone according to the Schwarzschild criterion; it's the height where $\grad_{\rm{ad}} = \grad_{\rm{rad}}$.
\item $L_{\rm{cz}}$ is the top of the convection zone; it's roughly the top of the region where convection flattens $\grad \rightarrow \grad_{\rm{ad}}$.
We generally get $L_{\rm{cz}} > L_s$.
\item The penetration depth is $\delta_p = L_{\rm{cz}} - L_s$.
\item The flux carried by convection for $z < L_s$ is $F_{\rm{conv,cz}} = Q \delta_H$, where $Q$ is the magnitude of the internal heating and $\delta_H$ is the depth of the heating layer.
\item $\overline{w}$ is the vertical profile of the characteristic (vertical) convective velocity, which is a constant $w_{\rm{cz}}$ for $z \leq L_{\rm{cz}}$.
\item Similarly, $\overline{\delta T}$ is the vertical profile of the characteristic temperature perturbation.
\end{enumerate}

And some key assumptions.
\begin{enumerate}
\item Convection flattens $\grad \rightarrow \grad_{\rm{ad}}$ for $z \leq L_{\rm{cz}}$ (baked into our definitions).
\item We assume a system in thermal equilibrium, at least in (adiabatic) convection zone with $z \leq L_{\rm{cz}}$.
Therefore $F_{\rm{conv}}(z) = F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)$, where $F$ is a flux and $F_{\rm{rad, ad}}$ is the radiative flux along the adiabatic gradient.
\item We assume $F_{\rm{conv}} = \overline{w T} \approx \overline{w}\overline{\delta T}$.
Combined with our previous assumption, we get
\begin{equation}
\overline{\delta T} \approx \frac{F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)}{\overline{w}}.
\end{equation}
\end{enumerate}
As we increase in height, the conductivity and thus $F_{\rm{rad, ad}}(z)$ also increases.
This means that $\overline{\delta T}$ has the opposite sign of $\overline{w}$ for $z > L_s$.
We presume that buoyancy breaking is the dominant mechanism which brings convective motions to a stop in this adiabatic layer,
\begin{equation}
\frac{d \overline{w}}{dt} = \overline{\delta T} = \frac{F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)}{\overline{w}}.
\end{equation}
If we multiply both sides by $\overline{w}$ and absorb it into the the derivative, then apply the chain rule with $d/dt = d/dz (dz/dt) = d/dz \overline{w}$, we retrieve,
\begin{equation}
\frac{1}{2} d\overline{w}^3 = \left[F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)\right]dz.
\end{equation}
We now replace $F_{\rm{rad, ad}}(z) = k_0(z) \grad_{\rm{ad}}$, and we assume that $k(z)$ instantaneously jumps from a low value $k_{\rm{cz}}$ to a high value $k_{\rm{rz}}$ at $z = L_s$.
Per this assumption, the convective flux is a negative constant for $z \geq L_s$.
We integrate from $z = L_s$ with $\overline{w} = w_{\rm{cz}}$ to $z = L_{s}$ with $\overline{w} = 0$, and get
\begin{equation}
-\frac{w_{\rm{cz}}^3}{2} = F_{\rm{conv,p}} \delta_p.
\end{equation}
By definition, the convective flux in the penetrative layer with $z > L_s$ is related to $\mathcal{P}$,
\begin{equation}
F_{\rm{conv,t}} = -\frac{F_{\rm{conv,cz}}}{\mathcal{P}},
\end{equation}
so we retrieve
\begin{equation}
\delta_p = \frac{w_{\rm{cz}}^3 \mathcal{P}}{2 F_{\rm{conv, cz}}},
\end{equation}
and the penetration depth scales with the cube of the velocity and linearly with $\mathcal{P}$.
This prediction does not exactly line up with the simulation results (this overpredicts the magnitude of $\delta_p$).
The important thing we need to determine is if it scales with $w_{\rm{cz}}$, $\mathcal{P}$, and $F_{\rm{conv,cz}}$ in the appropriate way.
So far, it seems to scale linearly with $\mathcal{P}$ at fixed other parameters.

\bibliography{biblio.bib}
\end{document}

### 2021-04-28 dedalus_code/plotting/threeD_plot_slices.py
threeD movie plots look a lot better

@@ -13,8 +13,9 @@ Options:
     --static_cbar                       If flagged, don't evolve the cbar with time
     --dpi=<dpi>                         Image pixel density [default: 200]
 
-    --col_inch=<in>                     Number of inches / column [default: 4]
-    --row_inch=<in>                     Number of inches / row [default: 2]
+    --horiz_inch=<in>                   Number of inches / horizontal plot [default: 4]
+    --vert_inch=<in>                    Number of inches / vertical plot [default: 2]
+    --pad=<inch>                        Plot padding inches [default: 0.5]
 
     --fig_type=<fig_type>               Type of figure to plot
                                             1 - T - horiz_avg(T), w
@@ -23,6 +24,7 @@ Options:
 import numpy as np
 from docopt import docopt
 args = docopt(__doc__)
+from plotpal.plot_grid import CustomPlotGrid
 from plotpal.slices import SlicePlotter
 import logging
 logger = logging.getLogger(__name__)
@@ -41,14 +43,24 @@ if root_dir is None:
 fig_name   = args['--fig_name']
 
 plotter = SlicePlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
-convergence_plotter = SlicePlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
 
-plotter_kwargs = { 'col_in' : int(args['--col_inch']), 'row_in' : int(args['--row_inch']), 'padding' : 100 }
 if int(args['--fig_type']) == 1:
-    plotter.setup_grid(2, 2, **plotter_kwargs)
+    h_inch = float(args['--horiz_inch'])
+    v_inch = float(args['--vert_inch'])
+    pad = float(args['--pad'])
+    title_offset = 0.5
+    height = v_inch + h_inch
+    width  = 2*h_inch
+    plot_grid = CustomPlotGrid()
+    plot_grid.add_spec((0,0), (0,          title_offset),            (h_inch, v_inch), cbar=True)
+    plot_grid.add_spec((0,1), (h_inch+pad, title_offset),            (h_inch, v_inch), cbar=True)
+    plot_grid.add_spec((1,0), (0,          title_offset+v_inch+pad), (h_inch, h_inch), cbar=True)
[…]

### 2021-04-28 dedalus_code/erf_step_3D.py
AE improvements:
* Adds a smart max AE step size
* AE steps always go in dLcz/dt direction now (even if its slope vs L is weird); think on this more.
* Adds 5-part convergence criterion for once AE starts overshooting and waffling around right answer.

@@ -567,15 +567,16 @@ def run_cartesian_instability(args):
         max_T_iters = int(args['--T_iters'])
         done_T_iters = 0
 
-        transient_wait = 20
+        transient_wait = 30
         transient_start = None
-        N = 40
+        N = 70
         halfN = int(N/2)
         avg_dLz_dt = 0
         top_cz_times = np.zeros(N)
         top_cz_z = np.zeros(N)
         good_times = np.zeros(N, dtype=bool)
         last_height_t = 0
+        completion_checks = np.zeros(5, dtype=bool)
 
         L_cz0 = None
         zmax = 0
@@ -630,16 +631,34 @@ def run_cartesian_instability(args):
                         Lz_end = np.mean(top_cz_z[halfN:])
                         delta_Lz = Lz_end - Lz_beg
                         delta_dLz_dt = dLz_dt_end - dLz_dt_beg
+                        avg_Lz = Lz_beg + delta_Lz/2
                         logger.info('Lz: {:.3f}/{:.3f}, deltaLz: {:.3e}'.format(Lz_beg, Lz_end, delta_Lz))
                         logger.info("dLz/dt: {:.3e}/{:.3e}, deltadLz/dt: {:.3e}".format(dLz_dt_beg, dLz_dt_end, delta_dLz_dt))
-                        if delta_Lz != 0 and delta_dLz_dt != 0:
-                            L_cz1 = Lz_beg - delta_Lz * (dLz_dt_beg/delta_dLz_dt)
+
+                        if dLz_dt_beg / dLz_dt_end <= 0:
+                            completion_checks[int(np.sum(completion_checks))] = True
+                            logger.info("{} completion checks done".format(np.sum(completion_checks)))
+                            good_times[:halfN] = False
+                            if np.sum(completion_checks) == completion_checks.shape[0]:
+                                logger.info("{} completion checks done; finishing AE.".format(completion_checks.shape[0]))
+                                done_T_iters = max_T_iters
+                        elif delta_Lz != 0 and delta_dLz_dt != 0:
+                            delta_L_cz = avg_dLz_dt * np.abs(delta_Lz / delta_dLz_dt)
+                            max_delta_L_cz = np.abs(2*(transient_wait+N)*dLz_dt_beg)
+                            if np.abs(delta_L_cz) > max_delta_L_cz:
+                                delta_L_cz *= max_delta_L_cz/np.abs(delta_L_cz)
+                            L_cz1 = avg_Lz + delta_L_cz
[…]

### 2021-04-28 notes/penetration_argument/penetration_argument.tex
updated dimensional penetration argument

@@
 
-%\section{Nondimensional equations}
-%The nondimensional system of equations we solve is
-%\begin{align}
-%&\grad\dot\vec{u} = 0 \\
-%&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \rm{Re}_0^{-1}\grad^2 \vec{u} \\
-%&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = \rm{Pe}_0^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
-%\end{align}
+\section{Dimensional equations}
+The dimensional Boussinesq equations are
+\begin{align}
+&\grad\dot\vec{u} = 0 \label{eqn:continuity} \\
+&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} \label{eqn:momentum} \\
+&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = \chi\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q \label{eqn:temperature} \\
+&\frac{\rho'}{\rho_0} = -|\alpha| T \label{eqn:boussinesq}
+\end{align}
+Where $\rho$ is the density, $T$ is the temperature, $\vec{g}$ is the gravitational acceleration, $\alpha$ is the coefficient of thermal expansion, $\nu$ and $\chi$ are the viscous and thermal diffusivity, $k$ is a radiative diffusivity, and $Q$ is a heating term.
+We have baked in an assumption that $\alpha < 0$ to make sign conventions more straightforward after substituting Eqn.~\ref{eqn:boussinesq} into Eqn.~\ref{eqn:momentum}.
 
@@
 \overline{\delta T} \approx \frac{F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)}{\overline{w}}.
+\label{eqn:dT_assumption}
 \end{equation}
@@
 This means that $\overline{\delta T}$ has the opposite sign of $\overline{w}$ for $z > L_s$.
-We presume that buoyancy breaking is the dominant mechanism which brings convective motions to a stop in this adiabatic layer,
+
+We presume that buoyancy breaking is the dominant mechanism which brings convective motions to a stop in this adiabatic layer.
+In other words, we assume that, if we drop the nonlinear, pressure, and viscous terms from Eqn.~\ref{eqn:momentum}, we describe the dynamics reasonably well,
 \begin{equation}
-\frac{d \overline{w}}{dt} = \overline{\delta T} = \frac{F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)}{\overline{w}}.
+\frac{d \overline{w}}{dt} = \frac{\overline{\rho'}}{\rho_0}(-g\hat{z}) = \alpha g\, \overline{\delta T} = \alpha g \, \frac{F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)}{\overline{w}}.
 \end{equation}
@@
 \begin{equation}
-\frac{1}{2} d\overline{w}^3 = \left[F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)\right]dz.
+\frac{1}{2} d\overline{w}^3 = \alpha g\, \left[F_{\rm{tot}}(z) - F_{\rm{rad, ad}}(z)\right]dz.
 \end{equation}
@@
 \begin{equation}
--\frac{w_{\rm{cz}}^3}{2} = F_{\rm{conv,p}} \delta_p.
+-\frac{w_{\rm{cz}}^3}{2} = \alpha g\, F_{\rm{conv,p}}\,  \delta_p.
 \end{equation}
@@
 \begin{equation}
-F_{\rm{conv,t}} = -\frac{F_{\rm{conv,cz}}}{\mathcal{P}},
+F_{\rm{conv,p}} = -\frac{F_{\rm{conv,cz}}}{\mathcal{P}},
 \end{equation}
@@
 \begin{equation}
-\delta_p = \frac{w_{\rm{cz}}^3 \mathcal{P}}{2 F_{\rm{conv, cz}}},
+\delta_p = \frac{w_{\rm{cz}}^3}{2\alpha g\, F_{\rm{conv, cz}}}  \mathcal{P},
 \end{equation}
@@
 
+Finally, we note that for an ideal gas with $P = \mathcal{R} \rho T$,
+\begin{equation}
+\alpha = \frac{\partial \ln\rho}{\partial T} = \frac{1}{\rho}\frac{\partial\rho}{\partial T} \approx - T^{-1}.
+\end{equation}
+If we had assumed that the convective flux had the form $\rho c_p w \delta T$ during Eqn.~\ref{eqn:dT_assumption}, we would have retrieved
+\begin{equation}
+\delta_p = \frac{\rho\, c_p\, w_{\rm{cz}}^3}{2\alpha g\, F_{\rm{conv, cz}}}  \mathcal{P}
+\qquad \Rightarrow \qquad
+\frac{\delta_p}{H_P} = \frac{\rho\, w_{\rm{cz}}^3}{2 F_{\rm{conv, cz}}}  \mathcal{P},
+\end{equation}
+with $H_P = c_P T / g$ the rough pressure scale height.
+
 \bibliography{biblio.bib}

### 2021-05-01 notes/linear_setup/linear_cartesian_setup.tex
adds writeup of linear conductivity setup

--- 2021-04-16 notes/erf_setup/erf_cartesian_setup.tex
@@
 
+\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
+\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
+\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
+\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
+\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
+\newcommand{\mP}{\ensuremath{\mathcal{P}}}
+\newcommand{\mR}{\ensuremath{\mathcal{R}}}
+\newcommand{\mS}{\ensuremath{\mathcal{S}}}
+\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
 \newcommand\Ra{\mathrm{Ra}}
-\newcommand\Pran{\mathrm{Pr}}
 \newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
@@
 &\grad\dot\vec{u} = 0 \\
-&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \rm{Re}_0^{-1}\grad^2 \vec{u} \\
-&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = \rm{Pe}_0^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
+&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
+&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = (\Pran\mR)^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
 \end{align}
@@
 I've confirmed with some simple tests that $|u|^2 \approx Q$, and therefore the convective frequency is $f_{\rm{conv}}^2 \approx Q$.
-\item The control freefall P\'{e}clet number, $\rm{Pe}_0$, and the diffusivity associated with it, only acts on fluctuations, not on the $k_x = 0$ mode.
+$|u|$ is also a weak function of $\mR$, but is a very strong function of $Q$.
+\item The control freefall Reynolds number (\mR) and P\'{e}clet number (\Pran\mR)---and the diffusivity associated with them---only act on fluctuations, not on the $k_x = 0$ mode.
 For the $k_x = 0$ mode, we model the radiative flux as $F_{\rm{rad}} = -k \grad \overline{T}$, where $k$ is a nonconstant coefficient, $k(z)$.
@@
 \section{Model Setup}
-We will study a two-layer model in $z = [0, L_z]$ in which the conductivity, $k(z)$ is a step function such that
+We will study a two-layer model in $z = [0, L_z]$ in which the gradient of the conductivity, $\partial_z k(z)$, is a step function,
 \begin{equation}
-k(z) = \begin{cases}
-k_b & z < L_{\rm{cz}} \\
-k_t & z \geq L_{\rm{cz}}
+\frac{\partial k(z)}{\partial z} = \partial_z k_{0}\begin{cases}
+1 & z < L_{\rm{cz}} \\
+\mP^{-1} & z \geq L_{\rm{cz}}
 \end{cases}
 \end{equation}
-where subscript ``t'' refers to the top layer and ``b'' refers to the bottom.
 Generally, we will set $L_{\rm{cz}} = 1$.
-(These won't be true discontinuities, but will be smooth step-like functions achieved with erfs.)
+The crucial thing here is that the CZ has a nondimensional slope of order $\partial_z k_0$, but above the place where the Schwarzschild criterion is met ($\gradrad = \gradad$) the slope is larger or smaller than that value according to the magnitude of \mP.
+$\mP$ therefore sets how quickly the magnitude of $\Frad$ conducted along a (constant) $\gradad$ varies with height.
 
-There will be two important input parameters in this system:
+Aside from $\mR$ and $\Pran$, there will be two important input parameters in this system:
 \begin{enumerate}
@@
 \begin{equation}
-\mathcal{S} = \frac{N_{t}^2}{f_{\mathrm{conv}}^2},
+\mathcal{S} = \frac{N_{\rm{RZ}}^2}{f_{\mathrm{conv}}^2},
 \end{equation}
-which is the ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
+which is the characteristic ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
+Since $N_{\rm{RZ}}^2$ (and $\gradrad$) will vary with height, we will nondimensionalize using its characteristic value at $z = 2 L_{\rm{cz}}$.
 \item $\mathcal{P}$, a parameter which sets the penetration depth.
-$\mathcal{P}$ determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
-We will define $\mathcal{P} = -F_{\rm{conv}}/F_{\rm{conv, rz}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \gg 1$ and none when $\mathcal{P} \ll 1$.
+$\mathcal{P}$ determines how steeply the value of $\Frad$ (conducted along $\gradad$ in the penetration zone) changes as a function of height.
+As a result, assuming flux conservation with $\Ftot = \Frad + \Fconv$, $\mP$ sets how rapidly the convective flux decreasing (into negative values) as a function of height.
+We will define $\mP$ using an atmosphere where $\grad = \gradad$ everywhere; In this atmosphere,
+\begin{equation}
+\mP \equiv -\frac{\Fconv|_{\rm{cz}}}{\Fconv|_{2L_{\rm{cz}}}}
+= -\frac{(\Ftot - \Frad)|_{\rm{cz}}}{(\Ftot - \Frad)|_{2L_{\rm{cz}}}}
+\end{equation}
+Our expectation is that we get a lot of convective penetration when $\mathcal{P} \gg 1$ and none when $\mathcal{P} \ll 1$.
 \end{enumerate}
@@
 We will choose $Q = 1$ and $\delta_H = 0.2$ so that $F_{\rm{conv}} = 0.2$; we will furthermore choose and $F_{\rm{bot}} = \zeta F_{\rm{conv}}$, where $\zeta$ is some arbitrary scalar that sets how much smaller $k$ is in the cz than the RZ; we'll set $\zeta = 10^{-3}$ for now.
+This choice sets a boundary condition on the integral of $k_0$ so that $k_0(z=0) = F_{\rm{bot}}/\gradad$.
 
@@
 \begin{enumerate}
-\item At some point, the adiabatic gradient is equal to the radiative gradient,
+\item At $z = L_{\rm{cz}}$, the adiabatic gradient is equal to the radiative gradient,
 \begin{equation}
@@
 \begin{equation}
-k_b \grad_{\rm{ad}} = F_{\rm{bot}}
+k_0(z=0) \grad_{\rm{ad}} = F_{\rm{bot}}
 \end{equation}
@@
 \begin{equation}
-k_{t} \grad_{\rm{rad,t}} = F_{\rm{tot}}
+k(z > L_{\rm{cz}}) \grad_{\rm{rad}} = (k_{\rm{ad}} + \partial_z k_0 \mP^{-1}(z - L_{\rm{cz}}))\gradrad = F_{\rm{tot}}
 \end{equation}
-\item Assuming $\grad T = -\grad_{\rm{ad}}$ everywhere, the convective flux in the top layer is $F_{\rm{conv,t}} = F_{\rm{conv}} - \Delta k \grad_{\rm{ad}}$, where $F_{\rm{conv}} = Q \delta_H$ and $\Delta k = k_t - k_b$.
-Thus, definitionally,
+\item The magnitude of $\mP$ is based on the radiative flux conducted along the adiabat at $z = 2 L_{\rm{cz}}$, where $k(z=2L_{\rm{cz}}) = k_{\rm{ad}} + \partial_z k_0 L_{\rm{cz}}\mP^{-1}$.
+Thus, with $\Fconv|_{\rm{cz}} = Q\delta_H$,
 \begin{equation}
-\mathcal{P} = -\frac{F_{\rm{conv}}}{F_{\rm{conv,t}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right)^{-1}.
+\mP = -\frac{\Fconv|_{\rm{cz}}}{\Fconv|_{2L_{\rm{cz}}}}
+= -\frac{Q\delta_H}{\partial_z k_0 L_{\rm{cz}}\mP^{-1}\gradad}
+\Rightarrow
+\mP^2 = \frac{Q \delta_H}{\gradad \partial_z k_0 L_{\rm{cz}}}
 \end{equation}
-\item Defining $f_{\rm{conv}}^2 \approx Q$ and $N^2 \approx -(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})$, the stiffness gives
+\item Defining $f_{\rm{conv}}^2 \approx Q$ and $N^2 \approx -(\grad_{\rm{rad}}|_{2L_{\rm{cz}}} - \grad_{\rm{ad}})$, the stiffness gives
 \begin{equation}
-\mathcal{S} = \frac{N^2}{f_{\mathrm{conv}}^2} = \frac{-(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})}{Q}
-= \frac{F_{\mathrm{tot}}}{Q}(k_{\rm{ad}}^{-1} - k_t^{-1})
+\mS = \frac{N^2}{f_{\mathrm{conv}}^2} = \frac{-(\grad_{\rm{rad}}|_{2L_{\rm{cz}}} - \grad_{\rm{ad}})}{Q}
+= \frac{F_{\mathrm{tot}}}{Q}(k_{\rm{ad}}^{-1} - [k_{\rm{ad}} + \partial_z k_0 \mP^{-1} L_{\rm{cz}}]^{-1})
 \end{equation}
@@
 \begin{align}
-k_t = \frac{\delta_H}{\mathcal{S} \mathcal{P}},\qquad
-k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}^{-1}},\qquad
-k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}^{-1}},\\
-\grad_{\rm{ad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta + \mathcal{P}^{-1}),\qquad
-\grad_{\rm{rad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta).
+\partial_z k_0 = \frac{\delta_H}{L \mP^2 \mS}\frac{1}{\xi},\qquad
+k_b = \frac{\delta }{\mS}\frac{\zeta}{\xi},\qquad
+k_{\rm{ad}} = \frac{\delta}{\mS}\frac{1 + \zeta}{\xi},\qquad
+\gradad = Q \mS \xi 
 \end{align}
+with $\xi \equiv 1 + \mP^3(1 + \zeta)$ and $\gradrad = F_{\rm{tot}}/k(z)$.
 

### 2021-05-01 notes/penetration_argument/penetration_argument.tex
adds writeup of linear conductivity setup

@@
-\documentclass[12pt,preprint]{article}
+\documentclass[12pt]{article}
 \usepackage{natbib}
-\bibliographystyle{plain}
+\bibliographystyle{aasjournal}
 \usepackage{latexsym}
@@
 \newcommand{\tbl}[1]{Table~(#1)}
+
+\newcommand{\aap}{A\&A}
 
@@
 
+\section{Zahn argument}
+Here we will work through a Boussinesq version of the argument in section 3.1 of \citet{zahn1991}.
+In the adiabatic penetrative region, we know that the radiative flux is
+\begin{equation}
+F_{\rm{rad}} = -k \frac{\partial T_{\rm{ad}}}{\partial z}
+\end{equation}
+Further, we know that the convective flux is the difference between the total total and radiative flux,
+\begin{equation}
+F_{\rm{conv}} = F_{\rm{tot}} - F_{\rm{rad}}.
+\end{equation}
+Furthermore, the convective flux is
+\begin{equation}
+F_{\rm{conv}} = \overline{w T} = f \, W(z) \, \delta T(z),
+\end{equation}
+where $f$ is the filling factor of the flows that carry the flux in the penetration zone (upflows) and $W$ and $T$ give the vertical shape of typical velocity and temperature perturbations.
+
+We next assume that the temperature and velocity are highly correlated in the overshooting convective motions (upflows).
+This allows us to describe the horizontal nature of all fields in upflows using a function $h(x,y)$ so that
+\begin{equation}
+w(x,y,z) = W(z) h(x,y)
+\qquad
+T'(x,y,z) = \delta T(z) h(x,y),
+\end{equation}
+where $T'$ are the temperature fluctuations away from the mean.
+By continuity and by our above definition of the convective flux, we have
+\begin{equation}
+\overline{h} = 0,
+\qquad
+\overline{h^2} = f.
+\end{equation}
+
 \bibliography{biblio.bib}

### 2021-05-01 dedalus_code/linear_3D.py
adds linear setup .py file; cleans up linear setup pdf

@@ -1,0 +1,742 @@
+"""
+Dedalus script for a two-layer, Boussinesq simulation.
+The bottom of the domain is at z = 0.
+The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ 1.
+
+There are 6 control parameters:
+    Re      - The approximate reynolds number = (u / diffusivity) of the evolved flows
+    Pr      - The Prandtl number = (viscous diffusivity / thermal diffusivity)
+    P       - The penetration parameter; When P >> 1 there is lots of convective penetration (of order P); when P -> 0 there is none.
+    S       - The stiffness: the characteristic ratio of N^2 (above the penetration region) compared to the square convective frequency.
+    zeta    - The fraction of the convective flux carried by the adiabatic gradient at z = 0 (below the heating layer)
+    Lz      - The height of the box
+    aspect  - The aspect ratio (Lx = aspect * Lz)
+
+Usage:
+    linear_3D.py [options] 
+    linear_3D.py <config> [options] 
+
+Options:
+    --Re=<Reynolds>            Freefall reynolds number [default: 1e2]
+    --Pr=<Prandtl>             Prandtl number = nu/kappa [default: 0.5]
+    --P=<penetration>          ratio of CZ convective flux / RZ convective flux [default: 1]
+    --S=<stiffness>            The stiffness [default: 1e2]
+    --zeta=<frac>              Fbot = zeta * F_conv [default: 1e-3]
+    --Lz=<L>                   Depth of domain [default: 2]
+    --aspect=<aspect>          Aspect ratio of domain [default: 2]
+    --L_cz=<L>                 Height of cz-rz erf step [default: 1]
+
+    --nz=<nz>                  Vertical resolution   [default: 256]
+    --nx=<nx>                  Horizontal (x) resolution [default: 32]
+    --ny=<ny>                  Horizontal (y) resolution (sets to nx by default)
+    --RK222                    Use RK222 timestepper (default: RK443)
+    --SBDF2                    Use SBDF2 timestepper (default: RK443)
+    --safety=<s>               CFL safety factor [default: 0.75]
+    --mesh=<m>                 Processor distribution mesh (e.g., "4,4")
+
[…]

### 2021-05-01 dedalus_code/erf_step_3D.py
final pre-run tweaks

@@ -561,9 +561,11 @@ def run_cartesian_instability(args):
     analysis_tasks = initialize_output(solver, data_dir, mode=mode, output_dt=t_ff)
 
     dense_scales = 20
+    dense_x_scales = 1#mesh[0]/nx
+    dense_y_scales = 1#mesh[1]/ny
     z_dense = domain.grid(-1, scales=dense_scales)
     dense_handler = solver.evaluator.add_dictionary_handler(sim_dt=1, iter=np.inf)
-    dense_handler.add_task("plane_avg(-T_z)", name='grad', scales=(1,1,dense_scales), layout='g')
+    dense_handler.add_task("plane_avg(-T_z)", name='grad', scales=(dense_x_scales, dense_y_scales, dense_scales), layout='g')
 
     flow = flow_tools.GlobalFlowProperty(solver, cadence=1)
     flow.add_property("Re", name='Re')

### 2021-05-01 dedalus_code/linear_3D.py

@@ -1,7 +1,7 @@
 """
 Dedalus script for a two-layer, Boussinesq simulation.
 The bottom of the domain is at z = 0.
-The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ 1.
+The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ L_cz.
 
 There are 6 control parameters:
     Re      - The approximate reynolds number = (u / diffusivity) of the evolved flows
@@ -372,8 +372,6 @@ def run_cartesian_instability(args):
     Q.antidifferentiate('z', ('left', Fbot), out=flux_of_z)
     flux = flux_of_z.interpolate(z=L_cz)['g'].min()
 
-    print(k0.interpolate(z=L_cz)['g'].min(), k_ad)
-
     T_ad_z['g'] = -grad_ad
     T_rad_z0['g'] = T_rad_func(flux_of_z['g'], k0['g'])
 
@@ -547,6 +545,9 @@ def run_cartesian_instability(args):
     ### 6. Setup output tasks; run main loop.
     analysis_tasks = initialize_output(solver, data_dir, mode=mode, output_dt=t_ff)
 
+    T_rad_z0.set_scales(domain.dealias)
+    delta_grad_de = grad_ad - (-T_rad_z0['g'][0,0,:]) #negative in RZ, positive in CZ
+
     dense_scales = 20
     z_dense = domain.grid(-1, scales=dense_scales)
     T_rad_z0.set_scales((1,1,dense_scales))
@@ -604,7 +605,7 @@ def run_cartesian_instability(args):
                         for fname in ['u', 'v', 'w', 'ωx', 'ωy', 'ωz', 'p']:
                             solver.state[fname].set_scales(domain.dealias, keep_data=True)
                             solver.state[fname]['g'] *= one_to_zero(z_de, 1, width=0.05)
-                        mean_T_z = -(grad_ad - zero_to_one(z_de, zmax, width=0.05)*delta_grad)
+                        mean_T_z = -(grad_ad - zero_to_one(z_de, zmax, width=0.05)*delta_grad_de)
                         mean_T1_z = mean_T_z - T0_z['g'][0,0,:]
                         T1_z['g'] -= flow.properties['mean_T1_z']['g']
                         T1_z['g'] *= one_to_zero(z_de, 1, width=0.05)
@@ -616,11 +617,11 @@ def run_cartesian_instability(args):
                     last_height_t = int(solver.sim_time)
[…]

### 2021-05-01 notes/penetration_argument/penetration_argument.tex
adds Zahn penetration argument; works through all of it for erf.

@@
 \end{equation}
+Furthermore, as in \citet{zahn1991}, $h$ is normalized so that its mean square averages to zero over the area where $h > 0$,
+\begin{equation}
+\overline{h^2 \mu(x,y)} = 1,
+\end{equation}
+where $\mu(x,y) = (1 + h/|h|)/2$, which is 1 when $h > 0$ and 0 when $h \leq 0$.
+
+Per the momentum equation, the deceleration of plumes in the penetration zone is described by buoyancy breaking,
+\begin{equation}
+\frac{d w^2}{dz} = \alpha g T'.
+\end{equation}
+Multiplying by $h$ (to preserve the LHS) and taking a horizontal average, we get
+\begin{equation}
+\frac{\overline{h^3}}{\alpha g f}d W^2 = \delta T dz.
+\end{equation}
+After elimination of $\delta T$ with the formula for $F_{\rm{conv}}$, we integrate
+\begin{equation}
+\frac{\overline{h^3}}{3 \alpha g}\int_{W_0}^0 dW^3 = \int_{L_{\rm{cz}}}^{L_{\rm{cz}} + L_p} F_{\rm{conv}}\, dz,
+\label{eqn:buoyancy_integral}
+\end{equation}
+assuming that the velocity drops to roughly $W = 0$ at $z = L_{\rm{cz}} + L_p$, where $L_{\rm{cz}}$ is the height where $\grad_{\rm{rad}} = \grad_{\rm{ad}}$.
+
+At this point we will consider two cases:
+\begin{enumerate}
+\item The ``erf'' simulations, where we assume that $F_{\rm{conv}}$ jumps from a value of $F_0$ in the CZ to a value of $-F_0/\mathcal{P}$ in the PZ.
+In this case, integration of a constant straightforwardly returns
+\begin{equation}
+L_p = \frac{\overline{h^3} W_0^3}{3\alpha g F_0}\mathcal{P}.
+\end{equation}
+\item The ``linear'' simulations, where we assume that $F_{\rm{conv}}$ decreases from a value of 0 at $L_{\rm{cz}}$ linearly, so $F(z > L_{\rm{cz}}) = -|\partial_z F_0|(z - L_{\rm{cz}})$.
+We set $|\partial_z F_0| \sim \mathcal{P}^{-1}$ in these simulations.
+In this case, integration yields
+\begin{equation}
+L_p = \left(\frac{2\overline{h^3} W_0^3}{3\alpha g|\partial_z F_0|}\right)^{1/2} \propto \sqrt{\mathcal{P}}.
+\end{equation}
+This is more directly the case mentioned by Zahn.
+\end{enumerate}
+
+Following a step further, we now adopt the assumption of MLT that the CZ flux is described by
+\begin{equation}
+F_{0} = \mathcal{F} W^3.
+\end{equation}
+The difficulty is in in determining the value of $\mathcal{F}$.
+To achieve this, we return to Eqn.~\ref{eqn:buoyancy_integral} and integrate over the relevant length scale in the CZ (for the Boussinesq case, this is just the depth of the CZ),
+\begin{equation}
+\frac{\overline{h_{\rm{cz}}^3}}{3 \alpha g}\int_0^{W_0} dW^3 = \int_{0}^{L_{\rm{cz}}} F_0\, dz
+\Rightarrow
+F_0 = \frac{\overline{h_{\rm{cz}}^3} W_0^3}{3 \alpha g L_{\rm{cz}}},
+\end{equation}
+where above I have performed the integral for the ``erf'' case and assumed a constant $F_0$ in the CZ (I should be more careful about this, because internal heating, and my length scale is slightly off).
+Plugging this expression for $F_0$ into the erf expression for $L_p$, we retrieve
+\begin{equation}
+\frac{L_p}{L_{\rm{cz}}} = \frac{\overline{h^3}}{\overline{h_{\rm{cz}}^3}} \mathcal{P},
+\end{equation}
+and we see that the penetration depth depends only on $\mathcal{P}$ and the horizontal extent of the upflows in the CZ compared to the PZ.
+We expect the latter of these factors to be a weak function of things like the stiffness or the Reynolds number.
+In the simulations I have thusfar conducted, I think I have found that the average filling factor $f$ of the flows decreases as you move upwards in the CZ (from something like 0.6 to 0.4); in the PZ it quickly returns to 0.5, and it stays 0.5 in the RZ (where waves dominate, and that makes sense).
+However, I did these calculations using a pure filling factor calculation (``what fraction of the horizontal volume is filled with an upflow?''); I think a better algorithm which attempts to determine where the convective plumes are would be ideal.
+Regardless, naively I think that $\overline{h^3} \approx f^{3/2}$ is probably a fine first assumption.
+By that assumption, with the above numbers I quoted ($f_{\rm{cz}} \approx 0.6$ and $f_{\rm{pz}} \approx 0.4$), we get
+\begin{equation}
+\frac{L_p}{L_{\rm{cz}}} \approx \frac{f_{\rm{pz}}^{3/2}}{f_{\rm{cz}}^{3/2}}\mathcal{P} \approx 0.54 \mathcal{P}.
+\end{equation}
+This is strikingly close to what we are seeing in these simulations.
 

### 2021-05-05 notes/outline/outline.tex
starts writing outline

\documentclass[12pt]{article}
\usepackage{natbib}
\bibliographystyle{aasjournal}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}

\usepackage{pb-diagram}

\parindent = 0.0 in
\parskip = 0.15 in

\newcommand\Beq{\begin{align}} 
\newcommand\Eeq{\end{align}}

\newcommand\Bfig{\begin{figure}} 
\newcommand\Efig{\end{figure}}

\newcommand\Ra{\mathrm{Ra}}
\newcommand\Pran{\mathrm{Pr}}
\newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
\newcommand\Ek{\mathrm{Ek}}
\newcommand\Ro{\mathrm{Ro}}
\newcommand\Nu{\mathrm{Nu}}
\newcommand\Sc{\mathrm{Sc}}

\newcommand\eps{\varepsilon}
\renewcommand\L {\mathcal{L}}

\newcommand{\n}{\\ \nonumber \\ }
\newcommand{\nn}{\nonumber}
\newcommand{\nnn}{\\ \nonumber \\ \nonumber}

\newcommand\ie{\textit{i.e.},~}
\newcommand\eg{\textit{e.g.},~}
\newcommand{\omicron}{o}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

\newcommand{\sump}[2]{\sideset{}{'}\sum_{{#1}=0}^{#2}}

\newcommand{\eq}[1]{eq.~(\ref{#1})}
\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\Eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\figs}[2]{Figs.~(\ref{#1})~\&~(\ref{#2})}

\newcommand{\tbl}[1]{Table~(#1)}

\newcommand{\aap}{A\&A}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\mnras}{MNRAS}
\newcommand{\araa}{Annual Review of Astronomy and Astrophysics}

\begin{document}
\title{Convective Penetration Paper Outline}
\maketitle

\section{Intro \& Background}
\begin{itemize}
\item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
Include sources on e.g., stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, helioseismology \citep[][]{christensen-dalsgaard_etal_2011}, stellar evolution \& remnants \citep{higgins_vink_2020}, stellar core convection overshoot \citep{claret_torres_2018}, $\sim$every MESA paper? Other things?
\item Terminology of overshoot vs penetration.
\item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
\item Miscellaneous theoretical or semianalytical arguments or models \citep{marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019} (also Roxburgh?).
\item Briefly review simulations:
\begin{itemize}
\item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018}
\end{itemize}
\item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
\item Say very clearly that \emph{the penetration depth depends on how steeply the radiative flux changes with depth} (and also convective structures).
Say that we're going to present simulations which agree with this.
\end{itemize}

\section{Theory}
\begin{itemize}
\item The dimensional modified Boussinesq equations (note that Zahn did the fully compressible one, we're simplifying for easier reading and math and alignment with sims).
\item Walk through $F_{\rm{conv}} = F_0 W^3$ argument in both the CZ and an adiabatic PZ in general terms.
Importantly, we need to leave this part general as a ratio of integrals of the flux around the point where $\grad_{\rm{ad}} = \grad_{\rm{rad}}$.
\item If this theory is correct, it should work regardless of the shape of $k$ and thus $F$. So we will do two experiments with different predictions to test it.
One where $k$ is discontinuous, and one where $\partial_z k$ is discontinuous.
\item Solve out the predictions for the two simulations we're going to do.
\item Comment on uncertainties (rotation, magnetism, density stratification) that we won't attempt to handle in this work.
Say that we won't handle them but that this is a first step.
\end{itemize}

\section{Simulation Details}
\begin{itemize}
\item Nondimensionalization details \& nondimensional eqns.
\item Parameters ($\mathcal{P}$, $\mathcal{R}$, Pr, $\mathcal{S}$, $Q$, $\zeta$)
\item Conductivity profiles (erf and linear), $\grad_{\rm{ad}}$, internal heating.
\item Mention Dedalus \citep{burns_etal_2020} and timestepping details.
\item Define a set of ``standard parameters:'' e.g., $\mathrm{R} = 400$, $\mathrm{Pr} = 0.5$, $Q = 1$, $\zeta = 10^{-3}$, $\mathcal{S} = 10^3$, $\mathcal{P} = 4$.
All of our cuts through our multi-D parameter space cut through these parameters, varying one parameter ($\mathcal{S}$, $\mathcal{P}$, $\mathcal{R}$) and holding the rest constant.
\item Forward ref an appendix on our initial conditions / accelerated evolution (appendix A) and also an appendix of tables of simulation details (appendix B).
\end{itemize}

\section{Results}

\subsection{Qualitative Description of Simulations}
\begin{itemize}
\item Description of the \emph{evolved state} of a turbulent simulation.
This is the ``put in some pretty convective dynamics picture'' section to orient people into what our simulations look like.
And to show them that we get sims where the ``MESA answer" does a really bad job of describing the final state.
Dynamics pictuer will show: pretty standard CZ dynamics; a developed PZ with the sign of $w$ and $T$ reversed from the CZ.
\item Here we'll also show one of our $|\grad T|$ plots to show that convection flattens $\grad \rightarrow \grad_{\rm{ad}}$ far above top of nominal CZ.
This is a good time to explain the definitions of penetration vs overshoot in words again with a picture.
This is also a good time to show pictorally what our measure of the height of the PZ is (currently it's where $\grad$ is 50\% between $\grad_{\rm{rad}}$ and $\grad_{\rm{ad}}$).
\end{itemize}

\subsection{Measured penetration zone scalings}
\begin{itemize}
\item Here we show that the predicted $\mathcal{P}$ scalings do a pretty good job.
This will include some parameter space plots (probably all in one figure) that show:
\begin{itemize}
\item $\delta_P$ depends on $\mathcal{P}$.
\item $\delta_P$ does not really depend strongly on $\mathcal{S}$ or $\mathcal{R}$.
\end{itemize}
\item Mention that 2D simulations produce more pronounced PZs (larger by a factor of $\sim 2$) but similar scalings with theory; we choose to omit 2D results and focus on more realistic 3D results.
\item our theory has $\delta_P = A \mathcal{P}$ (for erf sims) and $\delta_P = B \mathcal{P}^{1/2}$; we should report good-fits for $A$ and $B$.
These can be plugged directly into MESA as first guesses as the penetration depth there.
\end{itemize}

\section{A modified solar model}
\begin{itemize}
\item Here we briefly describe a new MESA algorithm where we have a paramterization like $\delta_P/\ell = \xi B \mathcal{P}^{1/2}$ put into MESA, where $\xi$ is a knob the user can turn and $\ell$ is the mixing length or some such.
We have two options here: state that $\mathcal{P} = 1$ is always true, or have MESA do a simple linear interpolation of $\grad_{\rm{rad}}$ over some depth like $\ell/2$ above and below the CZ boundary to get a value for $\mathcal{P}$.
\item We probably can use the lame / naive assumption that below $\delta_P$, MESA latches immediately onto $\grad_{\rm{rad}}$ (it is stiff, after all).
\item We calculate a few solar models with $\xi = [0.5, 1, 2]$ and show how these models change the structure at the base of the solar CZ.
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Say what we said again.
Penetration depth depends on how quickly $F_{\rm{rad}}$ changes with height.
\item Discuss the subtleties associated with filling factors and how boussinesq can't really appropriately capture that.
\item Discuss open questions (rotation, stratification [above], magnetism, geometry).
\item Round it off by calling back to how awesome it is that $\mathcal{P}$ totally determines $\delta_P$ in our work and that $\mathcal{S}$ and $\mathcal{Re}$ don't, which suggests we can actually use simulations to crack this long-standing problem in stellar physics.
\end{itemize}

\bibliography{biblio.bib}
\end{document}

### 2021-05-06 notes/outline/outline.tex
adds some sources to intro, etc.

@@
 \newcommand{\apjl}{ApJL}
+\newcommand{\apjs}{ApJS}
+\newcommand{\apss}{Astrophysics and Space Science}
 \newcommand{\mnras}{MNRAS}
@@
 \item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
-Include sources on e.g., stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, helioseismology \citep[][]{christensen-dalsgaard_etal_2011}, stellar evolution \& remnants \citep{higgins_vink_2020}, stellar core convection overshoot \citep{claret_torres_2018}, $\sim$every MESA paper?
-Other things?
+Include sources on e.g., 
+\begin{itemize}
+\item stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, 
+\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021},
+\item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
+\item stellar evolution \& remnants \citep{higgins_vink_2020}, 
+\\item stellar core convection overshoot \citep{claret_torres_2018}, 
+\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000} and ``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
+\item Other things?
+\end{itemize}
 \item Terminology of overshoot vs penetration.
 \item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-\item Miscellaneous theoretical or semianalytical arguments or models \citep{marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019} (also Roxburgh?).
+We will do a brief review but these are additional resources.
+\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019}.
 \item Briefly review simulations:
@@
 \item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
-\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
+\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
 \item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018}
@@
 \begin{itemize}
-\item Here we show that the predicted $\mathcal{P}$ scalings do a pretty good job.
+\item Profile verification of theory.
+Does $W$ go from $W_0$ to $\mathcal{O}(0)$ at the top of the PZ?
+Is it an e-folding?
+Also how does the rms Pe or Re scale with height?
+Does Zahn's ``thermal adjustment layer'' with Pe $\sim$ 1 hold in the PZ-RZ transition?
+\item Show that the predicted $\mathcal{P}$ scalings do a pretty good job.
 This will include some parameter space plots (probably all in one figure) that show:

### 2021-05-06 notes/outline/outline.tex
rough draft of outline done

@@
-\documentclass[12pt]{article}
+\documentclass[12pt, fullpage]{article}
 \usepackage{natbib}
-\bibliographystyle{aasjournal}
 \usepackage{latexsym}
@@
 \usepackage{epstopdf}
-\usepackage{hyperref}
+\usepackage[colorlinks=true, citecolor=blue]{hyperref}
 
@@
 \parskip = 0.15 in
+
+\addtolength{\oddsidemargin}{-.875in}
+\addtolength{\evensidemargin}{-.875in}
+\addtolength{\textwidth}{1.75in}
+
+\addtolength{\topmargin}{-.875in}
+\addtolength{\textheight}{1.75in}
 
@@
 \begin{itemize}
-\item stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, 
-\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021},
+\item stellar Lithium abundances \citep[fig 4 of][]{pinsonneault_1997, dumont_etal_2021}, 
+\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021},
 \item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
 \item stellar evolution \& remnants \citep{higgins_vink_2020}, 
-\\item stellar core convection overshoot \citep{claret_torres_2018}, 
-\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000} and ``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
+\item stellar core convection overshoot \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021}, 
+\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000}
+\item``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}. 
 \item Other things?
@@
 We will do a brief review but these are additional resources.
-\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019}.
+\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, rieutord2019, korre_etal_2019}.
+\item Quick mention of penetration in the geophysical context \citep[including neat lab experiments like][]{deardorff_etal_1969}.
 \item Briefly review simulations:
@@
 \item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
-\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
-\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018}
+\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020}.
+\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021}
 \end{itemize}
 \item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
-\item Say very clearly that \emph{the penetration depth depends on how steeply the radiative flux changes with depth} (and also convective structures).
-Say that we're going to present simulations which agree with this.
+\item Simulations that have noticed that overshoot and/or penetration depends in some way on the flux \citep{singh_etal_1998, hotta2017, kapyla2019}.
+\item State the conclusions of this work very clearly. 
+\emph{The penetration depth depends on how steeply the radiative flux changes with depth near the radiative-convective boundary}.
+Thus, the penetration depth depends on the slope of the radiative conductivity / the opacity near the boundaries of the CZ
+We have designed two simple numerical setups which demonstrate this point.
 \end{itemize}
@@
 Importantly, we need to leave this part general as a ratio of integrals of the flux around the point where $\grad_{\rm{ad}} = \grad_{\rm{rad}}$.
-\item If this theory is correct, it should work regardless of the shape of $k$ and thus $F$. So we will do two experiments with different predictions to test it.
+\item If this theory is correct, it should work regardless of the shape of $k$. 
+So we will do two experiments with different predictions to test the overall idea of this theory.
 One where $k$ is discontinuous, and one where $\partial_z k$ is discontinuous.
-\item Solve out the predictions for the two simulations we're going to do.
-\item Comment on uncertainties (rotation, magnetism, density stratification) that we won't attempt to handle in this work.
-Say that we won't handle them but that this is a first step.
+\item Solve out the theory to get function forms of $\delta_P/L_{\rm{cz}}$ for the two simulations we're doing.
+\item Comment briefly on the fact that this work will only be able to get at the \emph{shape of conductivity} portion of this theoretical prediction.
+Future work which includes density stratification would be required to understand the geometrical effects of the plumes, but that's beyond the scope of this work.
 \end{itemize}
@@
 \item Nondimensionalization details \& nondimensional eqns.
-\item Parameters ($\mathcal{P}$, $\mathcal{R}$, Pr, $\mathcal{S}$, $Q$, $\zeta$)
-\item Conductivity profiles (erf and linear), $\grad_{\rm{ad}}$, internal heating.
+\item Parameters ($\mathcal{P}$, $\mathcal{R}$, Pr, $\mathcal{S}$, $Q$, $\zeta$).
+We used fixed values of Pr, $Q$, $\zeta$ in this work and vary the others.
+\item Specification of conductivity profiles (erf and linear), $\grad_{\rm{ad}}$, internal heating.
+\item The magic sauce of internal heating that allows splitting $\mathcal{S}$ and $\mathcal{P}$, and a brief discussion of some prior work where those were implicitly tied.
 \item Mention Dedalus \citep{burns_etal_2020} and timestepping details.
@@
 All of our cuts through our multi-D parameter space cut through these parameters, varying one parameter ($\mathcal{S}$, $\mathcal{P}$, $\mathcal{R}$) and holding the rest constant.
+Note the different standard parameters for the erf (subscript E?) and linear (subscript L?) simulations.
 \item Forward ref an appendix on our initial conditions / accelerated evolution (appendix A) and also an appendix of tables of simulation details (appendix B).
@@
 This is the ``put in some pretty convective dynamics picture'' section to orient people into what our simulations look like.
-And to show them that we get sims where the ``MESA answer" does a really bad job of describing the final state.
-Dynamics pictuer will show: pretty standard CZ dynamics; a developed PZ with the sign of $w$ and $T$ reversed from the CZ.
+And to show them that we get sims where the standard answer (edge of CZ is where $\grad_{\rm{rad}} = \grad_{\rm{ad}}$) does a really bad job of describing the final state.
+Dynamics picture will show: pretty CZ dynamics, a developed PZ with the sign of $w$ and $T$ reversed from the CZ.
 \item Here we'll also show one of our $|\grad T|$ plots to show that convection flattens $\grad \rightarrow \grad_{\rm{ad}}$ far above top of nominal CZ.
-This is a good time to explain the definitions of penetration vs overshoot in words again with a picture.
+This is a good time to re-explain the definitions of penetration vs overshoot in words again with a picture.
 This is also a good time to show pictorally what our measure of the height of the PZ is (currently it's where $\grad$ is 50\% between $\grad_{\rm{rad}}$ and $\grad_{\rm{ad}}$).
+Could even label ``CZ'', ``PZ'', ``OZ'', ``RZ'' (convection, penetration, overshoot, radiative zones) on the profile picture.
 \end{itemize}
@@
 \begin{itemize}
-\item Profile verification of theory.
+\item Time-averaged 1D profile plots showing verification of theory.
 Does $W$ go from $W_0$ to $\mathcal{O}(0)$ at the top of the PZ?
@@
 Also how does the rms Pe or Re scale with height?
-Does Zahn's ``thermal adjustment layer'' with Pe $\sim$ 1 hold in the PZ-RZ transition?
-\item Show that the predicted $\mathcal{P}$ scalings do a pretty good job.
+Does Zahn's ``thermal adjustment layer'' with Pe $\sim$ 1 hold in the OZ?
+\item Show that the predicted $\mathcal{P}$ scalings do a good job (think about what the relevant error bars are on our measures).
 This will include some parameter space plots (probably all in one figure) that show:
@@
 \end{itemize}
+\item An additional figure (like above) for the linear sims, where we only vary $\mathcal{P}$.
 \item Mention that 2D simulations produce more pronounced PZs (larger by a factor of $\sim 2$) but similar scalings with theory; we choose to omit 2D results and focus on more realistic 3D results.
@@
 \begin{itemize}
-\item Here we briefly describe a new MESA algorithm where we have a paramterization like $\delta_P/\ell = \xi B \mathcal{P}^{1/2}$ put into MESA, where $\xi$ is a knob the user can turn and $\ell$ is the mixing length or some such.
+\item Here we briefly describe a new MESA algorithm where we have a parameterization like $\delta_P/\ell = \xi B \mathcal{P}^{1/2}$ put into MESA, where $\xi$ is a knob the user can turn and $\ell$ is the mixing length or some such.
 We have two options here: state that $\mathcal{P} = 1$ is always true, or have MESA do a simple linear interpolation of $\grad_{\rm{rad}}$ over some depth like $\ell/2$ above and below the CZ boundary to get a value for $\mathcal{P}$.
-\item We probably can use the lame / naive assumption that below $\delta_P$, MESA latches immediately onto $\grad_{\rm{rad}}$ (it is stiff, after all).
+\item We probably can use the lame / naive assumption that below $\delta_P$, MESA latches immediately onto $\grad_{\rm{rad}}$ (this means there is no OZ; stars are stiff, after all).
+Assume everything is mixed within the full CZ-PZ.
 \item We calculate a few solar models with $\xi = [0.5, 1, 2]$ and show how these models change the structure at the base of the solar CZ.
@@
 Penetration depth depends on how quickly $F_{\rm{rad}}$ changes with height.
-\item Discuss the subtleties associated with filling factors and how boussinesq can't really appropriately capture that.
+\item Discuss the subtleties associated with filling factors and how Boussinesq / incompressible can't really appropriately capture that.
+(And the confusion that \citet{massaguer_etal_1984} have a model that suggests \emph{more} penetration for downflows than upflows in stratified domains).
 \item Discuss open questions (rotation, stratification [above], magnetism, geometry).
-\item Round it off by calling back to how awesome it is that $\mathcal{P}$ totally determines $\delta_P$ in our work and that $\mathcal{S}$ and $\mathcal{Re}$ don't, which suggests we can actually use simulations to crack this long-standing problem in stellar physics.
+\item Round it off by calling back to how awesome it is that $\mathcal{P}$ totally determines $\delta_P$ in our work and that $\mathcal{S}$ and $\mathcal{R}$ don't, which suggests we can actually use simulations to crack this long-standing problem in stellar physics.
 \end{itemize}
 
+\section{Appendix A: Accelerated Evolution}
+\begin{itemize}
+\item Description of time evolution of simulation starting from ``schwarzschild'' ICs and how brutal the time evolution is.
+\item Description of newton iter-like procedure.
+\item Figure that shows things converging to the same answer to within a few \%.
+\end{itemize}
+
+\section{Appendix B: Table-o-sims}
+\begin{itemize}
+\item Housekeeping; show resolutions, etc.
+\end{itemize}
+
+\bibliographystyle{aasjournal}
+\setlength{\bibsep}{0pt plus 0.3ex}
 \bibliography{biblio.bib}

### 2021-05-08 data/plot_erf_delta_p.py
adds three initial figure mockup scripts

@@ -1,0 +1,92 @@
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('linear*/lin*/') + glob.glob('erf*/erf*/')
+
+data = []
+for d in dirs:
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        z_departure = f['z_departure'][()]
+        tot_time = times[-1] - times[0]
+        good_times = times > (times[-1] - 1000)
+        mean_departure = np.mean(z_departure[good_times])
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+    if '3D' in d:
+        threeD = True
+    else:
+        threeD = False
+    if 'erf' in d:
+        erf = True
+    else:
+        erf = False
+
+    data.append((S, P, Re, threeD, mean_departure, Lz, erf))
+data = np.array(data)
+
+S = data[:,0]
+P = data[:,1]
+Re = data[:,2]
+threeD = data[:,3]
+z_top = data[:,4]
+Lz = data[:,5]
+erf = data[:,6]
+
+fig = plt.figure(figsize=(page_width, col_width/golden_ratio))
+
+ax1 = fig.add_axes([0.04, 0, 0.32, 1])
+ax2 = fig.add_axes([0.36, 0, 0.32, 1])
+ax3 = fig.add_axes([0.68, 0, 0.32, 1])
+
+
+good = (erf == 1) * (Re == 4e2) * (S == 1e3)
+ax1.scatter(P[good], z_top[good] - 1, c='k', label="Simulations", zorder=100)
+
+x = np.logspace(-3, 2, 100)
+y1 = 0.125*x
+ax1.plot(x, y1, c='orange', label=r'Theory$\,\,(0.125 \mathcal{P}_E)$')
+ax1.legend(frameon=False)
[…]

### 2021-05-08 data/pull.sh

@@ -1,0 +1,135 @@
+PLEIADESROOT=/nobackup/eanders/convective_penetration_paper/dedalus_code/
+
+# linear P runs
+PLEIADESBASE=$PLEIADESROOT/paper_linear_P_cut/
+LOCALBASE=linear_P_cut/
+declare -a StringArray=(\
+"linear_3D_Re8e2_P1e-2_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.023"
+"linear_3D_Re8e2_P3e-2_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.04"
+"linear_3D_Re8e2_P1e-1_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.073"
+"linear_3D_Re8e2_P3e-1_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.126"
+"linear_3D_Re8e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.23"
+"linear_3D_Re8e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.325"
+"linear_3D_Re8e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.46"
+"linear_3D_Re8e2_P8e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.65"
+"linear_3D_Re8e2_P1.6e1_zeta1e-3_S1e3_Lz2.25_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.92"
+)
+for d in ${StringArray[@]}
+do
+	echo $d
+	LOCALDIR=$LOCALBASE/$d
+	PLEIADESDIR=$PLEIADESBASE/$d
+	mkdir $LOCALDIR/
+	scp pfe:$PLEIADESDIR/top_cz/cz_velocities.png ./$LOCALDIR/
+	scp pfe:$PLEIADESDIR/top_cz/trace_top_cz.png ./$LOCALDIR/
[…]

### 2021-05-08 notes/outline/outline.tex
small updates to outline tex file

@@
 \begin{itemize}
+\item The outline should be comprised of a few paragraphs, which basically say these things:
+\begin{enumerate}
+\item ``Convection is important in stars.''
+\item ``Understanding convective boundaries is important (because of all of these observational and simulation and theoretical data points that show we kinda don't).'
+\item People have thought about this problem theoretically in these ways.
+\item We think the theoretical arguments of \citet{zahn1991}, who suggested that this is what convective penetration is, are really promising.
+\item Here's what we do in this work.
+\end{enumerate}
 \item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
@@
 \item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
+\item black hole mass gap \citep{farmer_etal_2019}
 \item stellar evolution \& remnants \citep{higgins_vink_2020}, 

### 2021-05-12 data/plot_erf_delta_p.py
adds some changes to preliminary paper figs

@@ -12,12 +12,15 @@ dirs = glob.glob('linear*/lin*/') + glob.glob('erf*/erf*/')
 
 data = []
 for d in dirs:
+    print(d)
     with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
         times = f['times'][()]
         z_departure = f['z_departure'][()]
+        z_overshoot = f['z_overshoot'][()]
         tot_time = times[-1] - times[0]
-        good_times = times > (times[-1] - 1000)
+        good_times = times > (times[-1] - 500)
         mean_departure = np.mean(z_departure[good_times])
+        mean_overshoot = np.mean(z_overshoot[good_times])
     S = float(d.split('_S')[-1].split('_')[0])
     P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
     Re = float(d.split('_Re')[-1].split('_')[0])
@@ -30,8 +33,12 @@ for d in dirs:
         erf = True
     else:
         erf = False
+    if 'AE' in d:
+        ae = True
+    else:
+        ae = False
 
-    data.append((S, P, Re, threeD, mean_departure, Lz, erf))
+    data.append((S, P, Re, threeD, mean_departure, mean_overshoot, Lz, erf, ae))
 data = np.array(data)
 
 S = data[:,0]
@@ -39,54 +46,78 @@ P = data[:,1]
 Re = data[:,2]
 threeD = data[:,3]
 z_top = data[:,4]
-Lz = data[:,5]
-erf = data[:,6]
+z_ov = data[:,5]
+z_av = (z_top + z_ov)/2
+Lz = data[:,6]
+erf = data[:,7]
+ae = data[:,8]
 
-fig = plt.figure(figsize=(page_width, col_width/golden_ratio))
+fig = plt.figure(figsize=(page_width, page_width/(3*golden_ratio)))
 
-ax1 = fig.add_axes([0.04, 0, 0.32, 1])
-ax2 = fig.add_axes([0.36, 0, 0.32, 1])
-ax3 = fig.add_axes([0.68, 0, 0.32, 1])
+ax1 = fig.add_axes([0.04, 0, 0.29, 1])
[…]

### 2021-05-12 data/plot_linear_delta_p.py

@@ -7,16 +7,18 @@ import h5py
 col_width = 3.25
 golden_ratio = 1.61803398875
 
-dirs = glob.glob('linear*/lin*/') + glob.glob('erf*/erf*/')
+dirs = glob.glob('linear*/lin*/')
 
 data = []
 for d in dirs:
     with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
         times = f['times'][()]
         z_departure = f['z_departure'][()]
+        z_overshoot = f['z_overshoot'][()]
         tot_time = times[-1] - times[0]
         good_times = times > (times[-1] - 1000)
         mean_departure = np.mean(z_departure[good_times])
+        mean_overshoot = np.mean(z_overshoot[good_times])
     S = float(d.split('_S')[-1].split('_')[0])
     P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
     Re = float(d.split('_Re')[-1].split('_')[0])
@@ -30,7 +32,7 @@ for d in dirs:
     else:
         erf = False
 
-    data.append((S, P, Re, threeD, mean_departure, Lz, erf))
+    data.append((S, P, Re, threeD, mean_departure, mean_overshoot, Lz, erf))
 data = np.array(data)
 
 S = data[:,0]
@@ -38,19 +40,23 @@ P = data[:,1]
 Re = data[:,2]
 threeD = data[:,3]
 z_top = data[:,4]
-Lz = data[:,5]
-erf = data[:,6]
+z_ov  = data[:,5]
+z_av = (z_top + z_ov)/2
+Lz = data[:,6]
+erf = data[:,7]
 
 plt.figure(figsize=(col_width, col_width/golden_ratio))
 good = (erf == 0)
-plt.scatter(P[good], z_top[good] - 1, c='k', label="Simulations", zorder=100)
+plt.scatter(P[good], z_top[good] - 1, c='k', label=r"Simulations ($\delta_p$)", zorder=100, marker='^')
+plt.scatter(P[good], z_ov[good] - 1, c='k', label=r"Simulations ($\delta_{\rm{ov}}$)", zorder=100, marker='v')
+plt.scatter(P[good], z_av[good] - 1, c='k', zorder=100, marker='o')
 plt.xscale('log')
 plt.yscale('log')
 
 x = np.logspace(-3, 2, 100)
 y1 = 0.23*x**(1/2)
[…]

### 2021-05-12 manuscript/ms.tex
hey look, a really rough intro draft

% Preamble
\documentclass{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

%%%% Journal preamble
\received{}
\revised{}
\accepted{}
\published{}
\submitjournal{ApJ}

\shorttitle{SHORT TITLE}
\shortauthors{Anders et al}

\begin{document}

%%%% Title and Abstract
\title{This is a title}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{CCA, Flatiron Institute}
\author{Daniel Lecoanet}
\affiliation{ESAM \& CIERA, Northwestern University}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{APS Dept and LASP, University of Colorado, Boulder}

\correspondingauthor{Evan H. Anders}
\email{evan.anders@northwestern.edu}

\begin{abstract}
Blah Blah short description
\end{abstract}
\keywords{UAT keywords}

%%%% Body of paper
\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism over some fraction of the stellar radius for all stars at some point in the stellar lifetime [CITE].
These motions drive the magnetic dynamo of the Sun and other stars [CITE], leading to the host of emergent phenomena known as stellar activity.
Furthermore, convective motions impinge upon nearby stable layers, exciting gravity waves [CITE].
Convection is also responsible for mixing chemical compositions, which becomes increasingly important in the cores of evolved stars [CITE].
A complete and nuanced understanding is therefore crucial for understanding stellar structure, evolution, and observations.

One particular aspect of stellar convection which remains poorly understood even after decades of study is the class of mechanisms generally referred to as ``convective overshoot.''
Useful parameterizations of the way in which convective motions extend beyond the nominally Schwarzschild- or Ledoux- stable boundaries of the convective zone have historically been elusive.
Improved models of this ``overshoot'' could help to resolve many discrepancies between observations and theoretical model.
In the Sun and solar-type stars, better models of convective boundaries could help solve the mystery of low abundances of Li at the surface of solar-type stars \citep{pinsonneault1997, dumont_etal_2021}, the ``solar modeling problem'' \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021} and problems in helioseismic profiles near the base of the convection zone \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence that we do not understand the nature of convective mixing at the boundary of core convection zones \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021} which could have profound implications for the post-main sequence evolution and remnants of massive stars \citet{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes [CITE], these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, an improved theoretical understanding of the behavior of convective boundaries which can inform easy-to-calculate parameterizations is essential.

Convective overshoot and penetration have been studied in laboratory experiments and numerical simulations for decades, and has been reviewed by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
%Early experiments of convective penetration of water in the laboratory \citep{deardorff_etal_1969} or simple numerical plumes \citep{schmitt_etal_1984} have given way to a wide array of dynamical experiments in recent years.
A slew of simulations in Cartesian \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020} and spherical \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021} geometry have been studied.
Despite this lengthy list of experiments, no consensus model of convective overshoot or penetration has emerged.
Throughout the remainder of this work, we will use terminology from this hydrodynamical literature.
``Convective penetration'' refers to convective motions which extend beyond the nominal Schwarzschild boundary of the convection zone \emph{and} flatten the temperature gradient towards the adiabatic.
``Convective overshoot'' refers to the motions that extend beyond the convective boundary but do not modify the thermal structure.
Our main focus in this paper will be on convective penetration.

\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Some simulations \citep{hurlburt_etal_1994, rogers_etal_2006} have shown at least partial agreement with this theory.
A semianalytic model of solar overshoot \citep{rempel2004} also agreed with the early ideas of Zahn. 
Furthermore, some select simulations have found hints that convective overshoot or penetration may be sensitive the magnitude of the flux in some way \citep{singh_etal_1998, hotta2017, kapyla2019}.
These results suggest that the gradients of fluxes near convective boundaries deserve further examination.

In this work, we design two numerical experiments to test the theory of \citet{zahn1991}.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and re-derive his theory in our simplified limit.
The results of our simulations are in full agreement with Zahn's theory.
\begin{quote}
\emph{
Specifically, we find that the depth of convective penetration depends on the gradient of the radiative flux near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be approximated so long as the radiative conductivity, or likewise the opacity, is known at the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, re-derive the theory of \citet{zahn1991}, and retrieve predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

\section{Theory}
\label{sec:theory}

\section{Simulation Details}
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = (\Pran\mR)^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
\end{align}

\section{Results}
\label{sec:results}

\section{A modified solar model}
\label{sec:solar_model}

\section{Discussion}
\label{sec:discussion}

\begin{acknowledgments}
We'd like to thank
\end{acknowledgments}

\appendix

\section{Accelerated Evolution}

\section{Table of simulation parameters}

\bibliographystyle{aasjournal}
\bibliography{biblio}
\end{document}

### 2021-05-12 manuscript/ms.tex
starts writing theory

@@
 \label{sec:theory}
+Throughout this work, we will utilize a modified version of the Boussinesq equations of motion, similar to the model derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
+In dimensional form,
+\begin{align}
+&\grad\dot\vec{u} = 0 
+\label{eqn:incompressible} \\
+&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
+\label{eqn:momentum} \\
+&\partial_t T + \vec{u}\dot\grad T + w \gradad = \chi\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
+\label{eqn:temperature} \\
+&\frac{\rho'}{\rho_0} = -|\alpha| T.
+\label{eqn:boussinesq}
+\end{align}
+In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
+Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term [CITE], and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
+We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
+We assume that the classical thermal diffusion term $\chi \grad^2 T'$  only acts on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$.
 

### 2021-05-13 data/plot_AE_fig.py
adds initial document files for the time and AE figs

@@ -1,0 +1,103 @@
+from collections import OrderedDict
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+col_width = 3.25
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('erf_AE_cut/erf*/')
+dirs.append('erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.55/')
+
+
+
+plt.figure(figsize=(col_width, col_width/golden_ratio))
+
+data = OrderedDict()
+for d in dirs:
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+
+    if '3D' in d:
+        threeD = True
+    else:
+        threeD = False
+    if 'erf' in d:
+        erf = True
+    else:
+        erf = False
+
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        z_departure = f['z_departure'][()]
+        z_overshoot = f['z_overshoot'][()]
+    data[d] = [S, P, Re, threeD, Lz, erf, times, z_departure, z_overshoot]
+
+for d in dirs:
+    times = np.copy(data[d][-3])
+    z_departure = data[d][-2]
+    z_overshoot = data[d][-1]
+    if 'predictive0.4_noiters/' in d:
+        color = 'blue'
+        times -= times[-1]
+    elif 'schwarzschild/' in d or 'schwarzschild_restart/' in d:
+        color = 'k'
+        for d2 in dirs:
+            times2 = data[d2][-3]
+            if 'schwarzschild_restart/' in d2:
+                times -= times2[-1]
+                print(d, d2, times[-1])
+    elif 'predictive0.7/' in d or 'pertUpContinued/' in d:
+        color = 'green'
+        for d2 in dirs:
+            times2 = data[d2][-3]
+            if 'pertUpContinued/' in d2:
+                times -= times2[-1]
[…]

### 2021-05-13 data/plot_time_fig.py

@@ -1,0 +1,89 @@
+from collections import OrderedDict
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+from scipy.interpolate import interp1d
+
+
+col_width = 3.25
+golden_ratio = 1.61803398875
+
+d = "erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild/"
+
+fig = plt.figure(figsize=(col_width, 2*col_width/golden_ratio))
+ax1 = fig.add_axes([0, 0.52, 1, 0.45])
+ax2 = fig.add_axes([0, 0.03, 1, 0.45])
+
+
+data = OrderedDict()
+S = float(d.split('_S')[-1].split('_')[0])
+P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+Re = float(d.split('_Re')[-1].split('_')[0])
+Lz = float(d.split('_Lz')[-1].split('_')[0])
+
+if '3D' in d:
+    threeD = True
+else:
+    threeD = False
+if 'erf' in d:
+    erf = True
+else:
+    erf = False
+
+with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+    times = f['times'][()]
+    z_departure = f['z_departure'][()]
+    z_overshoot = f['z_overshoot'][()]
+
+cmap = mpl.cm.viridis
+norm = mpl.colors.Normalize(vmin=0, vmax=times.max())
+sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+
+colors = [sm.to_rgba(t) for t in times]
+for i in range(int(len(times)/10)-1):
+    ax1.plot(times[i*10:(i+1)*10], z_departure[i*10:(i+1)*10]-1, c=sm.to_rgba(times[int((i+0.5)*10)]))
+    ax1.plot(times[i*10:(i+1)*10], z_overshoot[i*10:(i+1)*10]-1, c=sm.to_rgba(times[int((i+0.5)*10)]))
+ax1.set_ylim(0, 0.3)
+ax1.set_xlim(0, times.max())
+ax1.xaxis.set_label_position('top')
[…]

### 2021-05-13 manuscript/ms.tex
adds draft of theory section

@@
 \newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
+\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
 \newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
@@
 \newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
+\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
 \newcommand{\mP}{\ensuremath{\mathcal{P}}}
+\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
+\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
 \newcommand{\mR}{\ensuremath{\mathcal{R}}}
@@
 \label{eqn:momentum} \\
-&\partial_t T + \vec{u}\dot\grad T + w \gradad = \chi\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
+&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
 \label{eqn:temperature} \\
@@
 
+The basis of the theory of \citet{zahn1991} is that the size of the convection zone is determined by the horizontally-averaged energetics and buoyancy breaking.
+We assume convection reaches a time-stationary, equilibrium state; we vertically integrate Eqn.~\ref{eqn:temperature} and take a horizontal average to find
+\begin{equation}
+\Ftot = \Frad + \Fconv = \int Q dz + \Fbot,
+\end{equation}
+with $\Fconv = \overline{w T}$ and $\Fbot$ the flux at the bottom of the convective domain and $\Ftot$ the total flux, which can vary in height according to integral of $Q$.
+We next assume that convection penetrates above the nominal schwarzschild boundary of the convection zone and mixes the temperature gradient towards the adiabatic in that region.
+Thus, in that region, the convective flux can be found,
+\begin{equation}
+\Fconv = \Ftot - F_{\rm{rad, ad}} = \Ftot - k \grad_{\rm{ad}}.
+\end{equation}
+By definition, in this region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, where $\grad_{\rm{rad}} = \Ftot/k$, so this requires that $\Fconv < 0$ in the convective penetration region.
+We next assume that the temperature and velocity are highly correlated in the penetrative region with very similar horizontal fluctuations,
+\begin{equation}
+w(x,y,z) = W(z)h(x,y),
+\qquad
+T'(x,y,z) = \delta T(z)h(x,y).
+\end{equation}
+We here assume that $\overline{h} = 0$ and $\overline{h^2} \neq 0$.
+We can then express the convective flux in terms of these vertically-varying profiles and an average over the horizontal structure of the flows,
+\begin{equation}
+\Fconv \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
+\label{eqn:Fconv_vertical}
+\end{equation}
+In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must be oppositely signed and the convective flows should eventually come to a stop through buoyancy breaking.
+This is achieved through a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
+\begin{equation}
+\frac{1}{2}\frac{d w^2}{dz} = |\alpha| g T'.
+\end{equation}
+Multiplying both sides by $h(x,y)$, taking a horizontal average, and then substituting $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation,
+\begin{equation}
+\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 = \Fconv dz.
+\label{eqn:theory_ode}
+\end{equation}
+This equation can be integrated over the depth of the convection zone from $W = 0$ to $W = W_0$ at the convective boundary, as well as over the penetration zone from $W = W_0$ to where $W = 0$.
+We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
+Integrating Eqn.~\ref{eqn:theory_ode} over the CZ and PZ and taking a ratio of these two equations, we find
+\begin{equation}
+-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} = 
+\frac{\int_{\rm{PZ}} \Fconv dz}{\int_{\rm{CZ}} \Fconv dz}.
+\label{eqn:theory_fraction}
+\end{equation}
+In order to move further with this theory, it is necessary to specify the vertical shape of $\Fconv$, which is in turn set by $Q$, $\gradad$, and $k$.
+We will assume that $\gradad$ has a constant value and that the internal heating $Q$ is localized near the bottom of the CZ so that a constant convective flux $\Fcz$ is carried in the bulk convection zone.
+As a result, the vertical profile of $\Frad$ and $\Fconv$ is determined completely by the behavior of $k(z)$ near the convective boundary.
+We will study two cases in this work: a discontinuous jump in $k(z)$ at the convective boundary, and a piecewise-linear profile of $k(z)$ whose derivative may be discontinuous at the convective boundary.
+
+\subsection{Case I: Discontinuous radiative conductivity}
+We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
+The values of $k$ are chosen so that the convective flux follows
+\begin{equation}
+\Fconv(z) = \begin{cases}
+\Fcz			&	z \leq \Lcz,\\
+-\mP_D^{-1} \Fcz & 	z > \Lcz 
+\end{cases}.
+\end{equation}
+Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
+\begin{equation}
+\frac{\dP}{\Lcz} = \mP_D
+\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
+\label{eqn:discontinuous_prediction}
+\end{equation}
+We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
+This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.
+
+\subsection{Case II: Piecewise linear radiative conductivity}
+We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
+As a result, the convective flux in the vicinity of the boundary takes the form
+\begin{equation}
+\Fconv(z) = 
+\begin{cases}
+(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
+-\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
+\end{cases},
+\end{equation}
+where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
+Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
+\begin{equation}
+\frac{\dP}{\Lcz} = \sqrt{\mP_L
+\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
+\label{eqn:linear_prediction}
+\end{equation}
+which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
+
 \section{Simulation Details}
@@
 &\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
-&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = (\Pran\mR)^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
+&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q
 \end{align}

### 2021-05-13 manuscript/ms.tex
writes draft simulation setup section

@@
 \newcommand\Pran{\ensuremath{\mathrm{Pr}}}
+\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}
 
+\newcommand{\angles}[1]{\langle #1 \rangle}
 \newcommand{\pd}[1]{\partial_{#1}}
@@
 \subsection{Case I: Discontinuous radiative conductivity}
+\label{sec:discontinuous_theory}
 We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
@@
 \subsection{Case II: Piecewise linear radiative conductivity}
+\label{sec:linear_theory}
 We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
@@
 which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
+In this work, we will test the predictions of Eqns.~\ref{eqn:linear_prediction} and \ref{eqn:discontinuous_prediction}.
+Our aim is to see if the predicted scalings with $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}$ in local simulations.
 
 \section{Simulation Details}
+We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the convection zone, the timescale of freefall across that convection zone, and the temperature scale of the internal heating over that freefall time,
+\begin{equation}
+\begin{split}
+&T^* = (\Delta T)T = Q_0 \tau T,\qquad
+\partial_{t^*} = \tau^{-1}\partial_t = \left(\frac{\alpha g Q_0}{\Lcz}\right)^{1/3} \partial_t,\qquad
+\grad^* = \Lcz^{-1} \grad,\qquad
+\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 \Lcz^2\right)^{1/3}\vec{u},
+\\
+&k^* = (\Lcz^2 \tau^{-1})k,\qquad
+Q^* = Q_0 Q,\qquad
+\mR = \frac{u_{\rm{ff}} \Lcz}{\nu},\qquad
+\Pran = \frac{\nu}{\chi}.
+\end{split}
+\end{equation}
+Here, quantities with $*$ (e.g., $T^*$) refer to the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, and going forward quantities without these (e.g., $T$) will be dimensionless.
+The equations of motion are therefore
 \label{sec:simulation_details}
 \begin{align}
-&\grad\dot\vec{u} = 0 \\
-&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
-&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q
+&\grad\dot\vec{u} = 0 
+\label{eqn:nondim_incompressible} \\
+&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
+\label{eqn:nondim_momentum} \\
+&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
+\label{eqn:nondim_temperature}
 \end{align}
+We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain contains at least two convection zone length scales according to the Schwarzschild criterion.
+We decompose the temperature field into a background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
+For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
+We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
+
+We impose an order unity internal heating which spans one fifth of the convection zone,
+\begin{equation}
+Q = \begin{cases}
+0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
+|Q_{\rm{mag}}|		& 0.1 \leq z \leq 0.1 + \delta_H
+\end{cases}.
+\end{equation}
+The integrated value of the flux through the system from the heating is therefore $F_H(z > 0.1 + \delta_H) = \int_0^z Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
+Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
+We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
+We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \zeta F_H$ and we choose $\zeta = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
+
+In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency $f_{\rm{conv}} \approx \angles{\vec{u}} \Lcz \approx 1$.
+We want to allow the stiffness of the radiative-convective interface to be a control parameter.
+The stiffness is defined,
+\begin{equation}
+\mS \equiv \frac{N^2}{f_{\rm{conv}}} \approx N^2,
+\end{equation}
+where $N^2$ is the \brunt$\,$frequency in the radiative zone.
+In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $T_0$ which in turn sets the value of $k$ in the radiative zone.
+
+The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, which determines the size of the convective penetration region.
+We define
+\begin{equation}
+\mP = -\frac{\Fconv|_{\rm{CZ}}}{\Fconv|_{PZ}},
+\end{equation}
+where $\Fconv|_{PZ}$ is the negative convective flux carried in a perfectly adiabatic convective penetration region.
+We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
+We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$.
+
+Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
+The value of $\mR$ roughly corresponds to the value of the peak Reynolds number measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
+Astrophysical convection is in the limit of $\Pran \ll 1$; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
+
+\subsection{Case I: Discontinuous radiative conductivity}
+Most of the simulations in this paper study simulations with a discontinuous radiative conductivity,
+\begin{equation}
+k_D(z) = \begin{cases}
+k_{\rm{CZ}}	&	z < 1 \\
+k_{\rm{RZ}} &	z \geq 1
+\end{cases}.
+\end{equation}
+Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry the $\Fbot$ at $z = 0$ and that the radiative gradient can carry the flux for $z \geq 1$ specifies this system fully,
+\begin{equation}
+k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
+k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
+\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
+\gradrad = \gradad - Q_{\rm{mag}}\mS.
+\end{equation}
+
+We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper (one in which we vary each parameter while holding the other parameters constant).
+We use ``Reference values'' of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all of our parameter space sweeps pass through this point in the three-dimensional parameter space.
+As in section \ref{sec:discontinuous_theory}, we expect $\delta_p \propto \mP_D$.
+
+\subsection{Case II: Piecewise linear radiative conductivity}
+We additionally study a select few simulations where the radiative conductivity's gradient is piecewise discontinuous,
+\begin{equation}
+\partial_z k = \partial_z k_0
+\begin{cases}
+1	&	z < 1 \\
+\mP_L^{-1} &	z \geq 1
+\end{cases}
+\end{equation}
+Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
+by this choice, we require
+\begin{equation}
+\partial_z k_0 = \frac{\delta_H}{\Lcz \mS \xi},\qquad
+k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
+\gradad = Q \mS \xi,
+\end{equation}
+where $\xi \equiv 1 + \mP_L(1 + \zeta)$.
+In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
+As in section \ref{sec:linear_theory}, we expect $\delta_p \propto \mP_L^{1/2}$.
+
+\subsection{Numerics}
+We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use X version} using timestepper RK443 [CITE].
+All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
+The aspect ratio of our domains is two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
+To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
+We produce the figures in this paper using matplotlib [CITE].
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repo, found at [CITE].
 
@@
 \section{Accelerated Evolution}
+\label{app:accelerated_evolution}
 
 \section{Table of simulation parameters}
+\label{app:simulation_table}
 

### 2021-05-14 manuscript/ms.tex
writes results section!

@@
 \author[0000-0002-3433-4733]{Evan H. Anders}
-\affiliation{CIERA, Northwestern University}
+\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
 \author[0000-0001-5048-9973]{Adam S. Jermyn}
-\affiliation{CCA, Flatiron Institute}
-\author{Daniel Lecoanet}
-\affiliation{ESAM \& CIERA, Northwestern University}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
+\author[0000-0002-7635-9728]{Daniel Lecoanet}
+\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
+\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}
 \author[0000-0001-8935-219X]{Benjamin P. Brown}
-\affiliation{APS Dept and LASP, University of Colorado, Boulder}
+\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}
 
@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism over some fraction of the stellar radius for all stars at some point in the stellar lifetime [CITE].
-These motions drive the magnetic dynamo of the Sun and other stars [CITE], leading to the host of emergent phenomena known as stellar activity.
-Furthermore, convective motions impinge upon nearby stable layers, exciting gravity waves [CITE].
-Convection is also responsible for mixing chemical compositions, which becomes increasingly important in the cores of evolved stars [CITE].
+Convection is a crucial heat transport mechanism over some fraction of the stellar radius for all stars at some point in the stellar lifetime \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
+These motions drive the magnetic dynamo of the Sun and other stars \citep{brun_browning_2017}, leading to the host of emergent phenomena known as stellar activity.
+Furthermore, convective motions impinge upon nearby stable layers, exciting gravity waves \citep{aerts2010}.
+Convection is also responsible for mixing chemical compositions, which becomes increasingly important in the cores of evolved stars \citep{salaris_cassisi_2017}.
 A complete and nuanced understanding is therefore crucial for understanding stellar structure, evolution, and observations.
@@
 In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
-While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes [CITE], these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
+While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
 In short, an improved theoretical understanding of the behavior of convective boundaries which can inform easy-to-calculate parameterizations is essential.
@@
 %Early experiments of convective penetration of water in the laboratory \citep{deardorff_etal_1969} or simple numerical plumes \citep{schmitt_etal_1984} have given way to a wide array of dynamical experiments in recent years.
-A slew of simulations in Cartesian \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020} and spherical \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021} geometry have been studied.
+A slew of simulations in Cartesian \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, andrassy_spruit_2015, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020} and spherical \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021} geometry have been studied.
 Despite this lengthy list of experiments, no consensus model of convective overshoot or penetration has emerged.
@@
 In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
-Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term [CITE], and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
+Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
 We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
@@
 
-We impose an order unity internal heating which spans one fifth of the convection zone,
+We impose a constant internal heating which spans only part of the convection zone,
 \begin{equation}
@@
 \subsection{Numerics}
-We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use X version} using timestepper RK443 [CITE].
+We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use X version} using timestepper RK443 \citep{ascher_etal_1997}.
 All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
@@
 To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
-We produce the figures in this paper using matplotlib [CITE].
+We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
 All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repo, found at [CITE].
+
+We can't use true discontinuities and so we use approximate Heaviside functions like follows (TODO).
+
+\subsection{Penetration depth measurements}
 
@@
 \label{sec:results}
+
+\subsection{Qualitative description of simulation evolution}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{time_evolution.pdf}
+\caption{(Top panel) we show traces of the time evolution of the points in the simulation where $\grad$ has departed from $\gradad$ by 10\% (bottom curve) and 90\% (top curve) of $\Delta = \gradad - \gradrad$.
+Time is plotted on the x-axis in freefall units which are roughly equal to convective overturn times; the color of the line represents the simulation time.
+While this evolution is initially fast (changing noticeably over hundreds of overturn times), as the convection zone approaches its final size its evolution drastically slows down.
+(Bottom panel) The vertical profile of $\grad/\gradad$ is plotted against height at different times (where the color denotes the time and matches the color of the top panel.
+The (constant) value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
+The 10\% and 90\% departure curves from the top panel are overplotted as red lines.
+\label{fig:time_evolution}
+}
+\end{figure}
+
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 2$ (TODO: change to 4) whose initial conditions set $\grad = -\partial_z T$ equal to $\gradad$ in the convection zone ($z < 1$) and equal to $\gradrad$ in the radiative zone ($z > 1)$.
+Initially, over hundreds of overturn times, the front of the convection zone drastically advances past the Schwarzschild boundary of the convection zone at $z = 1$.
+As the convection zone advances and mixes $\grad \rightarrow \gradad$ within itself; this steepening of $\grad$ within the PZ is accompanied by a flattening of $\grad < \gradrad$ at the base of the RZ along the front of the CZ.
+This flattening of $\grad$ increases the value of $N^2 = \gradad - \grad$ at the front of the convection zone, slowing the advancement of the convection zone until this disequilibrium state diffuses to the top boundary of the simulation.
+This stiffer radiative-convective interface, combined with the presence of an increasingly growing breaking region in the form of the PZ slows the advancement of the convective front and the final equilibration of the top boundary of the convection zone takes thousands of convective overturn times.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
+\caption{
+Instantaneous snapshots of a vertical slice through the simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ are shown.
+In both panels, the nominal Schwarzschild top of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the convection zone where $\grad$ departs from $\gradad$ by 10\% of $\Delta = \gradad - \gradrad$ is shown as a solid horizontal line.
+(Left) The vertical velocity is shown; convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\grad$ departs from $\gradad$.
+(Right) Temperature perturbations away from $\overline{T}$ are shown; these perturbations are normalized by their standard deviation at each height in order to make both the convective features (below the solid black line) and internal gravity waves excited by the convection (above) visible.
+Unlike in the vertical velocity slice, we see that the temperature perturbations switch sign at the Schwarzschild boundary of the convection zone (the dashed horizontal line); buoyancy thus switches from an accelerating force to a braking force.
+\label{fig:vertical_dynamics_panels}
+}
+\end{figure}
+
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mP_D = 4$ and $\mS = 10^3$ in an equilibrated state.
+We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone into a penetration zone.
+However, there is still a stable radiative zone with small vertical velocity perturbations into which the convection does not extend.
+On the right, we see that hot upwellings in the convective dynamics are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
+These upwellings impinge upon the stable radiative zone and excite gravity waves [cf., CITE], but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.
+
+\subsection{Measured penetration zone scalings}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{erf_3D_penetration_depths.pdf}
+\caption{
+We plot penetration depths against $\mP_D$ (left, at constant $\mR$, $\mS$), $\mR$ (center, at constant $\mP_D$, $\mS$), and $\mS$ (right, at constant $\mP_D$, $\mR$).
+Up-triangles are the location of 10\% departure, down-triangles are the location of 90\% departure, and circles are the location of 50\% departure.
+In the left panel, we plot a line corresponding to the theory of Eqn.~\ref{eqn:discontinuous_prediction}.
+We find that the penetration depth is a strong, roughly linear function of $\mP_E$, in good agreement with the theory.
+The horizontal lines in the left panel represent the full range of the right two panels; the effects of varying $\mS$ and $\mR$ are secondary to the effects of $\mP$.
+In the center panel, we see that the penetration depth increases at low $\mR$ as laminar dynamics give way to time-evolving dynamics.
+As we increase the turbulence, the penetration depth decreases weakly and appears to asymptote in the turbulent regime.
+In the right panel, we see little change in the 50\% departure point, and we see that 10\% and 90\% departure points converge to the central point as a function of stiffness.
+\label{fig:erf_3D_penetration_depths}
+}
+\end{figure}
+
+In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth from Case I (discontinuous $k$) simulations, quantified by the 10\%, 50\%, and 90\% departure points from $\gradad$.
+In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
+We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is equal to or greater in size than the nominal convection zone (of unit depth).
+We find that the value of $\mP_D$ is the primary parameter whose value modifies the height of the convection zone.
+While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
+
+In the center and rightmost panels of Fig.~\ref{fig:erf_3D_penetration_depths}, we focus on modifications to the measured penetration depths achieved by varying $\mR$ (turbulence) and $\mS$ (stiffness).
+We find that the penetration depth is smaller at very low (laminar) values of $\mR$ and at high (turbulent) values of $\mR$, with a peak at moderate values (for which dynamics are interesting and non-stationary, but not as turbulent as e.g., Fig.~\ref{fig:vertical_dynamics_panels}).
+Our data suggest that the penetration depth asymptotes as $\mR$ increases and so our results should be relevant for the astrophysical case in which $\mR \rightarrow \infty$.
+We note however that these simulations are expensive to run and cannot be converged to the same degree of confidence as the simulations for which $\mR \lesssim 10^3$, which we run for thousands of overturn times.
+We find that mean penetration depth (the 50\% departure point) shows little dependence on the stiffness (circles in the right panel).
+However, the depth of the transition region from the PZ to the RZ shows a strong dependence on stiffness.
+In stars, the stiffness is roughly determined by the Mach number ($\rm{Ma}^{-2} \sim \mS$), so for low-Mach convective stellar flows, the boundary of the PZ and RZ can likely be reasonably approximated as a step function in $\grad$.
+
+\begin{figure}[t!]
+\centering
+\includegraphics{linear_3D_penetration_depths.pdf}
+\caption{
+Similar to Fig.~\ref{fig:erf_3D_penetration_depths}, but for the Case II ``linear'' simulations where the slope of $k$ is discontinuous at the Schwarzschild point.
+We plot a line corresponding to the theory of Eqn.~\ref{eqn:linear_prediction} as well as the 10\% (up triangle), 50\% (circle), and 90\% (down triangle) departure points.
+We find that the theory describes our simulation measurements well.
+We note that at small values of $\mP_L \lesssim 10^{-1}$, the 10\% departure point approaches the Schwarzschild boundary of the convection zone, approaching zero and not appearing on this plot.
+\label{fig:linear_3D_penetration_depths}
+}
+\end{figure}
+
+Finally, in Fig.~\ref{fig:linear_3D_penetration_depths}, we plot penetration depths as a function of $\mP_L$ for the ``linear'' Case II simulations.
+We compare these depths to the theory of Eqn.~\ref{eqn:linear_prediction}.
+We hold $\mR = 800$ and $\mS = 10^3$ constant for these simulations.
+As in the discontinuous simulations, we find excellent agreement between the simulations and the theory.
+
+Our simulation results present a strong case for the validity of \citet{zahn1991}'s theory.
+The generalized Eqn.~\ref{eqn:theory_fraction}, and its solution for our simulation setups in Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction}, describe our data well.
+In addition to the flux-based penetration parameter $\mP$, the theory of Eqn.~\ref{eqn:theory_fraction} depends on the horizontal structure of the flux-carrying convective flows.
+In this work, from the theory lines plotted in Figs.~\ref{fig:erf_3D_penetration_depths} \& \ref{fig:linear_3D_penetration_depths}, we find
+\begin{equation}
+\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx 0.125 \,\,(\text{Case I: Discontinuous}),\qquad
+\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx 0.0625 \,\,(\text{Case II: Linear}).
+\end{equation}
+As the case II linear simulations are more applicable in the regime of stellar convection, we suggest that those simulations likely provide a starting guess for how to implement \citet{zahn1991}'s theory in 1D stellar models.
+We examine this further in the next section.
 
@@
 \label{app:accelerated_evolution}
+\citet{anders_etal_2018}
 

### 2021-05-14 manuscript/ms.tex
starts drafting out MESA section, discussion, AE section.

@@
 Improved models of this ``overshoot'' could help to resolve many discrepancies between observations and theoretical model.
-In the Sun and solar-type stars, better models of convective boundaries could help solve the mystery of low abundances of Li at the surface of solar-type stars \citep{pinsonneault1997, dumont_etal_2021}, the ``solar modeling problem'' \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021} and problems in helioseismic profiles near the base of the convection zone \citep{christensen-dalsgaard_etal_2011}.
+In the Sun and solar-type stars, better models of convective boundaries could help solve the mystery of low abundances of Li at the surface of solar-type stars \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}, the ``solar modeling problem'' \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021} and problems in helioseismic profiles near the base of the convection zone \citep{christensen-dalsgaard_etal_2011}.
 There is also ample evidence that we do not understand the nature of convective mixing at the boundary of core convection zones \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021} which could have profound implications for the post-main sequence evolution and remnants of massive stars \citet{farmer_etal_2019, higgins_vink_2020}.
@@
 \frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx 0.0625 \,\,(\text{Case II: Linear}).
+\label{eqn:fit_h_values}
 \end{equation}
@@
 \label{sec:solar_model}
+We now examine briefly how \citet{zahn1991}'s theory modifies a simple structure model of the Sun.
+We implement a simple prescription of convective penetration in MESA \citep{paxton_etal_2013} as follows:
+\begin{enumerate}
+\item Find the radial location of the radiative-convective boundary according to the Schwarzschild criterion, $r_{\rm{RCB}}$.
+Also evaluate the value of the mixing length $\ell$ at that location.
+\item Integrate the magnitude of the convective luminosity within the convection zone, $L_i = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
+\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for the horizontal dynamics in Eqn.~\ref{eqn:fit_h_values}, integrate $L_o = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delta_p} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
+We determine the value of $\delta_p$ according to Eqn.~\ref{eqn:theory_fraction} so that
+\begin{equation}
+C \equiv -\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx -0.1
+\Rightarrow
+L_o = C L_i.
+\label{eqn:mesa_equation}
+\end{equation}
+\item Override the value of $\grad$ in the MESA solver to set $\grad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
+\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_o$.
+\end{enumerate}
 
@@
 \label{sec:discussion}
+In this work, we discussed the theory of convective penetration put forward by \citet{zahn1991}, then designed and analyzed two sets of simulations which showed good agreement with that theory.
+We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
+We find that convection zones are bounded by ``penetration zones,'' whose depths are determined by the shape of the radiative gradient near the convective boundaries.
+For the proper choice of parameters, these penetration zones can be larger than the convection zones themselves; however, for realistic stellar values ($\mP_L \approx 1$), we find that they may be as large as 20\% of the convective length scale (the mixing length in a star).
+
+The simulations we presented in this work were the simplest possible simulations to try to test the basic tenents of \citet{zahn1991}'s theory.
+In particular, they show convincingly that the shape of the flux near the convective boundary is one of the factors that the determines the depth of the penetration zone.
+However, as discussed in Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_equation}, the structure of the penetrative convective flows is the other crucial ingredient in Zahn's theory.
+The scalar numerical estimates for how these dynamic sshould be handled in the theory, presented in Eqn.~\ref{eqn:fit_h_values}, of course come with the caveat that the local, Cartesian, Boussinesq flows studied here may be quite different from stars where spherical effects and density stratification come into account.
+Future work should aim to determine how much the values in Eqn.~\ref{eqn:fit_h_values} vary when these more realistic effects are taken into account.
+
+Furthermore, it is important to note that stellar opacities, and thus stellar conductivities, are functions of thermodynamic variables rather than radial location.
+As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep a penetration zone should form.
+Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state.
+
+Finally, we note that our work here assumes a uniform composition through the convective and radiative region.
+Frequently within stars, convective boundaries coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
+Future work should also aim to determine if stabilizing composition gradients can prevent the formation of penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
+
+In summary, we have provided a first step towards deconstructing the mysteries of the behavior of convection near convective boundaries.
+We find that the simple-but-elegant theory of \citet{zahn1991} provides an excellent starting point for building a better understanding of the nature of convective penetration in stellar interiors.
+In future work, we will aim to more robustly implement Zahn's theory into MESA.
 
 \begin{acknowledgments}
-We'd like to thank
+We'd like to thank Keaton Burns and Kyle Augustson for useful discussions which improved the content of this manuscript.
+EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
+Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
 \end{acknowledgments}
@@
 \label{app:accelerated_evolution}
-\citet{anders_etal_2018}
+As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
+In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure is possible.
+In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
+\begin{enumerate}
+\item Once a simulation has a volume-averaged Reynolds number greater than 1, we wait 50 freefall times.
+\item We measure the 50\% departure point ($\delta_p$) of the top of the convection zone every freefall time, and store this information for 50 freefall times.
+\item We measure $d\delta_p/dt$ using NumPy's \texttt{gradient} function. 
+If the average value of $d\delta_p/dt$ has a different sign over the first and last 25 freefall times in our collection window, we erase the first 25 freefall times of data and return to step 2 for 25 freefall times.
+If the average value of $d\delta_p/dt$ has the same sign over the first and last 25 freefall times, we accelerate the evolution of our simulations.
+\item We find a value of $\delta_p$ to adjust the simulation toward. TODO: here's how we do this.
+\item We zero out convective velocities above the schwarzschild point. TODO: here's how.
+\item We restart from step 1.
+\end{enumerate}
+If a simulation returns to step 2 from step 3 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
+This process effectively removes the long diffusive thermal evolution on display in the middle panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
+
+In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of the same simulation as in Fig.~\ref{fig:time_evolution}, and we compare it to three simulations which use this accelerated evolution procedure.
+We start these three simulations with penetration zones whose depths are $\delta_p = [0, 0.4, 0.7]$, and we expect the evolved penetration zone depth to be $\delta_p \approx 0.55$.
+While the standard evolution simulation takes tens of thousands of time units to reach the final state, the accelerated simulations reach the final state over the course of hundreds of freefall times.
 

### 2021-05-15 manuscript/ms.tex
decent cleanup of intro sources

@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism over some fraction of the stellar radius for all stars at some point in the stellar lifetime \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
-These motions drive the magnetic dynamo of the Sun and other stars \citep{brun_browning_2017}, leading to the host of emergent phenomena known as stellar activity.
-Furthermore, convective motions impinge upon nearby stable layers, exciting gravity waves \citep{aerts2010}.
-Convection is also responsible for mixing chemical compositions, which becomes increasingly important in the cores of evolved stars \citep{salaris_cassisi_2017}.
-A complete and nuanced understanding is therefore crucial for understanding stellar structure, evolution, and observations.
+Convection is a crucial heat transport mechanism over some fraction of the stellar radius for essentially all stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
+Convective dynamics drive many still poorly-understood phenomena in stars.
+For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
+Furthermore, convective motions excite both acoustic and gravity waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
+Convection is also responsible for compositional mixing, which can modify surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
+A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.
 
-One particular aspect of stellar convection which remains poorly understood even after decades of study is the class of mechanisms generally referred to as ``convective overshoot.''
-Useful parameterizations of the way in which convective motions extend beyond the nominally Schwarzschild- or Ledoux- stable boundaries of the convective zone have historically been elusive.
-Improved models of this ``overshoot'' could help to resolve many discrepancies between observations and theoretical model.
-In the Sun and solar-type stars, better models of convective boundaries could help solve the mystery of low abundances of Li at the surface of solar-type stars \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}, the ``solar modeling problem'' \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021} and problems in helioseismic profiles near the base of the convection zone \citep{christensen-dalsgaard_etal_2011}.
-There is also ample evidence that we do not understand the nature of convective mixing at the boundary of core convection zones \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021} which could have profound implications for the post-main sequence evolution and remnants of massive stars \citet{farmer_etal_2019, higgins_vink_2020}.
+One aspect of stellar convection which remains poorly understood despite decades of study is the class of mechanisms generally referred to as ``convective overshoot.''
+Broadly, in the stellar structure literature, convective overshoot refers to any mechanism which causes at least compositional mixing beyond the Schwarzschild or Ledoux stable convective boundary.
+Improved models of overshoot could resolve many discrepancies between observations and structure models.
+For example, observed surface lithium abundances in the Sun and solar-type stars align poorly with models, which could suggest a need for additional mixing below the solar convection zone \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
+Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; model and observation discrepancies can be reduced by appropriately incorporating mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
+There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
+Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
 In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
 While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
-In short, an improved theoretical understanding of the behavior of convective boundaries which can inform easy-to-calculate parameterizations is essential.
+In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.
+
+The host of mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
+The first of these classes is, confusingly, also called ``convective overshoot'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly \emph{do not adjust the thermodynamic profile}.
+The second of these classes is called ``convective penetration,'' in which convective motions mix the thermodynamic profiles beyond the convective boundary, thereby extending the convective boundary beyond the nominal Schwarzschild or Ledoux one.
+We will follow a deep history \citep{zahn1991, korre_etal_2019} and use this terminology throughout this work.
+The primary focus of this work will be on convective penetration, as this mechanism shows promise in aligning observations and models \citep{christensen-dalsgaard_etal_2011, pedersen_etal_2021}.
 
 Convective overshoot and penetration have been studied in laboratory experiments and numerical simulations for decades, and has been reviewed by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-%Early experiments of convective penetration of water in the laboratory \citep{deardorff_etal_1969} or simple numerical plumes \citep{schmitt_etal_1984} have given way to a wide array of dynamical experiments in recent years.
-A slew of simulations in Cartesian \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, andrassy_spruit_2015, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020} and spherical \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021} geometry have been studied.
-Despite this lengthy list of experiments, no consensus model of convective overshoot or penetration has emerged.
-Throughout the remainder of this work, we will use terminology from this hydrodynamical literature.
-``Convective penetration'' refers to convective motions which extend beyond the nominal Schwarzschild boundary of the convection zone \emph{and} flatten the temperature gradient towards the adiabatic.
-``Convective overshoot'' refers to the motions that extend beyond the convective boundary but do not modify the thermal structure.
-Our main focus in this paper will be on convective penetration.
+Experiments and simulations exhibiting extensive convective penetration in simplified, Boussinesq setups have been studied for decades \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}, with multiple recent studies suggesting that the penetration depth (or overshoot depth) is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018, korre_etal_2019}.
+Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that penetration and overshoot depths were determined by the stiffness of the radiative-convective interface \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
+However, a number of studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+Many modern simulations utilize stellar structure models as inspiration for their experimental setup, and find significant convective overshoot or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+Some simulations have found that the extension beyond the convection zone depends strongly on the input flux for their experimental setups \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+In this work, we follow the results of these last class of simulations and study how one aspect of the convective flux modifies the extent of the penetration region.
 
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
-Some simulations \citep{hurlburt_etal_1994, rogers_etal_2006} have shown at least partial agreement with this theory.
-A semianalytic model of solar overshoot \citep{rempel2004} also agreed with the early ideas of Zahn. 
-Furthermore, some select simulations have found hints that convective overshoot or penetration may be sensitive the magnitude of the flux in some way \citep{singh_etal_1998, hotta2017, kapyla2019}.
-These results suggest that the gradients of fluxes near convective boundaries deserve further examination.
+Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that the boosting of luminosity in stellar experiments compared to reference stars may be leading to wrong estimates of the penetrative dynamics.
+Indeed, some simulations have shown partial agreement with these ideas.
+In the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994, rogers_etal_2006} agree with Zahn's theory (although at high stiffness they disagree).
+Some simulations have used the magnitude of the system flux as a control parameter, and indeed found that the penetration depth was dependent on it \citep{singh_etal_1998, hotta2017, kapyla2019}.
+These results suggest that Zahn's theory deserves to be revisted.
 
@@
 
+We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
+This results in a discontinuous temperature profile, which would result in an acoustic ``glitch'' on the solar frequencies.
+Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which is smaller than what is found in our model \citep[see e.g., section 7.2.1 of][]{basu2016}.
+However, our results here are in line with the recent simulations of \citet{kapyla2019}, which suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
+
 \section{Discussion}
@@
 As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep a penetration zone should form.
-Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state.
+Future studies should follow e.g., \citet{kapyla_etal_2017, kapyla2019} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state.
 

### 2021-05-15 manuscript/ms.tex
adds prelim AE figure; adds heaviside function and some AE appendix details

@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism over some fraction of the stellar radius for essentially all stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
+Convection is a crucial heat transport mechanism in essentially all stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
 Convective dynamics drive many still poorly-understood phenomena in stars.
 For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
+Convection is also responsible for compositional mixing, which can modify surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
 Furthermore, convective motions excite both acoustic and gravity waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
-Convection is also responsible for compositional mixing, which can modify surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
 A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.
@@
 \end{cases}.
+\label{eqn:sim_Q}
 \end{equation}
@@
 \end{cases}.
+\label{eqn:sim_discontinuous_k}
 \end{equation}
@@
 \end{cases}
+\label{eqn:sim_linear_k}
 \end{equation}
@@
 
-We can't use true discontinuities and so we use approximate Heaviside functions like follows (TODO).
+Spectral methods with finite coefficient expansions cannot capture true discontinuities.
+In order to approximate discontinuous functions such as Eqns.~\ref{eqn:sim_Q}, \ref{eqn:sim_discontinuous_k}, \ref{eqn:sim_linear_k}, we must use smooth transitions.
+To create these smooth transitions, we define an approximate Heaviside step function using the error function,
+\begin{equation}
+H(z; z_0, \delta_w) = \frac{1}{2}\left(1 + \rm{erf}\left[\frac{z - z_0}{\delta_w}\right]\right).
+\label{eqn:heaviside}
+\end{equation}
+In the limit of that $\delta_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
+While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $\delta_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $\delta_w = 0.075$.
+In all other cases, we use $\delta_w = 0.05$.
 
@@
 If the average value of $d\delta_p/dt$ has the same sign over the first and last 25 freefall times, we accelerate the evolution of our simulations.
-\item We find a value of $\delta_p$ to adjust the simulation toward. TODO: here's how we do this.
-\item We zero out convective velocities above the schwarzschild point. TODO: here's how.
+\item We calculate $\Delta\delta_p$ as the minimum of 
+\begin{equation}
+\Delta\delta_{p,1} = \overline{\frac{d\delta_p}{dt}}\bigg|\frac{\Delta \delta_p}{\Delta d \delta_p / dt} \bigg|,\qquad
+\Delta\delta_{p,2} = 500\overline{\frac{d\delta_p}{dt}}.
+\end{equation}
+Here, $\Delta\delta_{p,1}$ essentially represents a newton iteration in $d\delta_p / dt$ vs. $\delta_p$ space towards the root value where $d\delta_p / dt = 0$.
+In some cases, $\Delta\delta_{p,1}$ becomes too large; we thus limit the maximum change to $\Delta\delta_{p,2}$, which represents an advancement of the convective boundary at the current evolutionary pace by 500 freefall time units.
+\item After determining a new value of $\delta_{\rm{p,ev}} = \delta_{p,0} + \Delta\delta_p$, we adjust the $m = 0$ temperature gradient to
+\begin{equation}
+\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{p,ev}}, 0.05) \Delta\grad,
+\label{eqn:initial_grad}
+\end{equation}
+where $H$ is defined in Eqn.~\ref{eqn:heaviside} and $\Delta\grad = \gradrad - \gradad$.
+We also multiply the temperature perturbations and full convective velocity field by $H(z; 1, 0.05)$.
+This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
 \item We restart from step 1.
@@
 In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of the same simulation as in Fig.~\ref{fig:time_evolution}, and we compare it to three simulations which use this accelerated evolution procedure.
-We start these three simulations with penetration zones whose depths are $\delta_p = [0, 0.4, 0.7]$, and we expect the evolved penetration zone depth to be $\delta_p \approx 0.55$.
-While the standard evolution simulation takes tens of thousands of time units to reach the final state, the accelerated simulations reach the final state over the course of hundreds of freefall times.
+We start these three simulations with initial temperature profiles defined by Eqn.~\ref{eqn:initial_grad} with initial values of $\delta_{\rm{p,ev}} = 0$ (red line), $\delta_{\rm{p,ev}} 0.4$ (purple line), or $\delta_{\rm{p,ev}} = 0.7$ (green line).
+For these simulations, we expect the evolved penetration zone depth to be $\delta_p \approx 0.55$, so these represent perturbations above and below this estimate, as well as the classical Schwarzschild initial conditions.
+While the simulation that we straightforwardly timestep (black line) takes tens of thousands of time units to reach the final state, the accelerated simulations reach the final state over the course of hundreds of freefall times.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{AE_time_figure.pdf}
+\caption{
+\label{fig:AE_time_figure}
+}
+\end{figure}
 

### 2021-05-15 manuscript/ms.tex
adds in initial departure point definitions

@@
 \subsection{Penetration depth measurements}
+In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\grad \approx \gradad$.
+In order to characterize the vertical extent of the penetrative (and subsequent overshoot) region, we measure how drastically $\grad$ has departed from $\gradad$.
+We define the difference between the adiabatic and radiative gradient,
+\begin{equation}
+\Delta\grad \equiv \gradad(z) - \gradrad(z).
+\end{equation}
+We measure penetration and overshoot depths in terms of ``departure points,'' that is, points at which the realized temperature gradient $\grad$ has evolved away from the adiabatic $\gradad$ by some fraction $f < 1$.
+Specifically,
+\begin{equation}
+1 + \delta_{f} = \rm{max}(z) \mid \grad > \gradad - f\Delta\grad.
+\end{equation}
+In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points, which are respectively at the top of the penetration zone, in the middle of the overshoot zone, and at the top of the overshoot zone.
+We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
 

### 2021-05-21 manuscript/ms.tex
theory updates from may 21; need to re-think eqns 9-10 (kinetic energy equation?)

@@
 \newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
+\newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
 \newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
@@
 \newcommand{\mP}{\ensuremath{\mathcal{P}}}
+\newcommand{\mD}{\ensuremath{\mathcal{D}}}
 \newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
@@
 \label{sec:theory}
-Throughout this work, we will utilize a modified version of the Boussinesq equations of motion, similar to the model derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
-In dimensional form,
+Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
 \begin{align}
@@
 \label{eqn:incompressible} \\
-&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
+&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
 \label{eqn:momentum} \\
@@
 \label{eqn:temperature} \\
-&\frac{\rho'}{\rho_0} = -|\alpha| T.
+&\frac{\rho_1}{\rho_0} = -|\alpha| T.
 \label{eqn:boussinesq}
 \end{align}
-In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
-Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
-We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
-We assume that the classical thermal diffusion term $\chi \grad^2 T'$  only acts on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$.
+Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
+We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
+These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
+The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
+Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
+We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.
 
-The basis of the theory of \citet{zahn1991} is that the size of the convection zone is determined by the horizontally-averaged energetics and buoyancy breaking.
-We assume convection reaches a time-stationary, equilibrium state; we vertically integrate Eqn.~\ref{eqn:temperature} and take a horizontal average to find
+\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
+Assuming convection reaches a time-stationary state, we horizontally-average the vertically integrated Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
-\Ftot = \Frad + \Fconv = \int Q dz + \Fbot,
+\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
 \end{equation}
-with $\Fconv = \overline{w T}$ and $\Fbot$ the flux at the bottom of the convective domain and $\Ftot$ the total flux, which can vary in height according to integral of $Q$.
-We next assume that convection penetrates above the nominal schwarzschild boundary of the convection zone and mixes the temperature gradient towards the adiabatic in that region.
-Thus, in that region, the convective flux can be found,
+where $\overline{\Fconv} = \overline{w T}$, is $\Fbot$ the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
+We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
+This assumption specifies the convective flux in the penetrative region,
 \begin{equation}
-\Fconv = \Ftot - F_{\rm{rad, ad}} = \Ftot - k \grad_{\rm{ad}}.
+\overline{\Fconv}(z \in [L_s, L_s + \delp]) = \Ftot - \overline{F_{\rm{rad, ad}}} = \Ftot - k \grad_{\rm{ad}}.
+\label{eqn:fconv_pz}
 \end{equation}
-By definition, in this region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, where $\grad_{\rm{rad}} = \Ftot/k$, so this requires that $\Fconv < 0$ in the convective penetration region.
-We next assume that the temperature and velocity are highly correlated in the penetrative region with very similar horizontal fluctuations,
+At this point it is useful to define the radiative gradient, $\grad_{\rm{rad}} = \Ftot/k$.
+Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
+Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
 \begin{equation}
@@
 \end{equation}
-We here assume that $\overline{h} = 0$ and $\overline{h^2} \neq 0$.
-We can then express the convective flux in terms of these vertically-varying profiles and an average over the horizontal structure of the flows,
+The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
+However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
+A vertically-varying formulation of the mean convective flux follows from this formulation,
 \begin{equation}
-\Fconv \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
+\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
 \label{eqn:Fconv_vertical}
 \end{equation}
-In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must be oppositely signed and the convective flows should eventually come to a stop through buoyancy breaking.
-This is achieved through a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
+In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
+In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
 \begin{equation}
-\frac{1}{2}\frac{d w^2}{dz} = |\alpha| g T'.
+\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
 \end{equation}
-Multiplying both sides by $h(x,y)$, taking a horizontal average, and then substituting $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation,
+Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
 \begin{equation}
-\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 = \Fconv dz.
+\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
 \label{eqn:theory_ode}
 \end{equation}
-This equation can be integrated over the depth of the convection zone from $W = 0$ to $W = W_0$ at the convective boundary, as well as over the penetration zone from $W = W_0$ to where $W = 0$.
+While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
+This equation can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
 We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
-Integrating Eqn.~\ref{eqn:theory_ode} over the CZ and PZ and taking a ratio of these two equations, we find
+Taking the ratio of these two integrals of Eqn.~\ref{eqn:theory_ode}, we find
 \begin{equation}
--\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} = 
-\frac{\int_{\rm{PZ}} \Fconv dz}{\int_{\rm{CZ}} \Fconv dz}.
+\mD \equiv \frac{(\overline{h^3}/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}},\qquad\qquad
+\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} = - \mD.
 \label{eqn:theory_fraction}
 \end{equation}
-In order to move further with this theory, it is necessary to specify the vertical shape of $\Fconv$, which is in turn set by $Q$, $\gradad$, and $k$.
-We will assume that $\gradad$ has a constant value and that the internal heating $Q$ is localized near the bottom of the CZ so that a constant convective flux $\Fcz$ is carried in the bulk convection zone.
-As a result, the vertical profile of $\Frad$ and $\Fconv$ is determined completely by the behavior of $k(z)$ near the convective boundary.
-We will study two cases in this work: a discontinuous jump in $k(z)$ at the convective boundary, and a piecewise-linear profile of $k(z)$ whose derivative may be discontinuous at the convective boundary.
+This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which is determined by the structure of the dynamics ($\mD$).
 
-\subsection{Case I: Discontinuous radiative conductivity}
+Eqn.~\ref{eqn:theory_fraction} is however not intuitively satisfying.
+In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
+We will study two cases in this work: a discontinuous jump in $\overline{\Fconv}$ at the convective boundary, and continuous piecewise-linear profile of $\overline{\Fconv}$ whose derivative may be discontinuous at the convective boundary.
+In both of these cases, we will define a nondimensional ``Penetration Parameter,''
+\begin{equation}
+\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)},
+\label{eqn:theory_P_defn}
+\end{equation}
+which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary (assuming the region above the boundary is an adiabatic penetrative zone).
+
+\subsection{Case I: Discontinuous flux}
 \label{sec:discontinuous_theory}
-We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
-The values of $k$ are chosen so that the convective flux follows
+We first consider a model which satisfies
 \begin{equation}
-\Fconv(z) = \begin{cases}
-\Fcz			&	z \leq \Lcz,\\
--\mP_D^{-1} \Fcz & 	z > \Lcz 
+\overline{\Fconv}(z) = \Fcz \begin{cases}
+1			&	z \leq \Lcz,\\
+-\mP_D^{-1}  & 	z > \Lcz 
 \end{cases}.
 \end{equation}
-Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
+Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D^{-1}$ is the penetration parameter (subscript D for discontinuous case).
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_p$ and the penetration zone from $z = L_p$ to $z = L_p + \delp$,
 \begin{equation}
-\frac{\dP}{\Lcz} = \mP_D
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
+\frac{\delp}{L_s} = \mP_D \mD.
 \label{eqn:discontinuous_prediction}
 \end{equation}
-We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
-This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.
+We see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the structure of the convective dynamics ($\mD$).
+Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.
 
-\subsection{Case II: Piecewise linear radiative conductivity}
+\subsection{Case II: Piecewise linear flux}
 \label{sec:linear_theory}
-We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
-As a result, the convective flux in the vicinity of the boundary takes the form
+We next assume that $\overline{\Fconv}(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be,
 \begin{equation}
-\Fconv(z) = 
+\overline{\Fconv}(z) = 
+\frac{\partial \Frad}{\partial z}\bigg|_{\rm{cz}}
 \begin{cases}
-(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
--\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
+(L_p - z) & z \leq L_p \\
+-\mP_L^{-1} (z - L_p) & z > L_p
 \end{cases},
 \end{equation}
-where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
+where $(\partial \Frad / \partial z)|_{\rm{cz}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
 Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
 \begin{equation}
-\frac{\dP}{\Lcz} = \sqrt{\mP_L
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
+\frac{\delp}{L_p} = \sqrt{\mP_L \mD},
 \label{eqn:linear_prediction}
@@
 which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
-In this work, we will test the predictions of Eqns.~\ref{eqn:linear_prediction} and \ref{eqn:discontinuous_prediction}.
-Our aim is to see if the predicted scalings with $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}$ in local simulations.
+In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
+Our aim is to see if the predicted scalings with the penetration parameter $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\mD$ in local simulations.
 
 \section{Simulation Details}
-We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the convection zone, the timescale of freefall across that convection zone, and the temperature scale of the internal heating over that freefall time,
+We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-defined convection zone ($L_s$), the timescale of freefall across that convection zone ($\tau_{\rm{ff}}$), and the temperature scale of the internal heating over that freefall time ($\Delta T$),
 \begin{equation}
 \begin{split}
-&T^* = (\Delta T)T = Q_0 \tau T,\qquad
-\partial_{t^*} = \tau^{-1}\partial_t = \left(\frac{\alpha g Q_0}{\Lcz}\right)^{1/3} \partial_t,\qquad
-\grad^* = \Lcz^{-1} \grad,\qquad
-\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 \Lcz^2\right)^{1/3}\vec{u},
+&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
+\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{\alpha g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
+\grad^* = L_s^{-1} \grad,\qquad
+\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 L_s^2\right)^{1/3}\vec{u},
 \\
-&k^* = (\Lcz^2 \tau^{-1})k,\qquad
+&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
+k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
 Q^* = Q_0 Q,\qquad
-\mR = \frac{u_{\rm{ff}} \Lcz}{\nu},\qquad
+\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
 \Pran = \frac{\nu}{\chi}.
@@
 \end{equation}
-Here, quantities with $*$ (e.g., $T^*$) refer to the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, and going forward quantities without these (e.g., $T$) will be dimensionless.
-The equations of motion are therefore
+For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
+Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
+The dimensionless equations of motion are therefore
 \label{sec:simulation_details}
@@
 where $N^2$ is the \brunt$\,$frequency in the radiative zone.
-In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $T_0$ which in turn sets the value of $k$ in the radiative zone.
+In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.
 
-The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, which determines the size of the convective penetration region.
-We define
-\begin{equation}
-\mP = -\frac{\Fconv|_{\rm{CZ}}}{\Fconv|_{PZ}},
-\end{equation}
-where $\Fconv|_{PZ}$ is the negative convective flux carried in a perfectly adiabatic convective penetration region.
+The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
 We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
@@
 Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
-The value of $\mR$ roughly corresponds to the value of the peak Reynolds number measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
-Astrophysical convection is in the limit of $\Pran \ll 1$; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
+The value of $\mR$ roughly corresponds to the value of the peak Reynolds number $\rm{Re} = \mR |\vec{u}|$ measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
+Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
 
-\subsection{Case I: Discontinuous radiative conductivity}
-Most of the simulations in this paper study simulations with a discontinuous radiative conductivity,
+\subsection{Case I: Discontinuous flux}
+Most of the simulations in this paper study simulations with a discontinuous convective flux at the Schwarzschild convective boundary.
+We achieve this by constructing a discontinuous radiative conductivity,
 \begin{equation}
@@
 
-\subsection{Case II: Piecewise linear radiative conductivity}
-We additionally study a select few simulations where the radiative conductivity's gradient is piecewise discontinuous,
+\subsection{Case II: Piecewise linear flux}
+We additionally study a select few simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
+We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
 \begin{equation}
@@
 
+One additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
+Dynamics in this regime may be different from those in the regime of Pr$\lesssim 1$ that we studied here, which could affect flow morphologies and thus penetration depths.
+Recently, \citet{kapyla2021} found that convective flows exhibited exhibited more overshoot at low Pr than high Pr.
+Future work should aim to understand how strongly the (TODO: symbol for h integrals) fraction depends on Pr.
+
 Finally, we note that our work here assumes a uniform composition through the convective and radiative region.

### 2021-05-22 manuscript/ms.tex
big revamp of theory section

@@
 \label{sec:theory}
+
+\subsection{Equations}
+\label{sec:theory_equations}
 Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
@@
 
-\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
-Assuming convection reaches a time-stationary state, we horizontally-average the vertically integrated Eqn.~\ref{eqn:temperature} to find
+\subsection{Vertical momentum equation balances}
+\label{sec:theory_momentum}
+Assuming a vertical and uniform gravitational acceleration $\vec{g} = -g\hat{z}$, the vertical component of Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq} is
+\begin{equation}
+\partial_t w + (\vec{u}\dot\grad)w = -\frac{1}{\rho_0}\partial_z p + |\alpha|g T + \nu\grad^2 \vec{u}.
+\label{eqn:momentum_z}
+\end{equation}
+We next horizontally average this equation; under the assumption that $\overline{w} = 0$ at some height (e.g., at an impenetrable boundary), Eqn.~\ref{eqn:incompressible} requires $\overline{w}$ = 0 everywhere.
+The horizontally-averaged equation is therefore
+\begin{equation}
+\frac{1}{\rho_0}\frac{d \overline{p}}{dz} = |\alpha| g \overline{T} - \overline{(\vec{u}\dot\grad)w} + \nu\overline{\grad_h^2 \vec{u}},
+\end{equation}
+where $\grad_h^2 = \partial_x^2 + \partial_y^2$.
+At this point we decompose $\overline{p} = \overline{p_s} + \overline{p_d}$, where $p_s$ is the ``structure'' component of of the pressure whose gradient balances the buoyant gradient (providing hydrostatic balance), and $p_d$ is the dynamical pressure whose mean balances the mean contributions of advection and dissipation.
+Accordingly, we define $\tilde{p} \equiv p - \overline{p_s}$, removing the mean structure component of the pressure.
+This construction leaves fluctuations ($p'$ and $\overline{p_d}$) which are set by the convective dynamics.
+Taking a time-average of Eqn.~\ref{eqn:momentum_z} and assuming that convection reaches a statistically stationary state and that viscous dissipation is unimportant \citep[which is a common assumption, but may not always apply in stellar contexts per][]{currie_browning_2017}, we retrieve
+\begin{equation}
+\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} = |\alpha| g T' - (\vec{u}\dot\grad)w.
+\label{eqn:fluc_momentum_z}
+\end{equation}
+In other words, convection reaches a state in which fluctuating buoyancy forces and nonlinear advection come into a balance and saturate at similar magnitudes.
+The pressure gradient rises to a similar magnitude to regulate the flows and ensure Eqn.~\ref{eqn:incompressible} is satisfied (and a similar argument could be made for e.g., anelastic convection).
+As a result, we can estimate that each of the terms in this equation have similar magnitudes,
+\begin{equation}
+\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} \sim |\alpha| g T' \sim (\vec{u}\dot\grad)w.
+\label{eqn:momentum_balance}
+\end{equation}
+
+\subsection{Kinetic energy \& the velocity-flux link}
+\label{sec:theory_energy}
+Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} (after removing $\overline{T}$ and $\overline{p_s}$, as in Eqn.~\ref{eqn:fluc_momentum_z}) reveals the kinetic energy equation,
+\begin{equation}
+\frac{\partial}{\partial t}\left(\frac{u^2}{2}\right) 
++ \grad\cdot\left[\vec{u}\left(\frac{u^2}{2} + \frac{\tilde{p}}{\rho_0}\right) - \nu\vec{u}\times\vec{\omega}\right]
+= \alpha g w T' - \nu\omega^2,
+\label{eqn:kinetic_energy}
+\end{equation}
+where $\vec{\omega} = \grad\times\vec{u}$ is the vorticity and $u^2 = \vec{u}\dot\vec{u}$ \& $\omega^2 = \vec{\omega}\dot\vec{\omega}$.
+Again neglecting viscosity, averaging horizontally and in time, and assuming a statistically stationary state, we retrieve
+\begin{equation}
+\frac{d}{dz}\left[\frac{\overline{w u^2}}{2} + \frac{\overline{w\tilde{p}}}{\rho_0}\right]
+= \alpha g \overline{\Fconv},
+\label{eqn:mean_ke}
+\end{equation}
+where $\overline{\Fconv} = \overline{w T'}$.
+At this point we now assume that the velocities are vertically dominated or isotropic so that $u^2 \sim w^2$.
+We furthermore assume that the balance in Eqn.~\ref{eqn:momentum_balance} is roughly correct, so that $\overline{w\tilde{p}} \sim \rho_0 \overline{w^3}$.
+Under these assumptions, we retrieve
+\begin{equation}
+\frac{d \overline{w^3}}{dz} \sim \alpha g \overline{\Fconv}
+\Rightarrow
+\frac{d \overline{w^3}}{dz} \approx \varsigma \alpha g \overline{\Fconv},
+\label{eqn:velocity_ode}
+\end{equation}
+where $\varsigma$ is a fudge factor which describes the quality of the assumptions we have made, and the fact that e.g., $w^2 < u^2$, the balance of Eqn.~\ref{eqn:momentum_balance} likely only holds to a factor of a few, etc..
+This equation is logically analagous to one used between Eqn.~3.8 \& 3.9 of \citet{zahn1991}, but we have not relied upon the assumption of a vertically invariant convective planform which likely does not hold for turbulent dynamics.
+Eqn.~\ref{eqn:velocity_ode} is also intuitively satisfying; it says that roughly $\overline{w^3} \sim \overline{\Fconv}$, which fits intuition from mixing length theory.
+
+\subsection{A flux-based penetration argument}
+According to an equation similar to Eqn.~\ref{eqn:velocity_ode}, \citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
+Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
@@
 \end{equation}
-where $\overline{\Fconv} = \overline{w T}$, is $\Fbot$ the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
+where $\Fbot$ is the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
 We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
@@
 Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
-Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
+
+%Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
+%\begin{equation}
+%w(x,y,z) = W(z)h(x,y),
+%\qquad
+%T'(x,y,z) = \delta T(z)h(x,y).
+%\end{equation}
+%The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
+%However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
+%A vertically-varying formulation of the mean convective flux follows from this formulation,
+%\begin{equation}
+%\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
+%\label{eqn:Fconv_vertical}
+%\end{equation}
+%In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
+%In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
+%\begin{equation}
+%\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
+%\end{equation}
+%Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
+%\begin{equation}
+%\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
+%\label{eqn:theory_ode}
+%\end{equation}
+%While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
+With the convective fluxes defined, Eqn.~\ref{eqn:velocity_ode} can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
+We assume however that the convective dynamics are not identical in the convection zone (CZ) and penetration zone (PZ), so that the fudge factor $\varsigma$ differs between the two zones.
+Taking the ratio of these two integrals, we find
 \begin{equation}
-w(x,y,z) = W(z)h(x,y),
-\qquad
-T'(x,y,z) = \delta T(z)h(x,y).
-\end{equation}
-The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
-However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
-A vertically-varying formulation of the mean convective flux follows from this formulation,
-\begin{equation}
-\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
-\label{eqn:Fconv_vertical}
-\end{equation}
-In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
-In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
-\begin{equation}
-\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
-\end{equation}
-Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
-\begin{equation}
-\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
-\label{eqn:theory_ode}
-\end{equation}
-While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
-This equation can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
-We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
-Taking the ratio of these two integrals of Eqn.~\ref{eqn:theory_ode}, we find
-\begin{equation}
-\mD \equiv \frac{(\overline{h^3}/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}},\qquad\qquad
-\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} = - \mD.
+\mD \equiv \frac{\varsigma_{\rm{CZ}}}{\varsigma_{\rm{PZ}}},\qquad\qquad
+\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} \approx - \mD.
 \label{eqn:theory_fraction}
 \end{equation}
-This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which is determined by the structure of the dynamics ($\mD$).
+This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which reflects the difference in the dynamics between the CZ and the PZ ($\mD$).
+More importantly, this integral ratio sets the size of the PZ.
 
-Eqn.~\ref{eqn:theory_fraction} is however not intuitively satisfying.
+Eqn.~\ref{eqn:theory_fraction} is unfortunately not intuitively satisfying.
 In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
-We will study two cases in this work: a discontinuous jump in $\overline{\Fconv}$ at the convective boundary, and continuous piecewise-linear profile of $\overline{\Fconv}$ whose derivative may be discontinuous at the convective boundary.
+We will study two cases in this work, laid out below.
 In both of these cases, we will define a nondimensional ``Penetration Parameter,''
@@
 \end{equation}
-which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary (assuming the region above the boundary is an adiabatic penetrative zone).
+which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone).
 
-\subsection{Case I: Discontinuous flux}
+\subsubsection{Case I: Discontinuous flux}
 \label{sec:discontinuous_theory}
@@
 \end{equation}
-Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D^{-1}$ is the penetration parameter (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_p$ and the penetration zone from $z = L_p$ to $z = L_p + \delp$,
+Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_s$ and the penetration zone from $z = L_s$ to $z = L_s + \delp$,
 \begin{equation}
@@
 
-\subsection{Case II: Piecewise linear flux}
+\subsubsection{Case II: Piecewise linear flux}
 \label{sec:linear_theory}
@@
 \end{equation}
-which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
+which aligns with the prediction of \citet{zahn1991}'s Eqn.~3.13 when we take $\mP_L = 1$.
+
 In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
-Our aim is to see if the predicted scalings with the penetration parameter $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\mD$ in local simulations.
+Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure preliminary values for $\mD$ in local simulations.
 

### 2021-05-27 dedalus_code/plotting/find_top_cz.py
adds f measure to find_top_cz outputs

@@ -218,13 +218,13 @@ if not plotter.idle:
             L_d09 = departures[2]
 
             enstrophy_full_domain = enstrophy_integ_field.interpolate(z=Lz)['g'].min() / Lz
-            enstrophy_full_cz     = enstrophy_integ_field.interpolate(z=L_d05)['g'].min() / L_d05
+            enstrophy_full_cz     = enstrophy_integ_field.interpolate(z=L_d09)['g'].min() / L_d09
             enstrophy_below_Ls    = enstrophy_integ_field.interpolate(z=Ls)['g'].min() / Ls
             vel_full_domain = vel_integ_field.interpolate(z=Lz)['g'].min() / Lz
-            vel_full_cz     = vel_integ_field.interpolate(z=L_d05)['g'].min() / L_d05
+            vel_full_cz     = vel_integ_field.interpolate(z=L_d09)['g'].min() / L_d09
             vel_below_Ls    = vel_integ_field.interpolate(z=Ls)['g'].min() / Ls
             fconv_full_domain = fconv_integ_field.interpolate(z=Lz)['g'].min() / Lz
-            fconv_full_cz     = fconv_integ_field.interpolate(z=L_d05)['g'].min() / L_d05
+            fconv_full_cz     = fconv_integ_field.interpolate(z=L_d09)['g'].min() / L_d09
             fconv_below_Ls    = fconv_integ_field.interpolate(z=Ls)['g'].min() / Ls
 
             grad_above05 = grad_integ_field.interpolate(z=L_d05)['g'].min() - grad_integ_field.interpolate(z=Lz)['g'].min()
@@ -331,8 +331,8 @@ if plotter.reader.comm.rank == 0:
     fig.savefig('{:s}/{:s}.png'.format(plotter.out_dir, 'cz_velocities'), dpi=400, bbox_inches='tight')
 
     fig = plt.figure()
-    plt.plot(times, enstrophy_full/Re_in, c='k', label=r'$\langle \omega^2 \rangle / \mathcal{R}$')
-    plt.plot(times, fconv_full,   c='orange', label=r'$\langle F_{\rm{conv}} \rangle$')
+    plt.plot(times, enstrophy_Ls/Re_in, c='k', label=r'$\langle \omega^2 \rangle / \mathcal{R}$ (Ls)')
[…]

### 2021-05-27 manuscript/ms.tex
another (and hopefully final) major overhaul of the theory

--- 2021-05-21 manuscript/ms.tex
@@
 \renewcommand{\dot}{\vec{\cdot}}
+\renewcommand{\bar}[1]{\overline{#1}}
 \newcommand{\grad}{\vec{\nabla}}
@@
 
+%\subsection{Vertical momentum equation balances}
+%\label{sec:theory_momentum}
+%Assuming a vertical and uniform gravitational acceleration $\vec{g} = -g\hat{z}$, the vertical component of Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq} is
+%\begin{equation}
+%\partial_t w + (\vec{u}\dot\grad)w = -\frac{1}{\rho_0}\partial_z p + |\alpha|g T + \nu\grad^2 w.
+%\label{eqn:momentum_z}
+%\end{equation}
+%We next horizontally average this equation; under the assumption that $\overline{w} = 0$ at some height (e.g., at an impenetrable boundary), Eqn.~\ref{eqn:incompressible} requires $\overline{w}$ = 0 everywhere.
+%The horizontally-averaged equation is therefore
+%\begin{equation}
+%\frac{1}{\rho_0}\frac{d \overline{p}}{dz} = |\alpha| g \overline{T} - \overline{(\vec{u}\dot\grad)w} + \nu\overline{\grad_h^2 w},
+%\end{equation}
+%where $\grad_h^2 = \partial_x^2 + \partial_y^2$.
+%At this point we decompose $\overline{p} = \overline{p_s} + \overline{p_d}$, where $p_s$ is the ``structure'' component of of the pressure whose gradient balances the buoyant gradient (providing hydrostatic balance), and $p_d$ is the dynamical pressure whose mean balances the mean contributions of advection and dissipation.
+%Accordingly, we define $\tilde{p} \equiv p - \overline{p_s}$, removing the mean structure component of the pressure.
+%This construction leaves fluctuations ($p'$ and $\overline{p_d}$) which are set by the convective dynamics.
+%Taking a time-average of Eqn.~\ref{eqn:momentum_z} and assuming that convection reaches a statistically stationary state and that viscous dissipation is unimportant \citep[which is a common assumption, but may not always apply in stellar contexts per][]{currie_browning_2017}, we retrieve
+%\begin{equation}
+%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} = |\alpha| g T' - (\vec{u}\dot\grad)w.
+%\label{eqn:fluc_momentum_z}
+%\end{equation}
+%In other words, convection reaches a state in which fluctuating buoyancy forces and nonlinear advection come into a balance and saturate at similar magnitudes.
+%The pressure gradient rises to a similar magnitude to regulate the flows and ensure Eqn.~\ref{eqn:incompressible} is satisfied (and a similar argument could be made for e.g., anelastic convection).
+%As a result, we can estimate that each of the terms in this equation have similar magnitudes,
+%\begin{equation}
+%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} \sim |\alpha| g T' \sim (\vec{u}\dot\grad)w.
+%\label{eqn:momentum_balance}
+%\end{equation}
+
+\subsection{Kinetic energy \& the vorticity-flux link}
+\label{sec:theory_energy}
+Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
+\begin{equation}
+\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
++ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
+= \alpha g w T - \nu|\vec{\omega}|^2,
+\label{eqn:kinetic_energy}
+\end{equation}
+where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
+Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution,
+\begin{equation}
+\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
+\label{eqn:ke_averages}
+\end{equation}
+where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
+It is counterintuitive to find that a viscous term is on the same order of magnitude as the convective flux.
+However, this term dimensionally behaves like $\nu u^2 / \ell^2$, where $\ell$ is the length scale of velocity gradients; if the average vorticity is dominated by gradients at the dissipation scale, then it makes sense that this term can persist even at small values of $\nu$.
+Furthermore, \citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of the viscous heating term remains large for turbulent flows.
+Since $\nu |\vec{\omega}^2|$ is the Boussinesq analog to the viscous heating, the importance of this term is perhaps not too surprising.
+
+We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
+Following Eqn.~\ref{eqn:ke_averages}, we can write
+\begin{equation}
+\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz = \frac{\nu}{\alpha g}(L_s + \delp) \angles{|\vec{\omega}|^2}.
+\label{eqn:flux_breakup}
+\end{equation}
+Rearranging, we can write
+\begin{equation}
+\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
+\qquad\rm{with}\qquad
+f \equiv \frac{\nu}{\alpha g}(L_s + \delp) \frac{\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
+= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
+\label{eqn:preliminary_flux_ratio}
+\end{equation}
+where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
+The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics.
+In order to say more, we must turn to a more in-depth examination of the fluxes in the PZ.
+
+%
+%Again neglecting viscosity, averaging horizontally and in time, and assuming a statistically stationary state, we retrieve
+%\begin{equation}
+%\frac{d}{dz}\left[\frac{\overline{w u^2}}{2} + \frac{\overline{w\tilde{p}}}{\rho_0}\right]
+%= \alpha g \overline{\Fconv},
+%\label{eqn:mean_ke}
+%\end{equation}
+%At this point we now assume that the velocities are vertically dominated or isotropic so that $u^2 \sim w^2$.
+%We furthermore assume that the balance in Eqn.~\ref{eqn:momentum_balance} is roughly correct, so that $\overline{w\tilde{p}} \sim \rho_0 \overline{w^3}$.
+%Under these assumptions, we retrieve
+%\begin{equation}
+%\frac{d \overline{w^3}}{dz} \sim \alpha g \overline{\Fconv}
+%\Rightarrow
+%\frac{d \overline{w^3}}{dz} \approx \varsigma \alpha g \overline{\Fconv},
+%\label{eqn:velocity_ode}
+%\end{equation}
+%where $\varsigma$ is a fudge factor which describes the quality of the assumptions we have made, and the fact that e.g., $w^2 < u^2$, the balance of Eqn.~\ref{eqn:momentum_balance} likely only holds to a factor of a few, etc..
+%This equation is logically analagous to one used between Eqn.~3.8 \& 3.9 of \citet{zahn1991}, but we have not relied upon the assumption of a vertically invariant convective planform which likely does not hold for turbulent dynamics.
+%Eqn.~\ref{eqn:velocity_ode} is also intuitively satisfying; it says that roughly $\overline{w^3} \sim \overline{\Fconv}$, which fits intuition from mixing length theory.
+%
+\subsection{A flux-based penetration argument}
 \citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
-Assuming convection reaches a time-stationary state, we horizontally-average the vertically integrated Eqn.~\ref{eqn:temperature} to find
+Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
@@
 Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
-Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
+
+With the knowledge that $\Fconv$ is negative in the PZ, we rewrite Eqn.~\ref{eqn:preliminary_flux_ratio}
 \begin{equation}
-w(x,y,z) = W(z)h(x,y),
-\qquad
-T'(x,y,z) = \delta T(z)h(x,y).
-\end{equation}
-The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
-However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
-A vertically-varying formulation of the mean convective flux follows from this formulation,
-\begin{equation}
-\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
-\label{eqn:Fconv_vertical}
-\end{equation}
-In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
-In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
-\begin{equation}
-\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
-\end{equation}
-Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
-\begin{equation}
-\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
-\label{eqn:theory_ode}
-\end{equation}
-While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
-This equation can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
-We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
-Taking the ratio of these two integrals of Eqn.~\ref{eqn:theory_ode}, we find
-\begin{equation}
-\mD \equiv \frac{(\overline{h^3}/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}},\qquad\qquad
-\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} = - \mD.
+\frac{|\int_{\rm{PZ}}\bar{\Fconv}\,dz|}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = (1 - f),
 \label{eqn:theory_fraction}
 \end{equation}
-This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which is determined by the structure of the dynamics ($\mD$).
+and note that $f < 1$ by its flux-based definition.
+While we have arrived here in a very different manner, this equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which relates to the convective dynamics.
+More importantly, if $\bar{\Fconv}$, and $f$ are known, this ratio directly sets the size of the PZ.
 
-Eqn.~\ref{eqn:theory_fraction} is however not intuitively satisfying.
 In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
-We will study two cases in this work: a discontinuous jump in $\overline{\Fconv}$ at the convective boundary, and continuous piecewise-linear profile of $\overline{\Fconv}$ whose derivative may be discontinuous at the convective boundary.
+We will study two cases in this work, laid out below.
 In both of these cases, we will define a nondimensional ``Penetration Parameter,''
@@
 \end{equation}
-Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D^{-1}$ is the penetration parameter (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_p$ and the penetration zone from $z = L_p$ to $z = L_p + \delp$,
+Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_s$ and the penetration zone from $z = L_s$ to $z = L_s + \delp$, we predict
 \begin{equation}
-\frac{\delp}{L_s} = \mP_D \mD.
+\frac{\delp}{L_s} = \mP_D (1 - f).
 \label{eqn:discontinuous_prediction}
 \end{equation}
-We see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the structure of the convective dynamics ($\mD$).
+Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is linearly proportional to $\mP_D$.
 Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.
+Furthermore, if $\mP_D$ doubles, the PZ magnitude of $\Fconv$ halves, and if $f$ does not change then the PZ must also double in size according to Eqn.~\ref{eqn:ke_averages}.
 
-\subsection{Case II: Piecewise linear flux}
+\subsubsection{Case II: Piecewise linear flux}
 \label{sec:linear_theory}
@@
 \begin{equation}
-\frac{\delp}{L_p} = \sqrt{\mP_L \mD},
+\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)}.
 \label{eqn:linear_prediction}
 \end{equation}
-which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
+
 In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
-Our aim is to see if the predicted scalings with the penetration parameter $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\mD$ in local simulations.
+Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure preliminary values for $\mD$ in local simulations.
 
@@
 As demonstrated in Fig.~\ref{fig:time_evolution}, the time evolution of simulations which start from a state based on the Schwarzschild criterion can be prohibitively long.
-In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure is possible.
+In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure can be done accurately.
 In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
 \begin{enumerate}
-\item Once a simulation has a volume-averaged Reynolds number greater than 1, we wait 50 freefall times.
-\item We measure the 50\% departure point ($\delta_p$) of the top of the convection zone every freefall time, and store this information for 50 freefall times.
-\item We measure $d\delta_p/dt$ using NumPy's \texttt{gradient} function. 
-If the average value of $d\delta_p/dt$ has a different sign over the first and last 25 freefall times in our collection window, we erase the first 25 freefall times of data and return to step 2 for 25 freefall times.
-If the average value of $d\delta_p/dt$ has the same sign over the first and last 25 freefall times, we accelerate the evolution of our simulations.
-\item We calculate $\Delta\delta_p$ as the minimum of 
+\item Once a simulation has a volume-averaged Reynolds number greater than 1, we wait 10 freefall times to allow dynamical transients to pass.
+\item We measure the departure points ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) every freefall time, and store this information for 30 freefall times.
+\item We linearly fit each of the departure points' evolution against time using NumPy's \texttt{polyfit} function.
+We assume that convective motions influence $\delta_{0.1}$ and $\delta_{0.5}$ more strongly than $\delta_{0.9}$.
+We measure the time-evolution of the convective front $\frac{d \delp}{dt}$ by averaging the slope of the linear fits for $\delta_{0.1}$ and $\delta{0.2}$.
+\item We take a large ``time step'' of size $\tau_{\rm{AE}}$ forward.
+We calculate $\Delta \delta_p = \tau_{\rm{AE}} \frac{d \delp}{dt}$.
+\begin{itemize}
+\item If $\Delta \delta_p < 0.005$, we erase the first 15 time units worth of departure point measures and return to step 2 for 15 time units.
+\item  If $\Delta \delta_p$ is large, we adjust the top of the PZ by setting $\delta_{0.5,\rm{new}} = \angles{\delta_{0.5}}_t + \Delta \delta_p$.
+If $\Delta \delta_p > 0.05$, we limit its value to 0.05.
+We calculate the width of the thermal adjustment layer $\delta_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
+We adjust the $m = 0$ temperature gradient to
 \begin{equation}
-\Delta\delta_{p,1} = \overline{\frac{d\delta_p}{dt}}\bigg|\frac{\Delta \delta_p}{\Delta d \delta_p / dt} \bigg|,\qquad
-\Delta\delta_{p,2} = 500\overline{\frac{d\delta_p}{dt}}.
-\end{equation}
-Here, $\Delta\delta_{p,1}$ essentially represents a newton iteration in $d\delta_p / dt$ vs. $\delta_p$ space towards the root value where $d\delta_p / dt = 0$.
-In some cases, $\Delta\delta_{p,1}$ becomes too large; we thus limit the maximum change to $\Delta\delta_{p,2}$, which represents an advancement of the convective boundary at the current evolutionary pace by 500 freefall time units.
-\item After determining a new value of $\delta_{\rm{p,ev}} = \delta_{p,0} + \Delta\delta_p$, we adjust the $m = 0$ temperature gradient to
-\begin{equation}
-\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{p,ev}}, 0.05) \Delta\grad,
+\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{0.5,\rm{new}}}, \delta_w) \Delta\grad,
 \label{eqn:initial_grad}
@@
 This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
+\end{itemize}
 \item We restart from step 1.
 \end{enumerate}
-If a simulation returns to step 2 from step 3 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
+If a simulation returns to step 2 from step 4 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
 This process effectively removes the long diffusive thermal evolution on display in the middle panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.

### 2021-05-29 manuscript/ms.tex
close to a draft for co-authors

@@
 \newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
+\newcommand{\justgrad}{\ensuremath{\nabla}}
 \newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
@@
 
-\shorttitle{SHORT TITLE}
+\shorttitle{Convective Penetration}
 \shortauthors{Anders et al}
@@
 %%%% Title and Abstract
-\title{This is a title}
+\title{Convective penetration is set by the flux and dissipation, not the stiffness}
 \author[0000-0002-3433-4733]{Evan H. Anders}
@@
 \begin{abstract}
-Blah Blah short description
+Convection is a crucial heat transport mechanism and excitation mechanism in planets and stars.
+While parameterizations like mixing length theory adequately describe convection in bulk convection zones, the behavior of convective motions near and beyond the Schwarzschild-stable convective boundary are not well understood.
+In this paper, we examine a simplified Boussinesq model of stellar convection with a radiative flux.
+We derive a ``penetration parameter'' $\mathcal{P}$ which compares how quickly the radiative gradient deviates from the adiabatic on either side of the convective boundary.
+In line with \citet{zahn1991}, we predict that the extend of the adiabatically stratified penetrative layer is strongly related to the magnitude of $\mathcal{P}$.
+We perform 3D numerical simulations using Dedlaus to test this theory, and find that the penetrative region strongly depends on the flux-based $\mathcal{P}$ and only weakly depends on the degree of turbulence in the flows or on the stiffness of the convective interface.
+In stellar contexts, we expect $\mathcal{P} \approx 1$ and our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20\% of a mixing length.
+We briefly examine a MESA solar model in which the bottom boundary of the convection zone is set according to our theory, and discuss the possible implications and future paths necessary for these findings.
 \end{abstract}
@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism in essentially all stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
-Convective dynamics drive many still poorly-understood phenomena in stars.
+Convection is a crucial heat transport mechanism in stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
 For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
-Convection is also responsible for compositional mixing, which can modify surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
-Furthermore, convective motions excite both acoustic and gravity waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
+Convection also mixes stars compositionally, which can modify observed surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
+Furthermore, convective motions excite waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
 A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.
 
-One aspect of stellar convection which remains poorly understood despite decades of study is the class of mechanisms generally referred to as ``convective overshoot.''
-Broadly, in the stellar structure literature, convective overshoot refers to any mechanism which causes at least compositional mixing beyond the Schwarzschild or Ledoux stable convective boundary.
-Improved models of overshoot could resolve many discrepancies between observations and structure models.
-For example, observed surface lithium abundances in the Sun and solar-type stars align poorly with models, which could suggest a need for additional mixing below the solar convection zone \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
-Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; model and observation discrepancies can be reduced by appropriately incorporating mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
+Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
+In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
+This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
+Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
 There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
 Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
-In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
+In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}, such as the classic Mixing Length Theory \citep{bohm-vitense1958}.
 While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
@@
 
-The host of mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
-The first of these classes is, confusingly, also called ``convective overshoot'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly \emph{do not adjust the thermodynamic profile}.
-The second of these classes is called ``convective penetration,'' in which convective motions mix the thermodynamic profiles beyond the convective boundary, thereby extending the convective boundary beyond the nominal Schwarzschild or Ledoux one.
-We will follow a deep history \citep{zahn1991, korre_etal_2019} and use this terminology throughout this work.
-The primary focus of this work will be on convective penetration, as this mechanism shows promise in aligning observations and models \citep{christensen-dalsgaard_etal_2011, pedersen_etal_2021}.
+The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
+The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
+The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the extent of the extent of the adiabatically-mixed convective region.
+We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
 
-Convective overshoot and penetration have been studied in laboratory experiments and numerical simulations for decades, and has been reviewed by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-Experiments and simulations exhibiting extensive convective penetration in simplified, Boussinesq setups have been studied for decades \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}, with multiple recent studies suggesting that the penetration depth (or overshoot depth) is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018, korre_etal_2019}.
-Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that penetration and overshoot depths were determined by the stiffness of the radiative-convective interface \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
-However, a number of studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
-Many modern simulations utilize stellar structure models as inspiration for their experimental setup, and find significant convective overshoot or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
-Some simulations have found that the extension beyond the convection zone depends strongly on the input flux for their experimental setups \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
-In this work, we follow the results of these last class of simulations and study how one aspect of the convective flux modifies the extent of the penetration region.
+Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+One parameter which is commonly linked to penetration or overshoot is the ``stiffness'' of the radiative-convective interface; the stiffness is a ratio which states how stable a radiative zone is compared to an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
+Experiments and simulations exhibiting extensive convective penetration in water or other simplified, Boussinesq setups have a long history \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}.
+Some of these recent simplified studies suggest that the penetration depth is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
+Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
+However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+This host of experiments indeed suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
 
+A few flux-based theories of convective penetration have been historically considered.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
-Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that the boosting of luminosity in stellar experiments compared to reference stars may be leading to wrong estimates of the penetrative dynamics.
-Indeed, some simulations have shown partial agreement with these ideas.
-In the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994, rogers_etal_2006} agree with Zahn's theory (although at high stiffness they disagree).
-Some simulations have used the magnitude of the system flux as a control parameter, and indeed found that the penetration depth was dependent on it \citep{singh_etal_1998, hotta2017, kapyla2019}.
-These results suggest that Zahn's theory deserves to be revisted.
+Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
+Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
+In light of these results, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
 
-In this work, we design two numerical experiments to test the theory of \citet{zahn1991}.
-We use a modified incompressible, Boussinesq model to study the simplest possible system, and re-derive his theory in our simplified limit.
-The results of our simulations are in full agreement with Zahn's theory.
+In this work, we design two numerical experiments to test \citet{zahn1991}'s idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+We use a modified incompressible, Boussinesq model to study the simplest possible system, and use \citet{roxburgh1989}'s constraint to derive a theory analogous to \citet{zahn1991}'s in this simplified limit.
 \begin{quote}
 \emph{
-Specifically, we find that the depth of convective penetration depends on the gradient of the radiative flux near the convective boundary.
+We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
 }
 \end{quote}
-Thus, the penetration depth can be approximated so long as the radiative conductivity, or likewise the opacity, is known at the convective boundary.
+Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) around the convective boundary.
 
 We present these findings as follows.
-In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, re-derive the theory of \citet{zahn1991}, and retrieve predictions for our two experimental designs from that theory.
+In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration similar to \citet{zahn1991}'s, and retrieve predictions for our two experimental designs from that theory.
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
@@
 \end{align}
-Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
+Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
 We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
-These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
-The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
-Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
-We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.
+We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
+The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
+The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
+Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
 
-%\subsection{Vertical momentum equation balances}
-%\label{sec:theory_momentum}
-%Assuming a vertical and uniform gravitational acceleration $\vec{g} = -g\hat{z}$, the vertical component of Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq} is
-%\begin{equation}
-%\partial_t w + (\vec{u}\dot\grad)w = -\frac{1}{\rho_0}\partial_z p + |\alpha|g T + \nu\grad^2 w.
-%\label{eqn:momentum_z}
-%\end{equation}
-%We next horizontally average this equation; under the assumption that $\overline{w} = 0$ at some height (e.g., at an impenetrable boundary), Eqn.~\ref{eqn:incompressible} requires $\overline{w}$ = 0 everywhere.
-%The horizontally-averaged equation is therefore
-%\begin{equation}
-%\frac{1}{\rho_0}\frac{d \overline{p}}{dz} = |\alpha| g \overline{T} - \overline{(\vec{u}\dot\grad)w} + \nu\overline{\grad_h^2 w},
-%\end{equation}
-%where $\grad_h^2 = \partial_x^2 + \partial_y^2$.
-%At this point we decompose $\overline{p} = \overline{p_s} + \overline{p_d}$, where $p_s$ is the ``structure'' component of of the pressure whose gradient balances the buoyant gradient (providing hydrostatic balance), and $p_d$ is the dynamical pressure whose mean balances the mean contributions of advection and dissipation.
-%Accordingly, we define $\tilde{p} \equiv p - \overline{p_s}$, removing the mean structure component of the pressure.
-%This construction leaves fluctuations ($p'$ and $\overline{p_d}$) which are set by the convective dynamics.
-%Taking a time-average of Eqn.~\ref{eqn:momentum_z} and assuming that convection reaches a statistically stationary state and that viscous dissipation is unimportant \citep[which is a common assumption, but may not always apply in stellar contexts per][]{currie_browning_2017}, we retrieve
-%\begin{equation}
-%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} = |\alpha| g T' - (\vec{u}\dot\grad)w.
-%\label{eqn:fluc_momentum_z}
-%\end{equation}
-%In other words, convection reaches a state in which fluctuating buoyancy forces and nonlinear advection come into a balance and saturate at similar magnitudes.
-%The pressure gradient rises to a similar magnitude to regulate the flows and ensure Eqn.~\ref{eqn:incompressible} is satisfied (and a similar argument could be made for e.g., anelastic convection).
-%As a result, we can estimate that each of the terms in this equation have similar magnitudes,
-%\begin{equation}
-%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} \sim |\alpha| g T' \sim (\vec{u}\dot\grad)w.
-%\label{eqn:momentum_balance}
-%\end{equation}
-
-\subsection{Kinetic energy \& the vorticity-flux link}
+\subsection{Kinetic energy \& the dissipation-flux link}
 \label{sec:theory_energy}
@@
 where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
-Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution,
+Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution: \citet{roxburgh1989}'s integral constraint,
 \begin{equation}
@@
 where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
-It is counterintuitive to find that a viscous term is on the same order of magnitude as the convective flux.
-However, this term dimensionally behaves like $\nu u^2 / \ell^2$, where $\ell$ is the length scale of velocity gradients; if the average vorticity is dominated by gradients at the dissipation scale, then it makes sense that this term can persist even at small values of $\nu$.
-Furthermore, \citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of the viscous heating term remains large for turbulent flows.
-Since $\nu |\vec{\omega}^2|$ is the Boussinesq analog to the viscous heating, the importance of this term is perhaps not too surprising.
+It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
+However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
+Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
+\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.
 
 We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
-Following Eqn.~\ref{eqn:ke_averages}, we can write
+Following Eqn.~\ref{eqn:ke_averages}, we write
 \begin{equation}
-\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz = \frac{\nu}{\alpha g}(L_s + \delp) \angles{|\vec{\omega}|^2}.
+\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{\alpha g} \angles{|\vec{\omega}|^2}.
 \label{eqn:flux_breakup}
 \end{equation}
-Rearranging, we can write
+Rearranging, we retrieve 
 \begin{equation}
@@
 \qquad\rm{with}\qquad
-f \equiv \frac{\nu}{\alpha g}(L_s + \delp) \frac{\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
+f \equiv \frac{(L_s + \delp)}{\alpha g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
 = \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
@@
 where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
-The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics.
-In order to say more, we must turn to a more in-depth examination of the fluxes in the PZ.
+The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics (the viscous dissipation), quantified by $f$.
+We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
+If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
+In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.
 
-%
-%Again neglecting viscosity, averaging horizontally and in time, and assuming a statistically stationary state, we retrieve
-%\begin{equation}
-%\frac{d}{dz}\left[\frac{\overline{w u^2}}{2} + \frac{\overline{w\tilde{p}}}{\rho_0}\right]
-%= \alpha g \overline{\Fconv},
-%\label{eqn:mean_ke}
-%\end{equation}
-%At this point we now assume that the velocities are vertically dominated or isotropic so that $u^2 \sim w^2$.
-%We furthermore assume that the balance in Eqn.~\ref{eqn:momentum_balance} is roughly correct, so that $\overline{w\tilde{p}} \sim \rho_0 \overline{w^3}$.
-%Under these assumptions, we retrieve
-%\begin{equation}
-%\frac{d \overline{w^3}}{dz} \sim \alpha g \overline{\Fconv}
-%\Rightarrow
-%\frac{d \overline{w^3}}{dz} \approx \varsigma \alpha g \overline{\Fconv},
-%\label{eqn:velocity_ode}
-%\end{equation}
-%where $\varsigma$ is a fudge factor which describes the quality of the assumptions we have made, and the fact that e.g., $w^2 < u^2$, the balance of Eqn.~\ref{eqn:momentum_balance} likely only holds to a factor of a few, etc..
-%This equation is logically analagous to one used between Eqn.~3.8 \& 3.9 of \citet{zahn1991}, but we have not relied upon the assumption of a vertically invariant convective planform which likely does not hold for turbulent dynamics.
-%Eqn.~\ref{eqn:velocity_ode} is also intuitively satisfying; it says that roughly $\overline{w^3} \sim \overline{\Fconv}$, which fits intuition from mixing length theory.
-%
 \subsection{A flux-based penetration argument}
-\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
+\citet{zahn1991} and Eqn.~\ref{eqn:preliminary_flux_ratio} suggest that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
 Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
@@
 \end{equation}
-where $\Fbot$ is the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
-We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
-This assumption specifies the convective flux in the penetrative region,
+where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
+We next assume that convection penetrates some distance $\delp$ above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the PZ.
+This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
+Defining the radiative gradient $\grad_{\rm{rad}} = \Ftot/k$, we can write the PZ convective flux
 \begin{equation}
-\overline{\Fconv}(z \in [L_s, L_s + \delp]) = \Ftot - \overline{F_{\rm{rad, ad}}} = \Ftot - k \grad_{\rm{ad}}.
+\overline{\Fconv}|_{\rm{PZ}} = \Ftot - \overline{\Frad} = k(\gradrad - \gradad).
 \label{eqn:fconv_pz}
 \end{equation}
-At this point it is useful to define the radiative gradient, $\grad_{\rm{rad}} = \Ftot/k$.
-Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
+Within the penetrative region, $\gradad > \gradrad$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv}|_{\rm{PZ}} < 0$.
 
-With the knowledge that $\Fconv$ is negative in the PZ, we rewrite Eqn.~\ref{eqn:preliminary_flux_ratio}
+With the knowledge that $\bar{\Fconv}$ is negative in the PZ, we rewrite Eqn.~\ref{eqn:preliminary_flux_ratio}
 \begin{equation}
@@
 \end{equation}
-and note that $f < 1$ by its flux-based definition.
-While we have arrived here in a very different manner, this equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which relates to the convective dynamics.
+and note that $f \leq 1$ by its tautological flux-based definition assuming $\delp \geq 0$.
+While we have arrived at Eqn.~\ref{eqn:theory_fraction} in a very different manner, this equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which relates to the convective dynamics.
 More importantly, if $\bar{\Fconv}$, and $f$ are known, this ratio directly sets the size of the PZ.
@@
 \begin{equation}
-\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)},
+\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
 \label{eqn:theory_P_defn}
 \end{equation}
-which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone).
+Following Eqn.~\ref{eqn:fconv_pz}, the sign of $\mP$ is positive and its magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone).
 
@@
 \end{equation}
-Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
+Here, $\Fcz$ is a constant value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
 Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_s$ and the penetration zone from $z = L_s$ to $z = L_s + \delp$, we predict
@@
 Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.
-Furthermore, if $\mP_D$ doubles, the PZ magnitude of $\Fconv$ halves, and if $f$ does not change then the PZ must also double in size according to Eqn.~\ref{eqn:ke_averages}.
 
@@
 \overline{\Fconv}(z) = 
-\frac{\partial \Frad}{\partial z}\bigg|_{\rm{cz}}
+\frac{\partial \Frad}{\partial z}\bigg|_{\rm{CZ}}
 \begin{cases}
@@
 \end{equation}
-where $(\partial \Frad / \partial z)|_{\rm{cz}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
+where $(\partial \Frad / \partial z)|_{\rm{CZ}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
 Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
@@
 \end{equation}
+This is strikingly similar to \citet{zahn1991}'s result, whose work corresponds to the case of $\mP_L = 1$.
 
 In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
-Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure preliminary values for $\mD$ in local simulations.
+Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ on various parameters in local simulations.
+We note that \citet{roxburgh1989}'s constraint puts an upper limit on the penetration depth in the limit that viscous dissipation is negligible ($f = 0$), but in practice we expect $f$ closer to 1.
 
 \section{Simulation Details}
-We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-defined convection zone ($L_s$), the timescale of freefall across that convection zone ($\tau_{\rm{ff}}$), and the temperature scale of the internal heating over that freefall time ($\Delta T$),
+We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
 \begin{equation}
@@
 \end{align}
-We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain contains at least two convection zone length scales according to the Schwarzschild criterion.
-We decompose the temperature field into a background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
+We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
+We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
 For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
@@
 \end{equation}
-The integrated value of the flux through the system from the heating is therefore $F_H(z > 0.1 + \delta_H) = \int_0^z Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
+The integrated value of the flux through the system from the heating is therefore $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
 Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
@@
 
-In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency $f_{\rm{conv}} \approx \angles{\vec{u}} \Lcz \approx 1$.
-We want to allow the stiffness of the radiative-convective interface to be a control parameter.
+In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
 The stiffness is defined,
@@
 where $N^2$ is the \brunt$\,$frequency in the radiative zone.
-In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.
+In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$.
+We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.
 
-The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
+The crucial place in which our model differs from that of prior work is that we define the ``Penetration Parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
 We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
-We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$.
+We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$, and therefore found negligible penetration for moderate to high stiffness.
 
-Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
+Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the degree of turbulence.
 The value of $\mR$ roughly corresponds to the value of the peak Reynolds number $\rm{Re} = \mR |\vec{u}|$ measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
@@
 \begin{equation}
-k_D(z) = \begin{cases}
+k = \begin{cases}
 k_{\rm{CZ}}	&	z < 1 \\
 k_{\rm{RZ}} &	z \geq 1
-\end{cases}.
+\end{cases},
 \label{eqn:sim_discontinuous_k}
 \end{equation}
-Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry the $\Fbot$ at $z = 0$ and that the radiative gradient can carry the flux for $z \geq 1$ specifies this system fully,
+where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
+Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H$ for $z \geq 1$ specifies this system fully,
 \begin{equation}
@@
 
-We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper (one in which we vary each parameter while holding the other parameters constant).
-We use ``Reference values'' of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all of our parameter space sweeps pass through this point in the three-dimensional parameter space.
-As in section \ref{sec:discontinuous_theory}, we expect $\delta_p \propto \mP_D$.
+We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper in which we hold two of these parameters constant and vary the other.
+We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
+According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
 
@@
 \begin{equation}
-\partial_z k_0 = \frac{\delta_H}{\Lcz \mS \xi},\qquad
+\partial_z k_0 = \frac{\delta_H}{L_s \mS \xi},\qquad
 k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
@@
 In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
-As in section \ref{sec:linear_theory}, we expect $\delta_p \propto \mP_L^{1/2}$.
+According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.
 
 \subsection{Numerics}
-We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use X version} using timestepper RK443 \citep{ascher_etal_1997}.
+We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008}.
 All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
@@
 We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
-All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repo, found at [CITE].
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
 
 Spectral methods with finite coefficient expansions cannot capture true discontinuities.
-In order to approximate discontinuous functions such as Eqns.~\ref{eqn:sim_Q}, \ref{eqn:sim_discontinuous_k}, \ref{eqn:sim_linear_k}, we must use smooth transitions.
+In order to approximate discontinuous functions such as Eqns.~\ref{eqn:sim_Q}, \ref{eqn:sim_discontinuous_k}, and \ref{eqn:sim_linear_k}, we must use smooth transitions.
 To create these smooth transitions, we define an approximate Heaviside step function using the error function,
@@
 \end{equation}
-In the limit of that $\delta_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
+In the limit that $\delta_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
 While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $\delta_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $\delta_w = 0.075$.
@@
 \subsection{Penetration depth measurements}
-In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\grad \approx \gradad$.
-In order to characterize the vertical extent of the penetrative (and subsequent overshoot) region, we measure how drastically $\grad$ has departed from $\gradad$.
+In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
+In order to characterize the vertical extent of the penetrative (and subsequent overshoot) region, we measure how drastically $\justgrad$ has departed from $\gradad$.
 We define the difference between the adiabatic and radiative gradient,
 \begin{equation}
-\Delta\grad \equiv \gradad(z) - \gradrad(z).
+\Delta\justgrad \equiv \gradad(z) - \gradrad(z).
 \end{equation}
-We measure penetration and overshoot depths in terms of ``departure points,'' that is, points at which the realized temperature gradient $\grad$ has evolved away from the adiabatic $\gradad$ by some fraction $f < 1$.
+We measure penetration and overshoot depths in terms of ``departure points,'' that is, points at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $f < 1$.
 Specifically,
 \begin{equation}
-1 + \delta_{f} = \rm{max}(z) \mid \grad > \gradad - f\Delta\grad.
+L_s + \delta_{f} = \rm{max}(z) \mid \justgrad > \gradad - f\Delta\grad.
 \end{equation}
-In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points, which are respectively at the top of the penetration zone, in the middle of the overshoot zone, and at the top of the overshoot zone.
+In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
+Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and bottom of the ``thermal adjustment layer.''
+We will simply refer to these as three different measures of the top of the PZ.
 We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
@@
 \includegraphics[width=\textwidth]{time_evolution.pdf}
-\caption{(Top panel) we show traces of the time evolution of the points in the simulation where $\grad$ has departed from $\gradad$ by 10\% (bottom curve) and 90\% (top curve) of $\Delta = \gradad - \gradrad$.
-Time is plotted on the x-axis in freefall units which are roughly equal to convective overturn times; the color of the line represents the simulation time.
-While this evolution is initially fast (changing noticeably over hundreds of overturn times), as the convection zone approaches its final size its evolution drastically slows down.
-(Bottom panel) The vertical profile of $\grad/\gradad$ is plotted against height at different times (where the color denotes the time and matches the color of the top panel.
-The (constant) value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
-The 10\% and 90\% departure curves from the top panel are overplotted as red lines.
+\caption{
+(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$), normalized by the appropriate convection zone height $\tilde{L_s}$ in our simulations.
+(Left middle panel) Shown is the average value of $(\justgrad - \gradrad)/\gradrad$, averaged over the full domain above $\delta_{0.5}$, as a function of time.
+This provides a measure of how far out of thermal equilibrium the RZ is above the PZ, and should trend towards zero in the long-time limit.
+(Left bottom panel) Shown is a rolling average over 50 freefall times of the dissipation constant $f$, defined in Eqn.~\ref{eqn:preliminary_flux_ratio}.
+The vertical lines in the top and bottom panels correspond to when that measure has converged to within 1\% of its final value, where the final value is the mean taken over the last 500 freefall times of evolution shown in these plots.
+(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
+The line color denotes the time, according to the time traces in the left panels.
+The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
+The departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
 \label{fig:time_evolution}
@@
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 2$ (TODO: change to 4) whose initial conditions set $\grad = -\partial_z T$ equal to $\gradad$ in the convection zone ($z < 1$) and equal to $\gradrad$ in the radiative zone ($z > 1)$.
-Initially, over hundreds of overturn times, the front of the convection zone drastically advances past the Schwarzschild boundary of the convection zone at $z = 1$.
-As the convection zone advances and mixes $\grad \rightarrow \gradad$ within itself; this steepening of $\grad$ within the PZ is accompanied by a flattening of $\grad < \gradrad$ at the base of the RZ along the front of the CZ.
-This flattening of $\grad$ increases the value of $N^2 = \gradad - \grad$ at the front of the convection zone, slowing the advancement of the convection zone until this disequilibrium state diffuses to the top boundary of the simulation.
-This stiffer radiative-convective interface, combined with the presence of an increasingly growing breaking region in the form of the PZ slows the advancement of the convective front and the final equilibration of the top boundary of the convection zone takes thousands of convective overturn times.
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions set $\justgrad = \gradad$ in the convection zone ($z < 1$) and $\justgrad = \gradrad$ in the radiative zone ($z > 1)$.
+In the top left panel, we display the extent of the penetrative region vs time \footnote{$\tilde{L_s} = 0.8L_s$.
+Our choice of internal heating function (Eqn.~\ref{eqn:sim_Q}) means that the integral of $\int\Fconv$ in the convection zone is 80\% what it would be if the full $z < L_s$ region carried the full flux $F_H$, and we must appropriately account for this when measuring the overshoot depth according to Eqn.~\ref{eqn:theory_fraction}.} $\delta_{\rm{0.5}}/\tilde{L_s}$.
+This region initially grows quickly over hundreds of overturn times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes thousands of freefall times.
+The steepening of $\justgrad$ in this penetrative region corresponds to a flattening of $\justgrad$ in the RZ above the PZ, which can be seen in the middle panel of Fig.~\ref{fig:time_evolution}.
+In the bottom left panel of Fig.~\ref{fig:time_evolution}, we show a rolling average over 50 freefall times of the vorticity-based value of $f$ from Eqn.~\ref{eqn:preliminary_flux_ratio}.
+Unlike the thermal stratification, this value quickly reaches a value close to its final value; for comparison, we plot grey vertical lines in the top and bottom panels of Fig.~\ref{fig:time_evolution} to indicate when each of those quantities converges to its average sampled over the last 500 freefall times displayed in that plot; we see that the dynamics converge rapidly but that the restratification is slow.
+In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
+$\gradad$ is plotted as a dashed line while $\gradrad$ is plotted as a grey solid line.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+We can see that the initial (fast) evolution establishes a sizeable PZ, but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
 
@@
 \caption{
-Instantaneous snapshots of a vertical slice through the simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ are shown.
-In both panels, the nominal Schwarzschild top of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the convection zone where $\grad$ departs from $\gradad$ by 10\% of $\Delta = \gradad - \gradrad$ is shown as a solid horizontal line.
-(Left) The vertical velocity is shown; convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\grad$ departs from $\gradad$.
-(Right) Temperature perturbations away from $\overline{T}$ are shown; these perturbations are normalized by their standard deviation at each height in order to make both the convective features (below the solid black line) and internal gravity waves excited by the convection (above) visible.
-Unlike in the vertical velocity slice, we see that the temperature perturbations switch sign at the Schwarzschild boundary of the convection zone (the dashed horizontal line); buoyancy thus switches from an accelerating force to a braking force.
+Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
+In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
+(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
+(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
+Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
 \label{fig:vertical_dynamics_panels}
@@
 
-In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mP_D = 4$ and $\mS = 10^3$ in an equilibrated state.
-We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone into a penetration zone.
-However, there is still a stable radiative zone with small vertical velocity perturbations into which the convection does not extend.
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ in an equilibrated state.
+We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
+Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
 On the right, we see that hot upwellings in the convective dynamics are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
-These upwellings impinge upon the stable radiative zone and excite gravity waves [cf., CITE], but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.
+These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.
 
 \subsection{Measured penetration zone scalings}
+
+In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) from Case I (discontinuous $k$) simulations.
+In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
+We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is roughly the same size as the nominal convection zone.
+We find that the value of $\mP_D$ is the primary parameter whose value modifies the height of the convection zone.
+While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
+This signifies that $f$, and thus the viscous dissipation, is smaller in 2D than in 3D; we speculate that this is a consequence of the inverse turbulent cascade in 2D.
 
@@
 \caption{
-We plot penetration depths against $\mP_D$ (left, at constant $\mR$, $\mS$), $\mR$ (center, at constant $\mP_D$, $\mS$), and $\mS$ (right, at constant $\mP_D$, $\mR$).
-Up-triangles are the location of 10\% departure, down-triangles are the location of 90\% departure, and circles are the location of 50\% departure.
-In the left panel, we plot a line corresponding to the theory of Eqn.~\ref{eqn:discontinuous_prediction}.
-We find that the penetration depth is a strong, roughly linear function of $\mP_E$, in good agreement with the theory.
-The horizontal lines in the left panel represent the full range of the right two panels; the effects of varying $\mS$ and $\mR$ are secondary to the effects of $\mP$.
+Shown are penetration depths against (left) $\mP_D$, (center) $\mR$, and (right) $\mS$.
+Up-triangles signify $\delta_{0.1}$, down-triangle signify $\delta_{0.9}$, and circles signify $\delta_{0.5}$.
+In all panels, we plot a line corresponding to the theory of Eqn.~\ref{eqn:discontinuous_prediction}, with $f = 0.875$ and under the assumption that $f$ does not vary.
+The penetration depth is a nearly linear function of $\mP_D$, in good agreement with the theory.
+The black horizontal lines in the left panel represent the full vertical range of the right two panels; the effects of varying $\mS$ and $\mR$ are secondary to that of $\mP$.
 In the center panel, we see that the penetration depth increases at low $\mR$ as laminar dynamics give way to time-evolving dynamics.
 As we increase the turbulence, the penetration depth decreases weakly and appears to asymptote in the turbulent regime.
-In the right panel, we see little change in the 50\% departure point, and we see that 10\% and 90\% departure points converge to the central point as a function of stiffness.
+In the right panel, we see that the width of the transition region $\delta_{0.9} - \delta_{0.1}$, is strongly related to the stiffness.
 \label{fig:erf_3D_penetration_depths}
@@
 
-In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth from Case I (discontinuous $k$) simulations, quantified by the 10\%, 50\%, and 90\% departure points from $\gradad$.
-In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
-We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is equal to or greater in size than the nominal convection zone (of unit depth).
-We find that the value of $\mP_D$ is the primary parameter whose value modifies the height of the convection zone.
-While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
-
 In the center and rightmost panels of Fig.~\ref{fig:erf_3D_penetration_depths}, we focus on modifications to the measured penetration depths achieved by varying $\mR$ (turbulence) and $\mS$ (stiffness).
 We find that the penetration depth is smaller at very low (laminar) values of $\mR$ and at high (turbulent) values of $\mR$, with a peak at moderate values (for which dynamics are interesting and non-stationary, but not as turbulent as e.g., Fig.~\ref{fig:vertical_dynamics_panels}).
-Our data suggest that the penetration depth asymptotes as $\mR$ increases and so our results should be relevant for the astrophysical case in which $\mR \rightarrow \infty$.
-We note however that these simulations are expensive to run and cannot be converged to the same degree of confidence as the simulations for which $\mR \lesssim 10^3$, which we run for thousands of overturn times.
+Our data suggest that the penetration depth, and thus the viscous dissipation, asymptotes as $\mR$ increases and so our results should be relevant for the astrophysical case in which $\mR \rightarrow \infty$ (COAUTHOR NOTE: high-$\mR$ and $\mS$ data is still preliminary, but I think that the general trends are right).
 We find that mean penetration depth (the 50\% departure point) shows little dependence on the stiffness (circles in the right panel).
-However, the depth of the transition region from the PZ to the RZ shows a strong dependence on stiffness.
-In stars, the stiffness is roughly determined by the Mach number ($\rm{Ma}^{-2} \sim \mS$), so for low-Mach convective stellar flows, the boundary of the PZ and RZ can likely be reasonably approximated as a step function in $\grad$.
+The depth of the transition region from the PZ to the RZ, which can be measured as $\delta_{0.9} - \delta_{0.1}$, shows a strong dependence on stiffness.
+In stars, the stiffness is roughly determined by the Mach number ($\rm{Ma}^{-2} \sim \mS$), so for low-Mach stellar flows, the PZ-RZ boundary can likely be reasonably approximated as a step function in $\justgrad$.
 
@@
 Similar to Fig.~\ref{fig:erf_3D_penetration_depths}, but for the Case II ``linear'' simulations where the slope of $k$ is discontinuous at the Schwarzschild point.
-We plot a line corresponding to the theory of Eqn.~\ref{eqn:linear_prediction} as well as the 10\% (up triangle), 50\% (circle), and 90\% (down triangle) departure points.
+We plot an orange line corresponding to the theory of Eqn.~\ref{eqn:linear_prediction} with $f = 0.925$ as well as up-triangles ($\delta_{0.1}$), down-triangle ($\delta_{0.9}$), and circles ($\delta_{0.5}$).
 We find that the theory describes our simulation measurements well.
-We note that at small values of $\mP_L \lesssim 10^{-1}$, the 10\% departure point approaches the Schwarzschild boundary of the convection zone, approaching zero and not appearing on this plot.
 \label{fig:linear_3D_penetration_depths}
@@
 
-Our simulation results present a strong case for the validity of \citet{zahn1991}'s theory.
+Our simulation results present a strong case for the validity of \citet{roxburgh1989}'s integral constraint and \citet{zahn1991}'s theory of the importance of the slope of the radiative gradient near the boundary.
 The generalized Eqn.~\ref{eqn:theory_fraction}, and its solution for our simulation setups in Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction}, describe our data well.
-In addition to the flux-based penetration parameter $\mP$, the theory of Eqn.~\ref{eqn:theory_fraction} depends on the horizontal structure of the flux-carrying convective flows.
+In addition to the flux-based penetration parameter $\mP$, Eqn.~\ref{eqn:theory_fraction} depends only on a quantity related to the volume-average magnitude of the viscous dissipation comapred to the convective flux in the Schwarzschild-unstable convection zone ($f$).
 In this work, from the theory lines plotted in Figs.~\ref{fig:erf_3D_penetration_depths} \& \ref{fig:linear_3D_penetration_depths}, we find
 \begin{equation}
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx 0.125 \,\,(\text{Case I: Discontinuous}),\qquad
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx 0.0625 \,\,(\text{Case II: Linear}).
+f \approx 0.875\,\,(\text{Case I: Discontinuous}),\qquad
+f \approx 0.925\,\,(\text{Case II: Linear}).
 \label{eqn:fit_h_values}
 \end{equation}
-As the case II linear simulations are more applicable in the regime of stellar convection, we suggest that those simulations likely provide a starting guess for how to implement \citet{zahn1991}'s theory in 1D stellar models.
-We examine this further in the next section.
+In both cases, $f$ is a parameter of order 0.9.
+With these results as an initial guess for the magnitude of $f$, Eqn.~\ref{eqn:theory_fraction} can be straightforwardly used to implement these penetrative zones in a 1D stellar structure code.
 
@@
 \label{sec:solar_model}
-We now examine briefly how \citet{zahn1991}'s theory modifies a simple structure model of the Sun.
+We now examine briefly how our theory modifies a simple structure model of the Sun.
 We implement a simple prescription of convective penetration in MESA \citep{paxton_etal_2013} as follows:
@@
 Also evaluate the value of the mixing length $\ell$ at that location.
-\item Integrate the magnitude of the convective luminosity within the convection zone, $L_i = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
-\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for the horizontal dynamics in Eqn.~\ref{eqn:fit_h_values}, integrate $L_o = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delta_p} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
-We determine the value of $\delta_p$ according to Eqn.~\ref{eqn:theory_fraction} so that
+\item Integrate the magnitude of the convective luminosity within the convection zone, $L_{\rm{CZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
+\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_h_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
+We determine the value of $\delp$ according to Eqn.~\ref{eqn:theory_fraction} so that
 \begin{equation}
-C \equiv -\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} \approx -0.1
-\Rightarrow
-L_o = C L_i.
+L_{\rm{PZ}} = (1 - f)L_{\rm{CZ}},
 \label{eqn:mesa_equation}
 \end{equation}
-\item Override the value of $\grad$ in the MESA solver to set $\grad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
-\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_o$.
+with an initial guess of $f = 0.9$.
+\item Override the value of $\justgrad$ in the MESA solver to set $\justgrad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
+\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_{\rm{PZ}}$.
 \end{enumerate}
+
+TODO: Implement this in MESA, and make a simple figure comparing some solar profiles near the base of the CZ!
 
@@
 \label{sec:discussion}
-In this work, we discussed the theory of convective penetration put forward by \citet{zahn1991}, then designed and analyzed two sets of simulations which showed good agreement with that theory.
+In this work, we used \citet{roxburgh1989}'s integral constraint and the theory of convective penetration put forward by \citet{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+We designed and analyzed two sets of simulations which showed good agreement with that theoretical parameterization.
 We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
-We find that convection zones are bounded by ``penetration zones,'' whose depths are determined by the shape of the radiative gradient near the convective boundaries.
-For the proper choice of parameters, these penetration zones can be larger than the convection zones themselves; however, for realistic stellar values ($\mP_L \approx 1$), we find that they may be as large as 20\% of the convective length scale (the mixing length in a star).
+Our results suggest that stellar convection zones should be bounded by penetration zones, whose depths are determined by the shape of the radiative gradient near the convective boundaries.
+In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale (the mixing length in a star).
 
-The simulations we presented in this work were the simplest possible simulations to try to test the basic tenents of \citet{zahn1991}'s theory.
-In particular, they show convincingly that the shape of the flux near the convective boundary is one of the factors that the determines the depth of the penetration zone.
-However, as discussed in Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_equation}, the structure of the penetrative convective flows is the other crucial ingredient in Zahn's theory.
-The scalar numerical estimates for how these dynamic sshould be handled in the theory, presented in Eqn.~\ref{eqn:fit_h_values}, of course come with the caveat that the local, Cartesian, Boussinesq flows studied here may be quite different from stars where spherical effects and density stratification come into account.
+The simulations we presented in this work were the simplest possible simulations to try to test the basic tenents of \citet{roxburgh1989} and \citet{zahn1991}'s theory.
+In particular, they demonstrate that indeed the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
+The precise value of $f$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be quite different from the value of $f \approx 0.9$ measured in this work.
 Future work should aim to determine how much the values in Eqn.~\ref{eqn:fit_h_values} vary when these more realistic effects are taken into account.
@@
 As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep a penetration zone should form.
-Future studies should follow e.g., \citet{kapyla_etal_2017, kapyla2019} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state.
+Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
 
-One additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
-Dynamics in this regime may be different from those in the regime of Pr$\lesssim 1$ that we studied here, which could affect flow morphologies and thus penetration depths.
-Recently, \citet{kapyla2021} found that convective flows exhibited exhibited more overshoot at low Pr than high Pr.
-Future work should aim to understand how strongly the (TODO: symbol for h integrals) fraction depends on Pr.
+An additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
+Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$.
+Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
+Future work should aim to understand whether $f$ depends on strongly on $\Pran$ in the turbulent regime.
+
+Two other interesting complications in stellar contexts are rotation and magnetism.
+In the rapidly rotating limit, rotation creates quasi-two-dimensional flows, which could affect the length scales on which dissipation acts and thus modify $f$.
+Furthermore, magnetism adds an additional ohmic dissipation term, which could in theory drastically change our initial estimate of $f \approx 0.9$.
 
@@
 
-In summary, we have provided a first step towards deconstructing the mysteries of the behavior of convection near convective boundaries.
-We find that the simple-but-elegant theory of \citet{zahn1991} provides an excellent starting point for building a better understanding of the nature of convective penetration in stellar interiors.
-In future work, we will aim to more robustly implement Zahn's theory into MESA.
+In summary, we have unified \citet{roxburgh1989}'s integral constraint with \citet{zahn1991}'s theory of flux-dependent penetration into a parameterized theory of convective penetration.
+We tested this theory with simulations and found good agreement between the theory and our simulations.
+In future work, we will aim to more robustly implement this theory into MESA and test some of the complicating factors we discussed here.
 
@@
 We'd like to thank Keaton Burns and Kyle Augustson for useful discussions which improved the content of this manuscript.
+TODO thank Nordita program.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
@@
 In \citet{anders_etal_2018}, we explored the long time evolution of simple convective simulations and found that fast-forwarding the evolution of a convective simulation's internal energy and thermal structure can be done accurately.
+This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
+This same separation of scales is observed in the top and bottom left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
+
 In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
@@
 We assume that convective motions influence $\delta_{0.1}$ and $\delta_{0.5}$ more strongly than $\delta_{0.9}$.
-We measure the time-evolution of the convective front $\frac{d \delp}{dt}$ by averaging the slope of the linear fits for $\delta_{0.1}$ and $\delta{0.2}$.
+We measure the time-evolution of the convective front $\frac{d \delp}{dt}$ by averaging the slope of the linear fits for $\delta_{0.1}$ and $\delta_{0.5}$.
 \item We take a large ``time step'' of size $\tau_{\rm{AE}}$ forward.
@@
 \item If $\Delta \delta_p < 0.005$, we erase the first 15 time units worth of departure point measures and return to step 2 for 15 time units.
-\item  If $\Delta \delta_p$ is large, we adjust the top of the PZ by setting $\delta_{0.5,\rm{new}} = \angles{\delta_{0.5}}_t + \Delta \delta_p$.
-If $\Delta \delta_p > 0.05$, we limit its value to 0.05.
-We calculate the width of the thermal adjustment layer $\delta_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
-We adjust the $m = 0$ temperature gradient to
+\item  If $\Delta \delta_p$ is large, we adjust the top of the PZ by setting $\delta_{0.5,\rm{new}} = \angles{\delta_{0.5}}_t + \Delta \delta_p$ (angles represent a time average).
+If $|\Delta \delta_p| > 0.05$, we limit its value to 0.05.
+We calculate the width of the thermal adjustment layer $d_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
+We adjust the mean temperature gradient to
 \begin{equation}
-\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{0.5,\rm{new}}}, \delta_w) \Delta\grad,
+\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{0.5,\rm{new}}}, d_w) \Delta\justgrad,
 \label{eqn:initial_grad}
 \end{equation}
-where $H$ is defined in Eqn.~\ref{eqn:heaviside} and $\Delta\grad = \gradrad - \gradad$.
-We also multiply the temperature perturbations and full convective velocity field by $H(z; 1, 0.05)$.
+where $H$ is defined in Eqn.~\ref{eqn:heaviside} and $\Delta\justgrad = \gradrad - \gradad$.
+We also multiply the temperature perturbations and full convective velocity field by $(1 - H(z; 1, 0.05))$.
 This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
@@
 If a simulation returns to step 2 from step 4 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
-This process effectively removes the long diffusive thermal evolution on display in the middle panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
+Additionally, in some simulations, we ensure that this process occurs no more than 25 times.
+This process effectively removes the long diffusive thermal evolution on display in the middle left panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
 
-In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of the same simulation as in Fig.~\ref{fig:time_evolution}, and we compare it to three simulations which use this accelerated evolution procedure.
-We start these three simulations with initial temperature profiles defined by Eqn.~\ref{eqn:initial_grad} with initial values of $\delta_{\rm{p,ev}} = 0$ (red line), $\delta_{\rm{p,ev}} 0.4$ (purple line), or $\delta_{\rm{p,ev}} = 0.7$ (green line).
-For these simulations, we expect the evolved penetration zone depth to be $\delta_p \approx 0.55$, so these represent perturbations above and below this estimate, as well as the classical Schwarzschild initial conditions.
-While the simulation that we straightforwardly timestep (black line) takes tens of thousands of time units to reach the final state, the accelerated simulations reach the final state over the course of hundreds of freefall times.
+In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of $\delp/\tilde{L_s}$ and $\angles{f}$ in the $\mP_D = [1,2,4]$ simulations using black lines.
+We overplot the evolution of simulations which use this accelerated evolution procedure using orange and green lines.
+For the orange-line simulations, we use initial conditions which specify a value of $\delp$ that is smaller than the expected evolved value of $\delp$.
+For the purple-line simulations, we use initial conditions which specify a value of $\delp$ that is larger than the expected evolve value.
+Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
+If these simulations are not in a stationary state after this procedure, we timestep them straightforwardly until we are satisfied that they have converged.
 
@@
 \label{fig:AE_time_figure}
+(top row) Time traces of $\delta_p/\tilde{L_s}$ for simulations which are computed using (black lines) standard timestepping, (green lines) accelerated evolution with large initial values of $\delp$, and (orange lines) accelerated evolution with small initial values of $\delp$.
+Accelerated evolution timesteps can be see as discontinuities in the $\delp/\tilde{L_s}$ trace.
+Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.
+(Bottom row) Same as top row, but where $\angles{f}$ is being shown.
 }

### 2021-05-29 manuscript/ms.tex
good-enough draft to send around

@@
 \begin{abstract}
-Convection is a crucial heat transport mechanism and excitation mechanism in planets and stars.
-While parameterizations like mixing length theory adequately describe convection in bulk convection zones, the behavior of convective motions near and beyond the Schwarzschild-stable convective boundary are not well understood.
-In this paper, we examine a simplified Boussinesq model of stellar convection with a radiative flux.
-We derive a ``penetration parameter'' $\mathcal{P}$ which compares how quickly the radiative gradient deviates from the adiabatic on either side of the convective boundary.
-In line with \citet{zahn1991}, we predict that the extend of the adiabatically stratified penetrative layer is strongly related to the magnitude of $\mathcal{P}$.
-We perform 3D numerical simulations using Dedlaus to test this theory, and find that the penetrative region strongly depends on the flux-based $\mathcal{P}$ and only weakly depends on the degree of turbulence in the flows or on the stiffness of the convective interface.
-In stellar contexts, we expect $\mathcal{P} \approx 1$ and our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20\% of a mixing length.
-We briefly examine a MESA solar model in which the bottom boundary of the convection zone is set according to our theory, and discuss the possible implications and future paths necessary for these findings.
+Convection is a crucial heat transport and dynamical excitation mechanism in stars.
+Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
+In this paper we examine how convective motions mix the background thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
+We use a simplified Boussinesq model of stellar convection with a radiative flux.
+We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the convective boundary.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
+We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
+In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20-30\% of a mixing length.
+We present a MESA solar model which uses our parameterization of convective penetration, and find that the base of the solar convection zone extends by (X amount for some choice of parameters).
+We briefly discuss future experiments which could verify and extend these results to stellar contexts.
 \end{abstract}
@@
 Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
-In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}, such as the classic Mixing Length Theory \citep{bohm-vitense1958}.
+In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
 While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
@@
 The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
-The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the extent of the extent of the adiabatically-mixed convective region.
+The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
 We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
@@
 Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
-In light of these results, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
+In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
 
@@
 The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
-The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
+The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
 Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
@@
 + \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
-= \alpha g w T - \nu|\vec{\omega}|^2,
+= |\alpha| g w T - \nu|\vec{\omega}|^2,
 \label{eqn:kinetic_energy}
@@
 \begin{equation}
-\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
+|\alpha| g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
 \label{eqn:ke_averages}
@@
 \begin{equation}
-\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{\alpha g} \angles{|\vec{\omega}|^2}.
+\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
 \label{eqn:flux_breakup}
@@
 \qquad\rm{with}\qquad
-f \equiv \frac{(L_s + \delp)}{\alpha g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
+f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
 = \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
@@
 where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
-The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics (the viscous dissipation), quantified by $f$.
+The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
 We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
@@
 This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
-Defining the radiative gradient $\grad_{\rm{rad}} = \Ftot/k$, we can write the PZ convective flux
+Defining the radiative gradient $\gradrad = \Ftot/k$, we can write the PZ convective flux
 \begin{equation}
@@
 &T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
-\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{\alpha g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
+\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
 \grad^* = L_s^{-1} \grad,\qquad
-\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 L_s^2\right)^{1/3}\vec{u},
+\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
 \\
@@
 \subsection{Case I: Discontinuous flux}
-Most of the simulations in this paper study simulations with a discontinuous convective flux at the Schwarzschild convective boundary.
+Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
 We achieve this by constructing a discontinuous radiative conductivity,
@@
 where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
-Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H$ for $z \geq 1$ specifies this system fully,
+Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
 \begin{equation}
@@
 Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
-by this choice, we require
+By this choice, we require
 \begin{equation}
@@
 \subsection{Numerics}
-We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008}.
+We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008} and safety factor 0.35.
 All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
@@
 \begin{equation}
-H(z; z_0, \delta_w) = \frac{1}{2}\left(1 + \rm{erf}\left[\frac{z - z_0}{\delta_w}\right]\right).
+H(z; z_0, d_w) = \frac{1}{2}\left(1 + \rm{erf}\left[\frac{z - z_0}{d_w}\right]\right).
 \label{eqn:heaviside}
 \end{equation}
-In the limit that $\delta_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
-While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $\delta_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $\delta_w = 0.075$.
-In all other cases, we use $\delta_w = 0.05$.
+In the limit that $d_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
+While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $d_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $d_w = 0.075$.
+In all other cases, we use $d_w = 0.05$.
 
@@
 In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
-In order to characterize the vertical extent of the penetrative (and subsequent overshoot) region, we measure how drastically $\justgrad$ has departed from $\gradad$.
+In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
 We define the difference between the adiabatic and radiative gradient,
@@
 \end{equation}
-We measure penetration and overshoot depths in terms of ``departure points,'' that is, points at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $f < 1$.
+We measure penetration and overshoot depths in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
 Specifically,
 \begin{equation}
-L_s + \delta_{f} = \rm{max}(z) \mid \justgrad > \gradad - f\Delta\grad.
+L_s + \delta_{h} = \rm{max}(z) \mid \justgrad > \gradad - h\,\Delta\justgrad.
 \end{equation}
 In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and bottom of the ``thermal adjustment layer.''
+Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and top of the ``thermal adjustment layer.''
 We will simply refer to these as three different measures of the top of the PZ.
@@
 In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions set $\justgrad = \gradad$ in the convection zone ($z < 1$) and $\justgrad = \gradrad$ in the radiative zone ($z > 1)$.
-In the top left panel, we display the extent of the penetrative region vs time \footnote{$\tilde{L_s} = 0.8L_s$.
-Our choice of internal heating function (Eqn.~\ref{eqn:sim_Q}) means that the integral of $\int\Fconv$ in the convection zone is 80\% what it would be if the full $z < L_s$ region carried the full flux $F_H$, and we must appropriately account for this when measuring the overshoot depth according to Eqn.~\ref{eqn:theory_fraction}.} $\delta_{\rm{0.5}}/\tilde{L_s}$.
-This region initially grows quickly over hundreds of overturn times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes thousands of freefall times.
-The steepening of $\justgrad$ in this penetrative region corresponds to a flattening of $\justgrad$ in the RZ above the PZ, which can be seen in the middle panel of Fig.~\ref{fig:time_evolution}.
-In the bottom left panel of Fig.~\ref{fig:time_evolution}, we show a rolling average over 50 freefall times of the vorticity-based value of $f$ from Eqn.~\ref{eqn:preliminary_flux_ratio}.
+In the top left panel, we display the extent of the penetrative region\footnote{$\tilde{L_s} = 0.8L_s$.
+Our choice of internal heating function (Eqn.~\ref{eqn:sim_Q}) means that the integral of $\int\Fconv$ in the convection zone is 80\% what it would be if the full $z < L_s$ region carried the full flux $F_H$, and we must appropriately account for this when measuring the overshoot depth according to Eqn.~\ref{eqn:theory_fraction}.} vs time, $\delta_{\rm{0.5}}/\tilde{L_s}$.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes thousands of freefall times.
+The steepening of $\justgrad\rightarrow\gradad$ in the growing penetrative region corresponds to a flattening of $\justgrad < \gradrad$ in the RZ above the PZ, which can be seen in the left-middle panel of Fig.~\ref{fig:time_evolution}.
+In the bottom left panel of Fig.~\ref{fig:time_evolution}, we show a rolling average over 50 freefall times of the volume-averaged vorticity-based value of $f$ from Eqn.~\ref{eqn:preliminary_flux_ratio}.
 Unlike the thermal stratification, this value quickly reaches a value close to its final value; for comparison, we plot grey vertical lines in the top and bottom panels of Fig.~\ref{fig:time_evolution} to indicate when each of those quantities converges to its average sampled over the last 500 freefall times displayed in that plot; we see that the dynamics converge rapidly but that the restratification is slow.
@@
 We can see that the initial (fast) evolution establishes a sizeable PZ, but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
+This occurs in part because the flattening of $\justgrad < \gradrad$ above the convection zone effectively increases the value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
 
@@
 We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is roughly the same size as the nominal convection zone.
-We find that the value of $\mP_D$ is the primary parameter whose value modifies the height of the convection zone.
+%We find that the value of $\mP_D$ is the primary parameter whose value modifies the extent of the PZ.
 While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
@@
 Our data suggest that the penetration depth, and thus the viscous dissipation, asymptotes as $\mR$ increases and so our results should be relevant for the astrophysical case in which $\mR \rightarrow \infty$ (COAUTHOR NOTE: high-$\mR$ and $\mS$ data is still preliminary, but I think that the general trends are right).
-We find that mean penetration depth (the 50\% departure point) shows little dependence on the stiffness (circles in the right panel).
-The depth of the transition region from the PZ to the RZ, which can be measured as $\delta_{0.9} - \delta_{0.1}$, shows a strong dependence on stiffness.
+We find that mean penetration depth shows little dependence on the stiffness.
+However, the depth of the transition region from the PZ to the RZ, which can be measured as $\delta_{0.9} - \delta_{0.1}$, shows a strong dependence on stiffness.
 In stars, the stiffness is roughly determined by the Mach number ($\rm{Ma}^{-2} \sim \mS$), so for low-Mach stellar flows, the PZ-RZ boundary can likely be reasonably approximated as a step function in $\justgrad$.
@@
 f \approx 0.925\,\,(\text{Case II: Linear}).
-\label{eqn:fit_h_values}
+\label{eqn:fit_f_values}
 \end{equation}
@@
 \item Integrate the magnitude of the convective luminosity within the convection zone, $L_{\rm{CZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
-\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_h_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
+\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_f_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
 We determine the value of $\delp$ according to Eqn.~\ref{eqn:theory_fraction} so that
@@
 \label{sec:discussion}
-In this work, we used \citet{roxburgh1989}'s integral constraint and the theory of convective penetration put forward by \citet{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+In this work, we used \citet{roxburgh1989}'s integral constraint and flux-based argument analagous to \citet{zahn1991}'s theory to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
 We designed and analyzed two sets of simulations which showed good agreement with that theoretical parameterization.
 We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
-Our results suggest that stellar convection zones should be bounded by penetration zones, whose depths are determined by the shape of the radiative gradient near the convective boundaries.
-In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale (the mixing length in a star).
+Our results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
+In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale (the mixing length).
 
@@
 In particular, they demonstrate that indeed the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
-The precise value of $f$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be quite different from the value of $f \approx 0.9$ measured in this work.
-Future work should aim to determine how much the values in Eqn.~\ref{eqn:fit_h_values} vary when these more realistic effects are taken into account.
+The precise value of $f$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from the value of $f \approx 0.9$ measured in this work.
+Future work should aim to determine how much the values in Eqn.~\ref{eqn:fit_f_values} vary when these more realistic effects are taken into account.
 
@@
 Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
-Future work should aim to understand whether $f$ depends on strongly on $\Pran$ in the turbulent regime.
+Future work should aim to understand whether $f$ depends strongly on $\Pran$ in the turbulent regime.
 
@@
 In the rapidly rotating limit, rotation creates quasi-two-dimensional flows, which could affect the length scales on which dissipation acts and thus modify $f$.
-Furthermore, magnetism adds an additional ohmic dissipation term, which could in theory drastically change our initial estimate of $f \approx 0.9$.
+Furthermore, magnetism adds an additional ohmic dissipation term, which could in theory drastically change our hydrodynamical measurement of $f \approx 0.9$.
 
@@
 \end{enumerate}
+In general, we start our simulations with an initial profile according to Eqn.~\ref{eqn:initial_grad} with a value $\delta_{0.5,\rm{new}} \geq 0$.
 If a simulation returns to step 2 from step 4 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.

### 2021-05-29 data/compare_time_traces.py

@@ -1,0 +1,54 @@
+"""
+Script for plotting movies of 1D profile movies showing the top of the CZ vs time.
+
+Usage:
+    compare_top_cz_traces.py <dirs>... [options]
+
+Options:
+    --dpi=<dpi>                         Image pixel density [default: 200]
+
+"""
+from collections import OrderedDict
+import h5py
+from mpi4py import MPI
+from docopt import docopt
+args = docopt(__doc__)
+from plotpal.file_reader import SingleFiletypePlotter as SFP
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mtick
+import scipy.optimize as sop
+from scipy.interpolate import interp1d
+import logging
+logger = logging.getLogger(__name__)
+
+dirs = args['<dirs>']
+
+fig = plt.figure(figsize=(8, 5))
+ax1 = fig.add_subplot(2,1,1)
+ax2 = fig.add_subplot(2,1,2)
+
+colors = ['k', 'b', 'g', 'r']
+
+for i, d in enumerate(dirs):
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        f_theory_enstrophy = f['f_theory_enstrophy'][()]
+
+    if 'predictive' in d:
+        label = d.split('predictive')[-1].split('/')[0]
+    else:
+        label = "?"
+    ax1.plot(times, L_d01s, c=colors[i], label=label)
+    ax1.plot(times, L_d05s, c=colors[i])
+    ax1.plot(times, L_d09s, c=colors[i])
+
+    ax2.plot(times, f_theory_enstrophy, c=colors[i])
+ax2.set_ylim(0.75, 0.95)
+ax1.legend()
+
+for d in dirs:
+    plt.savefig('{:s}/comparison_top_cz_trace.png'.format(d), dpi=int(args['--dpi']), bbox_inches='tight')

### 2021-05-29 data/dynamics_panels.py

@@ -114,3 +114,4 @@ for ax in axs:
 
 
 fig.savefig('turbulent_dynamics_panels.png', dpi=300, bbox_inches='tight')
+fig.savefig('../manuscript/turbulent_dynamics_panels.pdf', dpi=300, bbox_inches='tight')

### 2021-05-29 data/plot_AE_fig.py

@@ -89,7 +89,7 @@ for d in dirs:
         if P == 2:
             N_skip = 10
     elif ('predictive0.4/' in d and P == 4) or ('predictive0.1' in d and P == 2) or ('predictive0' in d and P == 1):
-        color = 'indigo'
+        color = 'orange'
         zorder = 1
         times -= times[-1]
         if P == 1:

### 2021-05-29 data/plot_erf_delta_p.py

@@ -72,26 +72,33 @@ ax3 = fig.add_axes([0.69, 0, 0.29, 1])
 second_plot_lower = 0.4
 second_plot_upper = 0.7
 
+line_P = np.linspace(0.5, 21, 100)
+approx_f = 0.875
+line_theory = line_P * (1 - approx_f)
+
 good = (erf == 1) * (Re == 4e2) * (S == 1e3) * (ae == 0)
 ax1.scatter(P[good], (L_d09[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.9}$", zorder=1, marker='v')
 ax1.scatter(P[good], (L_d05[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.5}$", zorder=1, marker='o')
 ax1.scatter(P[good], (L_d01[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.1}$", zorder=1, marker='^')
-ax1.scatter(P[good], theory[good], c='orange', label=r'$\mathcal{P}(1 - \langle f \rangle)$', marker='x')
+ax1.plot(line_P, line_theory, c='orange', label=r'theory'.format(approx_f), zorder=0)
+#ax1.plot(line_P, line_theory, c='orange', label=r'theory ($f$ = {})'.format(approx_f), zorder=0)
+#ax1.scatter(P[good], theory[good], c='orange', label=r'$\mathcal{P}(1 - \langle f \rangle)$', marker='x')
 print(Ls[good])
 
 #y1 = 0.11*x
-ax1.legend(frameon=True, fontsize=8, framealpha=1)#False)
-ax1.set_xlabel('$\mathcal{P}_E$')
-ax1.set_title('$\mathcal{P}_E|_{\mathcal{R} = 400, \mathcal{S} = 10^3}$')
-ax1.set_ylabel(r'$\delta_{\rm{p}}/L_s$')
-ax1.set_xlim(0, 21)
+ax1.legend(frameon=True, fontsize=8, framealpha=0.6)
+ax1.set_xlabel('$\mathcal{P}_D$')
+ax1.set_title('$\mathcal{P}_D|_{\mathcal{R} = 400, \mathcal{S} = 10^3}$')
+ax1.set_ylabel(r'$\delta_{\rm{p}}/\tilde{L_s}$')
+ax1.set_xlim(0, 11)
 ax1.set_ylim(0, 1.5)
 
[…]

### 2021-05-29 data/plot_linear_delta_p.py

@@ -63,12 +63,17 @@ ae = data[:,11]
 Lcz_norm = Ls - 0.2 #account for flux change at base of CZ.
 theory   = np.sqrt(P*(1 - enstrophy_f))
 
+line_P = np.logspace(-2, 2, 100)
+approx_f = 0.925
+line_theory = np.sqrt(line_P*(1-approx_f))
+
 plt.figure(figsize=(col_width, col_width/golden_ratio))
 good = (erf == 0)
 plt.scatter(P[good], (L_d09[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.9}$", zorder=1, marker='v')
 plt.scatter(P[good], (L_d05[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.5}$", zorder=1, marker='o')
 plt.scatter(P[good], (L_d01[good] - Ls[good])/Lcz_norm[good], c='k', label=r"$\delta_{0.1}$", zorder=1, marker='^')
-plt.scatter(P[good], theory[good], c='orange', label=r'$\sqrt{\mathcal{P}(1 - \langle f \rangle)}$', marker='x')
+#plt.scatter(P[good], theory[good], c='orange', label=r'$\sqrt{\mathcal{P}(1 - \langle f \rangle)}$', marker='x')
+plt.plot(line_P, line_theory, c='orange', zorder=0, label='theory')
 plt.xscale('log')
 plt.yscale('log')
 
@@ -77,7 +82,7 @@ plt.yscale('log')
 #plt.plot(x, y1, c='orange', label=r'Theory$\,\,(0.25 \mathcal{P}_L^{1/2})$')
 plt.legend(frameon=True, fontsize=8, loc='upper left')
 plt.xlabel('$\mathcal{P}_L$')
-plt.ylabel('$\delta_p$')
+plt.ylabel(r'$\delta_p/\tilde{L_s}$')
 plt.xlim(8e-3, 2e1)
 
 plt.savefig('linear_3D_penetration_depths.png', dpi=300, bbox_inches='tight')

### 2021-05-29 data/plot_time_fig.py

@@ -96,8 +96,13 @@ f_df = pd.DataFrame(data=f_data)
 rolledf = f_df.rolling(window=50, min_periods=25).mean()
 
 final_f = np.mean(theory_f_enstrophy[-500:])
-error = np.abs(1 - rolledf['f']/final_f)
-time_cross = times[error < 0.01][0]
+error_f = np.abs(1 - rolledf['f']/final_f)
+time_cross_f = times[error_f < 0.01][0]
+
+delta_d05 = (L_d05s - Ls)/Lcz_norm
+final_d05 = np.mean(delta_d05[-500:])
+error_d05 = np.abs(1 - (delta_d05/final_d05))
+time_cross_d05 = times[error_d05 < 0.01][0]
 
 
 cmap = mpl.cm.viridis
@@ -111,7 +116,8 @@ for i in range(int(len(times)/10)-1):
     ax2.plot(times[i*10:(i+1)*10], ((np.abs(grad_above)-np.abs(grad_rad_above))/np.abs(grad_rad_above))[i*10:(i+1)*10], c=sm.to_rgba(times[int((i+0.5)*10)]))
     ax3.plot(rolledf['sim_time'][i*10:(i+1)*10], rolledf['f'][i*10:(i+1)*10], c=sm.to_rgba(times[int((i+0.5)*10)]))
 #    ax3.plot(times[i*10:(i+1)*10], theory_f_enstrophy[i*10:(i+1)*10], c=sm.to_rgba(times[int((i+0.5)*10)]))
-ax3.axvline(time_cross, color='xkcd:dark grey')
+ax1.axvline(time_cross_d05/t_diff, color='xkcd:dark grey')
+ax3.axvline(time_cross_f, color='xkcd:dark grey')
 ax1.set_ylim(0, 0.6)
 ax1.set_xlim(0, times.max()/t_diff)
 ax2.set_xlim(0, times.max())
@@ -120,9 +126,9 @@ ax1.xaxis.set_label_position('top')
 ax1.xaxis.set_ticks_position('top')
 ax2.set_xticklabels(())
 ax1.set_yticks((0.2, 0.4, 0.6))
-ax1.set_ylabel(r'$\delta_{0.5}/L_s$')
-ax2.set_ylabel(r'$\frac{\nabla - \nabla_{\rm{rad}}}{\nabla_{\rm{rad}}}|_{z > \delta_{\rm{0.5}}}$')
-ax3.set_ylabel(r'$f$')
[…]

### 2021-05-29 data/plot_turbulence_velocities.py

@@ -1,0 +1,53 @@
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+col_width = 3.25
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('erf_Re_cut*/erf*/') + glob.glob('erf_P_cut*/erf*/')
+
+data = []
+for d in dirs:
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        cz_vel = f['cz_velocities'][()]
+        tot_time = times[-1] - times[0]
+        good_times = times > times[0] + tot_time/2
+        mean_vel = np.mean(cz_vel[good_times])
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+    if '3D' in d:
+        threeD = True
+    else:
+        threeD = False
+    if 'erf' in d:
+        erf = True
+    else:
+        erf = False
+
+    data.append((S, P, Re, threeD, mean_vel, Lz, erf))
+data = np.array(data)
+
+S = data[:,0]
+P = data[:,1]
+Re = data[:,2]
+threeD = data[:,3]
+vel = data[:,4]
+Lz = data[:,5]
+erf = data[:,6]
+
+plt.figure(figsize=(col_width, col_width/golden_ratio))
+good = (erf == 1) * (P == 4)
+plt.scatter(Re[good], vel[good], c='k')
+plt.xscale('log')
+#plt.yscale('log')
+
+plt.show()
+
+#plt.savefig('linear_3D_penetration_depths.png', dpi=300, bbox_inches='tight')
+#plt.savefig('../manuscript/linear_3D_penetration_depths.pdf', dpi=300, bbox_inches='tight')

### 2021-05-29 data/vertical_dynamics_panels.py

@@ -79,8 +79,8 @@ with h5py.File(dynamics_file, 'r') as f:
 cbar_w = plt.colorbar(pW, cax=caxs[0], orientation='horizontal')
 cbar_T = plt.colorbar(pT, cax=caxs[1], orientation='horizontal')
 
-caxs[0].text(0.5, 0.5, r"$w$", transform=caxs[0].transAxes, va='center', ha='center')
-caxs[1].text(0.5, 0.4, r"$T'$", transform=caxs[1].transAxes, va='center', ha='center')
+caxs[0].text(0.5, 0.5, r"$w$", transform=caxs[0].transAxes, va='center', ha='center', fontsize=10)
+caxs[1].text(0.5, 0.4, r"$T' / \overline{|T'|}$", transform=caxs[1].transAxes, va='center', ha='center', fontsize=8)
 
 for ind in [0, 1]:
     ax = axs[ind]

### 2021-06-26 dedalus_code/damping_erf_step_3D.py
adds damping sim script; many minor additions like stress-free / KE outputs

@@ -1,7 +1,7 @@
 """
 Dedalus script for a two-layer, Boussinesq simulation.
 The bottom of the domain is at z = 0.
-The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ L_cz.
+The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ 1.
 
 There are 6 control parameters:
     Re      - The approximate reynolds number = (u / diffusivity) of the evolved flows
@@ -13,8 +13,8 @@ There are 6 control parameters:
     aspect  - The aspect ratio (Lx = aspect * Lz)
 
 Usage:
-    linear_3D.py [options] 
-    linear_3D.py <config> [options] 
+    damping_erf_step_3D.py [options] 
+    damping_erf_step_3D.py <config> [options] 
 
 Options:
     --Re=<Reynolds>            Freefall reynolds number [default: 1e2]
@@ -142,9 +142,9 @@ def set_equations(problem):
                   (True, "True", "ωz - dx(v) + dy(u) = 0"),
                   (True, kx_n0,  "dx(u) + dy(v) + dz(w) = 0"), #Incompressibility
                   (True, kx_0,   "p = 0"), #Incompressibility
-                  (True, "True", "dt(u) + (dy(ωz) - dz(ωy))/Re0  + dx(p)        = v*ωz - w*ωy "), #momentum-x
-                  (True, "True", "dt(v) + (dz(ωx) - dx(ωz))/Re0  + dy(p)        = w*ωx - u*ωz "), #momentum-x
-                  (True, kx_n0,  "dt(w) + (dx(ωy) - dy(ωx))/Re0  + dz(p) - T1   = u*ωy - v*ωx "), #momentum-z
+                  (True, "True", "dt(u) + (dy(ωz) - dz(ωy))/Re0  + dx(p)       = v*ωz - w*ωy - damping * u "), #momentum-x
+                  (True, "True", "dt(v) + (dz(ωx) - dx(ωz))/Re0  + dy(p)       = w*ωx - u*ωz - damping * v "), #momentum-x
+                  (True, kx_n0,  "dt(w) + (dx(ωy) - dy(ωx))/Re0  + dz(p) - T1  = u*ωy - v*ωx - damping * w "), #momentum-z
                   (True, kx_0,   "w = 0"), #momentum-z
[…]

### 2021-06-26 dedalus_code/erf_step_3D.py

@@ -34,6 +34,8 @@ Options:
     --safety=<s>               CFL safety factor [default: 0.75]
     --mesh=<m>                 Processor distribution mesh (e.g., "4,4")
 
+    --stress_free              Use stress-free upper and lower boundary
+
     --run_time_wall=<time>     Run time, in hours [default: 119.5]
     --run_time_ff=<time>       Run time, in freefall times [default: 1.6e3]
 
@@ -154,10 +156,14 @@ def set_equations(problem):
 
     boundaries = ( (True, " left(T1_z) = 0", "True"),
                    (True, "right(T1) = 0", "True"),
-                   (True, " left(u) = 0", "True"),
-                   (True, "right(u) = 0", "True"),
-                   (True, " left(v) = 0", "True"),
-                   (True, "right(v) = 0", "True"),
+                   (not(args['--stress_free']), " left(u) = 0", "True"),
+                   (not(args['--stress_free']), "right(u) = 0", "True"),
+                   (not(args['--stress_free']), " left(v) = 0", "True"),
+                   (not(args['--stress_free']), "right(v) = 0", "True"),
+                   (args['--stress_free'], " left(ωx) = 0", "True"),
+                   (args['--stress_free'], "right(ωx) = 0", "True"),
+                   (args['--stress_free'], " left(ωy) = 0", "True"),
+                   (args['--stress_free'], "right(ωy) = 0", "True"),
                    (True, " left(w) = 0", kx_n0),
                    (True, "right(w) = 0", kx_n0),
                  )
@@ -227,6 +233,7 @@ def initialize_output(solver, data_dir, mode='overwrite', output_dt=2, iter=np.i
     profiles.add_task("plane_avg(u)", name='u')
     profiles.add_task("plane_avg(w)", name='w')
     profiles.add_task("plane_avg(vel_rms)", name='vel_rms')
+    profiles.add_task("plane_avg(vel_rms**2 / 2)", name='KE')
     profiles.add_task("plane_avg(sqrt((v*ωz - w*ωy)**2 + (u*ωy - v*ωx)**2))", name='advection')
     profiles.add_task("plane_avg(enstrophy)", name="enstrophy")
     profiles.add_task("plane_avg(bruntN2)", name="bruntN2")
@@ -272,6 +279,8 @@ def run_cartesian_instability(args):
[…]

### 2021-06-26 dedalus_code/plotting/find_threeD_filling_factor.py

@@ -1,0 +1,157 @@
+"""
+Script for plotting movies of 1D profile movies showing the top of the CZ vs time.
+
+Usage:
+    find_threeD_filling_factor.py <root_dir> [options]
+
+Options:
+    --fig_name=<fig_name>               Name of figure output directory & base name of saved figures [default: filling_factor]
+    --start_fig=<fig_start_num>         Number of first figure file [default: 1]
+    --start_file=<file_start_num>       Number of Dedalus output file to start plotting at [default: 1]
+    --n_files=<num_files>               Number of files to plot
+    --dpi=<dpi>                         Image pixel density [default: 200]
+
+    --col_inch=<in>                     Number of inches / column [default: 6]
+    --row_inch=<in>                     Number of inches / row [default: 3]
+"""
+from collections import OrderedDict
+import h5py
+from mpi4py import MPI
+from docopt import docopt
+args = docopt(__doc__)
+from plotpal.file_reader import SingleFiletypePlotter as SFP
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mtick
+import scipy.optimize as sop
+from scipy.interpolate import interp1d
+import logging
+logger = logging.getLogger(__name__)
+
+import dedalus.public as de
+
+from scipy.special import erf
+def one_to_zero(x, x0, width=0.1):
+    return (1 - erf( (x - x0)/width))/2
+
+def zero_to_one(*args, **kwargs):
+    return -(one_to_zero(*args, **kwargs) - 1)
+
+n_files     = args['--n_files']
+if n_files is not None: n_files = int(n_files)
+start_file  = int(args['--start_file'])
+start_fig = int(args['--start_fig']) - 1
+
+root_dir    = args['<root_dir>']
+if root_dir is None:
+    logger.error('No dedalus output dir specified, exiting')
+    import sys
+    sys.exit()
+fig_name   = args['--fig_name']
+logger.info("reading data from {}".format(root_dir))
+
+#therm_mach2 = float(root_dir.split("Ma2t")[-1].split("_")[0])
+#Lz = float(root_dir.split('Lz')[-1].split('_')[0])
[…]

### 2021-06-26 dedalus_code/plotting/threeD_plot_slices.py

@@ -13,12 +13,13 @@ Options:
     --static_cbar                       If flagged, don't evolve the cbar with time
     --dpi=<dpi>                         Image pixel density [default: 200]
 
-    --horiz_inch=<in>                   Number of inches / horizontal plot [default: 2]
-    --vert_inch=<in>                    Number of inches / vertical plot [default: 1]
+    --horiz_inch=<in>                   Number of inches / horizontal plot [default: 6]
+    --vert_inch=<in>                    Number of inches / vertical plot [default: 3]
     --pad=<inch>                        Plot padding inches [default: 0.5]
 
     --fig_type=<fig_type>               Type of figure to plot
                                             1 - T - horiz_avg(T), w
+                                            2 - kitchen sink
                                         [default: 1]
 """
 import numpy as np
@@ -45,6 +46,11 @@ fig_name   = args['--fig_name']
 plotter = SlicePlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
 
 if int(args['--fig_type']) == 1:
+    plotter_kwargs = { 'col_in' : int(args['--horiz_inch']), 'row_in' : int(args['--vert_inch']), 'padding' : 100 }
+    plotter.setup_grid(1, 2, **plotter_kwargs)
+    fnames = [  (("T1_y_mid",), {'remove_x_mean' : True, 'label' : 'T(y=Ly/2) - horiz_avg(T)'}),
+                (("w_y_mid",), {'cmap': 'PuOr_r'})]
+elif int(args['--fig_type']) == 2:
     h_inch = float(args['--horiz_inch'])
     v_inch = float(args['--vert_inch'])
     pad = float(args['--pad'])

### 2021-06-26 manuscript/ms.tex
rewrite of theory section

@@
 %%%% Title and Abstract
-\title{Convective penetration is set by the flux and dissipation, not the stiffness}
+\title{Convective penetration probably parameterizes convective overshoot}
 \author[0000-0002-3433-4733]{Evan H. Anders}
@@
 
-\subsection{Equations}
+\subsection{Equations \& flux definitions}
 \label{sec:theory_equations}
@@
 
-\subsection{Kinetic energy \& the dissipation-flux link}
-\label{sec:theory_energy}
-Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
-\begin{equation}
-\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
-+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
-= |\alpha| g w T - \nu|\vec{\omega}|^2,
-\label{eqn:kinetic_energy}
-\end{equation}
-where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
-Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution: \citet{roxburgh1989}'s integral constraint,
-\begin{equation}
-|\alpha| g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
-\label{eqn:ke_averages}
-\end{equation}
-where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
-It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
-However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
-Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
-\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.
-
-We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
-Following Eqn.~\ref{eqn:ke_averages}, we write
-\begin{equation}
-\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
-\label{eqn:flux_breakup}
-\end{equation}
-Rearranging, we retrieve 
-\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
-\qquad\rm{with}\qquad
-f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
-= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
-\label{eqn:preliminary_flux_ratio}
-\end{equation}
-where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
-The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
-We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
-If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
-In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.
-
-\subsection{A flux-based penetration argument}
-\citet{zahn1991} and Eqn.~\ref{eqn:preliminary_flux_ratio} suggest that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
 Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
@@
 \overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
+\label{eqn:flux_definition}
 \end{equation}
 where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
-We next assume that convection penetrates some distance $\delp$ above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the PZ.
-This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
-Defining the radiative gradient $\gradrad = \Ftot/k$, we can write the PZ convective flux
+We note that $k$ and the temperature gradient $\justgrad \equiv -\partial_z \bar{T}$ fully specify $\Frad$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
+We define the radiative gradient 
 \begin{equation}
-\overline{\Fconv}|_{\rm{PZ}} = \Ftot - \overline{\Frad} = k(\gradrad - \gradad).
-\label{eqn:fconv_pz}
+\gradrad = \frac{\bar{\Ftot}}{k}
+\label{eqn:gradrad_definition}
 \end{equation}
-Within the penetrative region, $\gradad > \gradrad$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv}|_{\rm{PZ}} < 0$.
+and note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.
 
-With the knowledge that $\bar{\Fconv}$ is negative in the PZ, we rewrite Eqn.~\ref{eqn:preliminary_flux_ratio}
+\subsection{Kinetic energy \& the dissipation-flux link}
+\label{sec:theory_energy}
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{theory_profiles.pdf}
+\caption{
+(left) The vertical profile of the kinetic energy fluxes $\mathcal{F}$.
+This profile goes to zero at the bottom boundary, again at the dashed line, and at the top of the PZ near $z \approx 1.5$; Eqn.~\ref{eqn:integral_constraint} holds between any two of these points.
+(middle) the evolved value of $\justgrad$ (green) compared to $\gradad$ (grey) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
+(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$.
+\label{fig:theory_profiles}
+}
+\end{figure}
+
+Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
 \begin{equation}
-\frac{|\int_{\rm{PZ}}\bar{\Fconv}\,dz|}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = (1 - f),
+\frac{\partial \mathcal{K}}{\partial t}
++ \grad\dot\mathcal{F}
+= \mathcal{B} - \Phi,
+%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
+%= |\alpha| g w T - \nu|\vec{\omega}|^2,
+\label{eqn:kinetic_energy}
+\end{equation}
+where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
+We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (which we will represent with $\bar{\,\cdot\,}$ for simplicity).
+Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
+\begin{equation}
+\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
+\label{eqn:kinetic_energy_1D}
+\end{equation}
+It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
+We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
+\begin{equation}
+\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
+\label{eqn:integral_constraint}
+\end{equation}
+Eqn.~\ref{eqn:integral_constraint} is the simple expression of \citet{roxburgh1989}'s integral constraint (is it?), and is the straightforward statement that work by buoyancy in the convection zone on large scales must be balanced by viscous dissipation on small scales.
+We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
+We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
+Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too.
+Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
+\begin{equation}
+\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
+\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
+\label{eqn:constraint_cz_pz_split}
+\end{equation}
+Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of energy are on the RHS.
+We see that the size of the PZ is set by some combination of buoyancy breaking and viscous dissipation, whose total effect cancels out any remaining work that dissipation in the convection zone did not itself cancel.
+we now find it instructive to define the fraction of the buoyant engine consumed by dissipation in the convection zone
+\begin{equation}
+f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz},
+\label{eqn:f_defn}
+\end{equation}
+and note two interesting limits,
+\begin{enumerate}
+\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
+It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:constraint_cz_pz_split} states that the PZ must be large enough to cancel out all of the buoyant work done by convection in the CZ by buoyancy breaking in the PZ.
+This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
+\item In the limit that $f \rightarrow 1$, viscous dissipation is extremely efficient in the convection zone and cancels out all of the work done by buoyancy.
+This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
+Per Eqn.~\ref{eqn:constraint_cz_pz_split}, the positive definite PZ terms must approach zero and no PZ develops in this limit.
+\end{enumerate}
+In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
+Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see Fig.~\ref{fig:theory_profiles}, right panel).
+
+In order to say more about the size of the penetration layer, we model $\bar{\Phi}$ as a linearly decreasing function of height in the PZ.
+We sets its value at the top of the PZ equal to the average of $\bar{\Phi}$ in the CZ of depth $L_{\rm{CZ}}$ so that $\int_{\rm{PZ}} \bar{\Phi}\,dz = (\delp/[2 L_{\rm{CZ}}])\int_{\rm{CZ}}\bar{\Phi}\,dz$ where $\delp$ is the penetration zone depth.
+Rearranging Eqn.~\ref{eqn:constraint_cz_pz_split} and dividing by $\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz$, and plugging in $\bar{\mathcal{B}} = |\alpha|g\bar{\Fconv}$, we can write
+\begin{equation}
+-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\frac{\delp}{2 L_{\rm{CZ}}}
+\approx (1 - f).
 \label{eqn:theory_fraction}
 \end{equation}
-and note that $f \leq 1$ by its tautological flux-based definition assuming $\delp \geq 0$.
-While we have arrived at Eqn.~\ref{eqn:theory_fraction} in a very different manner, this equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which relates to the convective dynamics.
-More importantly, if $\bar{\Fconv}$, and $f$ are known, this ratio directly sets the size of the PZ.
-
 In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
 We will study two cases in this work, laid out below.
-In both of these cases, we will define a nondimensional ``Penetration Parameter,''
+In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
 \begin{equation}
@@
 \end{equation}
-Following Eqn.~\ref{eqn:fconv_pz}, the sign of $\mP$ is positive and its magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone).
+Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
+
+%where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
+%It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
+%However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
+%Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
+%\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.
+%
+%We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
+%Following Eqn.~\ref{eqn:ke_averages}, we write
+%\begin{equation}
+%\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
+%\label{eqn:flux_breakup}
+%\end{equation}
+%Rearranging, we retrieve 
+%\begin{equation}
+%\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
+%\qquad\rm{with}\qquad
+%f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
+%= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
+%\label{eqn:preliminary_flux_ratio}
+%\end{equation}
+%where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
+%The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
+%We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
+%If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
+%In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.
 
@@
 Here, $\Fcz$ is a constant value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_s$ and the penetration zone from $z = L_s$ to $z = L_s + \delp$, we predict
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the CZ over a depth $L_{\rm{CZ}}$ below $L_s$ and the PZ over a depth $\delp$ above $L_s$, we predict
 \begin{equation}
-\frac{\delp}{L_s} = \mP_D (1 - f).
+\frac{\delp}{L_{\rm{CZ}}} \approx \mP_D \frac{1 - f}{1 + \mP_D f / 2}.
 \label{eqn:discontinuous_prediction}
 \end{equation}
-Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is linearly proportional to $\mP_D$.
-Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.
+Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is roughly linearly proportional to $\mP_D$ at small $\mP_D$, but saturates due to dissipation at large $\mP_D$.
+Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
 
@@
 where $(\partial \Frad / \partial z)|_{\rm{CZ}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
-Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
+Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux and integrating over $L_{\rm{CZ}}$ in the CZ and $\delp$ in the PZ, we retrieve a quadratic equation.
+This equation has two solution branches, only one of which corresponds to a positive value of $\delp$.
+On that branch, we find
 \begin{equation}
-\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)}.
+\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)} \,\,(\sqrt{\xi^2 + 1} - \xi),
 \label{eqn:linear_prediction}
 \end{equation}
-This is strikingly similar to \citet{zahn1991}'s result, whose work corresponds to the case of $\mP_L = 1$.
+where $\xi \equiv (f/4)\sqrt{\mP_L/(1-f)}$.
+So we expect the penetration depth to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
 
@@
 Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ on various parameters in local simulations.
-We note that \citet{roxburgh1989}'s constraint puts an upper limit on the penetration depth in the limit that viscous dissipation is negligible ($f = 0$), but in practice we expect $f$ closer to 1.
 

### 2021-06-30 notes/boundary_layers/boundary_layers.tex
adds a writeup about known unknowns

\documentclass[12pt]{article}
\usepackage{natbib}
\bibliographystyle{aasjournal}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}

\usepackage{pb-diagram}

\parindent = 0.0 in
\parskip = 0.15 in

\newcommand\Beq{\begin{align}} 
\newcommand\Eeq{\end{align}}

\newcommand\Bfig{\begin{figure}} 
\newcommand\Efig{\end{figure}}

\newcommand\Ra{\mathrm{Ra}}
\newcommand\Pran{\mathrm{Pr}}
\newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
\newcommand\Ek{\mathrm{Ek}}
\newcommand\Ro{\mathrm{Ro}}
\newcommand\Nu{\mathrm{Nu}}
\newcommand\Sc{\mathrm{Sc}}

\newcommand\eps{\varepsilon}
\renewcommand\L {\mathcal{L}}

\newcommand{\n}{\\ \nonumber \\ }
\newcommand{\nn}{\nonumber}
\newcommand{\nnn}{\\ \nonumber \\ \nonumber}

\newcommand\ie{\textit{i.e.},~}
\newcommand\eg{\textit{e.g.},~}
\newcommand{\omicron}{o}

\newcommand{\angles}[1]{\langle #1 \rangle}
\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}
\renewcommand{\bar}[1]{\overline{#1}}

\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mB}{\ensuremath{\mathcal{B}}}

\newcommand{\sump}[2]{\sideset{}{'}\sum_{{#1}=0}^{#2}}

\newcommand{\eq}[1]{eq.~(\ref{#1})}
\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\Eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\figs}[2]{Figs.~(\ref{#1})~\&~(\ref{#2})}

\newcommand{\tbl}[1]{Table~(#1)}

\newcommand{\aap}{A\&A}

\begin{document}

\section{Integral constraint}
Following arguments we've made a bunch of times, the time-stationary full convection zone (CZ and PZ) is bound by an integral constraint,
\begin{equation}
\int \bar{\mB}\,dz = \int \bar{\Phi}\,dz,
\end{equation}
where $\bar{\mB} \equiv \bar{\Fconv}$ is the buoyant KE generation rate and $\bar{\Phi} \equiv \mathcal{R}^{-1}\bar{|\vec{\omega}|^2}$ is the viscous dissipation rate.
We have generally found it instructive to break up the integrals above into CZ and PZ portions,
\begin{equation}
\int_{\rm{CZ}} \bar{\mB}\,dz = \int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} (-\bar{\mB})\,dz,
\end{equation}
where the LHS represents the total work done by buoyancy in the convection zone, and the RHS represents the viscous and (negative) PZ buoyancy work that cancels that work.
We have typically moved on to divide this equation by the LHS and define the parameter,
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}}\bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mB}\,dz},
\label{eqn:f_defn}
\end{equation}
and we have assumed that $f$ is a constant.
Unfortunately this is not in general true in our measurements, but it could be true in the infinite Reynolds number limit.

\section{Breaking out boundary layer contributions}
Further breaking apart the CZ integral into a bulk and BL contribution, the definition of Eqn.~\ref{eqn:f_defn} becomes
\begin{equation}
f \equiv 
\frac{\int_{\rm{bulk}}\bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mB}\,dz}
+
\frac{\int_{\rm{BL}}\bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mB}\,dz}.
\label{eqn:f_split}
\end{equation}
For simplicity, we will assume that $\bar{\Phi}$ is a constant value $\Phi_{\rm{CZ}}$ in the bulk of the convection zone.
This is a decent assumption which describes the simulations fairly well (but is not perfect).
We will then define
\begin{equation}
f_{\infty} \equiv \frac{\Phi_{\rm{CZ}} L_{\rm{CZ}}}{\int_{\rm{CZ}}\bar{\mB}\,dz},
\end{equation}
where here $L_{\rm{CZ}}$ is the depth of the full CZ from the bottom boundary to the upper Schwarzschild boundary (it's the range over with the $\int_{\rm{CZ}}$ integral is taken).
With this we can rewrite Eqn.~\ref{eqn:f_split},
\begin{equation}
f \approx f_{\infty} \frac{L_{\rm{bulk}}}{L_{\rm{CZ}}} + 
\frac{\int_{\rm{BL}}\bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mB}\,dz},
\label{eqn:f_approx}
\end{equation}
where $L_{\rm{bulk}} = L_{\rm{CZ}} - \delta_{\nu}$ is the depth of the bulk integral and $\delta_{\nu}$ is the viscous boundary layer depth.
To say more we need to talk about a specific type of boundary condition.

In general, in Rayleigh B\'{e}nard convection, we expect the viscous boundary layers to be the same size scale $\delta_{\nu} \sim \delta_{T}$ (where $\delta_T$ is the thermal boundary layer).
Furthermore, in RBC, the Nusselt number Nu $\sim \delta_T^{-1}$ and since essentially all RBC simulations are boundary controlled, $\rm{Nu} \propto \rm{Ra}^{1/3} \propto \rm{Re}^{2/3}$.
So we can generally expect boundary layers to scale like $\delta_{\nu} \propto \rm{Re}^{-2/3} \sim \mathcal{R}^{-2/3}$.
In our problem we have removed the bottom thermal boundary using our internal heating setup, so we can't really take the RBC intuition too much further and can't use it to bound $f$, for example.

\subsection{Stress-free boundaries}
In our simulations with stress-free boundaries, we see the dissipation decrease from its bulk value $\Phi_{\rm{CZ}}$ to a much lower value, close to zero, in the boundary layer.
As a zeroth order model, we can say $\int_{\rm{BL}}\bar{\Phi}\,dz \approx 0$, so Eqn.~\ref{eqn:f_approx} simply becomes the bulk portion,
\begin{equation}
f \approx f_{\infty}\left(1 - \frac{\delta_\nu}{L_{\rm{CZ}}}\right)
\sim
f_{\infty}\left(1 - \mathcal{R}^{-2/3}\right),
\label{eqn:stressfree_f}
\end{equation}
and we expect $f$ to converge to $f_{\infty}$ in the infinite Reynolds number limit.

\subsection{No-slip boundaries}
Here things are a bit more complicated.
Now the boundary layer is the location where dissipation peaks, because $\vec{u}$ must go from its bulk value $u_{\rm{rms}}$ to 0 at the boundary.
So we can estimate that the vorticity has a value $\omega \sim u_{\rm{rms}}/\delta_{\nu}$.
Thus the boundary layer dissipation is $\bar{\Phi_{\rm{BL}}} \approx \mathcal{R}^{-1} u_{\rm{rms}}^2/\delta_{\nu}^{2}$
Integrating this (constant) value over the boundary layer, we find
\begin{equation}
f \approx f_{\infty}\left(1 - \frac{\delta_\nu}{L_{\rm{CZ}}}\right) + \frac{C_0}{\mathcal{R}\delta_{\nu}}
\sim
f_{\infty}\left(1 - \mathcal{R}^{-2/3}\right) + C \mathcal{R}^{-1/3},
\end{equation}
where $C_0$ and $C$ are the sins of all of the constants I've been too lazy to carry along.
Anyways we see that in the infinite $\mathcal{R}$ limit, we get the same result $f_{\infty}$, but we have to go to higher $\mathcal{R}$ to get there.

\section{Dissipation in the penetration zone}
This remains a thorn in our side. 
I previously modeled this as linear but perhaps its best to model this as
\begin{equation}
\frac{\int_{\rm{PZ}}\bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mB}\,dz} \approx f\frac{\delta_p}{L_s}\xi,
\label{eqn:xi_defn}
\end{equation}
where $f$ is the same $f$ as above, $\delta_p$ is the penetration zone depth, $L_s$ is the schwarzshild-defined depth of the convection zone, and $\xi$ is a geometric factor that describes the shape of the dissipation in the PZ.
We can model the dissipation as a polynominally decreasing function,
\begin{equation}
\Phi_{\rm{PZ}} = \Phi_{\rm{CZ}}(1 - \tilde{z}^{n}),\qquad
\rm{with}\qquad
\tilde{z} = \frac{z - L_s}{\delta_p},
\end{equation}
where $\tilde{z}$ is a modified coordinate that is zero at the base of the PZ and 1 at the top of the PZ.
If we integrate,
\begin{equation}
\int_{0}^{1} \Phi_{\rm{CZ}}(1 - \tilde{z}^{n}) = \frac{n}{n+1}\Phi_{\rm{CZ}}.
\end{equation}
So we see that if $\Phi$ decreases linearly in the PZ ($n = 1$) then $\xi = 1/2$.
If $\Phi$ decreases quadratically then $\xi = 2/3$, and so on.
(This is not meant to be a perfect description, but we can measure $\xi$ in simulations and its value, combined with $n$ can give us a decent description).

\section{How does this look in the data?}
See Figs.~\ref{fig:profiles} and \ref{fig:f_and_xi}.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{viscous_boundary_layers.png}
\caption{
(Upper left) Dissipation profiles \emph{near the bottom boundary} for no-slip (solid lines) and stress-free (dashed lines) at various $\mathcal{R}$ (more purple = higher $\mathcal{R}$).
(Upper right) Dissipation profiles in the PZ.
We see large differences in morphology near the bottom boundary for different boundary condition choices, but not in the PZ.
(Bottom left) Viscous boundary layer length scales vs.~$\mathcal{R}$ with the prediction from standard RBC overplotted.
The fit is good.
(Bottom right) Viscous boundary layer length scales (circles) and penetration zone widths ($\delta_{0.9} - \delta_{0.1}$, diamonds) are compared.
At low $\mathcal{R}$, perhaps the classical RBC BL scaling applies.
Once the viscous BL becomes smaller than the width of the ``thermal adjustment layer'' (the thermal boundary layer, a constant for all of these simulations), the scaling levels out.
The viscous boundary layer also becoems much less pronounced in the PZ for these high-$\mathcal{R}$ simulations (see e.g., upper right).
\label{fig:profiles}
}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{f_scaling.png}
\caption{
(Left) measured values of $f$ from the data over the full CZ from $z = [0, L_s]$.
The simple prediction of Eqn.~\ref{eqn:stressfree_f} is overplotted with $f_{\infty} = 0.76$.
(Right) geometric factor $\xi$ calculated by rearranging Eqn.~\ref{eqn:xi_defn}.
We see that a linear description of PZ dissipation is decent at low $\mathcal{R}$ but at higher $\mathcal{R}$ a quadratic description is better.
A logical upper bound for $\xi$ is 1, and that could be used to provide a lower limit for the size of PZs in the infinite-$\mathcal{R}$ limit.
\label{fig:f_and_xi}
}
\end{figure}

\bibliography{biblio.bib}
\end{document}

### 2021-07-03 data/plot_AE_fig.py
adds reynolds number scaling figure

@@ -109,16 +109,16 @@ for d in dirs:
     elif 'schwarzschild_restart' in d:
         continue
     elif ('predictive0.7/' in d and P == 4) or ('predictive0.45' in d and P == 2) or ('predictive0.3' in d and P == 1):
-        color = 'green'
-        zorder = 2
+        color = 'orange'
+        zorder = 1
         times -= times[-1]
         if P == 1:
             N_skip = 0#10
         if P == 2:
             N_skip = 10
     elif ('predictive0.4/' in d and P == 4) or ('predictive0.1' in d and P == 2) or ('predictive0' in d and P == 1):
-        color = 'orange'
-        zorder = 1
+        color = 'green'
+        zorder = 2
         times -= times[-1]
         if P == 1:
             N_skip = 10

### 2021-07-03 data/plot_results_vs_re.py

@@ -1,0 +1,201 @@
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+from scipy.optimize import brentq
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('noslip_erf_Re_cut/erf*/')
+dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
+dirs += glob.glob('stressfree_erf_Re_cut/erf*/')
+dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
+
+#nz = 1024
+#Lz = 2
+#z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
+#domain = de.Domain([z_basis], grid_dtype=np.float64)
+#ke_rhs = domain.new_field()
+#ke_flux = domain.new_field()
+#domain_z = domain.grid(-1)
+
+cmap = "viridis_r"
+norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
+sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+
+data = []
+for i, d in enumerate(dirs):
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        modern_f = f['modern_f'][()]
+        modern_xi = f['modern_xi'][()]
+        fconv_Ls = f['fconv_Ls'][()]
+        Ls = np.mean(f['Ls'][()])
+        tot_time = times[-1] - times[0]
+        time_window = np.min((500, tot_time/2))
[…]

### 2021-07-03 data/plot_theory_profiles.py

@@ -42,35 +42,37 @@ fconv       = fconv_profiles[N,:]
 ke_eqn_rhs  = fconv - dissipation
 
 
-ax1.axhline(0, c='k', lw=0.5)
-ax1.plot(z, dissipation, c='indigo', label='$\omega^2 / \mathcal{R}$')
-ax1.plot(z, fconv, c='red', label=r'$F_{\rm{conv}}$')
-ax1.plot(z, ke_eqn_rhs, c='blue', label=r'$F_{\rm{conv}}$ - $\omega^2 / \mathcal{R}$')
-ax1.legend(loc='best', fontsize=8)
-ax1.set_ylim(-0.25, 0.25)
-ax1.set_ylabel('KE sources')
+ax3.axhline(0, c='k', lw=0.5)
+ax3.plot(z, dissipation/0.2, c='indigo', label='$\overline{\Phi}$')
+ax3.plot(z, fconv/0.2, c='red', label=r'$\overline{\mathcal{B}}$')
+ax3.plot(z, ke_eqn_rhs/0.2, c='blue', label=r'$\overline{\mathcal{B}} - \overline{\Phi}$')
+ax3.legend(loc='best', fontsize=8)
+ax3.set_ylim(-1.25, 1.25)
+ax3.set_ylabel('KE sources')
 
 f_ke_p = f_ke_profiles[N,:]
 
-ax2.axhline(0, c='k', lw=0.5)
-ax2.plot(z, f_ke_p, c='blue')
-ax2.axvline(brentq(interp1d(z, f_ke_p), 0.05, 0.9), c='k', ls='--')
-ax2.set_ylabel(r'$F_{\rm{KE}}$')
+ax1.axhline(0, c='k', lw=0.5)
+ax1.plot(z, f_ke_p, c='blue')
+ax1.axvline(brentq(interp1d(z, f_ke_p), 0.05, 0.9), c='k', ls='--')
+ax1.set_ylabel(r'$\overline{\mathcal{F}}$')
 
 
 grad = grad_profiles[N,:]
 grad_ad = grad_ad_profiles[N,:]
 grad_rad = grad_rad_profiles[N,:]
 
-ax3.axhline(1, c='k', lw=0.5)
-ax3.plot(z, grad/grad_ad, c='green', label=r'$\nabla/\nabla_{\rm{ad}}$')
[…]

### 2021-07-03 data/vertical_dynamics_panels.py

@@ -9,8 +9,8 @@ plt.style.use('apj')
 
 
 # Get data from files
-dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s8.h5'
-profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s8.h5'
+dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s9.h5'
+profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s9.h5'
 #dynamics_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/slices/slices_s5.h5'
 #profile_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/profiles/profiles_s5.h5'
 

### 2021-07-03 dedalus_code/plotting/find_top_cz.py
some new pleiades plot scripts

@@ -143,13 +143,15 @@ grad_rad_integ_field = domain.new_field()
 delta_grad_field = domain.new_field()
 vel_field = domain.new_field()
 vel_integ_field = domain.new_field()
+vel_horiz_field = domain.new_field()
+vel_horiz_integ_field = domain.new_field()
 enstrophy_field = domain.new_field()
 enstrophy_integ_field = domain.new_field()
 fconv_field = domain.new_field()
 fconv_integ_field = domain.new_field()
 
 bases_names = ['z',]
-fields = ['T', 'T_z', 'bruntN2', 'bruntN2_structure', 'F_rad', 'F_conv', 'T_rad_z', 'T_rad_z_IH', 'advection', 'vel_rms', 'effective_heating', 'T1', 'T1_z', 'heat_fluc_rad', 'heat_fluc_conv', 'T1_fluc', 'enstrophy', 'F_KE_p']
+fields = ['T', 'T_z', 'bruntN2', 'bruntN2_structure', 'F_rad', 'F_conv', 'T_rad_z', 'T_rad_z_IH', 'advection', 'vel_rms', 'effective_heating', 'T1', 'T1_z', 'heat_fluc_rad', 'heat_fluc_conv', 'T1_fluc', 'enstrophy', 'w']
 if not plotter.idle:
     init_fields = ['T_rad_z', 'T_rad_z_IH', 'F_rad', 'T', 'T_ad_z', 'flux_of_z', 'T_z']
     plotterOne.set_read_fields(bases_names, init_fields)
@@ -207,6 +209,8 @@ if not plotter.idle:
             grad_field.set_scales(dense_scales, keep_data=True)
             vel_field['g'] = roller.rolled_averages['vel_rms']
             vel_field.antidifferentiate('z', ('left', 0), out=vel_integ_field)
+            vel_horiz_field['g'] = np.sqrt(roller.rolled_averages['vel_rms']**2 - roller.rolled_averages['w']**2)
+            vel_horiz_field.antidifferentiate('z', ('left', 0), out=vel_horiz_integ_field)
             enstrophy_field['g'] = roller.rolled_averages['enstrophy']
             enstrophy_field.antidifferentiate('z', ('left', 0), out=enstrophy_integ_field)
             fconv_field['g'] = roller.rolled_averages['F_conv']
@@ -227,29 +231,18 @@ if not plotter.idle:
             L_d09 = departures[2]
[…]

### 2021-07-03 dedalus_code/plotting/plot_avg_profiles.py

@@ -35,7 +35,7 @@ fig_name   = args['--fig_name']
 
 plotter = ProfilePlotter(root_dir, file_dir='profiles', fig_name=fig_name, start_file=start_file, n_files=n_files)
 
-fields = ['T', 'T_z', 'bruntN2', 'F_rad', 'F_conv', 'T_rad_z', 'T_rad_z_IH', 'T_ad_z', 'vel_rms', 'effective_heating', 'T1', 'T1_z', 'heat_fluc_rad', 'heat_fluc_conv', 'T1_fluc', 'enstrophy', 'F_KE', 'F_KE_vert', 'F_KE_p']
+fields = ['T', 'T_z', 'bruntN2', 'F_rad', 'F_conv', 'T_rad_z', 'T_rad_z_IH', 'T_ad_z', 'vel_rms', 'effective_heating', 'T1', 'T1_z', 'heat_fluc_rad', 'heat_fluc_conv', 'T1_fluc', 'enstrophy', 'u', 'w', 'F_KE_p']
 for f in fields:
     plotter.add_profile(f, avg_writes)
 

### 2021-07-03 dedalus_code/plotting/vertical_dynamics_panels.py

@@ -1,0 +1,99 @@
+import matplotlib
+from collections import OrderedDict
+import numpy as np
+import matplotlib.pyplot as plt
+import h5py
+
+import dedalus.public as de
+from plotpal.file_reader import SingleFiletypePlotter as SFP
+
+
+# Get data from files
+start_file = 1
+n_files = np.inf
+root_dir = '../noslip_erf_Re_cut/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_256x256x256_restart/'
+plotter_slices = SFP(root_dir, file_dir='slices', fig_name='talk_snapshots', start_file=start_file, n_files=n_files, distribution='even')
+plotter_profiles = SFP(root_dir, file_dir='profiles', fig_name='talk_snapshots', start_file=start_file, n_files=n_files, distribution='even')
+
+with h5py.File('{:s}/top_cz/data_top_cz.h5'.format(root_dir), 'r') as f:
+    Ls = f['Ls'][()]
+    L_d09s = f['L_d09s'][()]
+
+# Set up figure subplots
+fig = plt.figure(figsize=(6.5, 2))
+cax_specs = [( 0,   0.92,   0.47,   0.08),
+             ( 0.53, 0.92,   0.47,   0.08)]
+ax_specs = [
+            ( 0,   0,       0.47,   0.8),
+            ( 0.53, 0,      0.47,   0.8),
+            ]
+axs  = [fig.add_axes(spec) for spec in ax_specs]
+caxs = [fig.add_axes(spec) for spec in cax_specs]
+
+Lz = 2
+Lx = Ly = 2*Lz
+nx = ny = nz = 256
+
+# Dedalus domain for interpolation
+x_basis = de.Fourier('x',   nx, interval=[0, Lx], dealias=1)
+z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
+vert_domain = de.Domain([x_basis, z_basis], grid_dtype=np.float64)
+hires_scales = 4
+
+vert_field  = vert_domain.new_field()
+
+#x_shift = 1
+x = vert_domain.grid(0, scales=hires_scales)
+#x -= x_shift
+#x[x < 0] += Lx
+count = 0
+zz_tb, xx_tb = np.meshgrid(vert_domain.grid(-1, scales=hires_scales), x)
+if not plotter_slices.idle:
[…]

### 2021-07-03 manuscript/ms.tex
adds some changes to theory section of ms.

@@
 \end{equation}
-Eqn.~\ref{eqn:integral_constraint} is the simple expression of \citet{roxburgh1989}'s integral constraint (is it?), and is the straightforward statement that work by buoyancy in the convection zone on large scales must be balanced by viscous dissipation on small scales.
+Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative convection by \citet{roxburgh1989}.
+Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
 We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
@@
 Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of energy are on the RHS.
-We see that the size of the PZ is set by some combination of buoyancy breaking and viscous dissipation, whose total effect cancels out any remaining work that dissipation in the convection zone did not itself cancel.
-we now find it instructive to define the fraction of the buoyant engine consumed by dissipation in the convection zone
+We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking, whose total effect cancels out any remaining work that dissipation in the convection zone did not itself cancel.
+we now find it instructive to parameterize the fraction of the buoyant engine consumed by CZ dissipation  
 \begin{equation}
-f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz},
+f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
 \label{eqn:f_defn}
 \end{equation}
-and note two interesting limits,
+Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
+\begin{equation}
+\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+= 1 - f,
+\label{eqn:first_pz_parameterization}
+\end{equation}
+and we can immediately read off limits on a hypothetical PZ according to $f$,
 \begin{enumerate}
 \item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
-It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:constraint_cz_pz_split} states that the PZ must be large enough to cancel out all of the buoyant work done by convection in the CZ by buoyancy breaking in the PZ.
+It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
-\item In the limit that $f \rightarrow 1$, viscous dissipation is extremely efficient in the convection zone and cancels out all of the work done by buoyancy.
+\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
 This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
-Per Eqn.~\ref{eqn:constraint_cz_pz_split}, the positive definite PZ terms must approach zero and no PZ develops in this limit.
+Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
 \end{enumerate}
 In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
-Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see Fig.~\ref{fig:theory_profiles}, right panel).
+Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).
 
-In order to say more about the size of the penetration layer, we model $\bar{\Phi}$ as a linearly decreasing function of height in the PZ.
-We sets its value at the top of the PZ equal to the average of $\bar{\Phi}$ in the CZ of depth $L_{\rm{CZ}}$ so that $\int_{\rm{PZ}} \bar{\Phi}\,dz = (\delp/[2 L_{\rm{CZ}}])\int_{\rm{CZ}}\bar{\Phi}\,dz$ where $\delp$ is the penetration zone depth.
-Rearranging Eqn.~\ref{eqn:constraint_cz_pz_split} and dividing by $\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz$, and plugging in $\bar{\mathcal{B}} = |\alpha|g\bar{\Fconv}$, we can write
+Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
 \begin{equation}
--\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\frac{\delp}{2 L_{\rm{CZ}}}
-\approx (1 - f).
+\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
+\end{equation}
+Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
+In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
+The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and the in which $\bar{\Phi}$ does not decline with height produces $\xi = 1$.
+Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
+With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
+\begin{equation}
+-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
+= (1 - f).
 \label{eqn:theory_fraction}
@@
 \begin{equation}
-\frac{\delp}{L_{\rm{CZ}}} \approx \mP_D \frac{1 - f}{1 + \mP_D f / 2}.
+\frac{\delp}{L_{\rm{CZ}}} = \mP_D \frac{1 - f}{1 + \xi f \mP_D}.
 \label{eqn:discontinuous_prediction}
@@
 \begin{equation}
-\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)} \,\,(\sqrt{\xi^2 + 1} - \xi),
+\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)} \,\,(\sqrt{\zeta^2 + 1} - \zeta),
 \label{eqn:linear_prediction}
 \end{equation}
-where $\xi \equiv (f/4)\sqrt{\mP_L/(1-f)}$.
+where $\zeta \equiv (\xi f/2)\sqrt{\mP_L/(1-f)}$.
 So we expect the penetration depth to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
@@
 \begin{equation}
-\mS \equiv \frac{N^2}{f_{\rm{conv}}} \approx N^2,
+\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
 \end{equation}

### 2021-07-07 manuscript/ms.tex
lots of MS updates, not quite a co-author draft

@@
 This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
-Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
+Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, bergemann_serenelli_2014, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
 There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
@@
 
-A few flux-based theories of convective penetration have been historically considered.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
+There are hints in the literature that convective penetration may be dependent upon energy fluxes.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts and upper limit on the size of a penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
@@
 
-In this work, we design two numerical experiments to test \citet{zahn1991}'s idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
-We use a modified incompressible, Boussinesq model to study the simplest possible system, and use \citet{roxburgh1989}'s constraint to derive a theory analogous to \citet{zahn1991}'s in this simplified limit.
+In this work, we design two numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+We use a modified incompressible, Boussinesq model to study the simplest possible system, and derive theoretical predictions for the size of the penetrative zone.
+We test this theory using 3D numerical simulations.
 \begin{quote}
@@
 We present these findings as follows.
-In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration similar to \citet{zahn1991}'s, and retrieve predictions for our two experimental designs from that theory.
+In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and retrieve predictions for our two experimental designs from that theory.
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
@@
 Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, and the adiabatic temperature gradient $\gradad$.
 We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
-We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
-The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
-The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
-Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
+The addition of a nonzero $\gradad$ to the standard Boussinesq equations was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
+In this work, we have modified the equations one step further to better model stellar environments and allow for a height-dependent radiative gradient $\gradrad$.
+We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
+As a result, we define $\gradrad \equiv F / k$, where $F$ is the total flux being carried by the system.
+In this model, the classic thermal diffusion term $\chi \grad^2 T'$ carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
+Crucially, we allow the mean temperature profile $\bar{T}$ which sets $\Frad$ and $T'$ to self-consistently evolve with time according to Eqn.~\ref{eqn:temperature}.
 
-Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
+In this work, we will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
+We will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
+Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
@@
 \int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
+\label{eqn:xi_defn}
 \end{equation}
@@
 Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
-
-%where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
-%It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
-%However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
-%Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
-%\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.
-%
-%We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
-%Following Eqn.~\ref{eqn:ke_averages}, we write
-%\begin{equation}
-%\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
-%\label{eqn:flux_breakup}
-%\end{equation}
-%Rearranging, we retrieve 
-%\begin{equation}
-%\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
-%\qquad\rm{with}\qquad
-%f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
-%= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
-%\label{eqn:preliminary_flux_ratio}
-%\end{equation}
-%where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
-%The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
-%We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
-%If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
-%In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.
+Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
+When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
+When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
+When $\mP \sim 1$, both terms matter.
 
@@
 L_s + \delta_{h} = \rm{max}(z) \mid \justgrad > \gradad - h\,\Delta\justgrad.
+\label{eqn:delta_p_measures}
 \end{equation}
@@
 \caption{
-(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$), normalized by the appropriate convection zone height $\tilde{L_s}$ in our simulations.
-(Left middle panel) Shown is the average value of $(\justgrad - \gradrad)/\gradrad$, averaged over the full domain above $\delta_{0.5}$, as a function of time.
-This provides a measure of how far out of thermal equilibrium the RZ is above the PZ, and should trend towards zero in the long-time limit.
-(Left bottom panel) Shown is a rolling average over 50 freefall times of the dissipation constant $f$, defined in Eqn.~\ref{eqn:preliminary_flux_ratio}.
-The vertical lines in the top and bottom panels correspond to when that measure has converged to within 1\% of its final value, where the final value is the mean taken over the last 500 freefall times of evolution shown in these plots.
+(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
+We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
+The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
 (Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
@@
 The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
-The departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
+The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
+The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
 \label{fig:time_evolution}
@@
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions set $\justgrad = \gradad$ in the convection zone ($z < 1$) and $\justgrad = \gradrad$ in the radiative zone ($z > 1)$.
-In the top left panel, we display the extent of the penetrative region\footnote{$\tilde{L_s} = 0.8L_s$.
-Our choice of internal heating function (Eqn.~\ref{eqn:sim_Q}) means that the integral of $\int\Fconv$ in the convection zone is 80\% what it would be if the full $z < L_s$ region carried the full flux $F_H$, and we must appropriately account for this when measuring the overshoot depth according to Eqn.~\ref{eqn:theory_fraction}.} vs time, $\delta_{\rm{0.5}}/\tilde{L_s}$.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes thousands of freefall times.
-The steepening of $\justgrad\rightarrow\gradad$ in the growing penetrative region corresponds to a flattening of $\justgrad < \gradrad$ in the RZ above the PZ, which can be seen in the left-middle panel of Fig.~\ref{fig:time_evolution}.
-In the bottom left panel of Fig.~\ref{fig:time_evolution}, we show a rolling average over 50 freefall times of the volume-averaged vorticity-based value of $f$ from Eqn.~\ref{eqn:preliminary_flux_ratio}.
-Unlike the thermal stratification, this value quickly reaches a value close to its final value; for comparison, we plot grey vertical lines in the top and bottom panels of Fig.~\ref{fig:time_evolution} to indicate when each of those quantities converges to its average sampled over the last 500 freefall times displayed in that plot; we see that the dynamics converge rapidly but that the restratification is slow.
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
+In the top left panel, we display the extent of the penetrative region vs.~time, $\delta_{\rm{0.5}}$.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
+We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$2.5 million cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution (see appendix \ref{app:accelerated_evolution} for details) for the bulk of the simulations in this work.
+
+The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
+We plot the rolling mean, averaged over 1000 freefall time units. 
+We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
+We quantify this by plotting a vertical line in each of the left three panels which corresponds to the first time in which the time-evolving average converges to within 1\% of the mean final value (calculated over the last 1000 freefall times of the simulation and plotted as a grey horizontal line).
+
 In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
-$\gradad$ is plotted as a dashed line while $\gradrad$ is plotted as a grey solid line.
+$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
+We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries \citep[as studied in e.g.,][]{horst_etal_2021}.
 The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We can see that the initial (fast) evolution establishes a sizeable PZ, but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
-This occurs in part because the flattening of $\justgrad < \gradrad$ above the convection zone effectively increases the value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
+We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
+This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
 
@@
 \caption{
-Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
+Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
 In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
@@
 
-In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 3.2 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ in an equilibrated state.
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state.
 We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
@@
 
-\subsection{Measured penetration zone scalings}
+\subsection{Dependence on $\mP$}
 
-In Fig.~\ref{fig:erf_3D_penetration_depths}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$) from Case I (discontinuous $k$) simulations.
-In the left panel we plot the predicted scaling with $\mP_D$ from Eqn.~\ref{eqn:discontinuous_prediction} as well as the measured penetration depths from our simulations.
-We find good agreement with the theory, and at large values of $\mP_D$ find equilibrated states in which the PZ is roughly the same size as the nominal convection zone.
-%We find that the value of $\mP_D$ is the primary parameter whose value modifies the extent of the PZ.
-While not presented in this work, we performed limited 2D simulations and found similar scalings, but with larger penetration zones for the same parameters in 2D than in 3D.
-This signifies that $f$, and thus the viscous dissipation, is smaller in 2D than in 3D; we speculate that this is a consequence of the inverse turbulent cascade in 2D.
+We find that the depth of the penetration zone is strongly dependent on $\mP$.
+In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
+We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
+At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (See e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution}).
+At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.
+
+In the middle and bottom panels of Fig.~\ref{fig:parameters_vs_p}, we plot average values of $f$ (middle panels) and $\xi$ (bottom panels) from our theory.
+These values are respectively defined in Eqns.~\ref{eqn:f_defn} \& \ref{eqn:xi_defn}.
+We find that $f$ has slightly smaller values in the discontinuous-$k$ simulations (left) than in the discontinuous-$\partial_z k$ simulations (right).
+We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
+In general we find a trend in which $f$ and $\xi$ are weakly inversely proportional to $\mP$ in some way.
+This likely relates to the changing nature of the PZ as a function of $\mP$.
+When $\mP \ll 1$, $\delp \rightarrow 0$ and the PZ is essentially an abrupt boundary layer at the top of the CZ.
+Convective motions run into an abrupt wall and fall off sharply, leading to higher values of $\xi$.
+This wall-like nature of the PZ pushes flows sideways and we find that the changes in $f$ can largely be explained by increased velocities within the CZ as $\mP$ decreases.
+In the case whree $\mP \gg 1$, $\delp$ becomes large and the PZ becomes similar in nature to the one shown in Fig.~\ref{fig:vertical_dynamics_panels}.
+Here the PZ acts as a large extension of the convection zone in which convective motions slowly brake under their own buoyancy.
+$\xi$ decreases in value as the dissipation profile falls off smoothly with height and $f$ decreases in value as the dynamics in the PZ become dominated by dissipation.
+(TODO: think about this more)
 
@@
 \centering
-\includegraphics[width=\textwidth]{erf_3D_penetration_depths.pdf}
+\includegraphics[width=\textwidth]{parameters_vs_p.pdf}
 \caption{
-Shown are penetration depths against (left) $\mP_D$, (center) $\mR$, and (right) $\mS$.
-Up-triangles signify $\delta_{0.1}$, down-triangle signify $\delta_{0.9}$, and circles signify $\delta_{0.5}$.
-In all panels, we plot a line corresponding to the theory of Eqn.~\ref{eqn:discontinuous_prediction}, with $f = 0.875$ and under the assumption that $f$ does not vary.
-The penetration depth is a nearly linear function of $\mP_D$, in good agreement with the theory.
-The black horizontal lines in the left panel represent the full vertical range of the right two panels; the effects of varying $\mS$ and $\mR$ are secondary to that of $\mP$.
-In the center panel, we see that the penetration depth increases at low $\mR$ as laminar dynamics give way to time-evolving dynamics.
-As we increase the turbulence, the penetration depth decreases weakly and appears to asymptote in the turbulent regime.
-In the right panel, we see that the width of the transition region $\delta_{0.9} - \delta_{0.1}$, is strongly related to the stiffness.
-\label{fig:erf_3D_penetration_depths}
+Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (Left, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (Right, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}).
+The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
+The discontinuous penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
+The discontinuous-gradient penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
+In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
+We generally find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration depths.
+In the bottom panels, we measure the evolved values of $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
+We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
+\label{fig:parameters_vs_p}
 }
@@
 
-In the center and rightmost panels of Fig.~\ref{fig:erf_3D_penetration_depths}, we focus on modifications to the measured penetration depths achieved by varying $\mR$ (turbulence) and $\mS$ (stiffness).
-We find that the penetration depth is smaller at very low (laminar) values of $\mR$ and at high (turbulent) values of $\mR$, with a peak at moderate values (for which dynamics are interesting and non-stationary, but not as turbulent as e.g., Fig.~\ref{fig:vertical_dynamics_panels}).
-Our data suggest that the penetration depth, and thus the viscous dissipation, asymptotes as $\mR$ increases and so our results should be relevant for the astrophysical case in which $\mR \rightarrow \infty$ (COAUTHOR NOTE: high-$\mR$ and $\mS$ data is still preliminary, but I think that the general trends are right).
-We find that mean penetration depth shows little dependence on the stiffness.
-However, the depth of the transition region from the PZ to the RZ, which can be measured as $\delta_{0.9} - \delta_{0.1}$, shows a strong dependence on stiffness.
-In stars, the stiffness is roughly determined by the Mach number ($\rm{Ma}^{-2} \sim \mS$), so for low-Mach stellar flows, the PZ-RZ boundary can likely be reasonably approximated as a step function in $\justgrad$.
+\subsection{Dependence on $\mS$}
+
+We find that the depth of the penetration zone is weakly dependent on $\mS$.
+In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
+We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
+In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ becomes smaller.
+To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
+We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
+This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
+
+We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
+As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$.
 
@@
 \centering
-\includegraphics{linear_3D_penetration_depths.pdf}
+\includegraphics{parameters_vs_s.pdf}
 \caption{
-Similar to Fig.~\ref{fig:erf_3D_penetration_depths}, but for the Case II ``linear'' simulations where the slope of $k$ is discontinuous at the Schwarzschild point.
-We plot an orange line corresponding to the theory of Eqn.~\ref{eqn:linear_prediction} with $f = 0.925$ as well as up-triangles ($\delta_{0.1}$), down-triangle ($\delta_{0.9}$), and circles ($\delta_{0.5}$).
-We find that the theory describes our simulation measurements well.
-\label{fig:linear_3D_penetration_depths}
+(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
+While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
+(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
+We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
+\label{fig:parameters_vs_s}
 }
@@
 
-Finally, in Fig.~\ref{fig:linear_3D_penetration_depths}, we plot penetration depths as a function of $\mP_L$ for the ``linear'' Case II simulations.
-We compare these depths to the theory of Eqn.~\ref{eqn:linear_prediction}.
-We hold $\mR = 800$ and $\mS = 10^3$ constant for these simulations.
-As in the discontinuous simulations, we find excellent agreement between the simulations and the theory.
+\subsection{Dependence on $\mR$}
 
-Our simulation results present a strong case for the validity of \citet{roxburgh1989}'s integral constraint and \citet{zahn1991}'s theory of the importance of the slope of the radiative gradient near the boundary.
-The generalized Eqn.~\ref{eqn:theory_fraction}, and its solution for our simulation setups in Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction}, describe our data well.
-In addition to the flux-based penetration parameter $\mP$, Eqn.~\ref{eqn:theory_fraction} depends only on a quantity related to the volume-average magnitude of the viscous dissipation comapred to the convective flux in the Schwarzschild-unstable convection zone ($f$).
-In this work, from the theory lines plotted in Figs.~\ref{fig:erf_3D_penetration_depths} \& \ref{fig:linear_3D_penetration_depths}, we find
+We find that the depth of the penetration zone is weakly dependent on $\mR$.
+In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth $\delta_{0.5}$ with the Reynolds number.
+In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
+We find that $f$ increases with increases $\mR$, but is perhaps leveling off.
+We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
+Indeed, we see in the bottom left panel that this variation of $\delp$ with $\mR$ can equally be seen as a variation of $\delp$ with $f$.
+We find that this is true both for simulations with stress-free lower boundary (open symbols, SF) and for no-slip lower boundaries (closed symbols, NS).
+
+In order to understand this better, we note that, at least in the SF simulations, the dissipation can roughly be modeled as a constant value in the CZ and zero in the viscous boundary layer (in the NS case, the dissipation becomes a maximum in the boundary layer).
+This means that we can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
 \begin{equation}
-f \approx 0.875\,\,(\text{Case I: Discontinuous}),\qquad
-f \approx 0.925\,\,(\text{Case II: Linear}).
-\label{eqn:fit_f_values}
+\int \bar{\Phi} dz = C ( L_s - \delta_\nu ),
 \end{equation}
-In both cases, $f$ is a parameter of order 0.9.
-With these results as an initial guess for the magnitude of $f$, Eqn.~\ref{eqn:theory_fraction} can be straightforwardly used to implement these penetrative zones in a 1D stellar structure code.
+where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
+In other words, under this model, we expect the dissipation, and thus $f$, to vary linearly with the viscous boundary layer depth.
+Indeed, we find this to roughly be the case for the stress-free simulations in the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}.
+We find that the NS simulations show a more complex increase as $\delta_\nu \rightarrow 0$ due to the fact that dissipation is maximized in the boundary layer and its magnitude there varies with $\mR$.
+Regardless, we find that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection \citep{ahlers_etal_2009, goluskin2016}, as shown in the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, and so we anticipate that the value of $f$ should saturate as $\mR$ increases into the astrophysical regime.
+
+Unfortunately, we are limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}), so we cannot extend our study to more turbulent simulations and higher values of $\mR$ than the ones shown here.
+We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
+However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- give us hope that PZ depths should saturate at high $\mR$.
+
+\begin{figure}[t!]
+\centering
+\includegraphics{parameters_vs_re.pdf}
+\caption{
+(Upper left panel) Penetration depths are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
+We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
+In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
+(Upper middle panel) We similarly see increases in the value of $f$ with $\mR$, although perhaps this measurement is leveling off at high values of $\mR$.
+(Upper right panel) We do not see large changes in the value of $\xi$ as $\mR$ increases, suggesting that the nature of dissipation in the PZ is not appreciably changing.
+(Lower left panel) In summary, we see a strong correlation between $\delta_{0.5}$ and $f$.
+(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\delta_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
+This makes sense, as more of the convective domain is available for the convective flows to dissipate energy.
+(Lower right panel) The viscous boundary layer follows a classical scaling laws seen in Rayleigh-B\'{e}nard convection, and so we anticipate that the trend in $\delta_{0.5}$ vs $\mR$ should saturate as $\delta_{\nu} \rightarrow 0$ and $f$ saturates.
+\label{fig:parameters_vs_re}
+}
+\end{figure}
 
@@
 \label{sec:solar_model}
-We now examine briefly how our theory modifies a simple structure model of the Sun.
-We implement a simple prescription of convective penetration in MESA \citep{paxton_etal_2013} as follows:
-\begin{enumerate}
-\item Find the radial location of the radiative-convective boundary according to the Schwarzschild criterion, $r_{\rm{RCB}}$.
-Also evaluate the value of the mixing length $\ell$ at that location.
-\item Integrate the magnitude of the convective luminosity within the convection zone, $L_{\rm{CZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
-\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_f_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
-We determine the value of $\delp$ according to Eqn.~\ref{eqn:theory_fraction} so that
+Our simulation results present a strong case for the validity of a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
+In general, out of the simulations presented in this work, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
+In this simulation, we found $f \approx 0.8$ and $\xi \approx 0.6$; the results of Fig.~\ref{fig:parameters_vs_re} suggest that $f$ could increase by $\sim 0.1$ as $\mR$ increases into the stellar regime but $\xi$ probably doesn't change much.
+As such, we take $f \approx 0.9$ and $\xi \approx 0.6$ as first-guess values for our theory of convective penetration in stellar regimes.
+These values should of course be confirmed and tuned in more realistic stellar settings which include spherical geometry and realistic density stratifications.
+
+In spherical geometry, if the horizontal averages of Eqn.~\ref{eqn:integral_constraint} are replaced with horizontal averages, the relevant integral constraint for convective penetration can be described in terms of the convective luminosity,
 \begin{equation}
-L_{\rm{PZ}} = (1 - f)L_{\rm{CZ}},
-\label{eqn:mesa_equation}
+\int |\alpha| g L_{\rm{conv}}\,dr =   \int 4\pi \rho_0 r^2\bar{\Phi}\,dr,
 \end{equation}
-with an initial guess of $f = 0.9$.
-\item Override the value of $\justgrad$ in the MESA solver to set $\justgrad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
-\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_{\rm{PZ}}$.
-\end{enumerate}
+where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$ and $r$ is the radial coordinate.
+Following the same logic as Sct.~\ref{sec:theory}, the equivalent of Eqn.~\ref{eqn:theory_frac} is
+\begin{equation}
+-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{(1 + [\delp/r_s])^3 - 1}{1 - (r_{\rm{CZ}}/r_s)^3} = (1 - f),
+\end{equation}
+where the CZ integral is taken from $r_{\rm{CZ}}$ to $r_s$ and the PZ integral is taken from $r_s$ to $r_s + \delp$, and the extra factors in the $\xi$ term come from accounting for spherical geometry.
+Linearly truncating a Taylor expansion of this geometric term around $\delp/r_s \approx 0$, we retrieve
+\begin{equation}
+-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + 3 f \xi \frac{\delp}{r_s}(1 - [r_{\rm{CZ}}/r_s]^3)^{-1} \approx (1 - f).
+\label{eqn:mesa_eqn}
+\end{equation}
+In the case of solar convection, $r_{\rm{CZ}} = R_{\odot}$, $r_s \approx 0.7R_{\odot}$ (the Schwarzschild-defined bottom of the CZ), and $\delp$ is some (negative) value so that the penetration zone ends at $r_s + \delp$.
+
+We ran a MESA solar model using Eqn.~\ref{eqn:mesa_eqn} with $f = 0.9$ and $\xi = 0.6$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
+The details of this implementation are laid out in Appendix \ref{app:mesa}.
+We of course note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
+We present this as a proof of concept and to inspire further work.
+
+In Fig.~\ref{} we display the profile of X quantity at the base of a solar model using a penetrative zone (as described above) and using X classical prescription.
+Note the differences in this thing and that thing.
 
@@
 We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
-This results in a discontinuous temperature profile, which would result in an acoustic ``glitch'' on the solar frequencies.
 Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which is smaller than what is found in our model \citep[see e.g., section 7.2.1 of][]{basu2016}.
 However, our results here are in line with the recent simulations of \citet{kapyla2019}, which suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
+We hope to improve this model and stuff in future work, please hang out with us and make it better.
 
@@
 \label{sec:discussion}
-In this work, we used \citet{roxburgh1989}'s integral constraint and flux-based argument analagous to \citet{zahn1991}'s theory to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
-We designed and analyzed two sets of simulations which showed good agreement with that theoretical parameterization.
+In this work, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these parameters and a new flux-based ``penetration parameter'' $\mP$.
+We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
 We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
 Our results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
-In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale (the mixing length).
+In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
 
-The simulations we presented in this work were the simplest possible simulations to try to test the basic tenents of \citet{roxburgh1989} and \citet{zahn1991}'s theory.
-In particular, they demonstrate that indeed the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
-The precise value of $f$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from the value of $f \approx 0.9$ measured in this work.
-Future work should aim to determine how much the values in Eqn.~\ref{eqn:fit_f_values} vary when these more realistic effects are taken into account.
+The simulations we presented in this work were the simplest possible simulations to try to test the basic tenets of our theory.
+In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
+The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} here.
+Future work should aim to understand how these parameters change when these realistic effects are taken into account.
 
 Furthermore, it is important to note that stellar opacities, and thus stellar conductivities, are functions of thermodynamic variables rather than radial location.
-As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep a penetration zone should form.
+As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep the penetration zone should be.
 Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
@@
 An additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
-Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$.
+Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$ and $\xi$.
 Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
-Future work should aim to understand whether $f$ depends strongly on $\Pran$ in the turbulent regime.
+Future work should aim to understand whether $f$ and $\xi$ depend strongly on $\Pran$ in the turbulent regime.
 
@@
 In the rapidly rotating limit, rotation creates quasi-two-dimensional flows, which could affect the length scales on which dissipation acts and thus modify $f$.
-Furthermore, magnetism adds an additional ohmic dissipation term, which could in theory drastically change our hydrodynamical measurement of $f \approx 0.9$.
+Furthermore, magnetism adds an additional ohmic dissipation term, which could in theory drastically change our hydrodynamical measurement of $f$.
 
@@
 \begin{acknowledgments}
-We'd like to thank Keaton Burns and Kyle Augustson for useful discussions which improved the content of this manuscript.
+We'd like to thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
 TODO thank Nordita program.
@@
 
+\section{MESA implementation}
+\label{app:mesa}
+We now examine briefly how our theory modifies a simple structure model of the Sun.
+We implement a simple prescription of convective penetration in MESA \citep{paxton_etal_2013} as follows:
+\begin{enumerate}
+\item Find the radial location of the radiative-convective boundary according to the Schwarzschild criterion, $r_{\rm{RCB}}$.
+Also evaluate the value of the mixing length $\ell$ at that location.
+\item Integrate the magnitude of the convective luminosity within the convection zone, $L_{\rm{CZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
+\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_f_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
+We determine the value of $\delp$ according to Eqn.~\ref{eqn:theory_fraction} so that
+\begin{equation}
+L_{\rm{PZ}} = (1 - f)L_{\rm{CZ}},
+\label{eqn:mesa_equation}
+\end{equation}
+with an initial guess of $f = 0.9$.
+\item Override the value of $\justgrad$ in the MESA solver to set $\justgrad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
+\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_{\rm{PZ}}$.
+\end{enumerate}
+
 \bibliographystyle{aasjournal}

### 2021-07-08 manuscript/ms.tex
minor manuscript clarifications

@@
 Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, and the adiabatic temperature gradient $\gradad$.
-We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
-The addition of a nonzero $\gradad$ to the standard Boussinesq equations was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
-In this work, we have modified the equations one step further to better model stellar environments and allow for a height-dependent radiative gradient $\gradrad$.
-We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
-As a result, we define $\gradrad \equiv F / k$, where $F$ is the total flux being carried by the system.
-In this model, the classic thermal diffusion term $\chi \grad^2 T'$ carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
-Crucially, we allow the mean temperature profile $\bar{T}$ which sets $\Frad$ and $T'$ to self-consistently evolve with time according to Eqn.~\ref{eqn:temperature}.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
+Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
+Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to this equation.
 
-In this work, we will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
-We will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
 Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
@@
 \end{equation}
-where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
-We note that $k$ and the temperature gradient $\justgrad \equiv -\partial_z \bar{T}$ fully specify $\Frad$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
-We define the radiative gradient 
+where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
+We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
+We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
+We define the gradient and radiative gradient 
 \begin{equation}
-\gradrad = \frac{\bar{\Ftot}}{k}
+\justgrad \equiv -\partial_z \bar{T} \qquad
+\gradrad \equiv \frac{\bar{\Ftot}}{k}.
 \label{eqn:gradrad_definition}
 \end{equation}
-and note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.
+We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions.
+Marginal stability is achieved when $\justgrad = \gradad$, a constant.
+We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.
+
+The addition of a nonzero $\gradad$ to Eqn.~\ref{eqn:temperature} was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
+In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
+Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but the same logic applies to the inverted problem.
 
@@
 \end{equation}
-Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative convection by \citet{roxburgh1989}.
+Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
 Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
+
 We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
 We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
-Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too.
+Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
 Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
@@
 \end{equation}
-Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of energy are on the RHS.
-We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking, whose total effect cancels out any remaining work that dissipation in the convection zone did not itself cancel.
-we now find it instructive to parameterize the fraction of the buoyant engine consumed by CZ dissipation  
+Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
+We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
+We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
 \begin{equation}
@@
 In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
-The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and the in which $\bar{\Phi}$ does not decline with height produces $\xi = 1$.
+The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and if $\bar{\Phi}$ does not decline with height then $\xi = 1$.
 Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
@@
 In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
-Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ on various parameters in local simulations.
+Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ and $\xi$ on various parameters in local simulations.
 
@@
 We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
+For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
 
@@
 0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
-|Q_{\rm{mag}}|		& 0.1 \leq z \leq 0.1 + \delta_H
+Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \delta_H
 \end{cases}.
@@
 where $N^2$ is the \brunt$\,$frequency in the radiative zone.
-In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$.
-We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.
+In our nondimensionalization, $N^2 = \gradad - \gradrad$.
+We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\justgrad$, which in turn sets the value of $k$ in the radiative zone.
 
@@
 We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper in which we hold two of these parameters constant and vary the other.
+We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
 We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
@@
 \begin{equation}
-\partial_z k_0 = \frac{\delta_H}{L_s \mS \xi},\qquad
-k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
-\gradad = Q \mS \xi,
+\partial_z k_0 = \frac{\delta_H}{L_s \mS \psi},\qquad
+k_b = \frac{\delta_H\zeta}{\mS\psi},\qquad
+\gradad = Q \mS \psi,
 \end{equation}
-where $\xi \equiv 1 + \mP_L(1 + \zeta)$.
+where $\psi \equiv 1 + \mP_L(1 + \zeta)$.
 In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
@@
 In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and top of the ``thermal adjustment layer.''
+Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ roughly represents the width of the ``thermal adjustment layer.''
 We will simply refer to these as three different measures of the top of the PZ.
@@
 In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
-In the top left panel, we display the extent of the penetrative region vs.~time, $\delta_{\rm{0.5}}$.
+In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
 This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.

### 2021-07-10 manuscript/ms.tex
two-column-ified things and updates to MESA section

@@
 % Preamble
-\documentclass{aastex631}
+\documentclass[twocolumn]{aastex631}
 \usepackage{natbib}
@@
 \begin{abstract}
-Convection is a crucial heat transport and dynamical excitation mechanism in stars.
+Convection is a crucial mechanism for heat transport and dynamical excitation in stars.
 Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
@@
 We use a simplified Boussinesq model of stellar convection with a radiative flux.
-We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the convective boundary.
+We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
 Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
 We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
-In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20-30\% of a mixing length.
-We present a MESA solar model which uses our parameterization of convective penetration, and find that the base of the solar convection zone extends by (X amount for some choice of parameters).
-We briefly discuss future experiments which could verify and extend these results to stellar contexts.
+In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
+We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
+We briefly discuss future experiments which could verify and extend these results in more realistic stellar contexts.
 \end{abstract}
@@
 We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
+We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
+We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.
 
@@
 \label{sec:theory_energy}
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
@@
 \caption{
-(left) The vertical profile of the kinetic energy fluxes $\mathcal{F}$.
-This profile goes to zero at the bottom boundary, again at the dashed line, and at the top of the PZ near $z \approx 1.5$; Eqn.~\ref{eqn:integral_constraint} holds between any two of these points.
-(middle) the evolved value of $\justgrad$ (green) compared to $\gradad$ (grey) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
-(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$.
+(left) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in a simulation. 
+$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
+Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
+(middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
+(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
 \label{fig:theory_profiles}
 }
-\end{figure}
+\end{figure*}
 
@@
 \begin{equation}
-\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
+%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
+\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
 \int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
@@
 \begin{equation}
-\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
+\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi}\,dz = \xi \delp \Phi_{\rm{CZ}}.
 \label{eqn:xi_defn}
 \end{equation}
-Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
+Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
 In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
@@
 &T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
-\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
-\grad^* = L_s^{-1} \grad,\qquad
-\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
+Q^* = Q_0 Q,
 \\
-&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
-k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
-Q^* = Q_0 Q,\qquad
+&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\,\,\,\,\,
+\grad^* = L_s^{-1} \grad,
+\\
+&\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
+p^* = \rho_0 u_{\rm{ff}}^2\varpi,
+\\
+&k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
 \mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
@@
 \label{eqn:nondim_momentum} \\
-&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
+\begin{split}
+\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}]\qquad\qquad 
+\\
+\qquad\qquad\qquad\qquad\qquad= (\Pran\mR)^{-1}\grad^2 T' + Q.
 \label{eqn:nondim_temperature}
+\end{split}
 \end{align}
@@
 \begin{equation}
-k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
-k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
-\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
+\begin{split}
+k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
+k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\\
+\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\\
 \gradrad = \gradad - Q_{\rm{mag}}\mS.
+\end{split}
 \end{equation}
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
@@
 }
-\end{figure}
+\end{figure*}
 
@@
 The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
-We plot the rolling mean, averaged over 1000 freefall time units. 
+We plot the rolling mean, averaged over 200 freefall time units. 
 We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
-We quantify this by plotting a vertical line in each of the left three panels which corresponds to the first time in which the time-evolving average converges to within 1\% of the mean final value (calculated over the last 1000 freefall times of the simulation and plotted as a grey horizontal line).
+We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
+The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.
 
@@
 
-In spherical geometry, if the horizontal averages of Eqn.~\ref{eqn:integral_constraint} are replaced with horizontal averages, the relevant integral constraint for convective penetration can be described in terms of the convective luminosity,
+In spherical geometry, if the horizontal averages of Eqn.~\ref{eqn:integral_constraint} are replaced with integrals over latitude and longitude, the relevant integral constraint for convective penetration can be described in terms of the convective luminosity,
 \begin{equation}
-\int |\alpha| g L_{\rm{conv}}\,dr =   \int 4\pi \rho_0 r^2\bar{\Phi}\,dr,
+\int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
 \end{equation}
-where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$ and $r$ is the radial coordinate.
-Following the same logic as Sct.~\ref{sec:theory}, the equivalent of Eqn.~\ref{eqn:theory_frac} is
+where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$ $r$ is the radial coordinate and we write the RHS as a volume integral.
+We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
 \begin{equation}
--\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{(1 + [\delp/r_s])^3 - 1}{1 - (r_{\rm{CZ}}/r_s)^3} = (1 - f),
+\int_{\rm{PZ}} \rho_0 \Phi dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi dV,
 \end{equation}
-where the CZ integral is taken from $r_{\rm{CZ}}$ to $r_s$ and the PZ integral is taken from $r_s$ to $r_s + \delp$, and the extra factors in the $\xi$ term come from accounting for spherical geometry.
-Linearly truncating a Taylor expansion of this geometric term around $\delp/r_s \approx 0$, we retrieve
+where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
+This is the generalized version of Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
+A first-guess at the equivalent of Eqn.~\ref{eqn:theory_fraction} in stellar contexts is
 \begin{equation}
--\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + 3 f \xi \frac{\delp}{r_s}(1 - [r_{\rm{CZ}}/r_s]^3)^{-1} \approx (1 - f).
+-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}} = (1 - f),
 \label{eqn:mesa_eqn}
 \end{equation}
-In the case of solar convection, $r_{\rm{CZ}} = R_{\odot}$, $r_s \approx 0.7R_{\odot}$ (the Schwarzschild-defined bottom of the CZ), and $\delp$ is some (negative) value so that the penetration zone ends at $r_s + \delp$.
 
-We ran a MESA solar model using Eqn.~\ref{eqn:mesa_eqn} with $f = 0.9$ and $\xi = 0.6$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
-The details of this implementation are laid out in Appendix \ref{app:mesa}.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.9$ and $\xi = 1$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
+We chose a value of $\xi = 1$ as it is the most conservative choice and should generally result in smaller penetration zones, and because it is unclear how our plane-parallel intuition for $\xi$ in this study maps into spherical geometry.
 We of course note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
@@
 We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
-Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which is smaller than what is found in our model \citep[see e.g., section 7.2.1 of][]{basu2016}.
-However, our results here are in line with the recent simulations of \citet{kapyla2019}, which suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
+Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
+However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
 We hope to improve this model and stuff in future work, please hang out with us and make it better.

### 2021-07-10 manuscript/ms.tex
paper draft basically exists. Need to comb through it.

@@
 \subsection{Numerics}
+\label{sct:numerics}
 We time-evolve equations \ref{eqn:nondim_incompressible}-\ref{eqn:nondim_temperature} using the Dedalus pseudospectral solver \citep{burns_etal_2020}\footnote{we use commit \href{https://github.com/DedalusProject/dedalus/commit/efb13bdaa09816dde3eee897bc2a15fc284ea2f1}{efb13bd}; the closest stable release to this commit is \href{https://github.com/DedalusProject/dedalus/releases/tag/v2.2006}{v2.2006}.} using timestepper SBDF2 \citep{wang&ruuth2008} and safety factor 0.35.
@@
 \caption{
-(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
+(Left top panel) Displayed is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
 We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
@@
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
-In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
-We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$2.5 million cpu-hours.
-It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution (see appendix \ref{app:accelerated_evolution} for details) for the bulk of the simulations in this work.
-
-The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
-We plot the rolling mean, averaged over 200 freefall time units. 
-We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
-We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
-The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.
-
-In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
-$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
-The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
-We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries \citep[as studied in e.g.,][]{horst_etal_2021}.
-The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
-This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
-
-\begin{figure*}[t!]
+\begin{figure*}[t]
 \centering
@@
 
-In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state.
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
+In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
+We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution of the bulk of the simulations in this work (see Appendix \ref{app:accelerated_evolution} for details).
+
+The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
+We plot the rolling mean, averaged over 200 freefall time units. 
+We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
+We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
+The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.
+
+In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
+$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
+We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
+
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
 We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
 Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
-On the right, we see that hot upwellings in the convective dynamics are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
+On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
 These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.
@@
 \subsection{Dependence on $\mP$}
-
-We find that the depth of the penetration zone is strongly dependent on $\mP$.
-In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
-We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
-At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (See e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution}).
-At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.
-
-In the middle and bottom panels of Fig.~\ref{fig:parameters_vs_p}, we plot average values of $f$ (middle panels) and $\xi$ (bottom panels) from our theory.
-These values are respectively defined in Eqns.~\ref{eqn:f_defn} \& \ref{eqn:xi_defn}.
-We find that $f$ has slightly smaller values in the discontinuous-$k$ simulations (left) than in the discontinuous-$\partial_z k$ simulations (right).
-We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
-In general we find a trend in which $f$ and $\xi$ are weakly inversely proportional to $\mP$ in some way.
-This likely relates to the changing nature of the PZ as a function of $\mP$.
-When $\mP \ll 1$, $\delp \rightarrow 0$ and the PZ is essentially an abrupt boundary layer at the top of the CZ.
-Convective motions run into an abrupt wall and fall off sharply, leading to higher values of $\xi$.
-This wall-like nature of the PZ pushes flows sideways and we find that the changes in $f$ can largely be explained by increased velocities within the CZ as $\mP$ decreases.
-In the case whree $\mP \gg 1$, $\delp$ becomes large and the PZ becomes similar in nature to the one shown in Fig.~\ref{fig:vertical_dynamics_panels}.
-Here the PZ acts as a large extension of the convection zone in which convective motions slowly brake under their own buoyancy.
-$\xi$ decreases in value as the dissipation profile falls off smoothly with height and $f$ decreases in value as the dynamics in the PZ become dominated by dissipation.
-(TODO: think about this more)
-
-\begin{figure*}[t!]
+\begin{figure*}[t]
 \centering
@@
 
+We find that the depth of the penetration zone is strongly dependent on $\mP$.
+In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
+We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
+At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
+At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.
+
+The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that it is reasonable but imprecise to assume that $f$ and $\xi$ are constant as a function of $\mP$.
+We find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
+We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
+Most of the trend of $f$ increasing as $\mP$ decreases can be explained by slight increases in the CZ velocities and corresponding increases in the dissipation.
+We speculate that, as $\mP$ decreases, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) more efficiently deflects convective velocities sideways before they have a chance to buoyantly break, thereby slightly increasing bulk-CZ velocities.
+A similar trend of $\xi$ increasing as $\mP$ decreases can be seen.
+This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
+As the size of the PZ shrinks, dynamics do not have the space to change from their bulk-CZ properties, and so $\xi$ is closer to one.
+
 \subsection{Dependence on $\mS$}
@@
 We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
-In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ becomes smaller.
+In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
 To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
@@
 We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
-As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$.
+As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our turbulent cases.
 
@@
 We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
-Indeed, we see in the bottom left panel that this variation of $\delp$ with $\mR$ can equally be seen as a variation of $\delp$ with $f$.
-We find that this is true both for simulations with stress-free lower boundary (open symbols, SF) and for no-slip lower boundaries (closed symbols, NS).
+Indeed, the variation of $\delp$ with $\mR$ can be seen as a variation of $\delp$ with $f$ in the bottom left panel.
+We find that this is true both for simulations with stress-free dynamical boundary conditions (open symbols, SF) and for no-slip conditions (closed symbols, NS).
 
-In order to understand this better, we note that, at least in the SF simulations, the dissipation can roughly be modeled as a constant value in the CZ and zero in the viscous boundary layer (in the NS case, the dissipation becomes a maximum in the boundary layer).
+In order to understand this better, we note that the dissipation profile can reasonably be approximated as a constant value in the CZ and zero in the bottom viscous boundary layer.
+We have visualized a NS dissipation profile in the right panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
 This means that we can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
 \begin{equation}
-\int \bar{\Phi} dz = C ( L_s - \delta_\nu ),
+\int_{\rm{CZ}} \bar{\Phi} dz = C ( L_s - \delta_\nu ),
 \end{equation}
@@
 In other words, under this model, we expect the dissipation, and thus $f$, to vary linearly with the viscous boundary layer depth.
-Indeed, we find this to roughly be the case for the stress-free simulations in the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}.
-We find that the NS simulations show a more complex increase as $\delta_\nu \rightarrow 0$ due to the fact that dissipation is maximized in the boundary layer and its magnitude there varies with $\mR$.
-Regardless, we find that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection \citep{ahlers_etal_2009, goluskin2016}, as shown in the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, and so we anticipate that the value of $f$ should saturate as $\mR$ increases into the astrophysical regime.
+We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
+In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \propto \delta_\nu$ is a decent description for the SF simulations (NS simulations show an increase at small $\delta_\nu$, but also have maximized dissipation in the bounary layer).
+In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
+If you assume the Nusselt Number dependence on the Rayleigh number is Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
+The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.} \citep{ahlers_etal_2009, goluskin2016}.
+Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $\delta_{0.5}$ to level off as $\mR$ increases to high values in the astrophysical regime.
 
@@
 We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
-However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- give us hope that PZ depths should saturate at high $\mR$.
+However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- suggest that PZ depths should saturate at high $\mR$.
 
@@
 This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
-This same separation of scales is observed in the top and bottom left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
+This same separation of scales is observed in the left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
 
@@
 We also multiply the temperature perturbations and full convective velocity field by $(1 - H(z; 1, 0.05))$.
-This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
+This sets all fluctuations above the nominal Schwarzschild convection zone to zero, thereby avoiding any strange dynamical transients caused by the old dynamics at the radiative-convective boundary (which has moved as a result of this process).
 \end{itemize}
@@
 Additionally, in some simulations, we ensure that this process occurs no more than 25 times.
-This process effectively removes the long diffusive thermal evolution on display in the middle left panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
+This process effectively removes the long diffusive thermal evolution on display in the upper left panel of Fig.~\ref{fig:time_evolution} by immediately setting the mean temperature profile to the radiative profile above the PZ.
 
-In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of $\delp/\tilde{L_s}$ and $\angles{f}$ in the $\mP_D = [1,2,4]$ simulations using black lines.
-We overplot the evolution of simulations which use this accelerated evolution procedure using orange and green lines.
-For the orange-line simulations, we use initial conditions which specify a value of $\delp$ that is smaller than the expected evolved value of $\delp$.
-For the purple-line simulations, we use initial conditions which specify a value of $\delp$ that is larger than the expected evolve value.
+In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of $\delp$ and $f$ in Case I simulations with $\mS = 10^3$, $\mR = 400$, and $\mP_D = [1,2,4]$ simulations using black lines.
+We overplot the evolution of simulations which use this accelerated evolution (AE) procedure using orange and green lines.
+Time units on the x-axis are normalized in terms of the total simulation run time in order to more thoroughly demonstrate the evolutionary differences between standard timestepping and AE.
+However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/8$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
+AE simulations with orange lines start with PZ depths which are much larger than the final depth, while green line solution start with initial PZ depths which are smaller than the expected depth.
 Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
-If these simulations are not in a stationary state after this procedure, we timestep them straightforwardly until we are satisfied that they have converged.
+After converging to within a few percent of the proper penetration zone depth, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
+These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration bfore jumping back towards it in the next iteration.
+If the PZ depth continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the evolution of $\delp$ vs.~time has flattened.
 
@@
 \label{fig:AE_time_figure}
-(top row) Time traces of $\delta_p/\tilde{L_s}$ for simulations which are computed using (black lines) standard timestepping, (green lines) accelerated evolution with large initial values of $\delp$, and (orange lines) accelerated evolution with small initial values of $\delp$.
-Accelerated evolution timesteps can be see as discontinuities in the $\delp/\tilde{L_s}$ trace.
+(top row) Time traces of $\delta_{0.1}$ and $\delta_{0.9}$ for simulations which are computed using (black lines) standard timestepping, (orange lines) accelerated evolution with large initial values of $\delp$, and (green lines) accelerated evolution with small initial values of $\delp$.
+The thin horizontal lines represent the final converged values from the standard timestepping simulations.
+Accelerated evolution timesteps can be see as discontinuities in the $\delp$ trace.
 Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.
-(Bottom row) Same as top row, but where $\angles{f}$ is being shown.
+Time units are normalized by the total run time of the simulation.
+All accelerated evolution simulations were run for $t_{\rm{sim}} = 3000$ freefall times.
+The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), or $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
+The vertical green-and-yellow bars show the total length of the accelerated simulation in terms of the classic simulation; so the vertical lines in the upper right panel show that the accelerated simulation was converged after $\sim$ 5\% of the classic simulation.
+(Bottom row) Same as top row, but where a rolling average of $f$ over 200 freefall times is shown.
 }
 \end{figure*}
+
+\section{MESA implementation}
+\label{app:mesa}
+Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
+We note that this impelementation is likely not universal or robust enough to be used in any stellar model, but it is robust enough to timestep stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
+Future work should improve upon this model.
+
+To find the extent of the penetrative region, we override MESA's TODO routine for writing $\justgrad$ and instead have the solver follow these steps:
+\begin{enumerate}
+\item At each timestep, we find the location of the Schwarzschild convective boundary, $r_s$.
+We measure the value of the mixing length $\lambda$ there, and choose a convection zone length scale $\ell_{\rm{CZ}} = \text{min}(\lambda, L_{\rm{CZ}})$, where $L_{\rm{CZ}}$ is the full depth of the Schwarzschild-unstable convective region.
+We take the ``CZ'' integrals in Eqn.~\ref{eqn:mesa_eqn} to span radially from the Schwarzschild boundary to a depth $\ell_{\rm{CZ}}$ within the convection zone.
+\item We calculate the buoyancy integral $\int_{\rm{CZ}} L_{\rm{conv}} dr$ and the convection zone volume $V_{\rm{CZ}}$.
+\item Starting at the Schwarzschild boundary, we iteratively expand the size of the PZ until Eqn.~\ref{eqn:mesa_eqn} is satisfied.
+For each radial bin $i$ below the convection zone, we calculate $\int_{\rm{PZ},i}L_{\rm{conv}} dr$ and $V_{\rm{PZ},i}$.
+We evaluate the LHS of Eqn.~\ref{eqn:mesa_eqn} using those values.
+If LHS $\geq$ RHS, we assume that the radial coordinate of bin $i$ is the boundary of the penetrative region.
+\item We enforce $\justgrad \approx \gradad$ in the PZ by doing TODO.
+\item We ensure that the transition from the PZ to the RZ is smooth.
+Outside of the PZ, we model $\justgrad$ as TODO.
+\end{enumerate}
+
+Using this procedure with $f = 0.8$ and $\xi = 1$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.
 
@@
 
-\section{MESA implementation}
-\label{app:mesa}
-We now examine briefly how our theory modifies a simple structure model of the Sun.
-We implement a simple prescription of convective penetration in MESA \citep{paxton_etal_2013} as follows:
-\begin{enumerate}
-\item Find the radial location of the radiative-convective boundary according to the Schwarzschild criterion, $r_{\rm{RCB}}$.
-Also evaluate the value of the mixing length $\ell$ at that location.
-\item Integrate the magnitude of the convective luminosity within the convection zone, $L_{\rm{CZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \ell} L_{\rm{conv}} dr$.
-\item Following Eqn.~\ref{eqn:theory_fraction} and the measured values for $f$ in Eqn.~\ref{eqn:fit_f_values}, integrate $L_{\rm{PZ}} = \int_{r_{\rm{RCB}}}^{r_{\rm{RCB}} + \delp} (L_{\rm{rad}} - L_{\rm{rad,ad}}) dr$, where $L_{\rm{rad}}$ is the radiative luminosity carried by $\gradrad$ and $L_{\rm{rad,ad}}$ is the radiative luminosity carried by $\gradad$.
-We determine the value of $\delp$ according to Eqn.~\ref{eqn:theory_fraction} so that
-\begin{equation}
-L_{\rm{PZ}} = (1 - f)L_{\rm{CZ}},
-\label{eqn:mesa_equation}
-\end{equation}
-with an initial guess of $f = 0.9$.
-\item Override the value of $\justgrad$ in the MESA solver to set $\justgrad = \gradad$ from $r_{\rm{RCB}}$ to $r_{\rm{RCB}} - \delta_p$.
-\item Mix within this new convection zone by setting the convective velocities according to the average convective luminosity in the penetration zone, $4\pi r^2 \rho v^3 \sim L_{\rm{PZ}}$.
-\end{enumerate}
-
 \bibliographystyle{aasjournal}

### 2021-07-10 data/plot_AE_fig.py

@@ -86,6 +86,7 @@ for d in dirs:
     L_d05 = data[d][8]
     L_d09 = data[d][9]
     f_theory    = data[d][10]
+    xi_theory    = data[d][11]
     Ls = data[d][-1]
     N_skip = 0
 
@@ -182,6 +183,7 @@ for d in dirs:
             ax5.axhline(np.mean((L_d01-Ls)[-1000:]), c='k', lw=0.5)
             ax5.axhline(np.mean((L_d09-Ls)[-1000:]), c='k', lw=0.5)
             ax6.axhline(np.mean(f_theory[-1000:]), c='k', lw=0.5)
+            print('f', np.mean(f_theory[-1000:]), 'xi', np.mean(xi_theory[-1000:]))
     data_chunks.append((P, t_sim, 'schwarzschild' in d, color))
 
 for P, ax in zip([1, 2, 4], [ax1, ax3, ax5]):
@@ -198,8 +200,8 @@ for P, ax in zip([1, 2, 4], [ax1, ax3, ax5]):
                 zorder = 1
             ax.axvline(c[1]/schwarz_time, c=c[3], lw=lw, zorder=zorder)
 
-
-
+for c in data_chunks:
+    print(c)
             
             
 
@@ -223,7 +225,7 @@ for ax in [ax4, ax6]:
 
 ax5.yaxis.set_ticks_position('right')
 ax1.set_ylabel(r'$\delta_{\rm{p}}$')
-ax2.set_ylabel(r'$\langle \frac{\omega^2}{\mathcal{R}} \rangle_{\rm{CZ}}$')
+ax2.set_ylabel(r'$f$')
 
 ax1.text(0.50, 0.85, r'$\mathcal{P}_D = 1$', transform=ax1.transAxes, ha='center')
 ax3.text(0.50, 0.85, r'$\mathcal{P}_D = 2$', transform=ax3.transAxes, ha='center')

### 2021-07-10 data/plot_results_vs_p.py

@@ -27,6 +27,7 @@ for d in dirs:
         modern_f = f['modern_f'][()]
         modern_xi = f['modern_xi'][()]
         fconv_Ls = f['fconv_Ls'][()]
+        vel_rms = f['vel_cz'][()]
         Ls = np.mean(f['Ls'][()])
         tot_time = times[-1] - times[0]
         time_window = np.min((500, tot_time/2))
@@ -37,12 +38,13 @@ for d in dirs:
         mean_f  = np.mean(modern_f[good_times])
         mean_xi = np.mean(modern_xi[good_times])
         mean_fconv_Ls = np.mean(fconv_Ls[good_times])
+        mean_vel_rms = np.mean(vel_rms[good_times])
     if 'erf' in d:
         erf = True
     else:
         erf = False
 
-    data.append((S, P, Re, Ls, Lz, erf, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, mean_xi, mean_fconv_Ls))
+    data.append((S, P, Re, Ls, Lz, erf, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, mean_xi, mean_fconv_Ls, mean_vel_rms))
 data = np.array(data)
 
 S = data[:,0]
@@ -58,6 +60,7 @@ L_d09 = data[:,8]
 theory_f  = data[:,9]
 theory_xi = data[:,10]
 fconv_Ls = data[:,11]
+vel_rms  = data[:,12]
 
 fig = plt.figure(figsize=(page_width, 2*page_width/(3*golden_ratio)))
 
@@ -67,9 +70,6 @@ ax1_1 = fig.add_axes([0.00, 0.25, 0.46, 0.25])
 ax1_2 = fig.add_axes([0.00, 0.00, 0.46, 0.25])
 ax2_1 = fig.add_axes([0.54, 0.25, 0.46, 0.25])
 ax2_2 = fig.add_axes([0.54, 0.00, 0.46, 0.25])
-second_plot_lower = 0.45
-second_plot_upper = 0.9
-
 
 good = (erf == 1) * (Re == 4e2) * (S == 1e3) 
 #Lcz_erf = (Ls*(fconv_Ls/(0.2*Ls)))[good]
[…]

### 2021-07-10 data/plot_time_fig.py

@@ -172,6 +172,7 @@ ax4.set_xlabel('z')
 ax4.set_ylabel(r'$\nabla/\nabla_{\rm{ad}}$')
 ax4.yaxis.set_ticks_position('right')
 ax4.yaxis.set_label_position('right')
+ax4.axvline(Ls, c='k', ls='--')
 
 plt.savefig('time_evolution.png', dpi=300, bbox_inches='tight')
 plt.savefig('../manuscript/time_evolution.pdf', dpi=300, bbox_inches='tight')

### 2021-07-10 manuscript/ms.tex
rough readthrough done!

@@
 \newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
-\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
+\newcommand{\Lcz}{\ensuremath{L_{\rm{CZ}}}}
 \newcommand{\mR}{\ensuremath{\mathcal{R}}}
@@
 Convection is a crucial mechanism for heat transport and dynamical excitation in stars.
-Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
-In this paper we examine how convective motions mix the background thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
-We use a simplified Boussinesq model of stellar convection with a radiative flux.
+Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of motions near convective boundaries are not well understood.
+In this paper we examine how convective motions mix thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
 We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
 Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
-We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
+We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
@@
 Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, bergemann_serenelli_2014, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
-There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
+Overshoot parameterizations in massive stars with convective cores must be finely tuned as a function of stellar mass, again suggesting our current parameterizations are missing some physics \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
 Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
 In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
-While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
-In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.
+While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are prohibitively expensive to perform at every timestep in a stellar evolution simulation.
+In order to resolve discrepancies between stellar evolution models and observations, a more complete and \emph{parameterizeable} understanding of convective overshoot is required.
 
 The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
-The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
+The first class is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
 The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
@@
 Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-One parameter which is commonly linked to penetration or overshoot is the ``stiffness'' of the radiative-convective interface; the stiffness is a ratio which states how stable a radiative zone is compared to an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
-Experiments and simulations exhibiting extensive convective penetration in water or other simplified, Boussinesq setups have a long history \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}.
-Some of these recent simplified studies suggest that the penetration depth is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
-Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
+Experiments exhibiting extensive convective penetration have a long history \citep[dating back to e.g.,][]{musman1968, deardorff_etal_1969, moore_weiss_1973}.
+Modern experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
+The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
+Some recent studies in simplified Boussinesq setups suggest that the penetration depth is highly dependent on the stiffness \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
+Many studies of density-stratified convective atmospheres find significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, dietrich_wicht_2018}.
 However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
 Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
-This host of experiments indeed suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
+This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but the precise results of past studies are often contradictory and no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
 
 There are hints in the literature that convective penetration may be dependent upon energy fluxes.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts and upper limit on the size of a penetrative region.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts and upper limit on the size of a theoretical penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
 Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
-Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
-Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
+Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
 In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
@@
 \end{equation}
-We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions.
+We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
 Marginal stability is achieved when $\justgrad = \gradad$, a constant.
@@
 Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
+Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
 (middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
@@
 where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
-We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (which we will represent with $\bar{\,\cdot\,}$ for simplicity).
+We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
 Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
@@
 
-We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
-We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
-Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
+We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
+We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
+Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
 Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
@@
 \begin{equation}
-\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
++ \frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
 = 1 - f,
@@
 \begin{enumerate}
-\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
-It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
+\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
+Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
-\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
-This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
+\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
 Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
+This is mathematically equivalent to standard boundary-driven convection experiments.
 \end{enumerate}
@@
 \end{equation}
-Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
-In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
-The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and if $\bar{\Phi}$ does not decline with height then $\xi = 1$.
-Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
-With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
+Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a measurable parameter bounded by ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
+In words, we assume that $\bar{\Phi}(z = L_s) \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and that $\bar{\Phi}$ decreases with height in the PZ.
+The shape of $\bar{\Phi}$ determines $\xi$; a linear falloff gives $\xi = 1/2$, a quadratic falloff gives $\xi = 2/3$, and $\xi = 1$ assumes no falloff.
+With this parameterization, and $\bar{\mathcal{B}} \propto \bar{\Fconv}$, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
 \begin{equation}
@@
 \end{equation}
-In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
+In order to derive a specific prediction for the PZ depth, one must specify the vertical shape of $\overline{\Fconv}$.
 We will study two cases in this work, laid out below.
-In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
+In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
 \begin{equation}
-\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
+\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
+= -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
 \label{eqn:theory_P_defn}
@@
 When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
-When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
+When $\mP \gg 1$, buoyancy is negligible and dissipation constrains the size of the PZ.
 When $\mP \sim 1$, both terms matter.
@@
 \overline{\Fconv}(z) = \Fcz \begin{cases}
-1			&	z \leq \Lcz,\\
--\mP_D^{-1}  & 	z > \Lcz 
+1			&	z \leq L_s,\\
+-\mP_D^{-1}  & 	z > L_s 
 \end{cases}.
@@
 \begin{equation}
-\frac{\delp}{L_{\rm{CZ}}} = \mP_D \frac{1 - f}{1 + \xi f \mP_D}.
+\frac{\delp}{\Lcz} = \mP_D \frac{1 - f}{1 + \xi f \mP_D}.
 \label{eqn:discontinuous_prediction}
 \end{equation}
-Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is roughly linearly proportional to $\mP_D$ at small $\mP_D$, but saturates due to dissipation at large $\mP_D$.
+Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is roughly linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation at large $\mP_D$.
 Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
@@
 \begin{cases}
-(L_p - z) & z \leq L_p \\
--\mP_L^{-1} (z - L_p) & z > L_p
+(L_s - z) & z \leq L_s \\
+-\mP_L^{-1} (z - L_s) & z > L_s
 \end{cases},
@@
 where $(\partial \Frad / \partial z)|_{\rm{CZ}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
+When $\mP_L = 1$, $\bar{\Fconv}$ is just a linear profile that crosses through zero at $z = L_s$.
 Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux and integrating over $L_{\rm{CZ}}$ in the CZ and $\delp$ in the PZ, we retrieve a quadratic equation.
@@
 \begin{equation}
-\frac{\delp}{L_p} = \sqrt{\mP_L (1 - f)} \,\,(\sqrt{\zeta^2 + 1} - \zeta),
+\frac{\delp}{\Lcz} = \sqrt{\mP_L (1 - f)} \,\,(\sqrt{\zeta^2 + 1} - \zeta),
 \label{eqn:linear_prediction}
@@
 In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
-Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ and $\xi$ on various parameters in local simulations.
+Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the values of $f$ and $\xi$.
 
@@
 For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
-Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
-The dimensionless equations of motion are therefore
+Henceforth, quantities without $*$ (e.g., $T$) are dimensionless.
+The dimensionless equations of motion are
 \label{sec:simulation_details}
@@
 \end{align}
-We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
-We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
-For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
-We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
+We construct a domain in the range $z \in [0, L_z]$ and choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
+We decompose the temperature field into a time-stationary initial background profile and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
+$T_0$ is constructed with $\justgrad = \gradad$ for $z \leq L_s$, and $\justgrad = \gradrad$ above $z > L_s$.
+We impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
+We generally impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
 For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
@@
 We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
-We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \zeta F_H$ and we choose $\zeta = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
+We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
 
-In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
+We expect the average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
 The stiffness is defined,
@@
 where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
-Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
+Leaving $\mS$ and $\mP_D$ as free parameters and requiring that $\gradad$ carries $\Fbot$ at $z = 0$ and that $\gradrad$ carries $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
 \begin{equation}
 \begin{split}
-k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
-k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\\
-\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\\
-\gradrad = \gradad - Q_{\rm{mag}}\mS.
+&k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
+&k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \mu + \mP_D^{-1}},\\
+&\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \mu + \mP_D^{-1}),\\
+&\gradrad = \gradad - Q_{\rm{mag}}\mS.
 \end{split}
@@
 We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
-We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
+%We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
 According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
@@
 \partial_z k_0 = \frac{\delta_H}{L_s \mS \psi},\qquad
-k_b = \frac{\delta_H\zeta}{\mS\psi},\qquad
+k_b = \frac{\delta_H\mu}{\mS\psi},\qquad
 \gradad = Q \mS \psi,
 \end{equation}
-where $\psi \equiv 1 + \mP_L(1 + \zeta)$.
-In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
+where $\psi \equiv 1 + \mP_L(1 + \mu)$.
+%In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
+We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$.
 According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.
@@
 All fields are represented as spectral expansions of $n_z$ Chebyshev coefficients in the vertical ($z$) direction and as ($n_x$,$n_y$) Fourier coefficients in the horizontal ($x$,$y$) directions; our domains are therefore horizontally periodic.
-The aspect ratio of our domains is two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
+We use a domain aspect ratio of two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
 To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
-We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
-All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
+In some simulations we start with $\bar{T} = T_0$, described above, and in others we impose an established penetrative zone in the initial state $\bar{T}$ according to Eqn.~\ref{eqn:initial_grad}.
 
@@
 
+A table describing all of the simulations presented in this work can be found in Appendix~\ref{app:simulation_table}.
+We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
+
 \subsection{Penetration depth measurements}
@@
 \begin{equation}
-L_s + \delta_{h} = \rm{max}(z) \mid \justgrad > \gradad - h\,\Delta\justgrad.
+L_s + \delta_{h} = \rm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta\justgrad).
 \label{eqn:delta_p_measures}
 \end{equation}
-In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
+In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
 Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ roughly represents the width of the ``thermal adjustment layer.''
@@
 We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{time_evolution.pdf}
+\caption{
+(left top panel) Shown is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
+We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
+The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
+(right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
+The line color denotes the time, according to the time traces in the left panels.
+The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
+The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
+The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
+\label{fig:time_evolution}
+}
+\end{figure*}
 
@@
 \subsection{Qualitative description of simulation evolution}
-
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=\textwidth]{time_evolution.pdf}
-\caption{
-(Left top panel) Displayed is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
-We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
-The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
-(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
-The line color denotes the time, according to the time traces in the left panels.
-The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
-The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
-The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
-\label{fig:time_evolution}
-}
-\end{figure*}
-
 \begin{figure*}[t]
@@
 On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
-These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are oppositely signed.
+These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
 
@@
 \caption{
-Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (Left, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (Right, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}).
+Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
 The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
-The discontinuous penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
-The discontinuous-gradient penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
+The Case I penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
+The Case II penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
 In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
@@
 In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
+The fixed values of $\mR$ and $\mS$ are shown above these panels.
 We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
 At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
-At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and the PZ depths are saturating.
+At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and PZ depths saturate.
 
@@
 We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
+We note a weak trend where $f$ increases as $\mP$ decreases.
 Most of the trend of $f$ increasing as $\mP$ decreases can be explained by slight increases in the CZ velocities and corresponding increases in the dissipation.
@@
 This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
-As the size of the PZ shrinks, dynamics do not have the space to change from their bulk-CZ properties, and so $\xi$ is closer to one.
+As the size of the PZ shrinks, dynamics do not have the space to change appreciably from their bulk-CZ properties, and so $\xi$ is closer to one.
 
@@
 We find that the depth of the penetration zone is weakly dependent on $\mR$.
-In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth $\delta_{0.5}$ with the Reynolds number.
+In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth with the Reynolds number.
 In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
-We find that $f$ increases with increases $\mR$, but is perhaps leveling off.
+We find that $f$ increases with increasing $\mR$, but is perhaps leveling off as $\mR$ becomes large.
 We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
@@
 We have visualized a NS dissipation profile in the right panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
-This means that we can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
+We can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
 \begin{equation}
-\int_{\rm{CZ}} \bar{\Phi} dz = C ( L_s - \delta_\nu ),
+\int_{\rm{CZ}} \bar{\Phi}\,dz \approx C ( L_s - \delta_\nu ),
 \end{equation}
 where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
-In other words, under this model, we expect the dissipation, and thus $f$, to vary linearly with the viscous boundary layer depth.
+In this model, we expect the dissipation and therefore $f$ to vary linearly with the viscous boundary layer depth.
 We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
@@
 The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.} \citep{ahlers_etal_2009, goluskin2016}.
-Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $\delta_{0.5}$ to level off as $\mR$ increases to high values in the astrophysical regime.
+Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $f$ and $\delp$ to level off as $\mR$ increases to high values in the astrophysical regime.
 
@@
 We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
-However, the link between $\delta_{0.5}$ and $f$ and the link between $f$ and $\delta_\nu$ -- both of which are effects we largely understand -- suggest that PZ depths should saturate at high $\mR$.
+However, the link between $\delp$ and $f$ and the link between $f$ and $\delta_\nu$ --- both of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
 
@@
 \end{equation}
-where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$ $r$ is the radial coordinate and we write the RHS as a volume integral.
+where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$, $r$ is the radial coordinate, and we write the RHS as a volume integral.
 We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
 \begin{equation}
-\int_{\rm{PZ}} \rho_0 \Phi dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi dV,
+\int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
 \end{equation}
@@
 We of course note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
-We present this as a proof of concept and to inspire further work.
+We present this model as a proof of concept and to inspire further work.
 
@@
 In this work, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
-We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these parameters and a new flux-based ``penetration parameter'' $\mP$.
+We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
 We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
-Our results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
+
+Our simulation results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
 In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
@@
 The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} here.
-Future work should aim to understand how these parameters change when these realistic effects are taken into account.
+Future work should aim to understand how these parameters and the theory presented in e.g., Eqn.~\ref{eqn:mesa_eqn} change when these realistic effects are taken into account.
 
 Furthermore, it is important to note that stellar opacities, and thus stellar conductivities, are functions of thermodynamic variables rather than radial location.
-As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the estimate of how deep the penetration zone should be.
+As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
 Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
@@
 We tested this theory with simulations and found good agreement between the theory and our simulations.
-In future work, we will aim to more robustly implement this theory into MESA and test some of the complicating factors we discussed here.
+In future work, we will aim to more robustly implement this theory into MESA and use simulations to test some of the complicating factors we discussed here.
 
@@
 \end{enumerate}
-In general, we start our simulations with an initial profile according to Eqn.~\ref{eqn:initial_grad} with a value $\delta_{0.5,\rm{new}} \geq 0$.
+In general, the initial profile of $\bar{T}$ that we use when we start our simulations is given by Eqn.~\ref{eqn:initial_grad} with a value $\delta_{0.5,\rm{new}} \geq 0$.
+We then evolve $\bar{T}$ towards a statistically stationary state using the above algorithm and standard timestepping.
 If a simulation returns to step 2 from step 4 ten times over the course of its evolution, we assume that it has converged near its answer, stop this iterative loop, and allow the simulation to timestep normally.
@@
 After converging to within a few percent of the proper penetration zone depth, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
-These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration bfore jumping back towards it in the next iteration.
+These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration before jumping back towards it in the next iteration.
 If the PZ depth continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the evolution of $\delp$ vs.~time has flattened.
@@
 The thin horizontal lines represent the final converged values from the standard timestepping simulations.
-Accelerated evolution timesteps can be see as discontinuities in the $\delp$ trace.
+Accelerated evolution timesteps can be seen as discontinuities in the $\delp$ trace.
 Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.

### 2021-07-10 data/plot_results_vs_p.py

@@ -96,7 +96,6 @@ ax2.set_title('$\mathcal{P}_L|_{\mathcal{R} = 800, \mathcal{S} = 10^3}$')
 ax1.set_ylabel(r'$\delta_{\rm{p}}$')
 ax1_1.set_ylabel(r'$f$')
 ax1_2.set_ylabel(r'$\xi$')
-ax1.set_ylim(1e-2, 1)
 ax1.set_yticks((0.25, 0.5, 0.75, 1, 1.25))
 
 
@@ -130,7 +129,8 @@ theory_plot = ax2.plot(line_P, line_theory, c='orange', label=r'$\propto \mathca
 ax2.legend(frameon=True, fontsize=8, framealpha=0.6)
 
 
-
+for ax in [ax1, ax2]:
+    ax.set_ylim(8e-3, 2)
 
 
 for ax in [ax1_1, ax2_1]:

### 2021-07-10 data/output_simulation_details.py
adds table-o-sims

@@ -1,0 +1,78 @@
+"""
+Outputs sim info for table
+
+Usage:
+    plot_slices.py <dirs>... [options]
+
+"""
+
+from collections import OrderedDict
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+import pandas as pd
+
+from docopt import docopt
+args = docopt(__doc__)
+
+dirs = args['<dirs>']
+
+data_chunks = []
+for d in dirs:
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+
+    if '3D' in d:
+        threeD = True
+    else:
+        threeD = False
+    if 'erf' in d:
+        erf = True
+    else:
+        erf = False
+
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        Ls = f['Ls'][()]
+        L_d09s = f['L_d09s'][()]
+        enstrophy_Ls = f['enstrophy_Ls'][()]
+        enstrophy_cz = f['enstrophy_cz'][()]
+        fconv_Ls = f['fconv_Ls'][()]
+        vel_Ls = f['vel_Ls'][()]
+
+        try:
+            modern_f = f['modern_f'][()]
+            modern_xi = f['modern_xi'][()]
+        except:
+            L_pz = L_d09s - Ls
+            dissipation_cz   = enstrophy_cz/Re
+            dissipation_Ls   = enstrophy_Ls/Re
+            dissipation_pz   = (dissipation_cz * L_d09s - dissipation_Ls * Ls) / L_pz
+       
+            modern_f         = dissipation_Ls/fconv_Ls
+            modern_xi        = ( (dissipation_pz*L_pz) / (fconv_Ls*Ls) ) / (modern_f * (L_pz/Ls))
+
+    if P == 0.03 and erf == False:
+        N = 900
+    else:
+        N = 1000
+
[…]

### 2021-07-12 manuscript/ms.tex
adds first-draft simulation table
Wordsmithing on abstract

@@
 \begin{abstract}
-Convection is a crucial mechanism for heat transport and dynamical excitation in stars.
-Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of motions near convective boundaries are not well understood.
-In this paper we examine how convective motions mix thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
-We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
-Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
+Most stars host convection zones, in which heat is transported directly by fluid motion.
+Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
+Here we examine how convective motions mix entropy and in turn extend the size of the convection zone, a process referred to as convective penetration.
+We derive a ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we construct a model of penetration based on an energy balance, and find that the extent of penetration is controlled by $\mP$.
 We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
@@
 We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
-We briefly discuss future experiments which could verify and extend these results in more realistic stellar contexts.
+We further discuss prospects for extending these results to more realistic stellar contexts.
 \end{abstract}
@@
 
+\begin{deluxetable*}{c c c c c c c c c c}
+\tabletypesize{\footnotesize}
+\caption{Table of simulation information
+\label{table:simulation_info}
+}
+\tablehead{
+\colhead{Type} 	& \colhead{$\mP$}	& \colhead{$\mS$}	& \colhead{$\mR$}	& \colhead{$nz \times (nx \times ny)$}	&	\colhead{$t_{\rm{sim}}$}	&	\colhead{$(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$}	& \colhead{$f$}	& \colhead{$\xi$}	& \colhead{$\angles{u}$}
+}
+\startdata
+\multicolumn{3}{l}{\textbf{``Standard timestepping'' simulations}}\\
+D	& 1	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 12347	& ($0.078, 0.112, 0.136$)	& 0.81	& 0.70	& 0.61 \\
+D	& 2	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 22593	& ($0.191, 0.220, 0.242$)	& 0.75	& 0.62	& 0.62 \\
+D	& 4	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 57170	& ($0.434, 0.461, 0.483$)	& 0.67	& 0.58	& 0.62 \\
+\hline
+\multicolumn{3}{l}{\textbf{``Accelerated Evolution'' simulations}}\\
+D		& 0.1,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4561 	& ($0.017, 0.042, 0.069$)	&  0.83	&  0.77	& 0.59 \\
+D		& 0.3,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4681 	& ($0.030, 0.064, 0.092$)	&  0.81	&  0.80	& 0.62 \\
+D		& 1,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 3000 	& ($0.082, 0.116, 0.140$)	&  0.80	&  0.69	& 0.62 \\
+D		& 2,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.199, 0.228, 0.252$)	&  0.75	&  0.60	& 0.64 \\
+D		& 4,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.452, 0.480, 0.505$)	&  0.67	&  0.55	& 0.62 \\
+D		& 6,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 6000 	& ($0.620, 0.647, 0.667$)	&  0.64	&  0.53	& 0.60 \\
+D		& 8,    & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4357 	& ($0.731, 0.757, 0.778$)	&  0.64	&  0.48	& 0.59 \\
+D		& 10,   & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4226 	& ($0.857, 0.884, 0.903$)	&  0.63	&  0.45	& 0.59 \\
+D   	& 4		& $10^3$			& 25				& 256$\times$16$^2$ 	& 3000	& (0.321, 0.379, 0.437)	& 0.77	& 0.27	& 0.34 \\
+D   	& 4		& $10^3$			& 50				& 256$\times$32$^2$ 	& 3000	& (0.398, 0.442, 0.487)	& 0.73	& 0.36	& 0.42 \\
+D   	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 3000	& (0.469, 0.503, 0.534)	& 0.67	& 0.46	& 0.48 \\
+D   	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$64$^2$ 	& 3000	& (0.485, 0.515, 0.542)	& 0.65	& 0.55	& 0.55 \\
+D   	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 3000	& (0.407, 0.434, 0.455)	& 0.69	& 0.57	& 0.68 \\
+D   	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 3000	& (0.366, 0.397, 0.419)	& 0.71	& 0.57	& 0.72 \\
+D   	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2469	& (0.313, 0.350, 0.372)	& 0.73	& 0.60	& 0.75 \\
+D   	& 4		& $10^3$			& $6.4 \times 10^3$	& 384$^3$				& 414 	& (0.277, 0.314, 0.335)	& 0.74	& 0.62	& 0.76 \\
+D/SF	& 4		& $10^3$			& 50				& 256$\times$16$^2$ 	& 5000	& (0.435, 0.477, 0.516)	& 0.68	& 0.42	& 0.50 \\
+D/SF	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.482, 0.516, 0.547)	& 0.64	& 0.54	& 0.57 \\
+D/SF	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.490, 0.520, 0.547)	& 0.63	& 0.59	& 0.64 \\
+D/SF	& 4		& $10^3$			& $4 \times 10^2$	& 256$\times$64$^2$ 	& 8000	& (0.474, 0.502, 0.531)	& 0.65	& 0.59	& 0.69 \\
+D/SF	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.410, 0.437, 0.461)	& 0.68	& 0.59	& 0.73 \\
+D/SF	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 5710	& (0.368, 0.400, 0.426)	& 0.70	& 0.59	& 0.76 \\
+D/SF	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2933	& (0.315, 0.352, 0.381)	& 0.73	& 0.59	& 0.77 \\
+D		& 4		& $10^2$			& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.377, 0.505, 0.581)	& 0.65	& 0.53	& 0.62 \\
+D		& 4		& $3\times 10^2$	& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.420, 0.477, 0.514)	& 0.66	& 0.55	& 0.62 \\
+D		& 4		& $3\times 10^3$	& $4 \times 10^2$	& 256$\times$128$^2$	& 1170	& (0.455, 0.472, 0.487)	& 0.66	& 0.58	& 0.62 \\
+L		& 0.01	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1139	& (0.017, 0.030, 0.052)	& 0.87	& 0.79	& 0.45 \\
+L		& 0.03	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 929 	& (0.021, 0.045, 0.070)	& 0.86	& 0.79	& 0.45 \\
+L		& 0.1	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1142	& (0.084, 0.076, 0.102)	& 0.85	& 0.72	& 0.45 \\
+L		& 0.3	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1109	& (0.077, 0.130, 0.158)	& 0.82	& 0.66	& 0.45 \\
+L		& 1		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.182, 0.225, 0.251)	& 0.79	& 0.60	& 0.44 \\
+L		& 2		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.278, 0.315, 0.340)	& 0.76	& 0.57	& 0.44 \\
+L		& 4		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.396, 0.427, 0.449)	& 0.73	& 0.53	& 0.43 \\
+L		& 8		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.519, 0.545, 0.562)	& 0.72	& 0.48	& 0.42 \\
+L		& 16	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 8000	& (0.687, 0.709, 0.723)	& 0.70	& 0.44	& 0.42 \\
+\enddata                                                   	
+\tablecomments{                                            	
+}                                                          	
+\end{deluxetable*}
+
 \bibliographystyle{aasjournal}

### 2021-07-13 manuscript/ms.tex
intro edits

@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism in stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
-For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
-Convection also mixes stars compositionally, which can modify observed surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
+Convection is a crucial mechanism for transporting heat in stars~\citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
+For example, convection drives the magnetic dynamo of the Sun, leading to a whole host of emergent phenomena collectively known as solar activity \citep{brun_browning_2017}.
+Convection also mixes chemical elements in stars, which can modify observed surface abundances or inject additional fuel into their cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
 Furthermore, convective motions excite waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
-A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.
+A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure and evolution, and for connecting this understand to observations.
 
 Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
-In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
-This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
+In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the Ledoux-unstable zone.
+This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars, which align poorly with theoretical predictions \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
 Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, bergemann_serenelli_2014, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
-Overshoot parameterizations in massive stars with convective cores must be finely tuned as a function of stellar mass, again suggesting our current parameterizations are missing some physics \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
+
+Beyond the Sun, overshooting in massive stars with convective cores must be finely tuned as a function of stellar mass, again pointing to missing physics in our current parameterizations \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
 Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.

### 2021-07-13 manuscript/ms.tex
typo

@@
 Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
+
 In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
@@
 There are hints in the literature that convective penetration may be dependent upon energy fluxes.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts and upper limit on the size of a theoretical penetrative region.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.

### 2021-07-13 manuscript/ms.tex
Finished intro sweep

@@
 Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
-In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
+In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
 
@@
 \end{quote}
-Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) around the convective boundary.
+Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
 
 We present these findings as follows.
-In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and retrieve predictions for our two experimental designs from that theory.
+In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.

### 2021-07-13 manuscript/ms.tex
Minor edits in 2

@@
 Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
-Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to this equation.
+Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.
 

### 2021-07-14 manuscript/ms.tex
incorporate comments from daniel with some decent sized restructuring.

@@
 We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
+We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
@@
 \label{sec:introduction}
+
+\subsection{Context}
 Convection is a crucial mechanism for transporting heat in stars~\citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
@@
 
-Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-Experiments exhibiting extensive convective penetration have a long history \citep[dating back to e.g.,][]{musman1968, deardorff_etal_1969, moore_weiss_1973}.
-Modern experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
+Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
 The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
-Some recent studies in simplified Boussinesq setups suggest that the penetration depth is highly dependent on the stiffness \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
-Many studies of density-stratified convective atmospheres find significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, dietrich_wicht_2018}.
-However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
-Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
-This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but the precise results of past studies are often contradictory and no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
+Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
+Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent overshoot \citep{korre_etal_2019}.
+While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.
+
+Studies which more closely model the conditions inside of stars have presented confusing results.
+Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
+However, fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
 
@@
 
-In this work, we design two numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
-We use a modified incompressible, Boussinesq model to study the simplest possible system, and derive theoretical predictions for the size of the penetrative zone.
-We test this theory using 3D numerical simulations.
+\subsection{Convective penetration \& this study's findings}
+
+The Schwarzschild criterion for convective stability separates regions where convective motions are required to carry the flux from regions where radiation is capable of carrying the flux stably.
+\emph{Convective penetration} is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
+\begin{quote}
+\emph{
+In this paper, we present simulations which consistently exhibit convective penetration.
+}
+\end{quote}
+These simulations exhibit nearly adiabatic regions beyond the Schwarzschild boundaries of the convection zone.
+This process is phenomenologically described in Sec.~\ref{sec:central_results}.
+
+In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
+We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
 \begin{quote}
@@
 We present these findings as follows.
+In Sec.~\ref{sec:central_results}, we note the central results of this work.
 In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
@@
 In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
-Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.
+Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
+\caption{
+Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
+The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
+The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
+(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
+(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
+%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
+\label{fig:vertical_dynamics_panels}
+}
+\end{figure*}
+
+\section{Central Results}
+\label{sec:central_results}
+
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display a snapshot of dynamics in an evolved simulation which exhibits convective penetration.
+The simulation domain is a 3D Cartesian box, and this figure shows a vertical slice through the center of the domain.
+In the left panel, we display the vertical velocity.
+We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
+These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the gradient departs from the adiabatic towards the radiative gradient.
+In the right panel, we display temperature perturbations from the time-evolving mean temperature profile, normalized by the standard deviation of these fluctuations at each height.
+We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).
+
+In Fig.~\ref{fig:grad_profiles}, we display time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
+The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
+The radiative gradient $\gradrad$ is shown in orange.
+The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
+Above this point, $\gradrad < \gradad$ and is Schwarzschild-stable.
+However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have flattened $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
+Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
+
+Our goal in this paper is to understand how these PZs form, and to begin to understand how to parameterize this effect so that it can be included in 1D stellar evolution calculations.
 
@@
 \label{sec:theory_energy}
-\begin{figure*}[t!]
+
+\begin{figure}[t]
 \centering
-\includegraphics[width=\textwidth]{theory_profiles.pdf}
+\includegraphics[width=\columnwidth]{grad_profiles.pdf}
 \caption{
-(left) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in a simulation. 
-$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
-Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
-Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
-(middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
-(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
-\label{fig:theory_profiles}
+Measured time- and horizontally-averaged vertical profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
+We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
+\label{fig:grad_profiles}
 }
-\end{figure*}
+\end{figure}
 
-Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
+Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
 \begin{equation}
@@
 Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{theory_profiles.pdf}
+\caption{
+(upper) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in the simulation shown in Fig.~\ref{fig:vertical_dynamics_panels}. 
+$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
+Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
+Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
+(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
+\label{fig:theory_profiles}
+}
+\end{figure}
 
@@
 When $\mP \sim 1$, both terms matter.
+
+The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
+The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations.
+In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
 
@@
 We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
-We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
+Furthermore, since the conductivity is not zero at the bottom boundary, the adiabatic temperature gradient there carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
 
-We expect the average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
+We expect the average convective velocities to depend on the magnitude of the heating, $\angles{\vec{|u|}} \approx Q_{\rm{mag}}^{1/3} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{|u|}} / L_s \approx 1$.
 The stiffness is defined,
@@
 We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
-We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$, and therefore found negligible penetration for moderate to high stiffness.
+We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
+However, more fundamentally (as we will show in Sec.~\ref{sec:results}), the development of penetrative zones is a slow process and it is possible that many prior studies did not evolve simulations for long enough to see these regions saturate.
 
@@
 We use a domain aspect ratio of two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
+To avoid aliasing errors, we use the 3/2-dealiasing rule in all directions.
 To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
@@
 \begin{equation}
-H(z; z_0, d_w) = \frac{1}{2}\left(1 + \rm{erf}\left[\frac{z - z_0}{d_w}\right]\right).
+H(z; z_0, d_w) = \frac{1}{2}\left(1 + \mathrm{erf}\left[\frac{z - z_0}{d_w}\right]\right).
 \label{eqn:heaviside}
@@
 All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{time_evolution.pdf}
+\caption{
+(left top panel) Shown is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
+We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
+The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
+(right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
+The line color denotes the time, according to the time traces in the left panels.
+The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
+The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
+The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
+\label{fig:time_evolution}
+}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=\textwidth]{time_evolution.pdf}
-\caption{
-(left top panel) Shown is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
-We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
-The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
-(right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
-The line color denotes the time, according to the time traces in the left panels.
-The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
-The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
-The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
-\label{fig:time_evolution}
-}
-\end{figure*}
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Qualitative description of simulation evolution}
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
-\caption{
-Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
-In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
-(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
-(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
-Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
-\label{fig:vertical_dynamics_panels}
-}
-\end{figure*}
-
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
-In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
-We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
-It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution of the bulk of the simulations in this work (see Appendix \ref{app:accelerated_evolution} for details).
-
-The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
-We plot the rolling mean, averaged over 200 freefall time units. 
-We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
-We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
-The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.
-
-In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
-$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
-The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
-We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
-The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
-This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
-
-In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
-We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
-Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
-On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
-These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
-
-\subsection{Dependence on $\mP$}
-\begin{figure*}[t]
-\centering
 \includegraphics[width=\textwidth]{parameters_vs_p.pdf}
@@
 
+\section{Results}
+\label{sec:results}
+
+\subsection{Qualitative description of simulation evolution}
+
+%\begin{figure*}[t]
+%\centering
+%\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
+%\caption{
+%Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
+%In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
+%(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
+%(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
+%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
+%\label{fig:vertical_dynamics_panels}
+%}
+%\end{figure*}
+
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
+In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
+The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
+We plot their rolling mean, averaged over 200 freefall time units. 
+We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
+We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
+The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation negative buoyancy work.
+The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.
+
+In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
+$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
+We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
+
+We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of the bulk of the simulations in this work.
+To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
+We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
+Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
+While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
+For details on precisely how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
+
+%In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
+%We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
+%Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
+%On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
+%These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
+
+\begin{figure*}[t]
+\centering
+\includegraphics{parameters_vs_s.pdf}
+\caption{
+(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
+While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
+(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
+We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
+\label{fig:parameters_vs_s}
+}
+\end{figure*}
+
+\subsection{Dependence on $\mP$}
 We find that the depth of the penetration zone is strongly dependent on $\mP$.
@@
 We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
-At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
+At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
 At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and PZ depths saturate.
@@
 We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
-We note a weak trend where $f$ increases as $\mP$ decreases.
-Most of the trend of $f$ increasing as $\mP$ decreases can be explained by slight increases in the CZ velocities and corresponding increases in the dissipation.
-We speculate that, as $\mP$ decreases, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) more efficiently deflects convective velocities sideways before they have a chance to buoyantly break, thereby slightly increasing bulk-CZ velocities.
-A similar trend of $\xi$ increasing as $\mP$ decreases can be seen.
+We note a weak trend where $f$ decreases as $\mP$ increases.
+Most of this trend can be explained by slight decreases in the CZ velocities and corresponding decreases in the dissipation.
+We speculate that when $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
+As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
+A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
 This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
-As the size of the PZ shrinks, dynamics do not have the space to change appreciably from their bulk-CZ properties, and so $\xi$ is closer to one.
+As the size of the PZ grows, dynamics have the space to change appreciably from their bulk-CZ properties, and so $\xi$ shrinks.
 
@@
 We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
-This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
+%This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
 
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[t]
 \centering
-\includegraphics{parameters_vs_s.pdf}
+\includegraphics[width=\textwidth]{parameters_vs_re.pdf}
 \caption{
-(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
-While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
-(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
-We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
-\label{fig:parameters_vs_s}
+(Upper left panel) Penetration depths are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
+We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
+In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
+(Upper middle panel) We similarly see increases in the value of $f$ with $\mR$, although perhaps this measurement is leveling off at high values of $\mR$.
+(Upper right panel) We do not see large changes in the value of $\xi$ as $\mR$ increases, suggesting that the nature of dissipation in the PZ is not appreciably changing.
+(Lower left panel) In summary, we see a strong correlation between $\delta_{0.5}$ and $f$.
+(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
+This makes sense, as more of the convective domain is available for the convective flows to dissipate energy.
+(Lower right panel) The viscous boundary layer follows a classical scaling laws seen in Rayleigh-B\'{e}nard convection, and so we anticipate that the trend in $\delta_{0.5}$ vs $\mR$ should saturate as $\delta_{\nu} \rightarrow 0$ and $f$ saturates.
+\label{fig:parameters_vs_re}
 }
@@
 In order to understand this better, we note that the dissipation profile can reasonably be approximated as a constant value in the CZ and zero in the bottom viscous boundary layer.
-We have visualized a NS dissipation profile in the right panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
-We can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
+We have visualized a NS dissipation profile in the bottom panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
+We can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as a constant in the bulk and zero in the boundary layer,
 \begin{equation}
-\int_{\rm{CZ}} \bar{\Phi}\,dz \approx C ( L_s - \delta_\nu ),
+\int_{\rm{CZ}} \bar{\Phi}\,dz \approx C \left( 1 - \frac{\ell_\nu}{L_s}\right)
+\,\,\Rightarrow\,\,
+f \propto \left(1 - \frac{\ell_\nu}{L_s}\right),
 \end{equation}
-where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
+where $C$ is a constant and $\ell_\nu$ is the boundary layer depth.
 In this model, we expect the dissipation and therefore $f$ to vary linearly with the viscous boundary layer depth.
 We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
-In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \propto \delta_\nu$ is a decent description for the SF simulations (NS simulations show an increase at small $\delta_\nu$, but also have maximized dissipation in the bounary layer).
+In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \approx 0.755(1 - 2\ell_\nu/L_s)$ is a decent description of the high-$\mR$ behavior of these simulations.
+The additional factor of 2 arises because of how we find the boundary layer depth (the extremum of the viscous flux likely occurs halfways through the boundary layer spatially).
+We find that this is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore this model poorly describes them.
 In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
-If you assume the Nusselt Number dependence on the Rayleigh number is Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
-The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.} \citep{ahlers_etal_2009, goluskin2016}.
+If you assume the Nusselt Number dependence on the Rayleigh number is throttled by the boundaries, Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
+The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.
+} \citep{ahlers_etal_2009, goluskin2016}.
 Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $f$ and $\delp$ to level off as $\mR$ increases to high values in the astrophysical regime.
 
-Unfortunately, we are limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}), so we cannot extend our study to more turbulent simulations and higher values of $\mR$ than the ones shown here.
-We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
-However, the link between $\delp$ and $f$ and the link between $f$ and $\delta_\nu$ --- both of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
+Indeed, we use the fitted function of $f$ from the bottom middle panel, along with Eqn.~\ref{eqn:discontinuous_prediction}, to estimate $\delta_{0.5}$ in the bottom left panel, and we overplot that as a line.
+We need to multiply this equation by a factor of 0.9, which accounts for three differences between the simulations and the theory.
+First, due to internal heating and the finite width of the conductivity transition around the Schwarzschild boundary, the convective flux is not truly constant through the full depth of the CZ
+Thus, we expect $L_{\rm{CZ}}$ to be smaller than 1.
+Furthermore, we are measuring $\delta_0.5$, and the theory is derived in the limit of an instantaneous tarnsition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$.
+Despite these subtle differences, we find this agreement to be good.
 
-\begin{figure*}[t!]
-\centering
-\includegraphics{parameters_vs_re.pdf}
-\caption{
-(Upper left panel) Penetration depths are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
-We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
-In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
-(Upper middle panel) We similarly see increases in the value of $f$ with $\mR$, although perhaps this measurement is leveling off at high values of $\mR$.
-(Upper right panel) We do not see large changes in the value of $\xi$ as $\mR$ increases, suggesting that the nature of dissipation in the PZ is not appreciably changing.
-(Lower left panel) In summary, we see a strong correlation between $\delta_{0.5}$ and $f$.
-(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\delta_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
-This makes sense, as more of the convective domain is available for the convective flows to dissipate energy.
-(Lower right panel) The viscous boundary layer follows a classical scaling laws seen in Rayleigh-B\'{e}nard convection, and so we anticipate that the trend in $\delta_{0.5}$ vs $\mR$ should saturate as $\delta_{\nu} \rightarrow 0$ and $f$ saturates.
-\label{fig:parameters_vs_re}
-}
-\end{figure*}
+Using the value of $f = 0.755$ expected at $\ell_\nu = 0$, we calculate that we expect $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and overplot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
+This value is coincidentally very near the value of $\delta_{0.5}$ achieved in our highest-$\mR$ simulations.
+Unfortunately, we cannot probe more turbulent simulations than these.
+We can only run the highest-$\mR$ simulations for a few hundred freefall times.
+Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}).
+Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ depths of these simulations are converged to within a few percent.
+Future work should aim to understand the trend of PZ depth with turbulence better.
+However, the link between $\delp$ and $f$ and the link between $f$ and $\ell_\nu$ --- both of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
 
@@
 In general, out of the simulations presented in this work, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
-In this simulation, we found $f \approx 0.8$ and $\xi \approx 0.6$; the results of Fig.~\ref{fig:parameters_vs_re} suggest that $f$ could increase by $\sim 0.1$ as $\mR$ increases into the stellar regime but $\xi$ probably doesn't change much.
-As such, we take $f \approx 0.9$ and $\xi \approx 0.6$ as first-guess values for our theory of convective penetration in stellar regimes.
+In this simulation, we found $f \approx 0.8$ and $\xi \approx 0.6$.
+We note that Fig.~\ref{fig:parameters_vs_re} suggests that $f$ could increase by $\sim 0.1$ as $\mR$ increases into the stellar regime but $\xi$ probably doesn't change much.
+As such, we take $f = 0.9$ and $\xi = 0.6$ as first-guess values for our theory of convective penetration in stellar regimes.
 These values should of course be confirmed and tuned in more realistic stellar settings which include spherical geometry and realistic density stratifications.
@@
 
-In Fig.~\ref{} we display the profile of X quantity at the base of a solar model using a penetrative zone (as described above) and using X classical prescription.
+In Fig.~\ref{fig:mesa} we display the profile of X quantity at the base of a solar model using a penetrative zone (as described above) and using X classical prescription.
 Note the differences in this thing and that thing.
@@
 We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
-Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
+Early studies suggest that the maximum depth of a PZ should be 0.1 $H_p$ \citep{basu_etal_1994}.
+More rent work puts tighter helioseismic constraints on observations of $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
 However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
@@
 We'd like to thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
-TODO thank Nordita program.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
+We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
 Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[t]
 \centering
@@
 
+\newpage
 \section{Table of simulation parameters}

### 2021-07-14 manuscript/ms.tex
incorporates (I think?) all suggestions from Daniel; cleans up a few rough edges.

@@
 
-The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
-The first class is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
-The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
-We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
-We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
-We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.
+The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes.
+The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
+The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
+We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology.
+Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
+The primary focus of this work is convective penetration.
 
@@
 Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
-Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent overshoot \citep{korre_etal_2019}.
+Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
 While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.
@@
 These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
-However, fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
 This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
@@
 
-The Schwarzschild criterion for convective stability separates regions where convective motions are required to carry the flux from regions where radiation is capable of carrying the flux stably.
-\emph{Convective penetration} is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
+Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
 \begin{quote}
 \emph{
-In this paper, we present simulations which consistently exhibit convective penetration.
+In this paper, we present simulations which exhibit convective penetration.
 }
 \end{quote}
-These simulations exhibit nearly adiabatic regions beyond the Schwarzschild boundaries of the convection zone.
 This process is phenomenologically described in Sec.~\ref{sec:central_results}.
@@
 In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
-We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
 \begin{quote}
@@
 We present these findings as follows.
-In Sec.~\ref{sec:central_results}, we note the central results of this work.
-In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
+In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
+In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
@@
 
-\section{Central Results}
+\section{Central Result: Convective Penetration}
 \label{sec:central_results}
@@
 These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the gradient departs from the adiabatic towards the radiative gradient.
-In the right panel, we display temperature perturbations from the time-evolving mean temperature profile, normalized by the standard deviation of these fluctuations at each height.
+In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
 We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).
 
-In Fig.~\ref{fig:grad_profiles}, we display time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
+We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
 The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
@@
 The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
-Above this point, $\gradrad < \gradad$ and is Schwarzschild-stable.
-However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have flattened $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
+Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
+However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
 Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
 
-Our goal in this paper is to understand how these PZs form, and to begin to understand how to parameterize this effect so that it can be included in 1D stellar evolution calculations.
+Our goals in this paper are to understand how these PZs form, and to parameterize this effect so that it can be included in 1D stellar evolution calculations.
 
+\newpage
 \section{Theory}
@@
 \label{sec:theory_equations}
-Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
+Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
 \begin{align}
@@
 Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
 We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
@@
 \end{equation}
-It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
+It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
 We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
@@
 \begin{equation}
-\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
-+ \frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
-= 1 - f,
+\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
++ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+= (1 - f),
 \label{eqn:first_pz_parameterization}
@@
 In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
-Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).
+Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).
 
@@
 The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
+This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary (which we quantify in Eqn.~\ref{eqn:theory_P_defn}).
 The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations.
@@
 We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
-The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation negative buoyancy work.
+The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
 The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.
 
-In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
+In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals, where the color of the profiles corresponds to time, as in the left panels.
 $\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
@@
 The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
-This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
+We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+%This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.
 
@@
 A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
-This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
+This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ compared to the PZ.
 As the size of the PZ grows, dynamics have the space to change appreciably from their bulk-CZ properties, and so $\xi$ shrinks.
@@
 In this model, we expect the dissipation and therefore $f$ to vary linearly with the viscous boundary layer depth.
-We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
+We take the value of $\ell_\nu$ to be the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
 In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \approx 0.755(1 - 2\ell_\nu/L_s)$ is a decent description of the high-$\mR$ behavior of these simulations.
-The additional factor of 2 arises because of how we find the boundary layer depth (the extremum of the viscous flux likely occurs halfways through the boundary layer spatially).
-We find that this is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore this model poorly describes them.
+The additional factor of 2 arises because of how we find the boundary layer depth (the extremum of the viscous flux likely occurs halfway through the boundary layer spatially).
+We find that this is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore this model poorly describes them from a phenomenological perspective.
 In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
@@
 Indeed, we use the fitted function of $f$ from the bottom middle panel, along with Eqn.~\ref{eqn:discontinuous_prediction}, to estimate $\delta_{0.5}$ in the bottom left panel, and we overplot that as a line.
-We need to multiply this equation by a factor of 0.9, which accounts for three differences between the simulations and the theory.
-First, due to internal heating and the finite width of the conductivity transition around the Schwarzschild boundary, the convective flux is not truly constant through the full depth of the CZ
-Thus, we expect $L_{\rm{CZ}}$ to be smaller than 1.
-Furthermore, we are measuring $\delta_0.5$, and the theory is derived in the limit of an instantaneous tarnsition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$.
-Despite these subtle differences, we find this agreement to be good.
+We need to multiply this equation by a factor of 0.9, which accounts for some differences between the simulations and the idealized ``discontinuous flux'' theoretical model.
+First, due to internal heating and the finite width of the conductivity transition around the Schwarzschild boundary, the convective flux is not truly constant through the full depth of the CZ.
+Thus, we expect $L_{\rm{CZ}}$  in Eqn.~\ref{eqn:discontinuous_prediction} to be smaller than 1.
+Furthermore, the theory is derived in the limit of an instantaneous tarnsition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$; our simulations have a finite transition width.
+Despite these subtle differences, we find good agreement.
 
@@
 Unfortunately, we cannot probe more turbulent simulations than these.
-We can only run the highest-$\mR$ simulations for a few hundred freefall times.
-Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}).
+We can only run the $\mR = 6.4 \times 10^{3}$ simulations for a few hundred freefall times.
+Our accuracy in measuring results from these simulations is limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}).
 Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ depths of these simulations are converged to within a few percent.
-Future work should aim to understand the trend of PZ depth with turbulence better.
-However, the link between $\delp$ and $f$ and the link between $f$ and $\ell_\nu$ --- both of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
+Future work should aim to better understand the trend of PZ depth with turbulence.
+However, the displayed relationships between $\delp$ and $f$, $f$ and $\ell_\nu$, and $\ell_\nu$ and $\mR$ --- all of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
 
@@
 
-We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.9$ and $\xi = 1$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.9$ and $\xi = 0.6$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
 We chose a value of $\xi = 1$ as it is the most conservative choice and should generally result in smaller penetration zones, and because it is unclear how our plane-parallel intuition for $\xi$ in this study maps into spherical geometry.
@@
 Early studies suggest that the maximum depth of a PZ should be 0.1 $H_p$ \citep{basu_etal_1994}.
-More rent work puts tighter helioseismic constraints on observations of $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
+More recent work puts tighter helioseismic constraints on observations of $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
 However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
@@
 \label{sec:discussion}
-In this work, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild convective boundary.
+To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
 We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.

### 2021-07-16 manuscript/ms.tex
end-of-week revisions to manuscript

@@
 \begin{abstract}
-Most stars host convection zones, in which heat is transported directly by fluid motion.
+Most stars host convection zones in which heat is transported directly by fluid motion.
 Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
@@
 
-Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
-The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
-Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
-Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
-While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.
-
-Studies which more closely model the conditions inside of stars have presented confusing results.
-Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
-These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
-Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
-This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
-
-There are hints in the literature that convective penetration may be dependent upon energy fluxes.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
-\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
-Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
-Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
-Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
-In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
-
-\subsection{Convective penetration \& this study's findings}
-
-Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
-\begin{quote}
-\emph{
-In this paper, we present simulations which exhibit convective penetration.
-}
-\end{quote}
-This process is phenomenologically described in Sec.~\ref{sec:central_results}.
-
-In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
-%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
-\begin{quote}
-\emph{
-We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
-}
-\end{quote}
-Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
-
-We present these findings as follows.
-In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
-In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
-In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
-In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
-In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
-Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.
-
 \begin{figure*}[t]
@@
 
+Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
+The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
+Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
+Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
+While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.
+
+Studies which more closely model the conditions inside of stars have presented confusing results.
+Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
+Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
+
+There are hints in the literature that convective penetration may be dependent upon energy fluxes.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
+\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
+Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
+Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
+In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.
+
+\subsection{Convective penetration \& this study's findings}
+
+Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
+\begin{quote}
+\emph{
+In this paper, we present simulations which exhibit convective penetration.
+}
+\end{quote}
+This process is phenomenologically described in Sec.~\ref{sec:central_results}.
+
+In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
+%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+\begin{quote}
+\emph{
+We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
+}
+\end{quote}
+Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
+
+We present these findings as follows.
+In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
+In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
+In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
+In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
+In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
+Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.
+
 \section{Central Result: Convective Penetration}
@@
 We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
-These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the gradient departs from the adiabatic towards the radiative gradient.
+These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the temperature gradient departs from adiabatic towards the radiative gradient.
 In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
@@
 
-\newpage
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth]{grad_profiles.pdf}
+\caption{
+Measured time- and horizontally-averaged vertical profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
+We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
+\label{fig:grad_profiles}
+}
+\end{figure}
+
 \section{Theory}
 \label{sec:theory}
+We will now derive a theoretical model in which to understand convective penetration.
+We will build this model through an examination of the energetics and energy fluxes within the convecting region.
+In Sec.~\ref{sec:theory_equations}, we will describe our equations and problem setup and define the heat fluxes.
+In Sec.~\ref{sec:theory_energy}, we will build a parameterized theory based on the kinetic energy equation and these fluxes.
+We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
 
@@
 
-Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
+Assuming convection reaches a time-stationary state, the heat fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
@@
 In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
-Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but the same logic applies to the inverted problem.
+Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but in this incompressible model where there is no density stratification to break the symmetry of upflows and downflows precisely the same arguments can be applied to the inverted problem.
 
@@
 \label{sec:theory_energy}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth]{grad_profiles.pdf}
-\caption{
-Measured time- and horizontally-averaged vertical profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
-We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
-\label{fig:grad_profiles}
-}
-\end{figure}
-
-Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
-\begin{equation}
-\frac{\partial \mathcal{K}}{\partial t}
-+ \grad\dot\mathcal{F}
-= \mathcal{B} - \Phi,
-%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
-%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
-%= |\alpha| g w T - \nu|\vec{\omega}|^2,
-\label{eqn:kinetic_energy}
-\end{equation}
-where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
-We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
-Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
-\begin{equation}
-\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
-\label{eqn:kinetic_energy_1D}
-\end{equation}
-It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
-We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
-\begin{equation}
-\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
-\label{eqn:integral_constraint}
-\end{equation}
-Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
-Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
 
@@
 
+Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
+\begin{equation}
+\frac{\partial \mathcal{K}}{\partial t}
++ \grad\dot\mathcal{F}
+= \mathcal{B} - \Phi,
+%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
+%= |\alpha| g w T - \nu|\vec{\omega}|^2,
+\label{eqn:kinetic_energy}
+\end{equation}
+where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
+We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
+Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
+\begin{equation}
+\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
+\label{eqn:kinetic_energy_1D}
+\end{equation}
+It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
+We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
+\begin{equation}
+\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
+\label{eqn:integral_constraint}
+\end{equation}
+Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
+Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
+
 We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
@@
 Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
-We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
-We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
+If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
+This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
+We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
+We now parameterize the fraction of the buoyant engine consumed by CZ dissipation,
 \begin{equation}
@@
 + \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
-= (1 - f),
+= (1 - f).
 \label{eqn:first_pz_parameterization}
 \end{equation}
-and we can immediately read off limits on a hypothetical PZ according to $f$,
+We will measure and report the values of $f$ achieved in our simulations in this work.
+Eqn.~\ref{eqn:first_pz_parameterization} provides two limits on a hypothetical PZ:
 \begin{enumerate}
 \item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
-Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
+Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
@@
 We will study two cases in this work, laid out below.
-In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
+In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant small length $\epsilon$ above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
 \begin{equation}
@@
 This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary (which we quantify in Eqn.~\ref{eqn:theory_P_defn}).
-The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations.
+The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
 In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
@@
 \section{Simulation Details}
+We will now describe a set of simulations that we have made to test the predictions in Sec.~\ref{sec:theory}.
+While many simulations of convection interacting with radiative zones have been performed by previous authors, ours differ in two crucial ways.
+First, we define the ``Penetration Parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
+We construct our experiments so that $\mP$ and $\mS$ (the stiffness, Eqn.~\ref{eqn:stiffness}) can be varied separately.
+We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
+Second, as we will show in Sec.~\ref{sec:results}, the development of penetrative zones is a slow process and it is possible that many prior studies did not evolve simulations for long enough to see these regions saturate.
+
 We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
@@
 \mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
+\label{eqn:stiffness}
 \end{equation}
@@
 We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\justgrad$, which in turn sets the value of $k$ in the radiative zone.
-
-The crucial place in which our model differs from that of prior work is that we define the ``Penetration Parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
-We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
-We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
-However, more fundamentally (as we will show in Sec.~\ref{sec:results}), the development of penetrative zones is a slow process and it is possible that many prior studies did not evolve simulations for long enough to see these regions saturate.
 
@@
 
+We will now present on the results of the 3D dynamical simulations described in the previous section.
+Dynamics in these simulations resemble those previously shown in Fig.~\ref{fig:vertical_dynamics_panels}.
+To quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory}, we will present time- and volume-averaged scalar quantities, as well as some select horizontally-averaged vertical profiles.
+
 \subsection{Qualitative description of simulation evolution}
@@
 
-We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
 It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of the bulk of the simulations in this work.
@@
 For details on precisely how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
+``We reinitialize the simulation with a better guess''.
 
@@
 In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
-We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
+We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat more strongly.
 In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
@@
 
-We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
+We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
 As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our turbulent cases.
@@
 
-In order to understand this better, we note that the dissipation profile can reasonably be approximated as a constant value in the CZ and zero in the bottom viscous boundary layer.
+We now examine why $f$ increases as $\mR$ increases.
+In the SF simulations, within the CZ, We can reasonably approximate $\bar{\Phi}$ as a constant in the bulk and zero within the viscous boundary layer,
+\begin{equation}
+\bar{\Phi}(z) = 
+\begin{cases}
+\Phi_{\rm{CZ}} 	& z > \ell_\nu \\
+0				& z \leq \ell_\nu
+\end{cases},
+\label{eqn:cz_dissipation_model}
+\end{equation}
+where $\Phi_{\rm{CZ}}$ is a constant and $\ell_\nu$ is the viscous boundary layer depth.
 We have visualized a NS dissipation profile in the bottom panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
-We can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as a constant in the bulk and zero in the boundary layer,
-\begin{equation}
-\int_{\rm{CZ}} \bar{\Phi}\,dz \approx C \left( 1 - \frac{\ell_\nu}{L_s}\right)
-\,\,\Rightarrow\,\,
-f \propto \left(1 - \frac{\ell_\nu}{L_s}\right),
-\end{equation}
-where $C$ is a constant and $\ell_\nu$ is the boundary layer depth.
-In this model, we expect the dissipation and therefore $f$ to vary linearly with the viscous boundary layer depth.
-We take the value of $\ell_\nu$ to be the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
-In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \approx 0.755(1 - 2\ell_\nu/L_s)$ is a decent description of the high-$\mR$ behavior of these simulations.
-The additional factor of 2 arises because of how we find the boundary layer depth (the extremum of the viscous flux likely occurs halfway through the boundary layer spatially).
-We find that this is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore this model poorly describes them from a phenomenological perspective.
+Under this model, we have
+\begin{equation}
+\int_{\rm{CZ}} \bar{\Phi}\,dz \approx \Phi_{\rm{CZ}} \left( L_s - \ell_\nu \right),
+\end{equation}
+and so per Eqn.~\ref{eqn:f_defn},
+\begin{equation}
+f = f_\infty\left(1 - \frac{\ell_\nu}{L_s}\right),
+\label{eqn:f_infty}
+\end{equation}
+where $f_\infty$ is the expected value of $f$ at $\mR = \infty$ when $\ell_\nu = 0$.
+So we see that the CZ dissipation and therefore $f$ vary linearly with $\ell_\nu$.
+
+In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that Eqn.~\ref{eqn:f_infty} with $f_\infty = 0.755$ describes the high-$\mR$ data well.
+We measure the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary, and take $\ell_\nu$ to be the twice that height.
+We find that Eqn.~\ref{eqn:f_defn} is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore Eqn.~\ref{eqn:cz_dissipation_model} is a poor model for $z \leq \ell_\nu$.
 In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
@@
 } \citep{ahlers_etal_2009, goluskin2016}.
-Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $f$ and $\delp$ to level off as $\mR$ increases to high values in the astrophysical regime.
+Combining these trends, we expect 
+\begin{equation}
+f = f_\infty(1 - C \mR^{-2/3})
+\end{equation}
+for a constant $C$.
+Thus as $\mR \rightarrow \infty$, $f \rightarrow f_\infty$.
 
@@
 Thus, we expect $L_{\rm{CZ}}$  in Eqn.~\ref{eqn:discontinuous_prediction} to be smaller than 1.
-Furthermore, the theory is derived in the limit of an instantaneous tarnsition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$; our simulations have a finite transition width.
+Furthermore, the theory is derived in the limit of an instantaneous transition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$; our simulations have a finite transition width.
 Despite these subtle differences, we find good agreement.
 
-Using the value of $f = 0.755$ expected at $\ell_\nu = 0$, we calculate that we expect $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and overplot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
+Using $f_\infty = 0.755$ we estimate that $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and overplot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
 This value is coincidentally very near the value of $\delta_{0.5}$ achieved in our highest-$\mR$ simulations.
@@
 
+In summary, we find that $\delp$ decreases as $\mR$ increases.
+We find that these changes are likely caused by increases in $f$.
+In our simulations, these increases in $f$ seem to be caused by changes in the size of the viscous boundary layer $\ell_\nu$.
+By measuring $f$ and $\ell_\nu$ in a simulation, the value of $f_\infty$ can be found from Eqn.~\ref{eqn:f_infty}.
+
+While we have examine a Case I simulation with $\mP = 4$ here, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
+In this simulation, we measure $\xi \approx 0.6$, $f \approx 0.785$, $\ell_\nu \approx 0.08$, and $L_s = 1$.
+We therefore estimate that
+\begin{equation}
+f_\infty = 0.86\qquad\rm{and}\qquad
+\xi = 0.6
+\label{eqn:f_xi_estimates}
+\end{equation}
+are good first estimates for $f$ and $\xi$ when applying our theory of penetrative convection to stellar models.
+
 \section{A modified solar model}
 \label{sec:solar_model}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth]{mesa_profiles.pdf}
+\caption{
+(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a MESA solar model with a penetration zone.
+(bottom) The difference in the sound speed in the MESA model with a PZ that is presented in the top panel compared to a model run at identical parameters but without a PZ.
+We see that the addition of a PZ increases the sound speed in a bump by O(1-2\%) below the convection zone.
+\label{fig:mesa_profiles}
+}
+\end{figure}
+
 Our simulation results present a strong case for the validity of a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
-In general, out of the simulations presented in this work, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
-In this simulation, we found $f \approx 0.8$ and $\xi \approx 0.6$.
-We note that Fig.~\ref{fig:parameters_vs_re} suggests that $f$ could increase by $\sim 0.1$ as $\mR$ increases into the stellar regime but $\xi$ probably doesn't change much.
-As such, we take $f = 0.9$ and $\xi = 0.6$ as first-guess values for our theory of convective penetration in stellar regimes.
-These values should of course be confirmed and tuned in more realistic stellar settings which include spherical geometry and realistic density stratifications.
-
-In spherical geometry, if the horizontal averages of Eqn.~\ref{eqn:integral_constraint} are replaced with integrals over latitude and longitude, the relevant integral constraint for convective penetration can be described in terms of the convective luminosity,
+In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
+To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
 \begin{equation}
@@
 \int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
+\label{eqn:sphere_xi_defn}
 \end{equation}
 where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
-This is the generalized version of Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
-A first-guess at the equivalent of Eqn.~\ref{eqn:theory_fraction} in stellar contexts is
+Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
+Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
 \begin{equation}
@@
 
-We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.9$ and $\xi = 0.6$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
-We chose a value of $\xi = 1$ as it is the most conservative choice and should generally result in smaller penetration zones, and because it is unclear how our plane-parallel intuition for $\xi$ in this study maps into spherical geometry.
-We of course note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
+We note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
 We present this model as a proof of concept and to inspire further work.
 
-In Fig.~\ref{fig:mesa} we display the profile of X quantity at the base of a solar model using a penetrative zone (as described above) and using X classical prescription.
-Note the differences in this thing and that thing.
-
-TODO: Implement this in MESA, and make a simple figure comparing some solar profiles near the base of the CZ!
-
-We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
-Early studies suggest that the maximum depth of a PZ should be 0.1 $H_p$ \citep{basu_etal_1994}.
-More recent work puts tighter helioseismic constraints on observations of $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
-However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
-We hope to improve this model and stuff in future work, please hang out with us and make it better.
+In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from a 1 $M_\odot$ MESA model which has been evolved to an age of 4.56 Gyr and which includes convective penetration.
+Note that $\justgrad$ (green) remains close to $\gradad$ (purple) below the Schwarzschild convective boundary ($\gradad = \gradrad$) in a penetration zone.
+After some depth $\justgrad \rightarrow \gradrad$ (orange) in the star's interior.
+We additionally evolved a standard solar MESA model to a 4.56 Gyr age without the inclusion of a PZ.
+We compare the sound speed profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
+We see that the inclusion of a PZ leads to an O(1-2\%) bump-like increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
+
+At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.030R_\odot$, such that this PZ extends $\sim 36$\% of a scale height below the convection zone.
+Helioseismic studies have suggested that a PZ depth should be constrained to 5-10\% of $H_P$ \citep{basu_etal_1994, basu2016}; these constraints are significantly smaller than our crude model.
+Some recent simulations \citep{kapyla2019} have suggested that solar convection could exhibit penetration depths of $0.2 H_P$, which are closer to these models but still smaller than what we measure.
+Despite these discrepancies, Fig.~\ref{fig:mesa_profiles} shows the promise of a convective penetration parameterization such as the one presented here.
+Pathways for improving our parameterization will be discussed in the following section.
 
@@
 \begin{acknowledgments}
-We'd like to thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
+We thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
@@
 Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
+The Flatiron Institute is supported by the Simons Foundation.
 \end{acknowledgments}
@@
 \label{app:simulation_table}
+Input parameters and measured output values of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.
 
@@
 \tabletypesize{\footnotesize}
-\caption{Table of simulation information
+\caption{Table of simulation information TODO describe it better.
 \label{table:simulation_info}

### 2021-07-16 data/plot_results_vs_re.py

@@ -44,6 +44,7 @@ for i, d in enumerate(dirs):
         modern_f = f['modern_f'][()]
         modern_xi = f['modern_xi'][()]
         fconv_Ls = f['fconv_Ls'][()]
+        fconv_cz = f['fconv_cz'][()]
         Ls = np.mean(f['Ls'][()])
         tot_time = times[-1] - times[0]
         time_window = np.min((500, tot_time/2))
@@ -55,6 +56,7 @@ for i, d in enumerate(dirs):
         std_f   = np.std(modern_f[good_times])/np.sqrt(len(modern_f[good_times]))
         mean_xi = np.mean(modern_xi[good_times])
         mean_fconv_Ls = np.mean(fconv_Ls[good_times])
+        mean_fconv_cz = np.mean(fconv_cz[good_times])
     if 'stressfree' in d:
         sf = True
     else:
@@ -97,7 +99,7 @@ for i, d in enumerate(dirs):
             pz_visc_bl = visc_bl_upper_top - visc_bl_upper_bot
 
 
-    data.append((S, P, Re, Ls, Lz, sf, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, mean_xi, mean_fconv_Ls, bot_visc_bl, pz_visc_bl, std_f))
+    data.append((S, P, Re, Ls, Lz, sf, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, mean_xi, mean_fconv_Ls, mean_fconv_cz, bot_visc_bl, pz_visc_bl, std_f))
 data = np.array(data)
 S = data[:,0]
 P = data[:,1]
@@ -112,18 +114,19 @@ L_d09 = data[:,8]
 theory_f  = data[:,9]
 theory_xi = data[:,10]
 fconv_Ls = data[:,11]
-bot_bl = data[:,12]
-pz_bl  = data[:,13]
-std_f  = data[:,14]
+fconv_cz = data[:,12]
+bot_bl = 2*data[:,13]
+pz_bl  = data[:,14]
+std_f  = data[:,15]
 
 fig = plt.figure(figsize=(page_width, 2*page_width/(3*golden_ratio)))
 
[…]

### 2021-07-16 data/plot_results_vs_s.py

@@ -79,7 +79,7 @@ ax1.set_ylabel(r'$\delta_{\rm{p}}$')
 smooth_S = np.logspace(1, 4, 100)
 ax2.plot(smooth_S, 1.5*smooth_S**(-1/2), c='orange', label=r'$\mathcal{S}^{-1/2}$')
 ax2.scatter(S[good], L_d09[good] - L_d01[good], c='k')
-ax2.legend(frameon=True, fontsize=8, framealpha=0.6)
+ax2.legend(loc='lower left', frameon=True, fontsize=8, framealpha=0.6)
 ax2.set_yscale('log')
 ax2.set_xlim(80, 4000)
 ax2.set_ylim(2e-2, 3e-1)

### 2021-07-16 data/plot_theory_profiles.py

@@ -13,8 +13,13 @@ import pandas as pd
 col_width = 3.25
 golden_ratio = 1.61803398875
 
+brewer_green  = np.array(( 27,158,119, 255))/255
+brewer_orange = np.array((217, 95,  2, 255))/255
+brewer_purple = np.array((117,112,179, 255))/255
+
 #d = directory = 'erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart4/'
-d = directory = 'new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/'
+#d = directory = 'new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/'
+d = directory = 'noslip_erf_Re_cut/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/'
 filename = directory + '/avg_profs/averaged_avg_profs.h5'
 
 S = float(d.split('_S')[-1].split('_')[0])
@@ -22,10 +27,13 @@ P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
 Re = float(d.split('_Re')[-1].split('_')[0])
 Lz = float(d.split('_Lz')[-1].split('_')[0])
 
-fig = plt.figure(figsize=(2*col_width, 0.7*col_width/golden_ratio))
-ax1 = fig.add_axes([0.00,    0, 0.27, 1])
-ax2 = fig.add_axes([0.38,    0, 0.27, 1])
-ax3 = fig.add_axes([0.75,    0, 0.27, 1])
+fig_grad = plt.figure(figsize=(col_width, col_width/golden_ratio))
+fig_theory = plt.figure(figsize=(col_width, 1.5*col_width/golden_ratio))
+
+ax_grad = fig_grad.add_subplot(1,1,1)
+
+ax_flux   = fig_theory.add_axes([0.00, 0.50, 1, 0.5])
+ax_source = fig_theory.add_axes([0.00, 0.00, 1, 0.5])
 
[…]

### 2021-07-19 manuscript/ms.tex
updates with most of Daniel's recommendations

@@
 
-The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes.
+The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes \citep{zahn1991, brummell_etal_2002, korre_etal_2019}.
 The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
 The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
-We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology.
 Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
@@
 \caption{
-Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
+Vertical slice through a simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
 The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
 The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
-(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
-(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
+(Left) Vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly at the top of the penetration zone where $\justgrad$ departs from $\gradad$.
+(Right) Temperature fluctuations, normalized by their average magnitude at each height to clearly display all dynamical features.
 %Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
@@
 Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
-While a clear link between stiffness and entrainment and overshoot has seemingly emerged in these simple simulation setups, a clear mechanism for penetration remains elusive.
+While a link between stiffness and entrainment and overshoot processes has seemingly emerged in previous work, a mechanism for penetration remains elusive.
 
@@
 There are hints in the literature that convective penetration may be dependent upon energy fluxes.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
 Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
-Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
 Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
@@
 
-Convective penetration is the process by which realistic convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient towards the adiabatic.
+Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
 \begin{quote}
@@
 \end{quote}
-Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
+Thus, the penetration length can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
 
@@
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
-In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
+In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
 In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
@@
 \caption{
-Measured time- and horizontally-averaged vertical profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
+Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
 We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
@@
 \label{sec:theory}
-We will now derive a theoretical model in which to understand convective penetration.
-We will build this model through an examination of the energetics and energy fluxes within the convecting region.
-In Sec.~\ref{sec:theory_equations}, we will describe our equations and problem setup and define the heat fluxes.
-In Sec.~\ref{sec:theory_energy}, we will build a parameterized theory based on the kinetic energy equation and these fluxes.
+In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the convection and penetration zones.
+In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
+In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
+We find that excess KE in the convection zone can cause a penetration zone to form.
+By balancing the excess KE in the convection zone with a buoyancy-braking work term in the PZ, we are able to derive the size of the PZ.
 We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
@@
 Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
 We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
@@
 where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
-We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
+The mean temperature profile $\overline{T}$ carries the radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
 We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
-We define the gradient and radiative gradient 
+We define the temperature gradient and radiative temperature gradient 
 \begin{equation}
@@
 We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
-Marginal stability is achieved when $\justgrad = \gradad$, a constant.
+Marginal stability is achieved when $\justgrad = \gradad$, which we take to be a constant.
 We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.
@@
 \caption{
-(upper) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in the simulation shown in Fig.~\ref{fig:vertical_dynamics_panels}. 
-$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
-Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
-Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
-(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
+Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
+The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
+(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
+(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
+The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
 \label{fig:theory_profiles}
@@
 \end{equation}
-It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, upper panel).
+Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panel}.
+As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
+In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous terms which are only nonzero near the bottom boundary.
+We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
+In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.
+
+At the boundaries of the convecting region, $\bar{\mathcal{F}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
 We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
@@
 
-We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
-We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
+We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
+The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
 Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
@@
 \end{equation}
-Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
+Eqn.~\ref{eqn:constraint_cz_pz_split} is arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
 If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
@@
 \begin{enumerate}
-\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
-Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
+\item In the limit that $f \rightarrow 0$, viscous dissipation is inefficient.
+Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
@@
 \end{enumerate}
-In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
+In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured from simulations.
 Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).
-
-Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
+Our simulations produce typical values of $f \sim 0.7$.
+
+Assuming that a PZ of height $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
 \begin{equation}
@@
 \end{equation}
-Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a measurable parameter bounded by ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
+Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation rate in the CZ and $\xi$ is a measurable parameter in ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
 In words, we assume that $\bar{\Phi}(z = L_s) \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and that $\bar{\Phi}$ decreases with height in the PZ.
@@
 \end{equation}
-In order to derive a specific prediction for the PZ depth, one must specify the vertical shape of $\overline{\Fconv}$.
+The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
+This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary.
+A parameterization like Eqn.~\ref{eqn:theory_fraction} can be implemented in stellar structure codes and used to find the extent of penetration zones under the specification of $f$ and $\xi$.
+The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
+In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
+
+In order to derive a specific prediction for the PZ height, one must specify the vertical shape of $\overline{\Fconv}$.
 We will study two cases in this work, laid out below.
-In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant small length $\epsilon$ above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
-\begin{equation}
-\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
-= -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
+In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux slightly above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
+\begin{equation}
+%\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
+\mP \equiv -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
 \label{eqn:theory_P_defn}
@@
 
-The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
-This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary (which we quantify in Eqn.~\ref{eqn:theory_P_defn}).
-The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
-In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
-
 \subsubsection{Case I: Discontinuous flux}
@@
 Here, $\Fcz$ is a constant value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the CZ over a depth $L_{\rm{CZ}}$ below $L_s$ and the PZ over a depth $\delp$ above $L_s$, we predict
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the CZ over a depth $L_{\rm{CZ}}$ below $L_s$ and the PZ over a height $\delp$ above $L_s$, we predict
 \begin{equation}
@@
 \end{equation}
-Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is roughly linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation at large $\mP_D$.
+Assuming that $f$ and $\xi$ are weak functions of $\mP_D$, we see that, for small $\mP_D$, the size of the penetration region is linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation.
 Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
@@
 where $\zeta \equiv (\xi f/2)\sqrt{\mP_L/(1-f)}$.
-So we expect the penetration depth to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
+We expect the penetration height to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
 
@@
 \section{Simulation Details}
-We will now describe a set of simulations that we have made to test the predictions in Sec.~\ref{sec:theory}.
+We will now describe a set of simulations that test the predictions in Sec.~\ref{sec:theory}.
 While many simulations of convection interacting with radiative zones have been performed by previous authors, ours differ in two crucial ways.
-First, we define the ``Penetration Parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
-We construct our experiments so that $\mP$ and $\mS$ (the stiffness, Eqn.~\ref{eqn:stiffness}) can be varied separately.
+First, we construct our experiments so that $\mP$ and $\mS$ can be varied separately.
+$\mP$ is the ``Penetration Parameter,'' defined in Eqn.~\ref{eqn:theory_P_defn}, which compares the magnitude of the convective flux in the CZ and PZ; $\mS$ is the ``stiffness,'' defined in Eqn.~\ref{eqn:stiffness}, and compares the buoyancy frequency in the stable radiative zone to the convective frequency.
 We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
-Second, as we will show in Sec.~\ref{sec:results}, the development of penetrative zones is a slow process and it is possible that many prior studies did not evolve simulations for long enough to see these regions saturate.
+Second, as we will show in Sec.~\ref{sec:results}, the development of penetrative zones is a slow process and many prior studies did not evolve simulations for long enough to see these regions grow and saturate.
 
@@
 Q = \begin{cases}
-0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
-Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \delta_H
+0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \Delta_H,\\
+Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \Delta_H
 \end{cases}.
@@
 \end{equation}
-The integrated value of the flux through the system from the heating is therefore $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
-Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
+The integrated flux through the system from heating is $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\Delta_H$.
+Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\Delta_H = 0.2$ so $F_H = 0.2$.
 We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
@@
 
-We expect the average convective velocities to depend on the magnitude of the heating, $\angles{\vec{|u|}} \approx Q_{\rm{mag}}^{1/3} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{|u|}} / L_s \approx 1$.
+The average convective velocity depends on the magnitude of the heating, $\angles{\vec{|u|}} \approx Q_{\rm{mag}}^{1/3} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{|u|}} / L_s \approx 1$.
 The stiffness is defined,
@@
 In our nondimensionalization, $N^2 = \gradad - \gradrad$.
-We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\justgrad$, which in turn sets the value of $k$ in the radiative zone.
-
-Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the degree of turbulence.
-The value of $\mR$ roughly corresponds to the value of the peak Reynolds number $\rm{Re} = \mR |\vec{u}|$ measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
+We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\gradrad$, which in turn sets the value of $k$ in the radiative zone.
+
+Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
+The value of $\mR$ roughly corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
 Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
@@
 \begin{split}
-&k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
+&k_{\rm{RZ}} = \frac{\Delta_H}{\mS\mP_D},\\
 &k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \mu + \mP_D^{-1}},\\
@@
 \subsection{Case II: Piecewise linear flux}
-We additionally study a select few simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
+We also study simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
 We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
@@
 \begin{equation}
-\partial_z k_0 = \frac{\delta_H}{L_s \mS \psi},\qquad
-k_b = \frac{\delta_H\mu}{\mS\psi},\qquad
+\partial_z k_0 = \frac{\Delta_H}{L_s \mS \psi},\qquad
+k_b = \frac{\Delta_H\mu}{\mS\psi},\qquad
 \gradad = Q \mS \psi,
@@
 In the limit that $d_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
-While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $d_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $d_w = 0.075$.
+For Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $d_w = 0.02$; while for Eqn.~\ref{eqn:sim_discontinuous_k} we use $d_w = 0.075$.
 In all other cases, we use $d_w = 0.05$.
@@
 We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
-All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [TODO CITE].
 
@@
 \caption{
-(left top panel) Shown is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
+(left top panel) The PZ height $\delta_{0.5}$ vs.~time.
 We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
@@
 (right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
-The line color denotes the time, according to the time traces in the left panels.
+The line color denotes the time, following the time traces in the left panels.
 The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
@@
 
-\subsection{Penetration depth measurements}
+\subsection{Penetration height measurements}
 In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
@@
 \begin{equation}
-\Delta\justgrad \equiv \gradad(z) - \gradrad(z).
-\end{equation}
-We measure penetration and overshoot depths in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
+\Delta \equiv \gradad(z) - \gradrad(z).
+\end{equation}
+We measure penetration and overshoot heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
 Specifically,
 \begin{equation}
-L_s + \delta_{h} = \rm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta\justgrad).
+L_s + \delta_{h} = \mathrm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta).
 \label{eqn:delta_p_measures}
@@
 In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ roughly represents the width of the ``thermal adjustment layer.''
+Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
 We will simply refer to these as three different measures of the top of the PZ.
@@
 Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
-The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
-The Case I penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
-The Case II penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
-In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
-We generally find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration depths.
-In the bottom panels, we measure the evolved values of $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
+The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
+The Case I penetration heights (upper left) vary linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
+The Case II penetration heights (upper right) vary like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
+In the middle panels, we measure $f$ according to Eqn.~\ref{eqn:f_defn}.
+We find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
+In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
 We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
@@
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
-In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose temperature profile has $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
+In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of convective overturn (freefall) times.
 The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
 We plot their rolling mean, averaged over 200 freefall time units. 
-We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
+We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full height.
 We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
-The evolved value of $f$ indicates that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
+The evolved value of $f$ indicates that roughly 2/3 of the buoyancy driving is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
 The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.
 
-In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals, where the color of the profiles corresponds to time, as in the left panels.
+In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
 $\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
@@
 The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
 %This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.
 
-We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
-It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of the bulk of the simulations in this work.
+This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
 To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
@@
 While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
-For details on precisely how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
-``We reinitialize the simulation with a better guess''.
+In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
+For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
 
@@
 \caption{
-(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
-While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
+(Left panel) Penetration heights are shown as a function of stiffness for simulations with a discontinuous conductivity.
+While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
 (Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
@@
 \subsection{Dependence on $\mP$}
-We find that the depth of the penetration zone is strongly dependent on $\mP$.
-In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
+We find that the height of the penetration zone is strongly dependent on $\mP$.
+In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot the penetration height ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
 The fixed values of $\mR$ and $\mS$ are shown above these panels.
 We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
-At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
-At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and PZ depths saturate.
-
-The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that it is reasonable but imprecise to assume that $f$ and $\xi$ are constant as a function of $\mP$.
-We find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
+At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
+At large values of $\mP$, penetration height falls off of these predicted scaling laws.
+In this regime, dissipation dominates over buoyancy in the PZ and PZ heights saturate.
+
+The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that that $f$ and $\xi$ are to leading order constant with $\mP$.
+However, we find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
 We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
 We note a weak trend where $f$ decreases as $\mP$ increases.
-Most of this trend can be explained by slight decreases in the CZ velocities and corresponding decreases in the dissipation.
-We speculate that when $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
+As $\mP$ incraeses, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
+When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
 As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
 A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
-This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ compared to the PZ.
-As the size of the PZ grows, dynamics have the space to change appreciably from their bulk-CZ properties, and so $\xi$ shrinks.
+Recall that smaller values of $\xi$ indicate the dissipative dynamics are rather different in the PZ and CZ.
+As the size of the PZ grows, the dynamical structures of the PZ shift from what is found in the CZ, and so $\xi$ shrinks.
 
@@
 
-We find that the depth of the penetration zone is weakly dependent on $\mS$.
-In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
-We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat more strongly.
-In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
+We find that the height of the penetration zone is weakly dependent on $\mS$.
+In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
+We find that the mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
+In other words, the transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
 To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
-We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
+We find that the width of this region varies according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
 %This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
 
-We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
-As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our turbulent cases.
+Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
+As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
+
+\subsection{Dependence on $\mR$}
+
+We find that the height of the penetration zone is weakly dependent on $\mR$.
+In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration height with the Reynolds number.
+In order to understand how this could happen at fixed $\mP$, we also plot the output values of $f$ (upper middle) and $\xi$ (upper right).
+We find that $f$ increases with increasing $\mR$, but is perhaps leveling off as $\mR$ becomes large.
+We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
+Eqn.~\ref{eqn:discontinuous_prediction} predicts that $\delp$ should change at fixed $\mP$ and $\xi$ if $f$ is changing.
+In the bottom left panel, we show that the change in $\delp$ is due to this change in $f$.
+We find that this is true both for simulations with stress-free dynamical boundary conditions (open symbols, SF) and for no-slip conditions (closed symbols, NS).
 
@@
 \caption{
-(Upper left panel) Penetration depths are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
+(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
 We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
 In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
-(Upper middle panel) We similarly see increases in the value of $f$ with $\mR$, although perhaps this measurement is leveling off at high values of $\mR$.
-(Upper right panel) We do not see large changes in the value of $\xi$ as $\mR$ increases, suggesting that the nature of dissipation in the PZ is not appreciably changing.
-(Lower left panel) In summary, we see a strong correlation between $\delta_{0.5}$ and $f$.
+(Upper middle panel) $f$ also increases with $\mR$.
+(Upper right panel) $\xi$ does not change appreciably with $\mR$ for turbulent simulations with $\mR \geq 200$.
+(Lower left panel) There is a strong correlation between $\delta_{0.5}$ and $f$, agreeing with our theoretical model of Eqn.~\ref{eqn:discontinuous_prediction}.
 (Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
-This makes sense, as more of the convective domain is available for the convective flows to dissipate energy.
-(Lower right panel) The viscous boundary layer follows a classical scaling laws seen in Rayleigh-B\'{e}nard convection, and so we anticipate that the trend in $\delta_{0.5}$ vs $\mR$ should saturate as $\delta_{\nu} \rightarrow 0$ and $f$ saturates.
+(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\delta_{\nu} \rightarrow 0$.
 \label{fig:parameters_vs_re}
@@
 
-\subsection{Dependence on $\mR$}
-
-We find that the depth of the penetration zone is weakly dependent on $\mR$.
-In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth with the Reynolds number.
-In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
-We find that $f$ increases with increasing $\mR$, but is perhaps leveling off as $\mR$ becomes large.
-We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
-Indeed, the variation of $\delp$ with $\mR$ can be seen as a variation of $\delp$ with $f$ in the bottom left panel.
-We find that this is true both for simulations with stress-free dynamical boundary conditions (open symbols, SF) and for no-slip conditions (closed symbols, NS).
-
-We now examine why $f$ increases as $\mR$ increases.
-In the SF simulations, within the CZ, We can reasonably approximate $\bar{\Phi}$ as a constant in the bulk and zero within the viscous boundary layer,
+We now examine why $f$ increases as $\mR$ increasesIn the SF simulations, within the CZ, we can reasonably approximate $\bar{\Phi}$ as a constant $\Phi_{\rm{CZ}}$ in the bulk and zero within the viscous boundary layer,
 \begin{equation}
@@
 \end{equation}
-where $\Phi_{\rm{CZ}}$ is a constant and $\ell_\nu$ is the viscous boundary layer depth.
+where $\ell_\nu$ is the viscous boundary layer depth.
 We have visualized a NS dissipation profile in the bottom panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
-Under this model, we have
+Then, we have
 \begin{equation}
@@
 
-In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that Eqn.~\ref{eqn:f_infty} with $f_\infty = 0.755$ describes the high-$\mR$ data well.
-We measure the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary, and take $\ell_\nu$ to be the twice that height.
+In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that Eqn.~\ref{eqn:f_infty} with $f_\infty = 0.755$ captures the high-$\mR$ behavior.
+To measure $\ell_\nu$, we first measure the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary, and take $\ell_\nu$ to be the twice that height.
 We find that Eqn.~\ref{eqn:f_defn} is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore Eqn.~\ref{eqn:cz_dissipation_model} is a poor model for $z \leq \ell_\nu$.
@@
 
-Indeed, we use the fitted function of $f$ from the bottom middle panel, along with Eqn.~\ref{eqn:discontinuous_prediction}, to estimate $\delta_{0.5}$ in the bottom left panel, and we overplot that as a line.
+We use the fitted function of $f$ from the bottom middle panel, along with Eqn.~\ref{eqn:discontinuous_prediction}, to estimate $\delta_{0.5}$ in the bottom left panel.
 We need to multiply this equation by a factor of 0.9, which accounts for some differences between the simulations and the idealized ``discontinuous flux'' theoretical model.
@@
 
-Using $f_\infty = 0.755$ we estimate that $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and overplot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
+Using $f_\infty = 0.755$ we estimate that $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and plot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
 This value is coincidentally very near the value of $\delta_{0.5}$ achieved in our highest-$\mR$ simulations.
-Unfortunately, we cannot probe more turbulent simulations than these.
-We can only run the $\mR = 6.4 \times 10^{3}$ simulations for a few hundred freefall times.
-Our accuracy in measuring results from these simulations is limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}).
-Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ depths of these simulations are converged to within a few percent.
-Future work should aim to better understand the trend of PZ depth with turbulence.
-However, the displayed relationships between $\delp$ and $f$, $f$ and $\ell_\nu$, and $\ell_\nu$ and $\mR$ --- all of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
+Unfortunately, we cannot probe more turbulent simulations.
+We can only run the $\mR = 6.4 \times 10^{3}$ simulation for a few hundred freefall times.
+Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of the simulation (see Fig.~\ref{fig:time_evolution}).
+Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ heights of this simulation are converged to within a few percent.
+Future work should aim to better understand the trend of PZ height with turbulence.
+However, the displayed relationships between $\delp$ and $f$, $f$ and $\ell_\nu$, and $\ell_\nu$ and $\mR$ --- all of which are effects we largely understand --- suggest that PZ heights should saturate at high $\mR$.
 
 In summary, we find that $\delp$ decreases as $\mR$ increases.
-We find that these changes are likely caused by increases in $f$.
+We find that these changes are caused by increases in $f$.
 In our simulations, these increases in $f$ seem to be caused by changes in the size of the viscous boundary layer $\ell_\nu$.
 By measuring $f$ and $\ell_\nu$ in a simulation, the value of $f_\infty$ can be found from Eqn.~\ref{eqn:f_infty}.
+Stellar convection zones are not adjacent to hard walls and so should be represented by the $\ell_\nu \rightarrow 0$ limited.
+Core convection zones geometrically have no lower boundary, and convective shells should be bounded both above and below by penetrative regions.
 
@@
 (bottom) The difference in the sound speed in the MESA model with a PZ that is presented in the top panel compared to a model run at identical parameters but without a PZ.
-We see that the addition of a PZ increases the sound speed in a bump by O(1-2\%) below the convection zone.
+We see that the addition of a PZ increases the sound speed by $\mathcal{O}$(1-2\%) below the convection zone.
 \label{fig:mesa_profiles}
@@
 
-Our simulation results present a strong case for the validity of a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
+Our simulation results present a strong case for a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
 In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
@@
 
-We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
-We note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to determine an estimate of how the convective overshoot parameterization presented in this work might adjust a familiar stellar model.
+We note that the simulations that we have presented here do not include many of the complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
 We present this model as a proof of concept and to inspire further work.
@@
 We compare the sound speed profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
-We see that the inclusion of a PZ leads to an O(1-2\%) bump-like increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
+We see that the inclusion of a PZ leads to an $\mathcal{O}$(1-2\%) increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
 
@@
 \label{sec:discussion}
-In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild convective boundary.
+In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild boundary.
 To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
 In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
-We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
+We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
-We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
-
-Our simulation results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
-In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
-
-The simulations we presented in this work were the simplest possible simulations to try to test the basic tenets of our theory.
-In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
+We briefly examined what the impliciations of this theory could be for a simple solar model.
+
+Our simulation results suggest that stellar convection zones should be bounded by sizeable penetration zones.
+In extreme simulations, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
+
+The simulations we presented in this work use a simplified setup to test the basic tenets of our theory.
+In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together determine the height of the penetration zone.
 The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} here.
@@
 Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
-Future work should aim to understand whether $f$ and $\xi$ depend strongly on $\Pran$ in the turbulent regime.
+Future work should aim to understand whether $f$ and/or $\xi$ depend strongly on $\Pran$ in the turbulent regime.
 
@@
 
-Finally, we note that our work here assumes a uniform composition through the convective and radiative region.
-Frequently within stars, convective boundaries coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
-Future work should also aim to determine if stabilizing composition gradients can prevent the formation of penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
+Our work here assumes a uniform composition through the convective and radiative region.
+Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
+Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
 
@@
 We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
+This work was supported by NASA HTMS grant 80NSSC20K1280.
 Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
@@
 This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
-This same separation of scales is observed in the left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
-
-In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
+This same separation of scales is observed in the penetrative dynamics in this work, and so similar techniques should be applicable.
+
+To more quickly determine the final size of the evolved penetration zones we use the following algorithm.
 \begin{enumerate}
@@
 \end{itemize}
-\item We restart from step 1.
+\item Return to step 1.
 \end{enumerate}
@@
 However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/8$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
-AE simulations with orange lines start with PZ depths which are much larger than the final depth, while green line solution start with initial PZ depths which are smaller than the expected depth.
+AE simulations with orange lines start with PZ heights which are much larger than the final height, while green line solution start with initial PZ heights which are smaller than the expected height.
 Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
-After converging to within a few percent of the proper penetration zone depth, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
+After converging to within a few percent of the proper penetration zone height, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
 These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration before jumping back towards it in the next iteration.
-If the PZ depth continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the evolution of $\delp$ vs.~time has flattened.
+If the PZ height continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the changes of $\delp$ have diminished.
 
@@
 \label{fig:AE_time_figure}
-(top row) Time traces of $\delta_{0.1}$ and $\delta_{0.9}$ for simulations which are computed using (black lines) standard timestepping, (orange lines) accelerated evolution with large initial values of $\delp$, and (green lines) accelerated evolution with small initial values of $\delp$.
+(top row) Time traces of $\delta_{0.5}$ for simulations using standard timestepping (black lines), accelerated evolution with large initial values of $\delp$ (orange lines), and accelerated evolution with small initial values of $\delp$ (green lines).
 The thin horizontal lines represent the final converged values from the standard timestepping simulations.
-Accelerated evolution timesteps can be seen as discontinuities in the $\delp$ trace.
+Accelerated evolution timesteps can be seen as jumps in the $\delp$ trace.
 Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.
@@
 All accelerated evolution simulations were run for $t_{\rm{sim}} = 3000$ freefall times.
-The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), or $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
-The vertical green-and-yellow bars show the total length of the accelerated simulation in terms of the classic simulation; so the vertical lines in the upper right panel show that the accelerated simulation was converged after $\sim$ 5\% of the classic simulation.
-(Bottom row) Same as top row, but where a rolling average of $f$ over 200 freefall times is shown.
+The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), and $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
+The vertical green-and-yellow bars show the total simulation time of the accelerated simulation in terms of the direct simulation time; i.e., the accelerated simulation converged in only $\sim$ 5\% of the simulation time of the direct simulation for $\mP = 4$.
+(Bottom row) Rolling average of $f$ over 200 freefall times, plotted in the same way as $\delta_{0.5}$.
 }
@@
 \label{app:simulation_table}
-Input parameters and measured output values of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.
+Input parameters and summary statistics of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.
 
@@
 \tabletypesize{\footnotesize}
-\caption{Table of simulation information TODO describe it better.
+\caption{Table of simulation information.
 \label{table:simulation_info}
@@
 \tablecomments{                          
+Simulation type is specified as ``D'' for discontinuous/Case I or ``L'' for linear/Case II.
+``D/SF'' simulations have stress-free boundary conditions.
+Input control parameters are listed for each simulation: the penetration parameter $\mP$, stiffness $\mS$, and freefall Reynolds number $\mR$.
+We also note the coefficient resolution (Chebyshev coefficients $nz$ and Fourier coeficients $nx$, $ny$).
+We report the number of freefall time units each simulation was run for $t_{\rm{sim}}$.
+Time-averaged values of the departure heights ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$), the dissipation fraction $f$, and the dissipation fall-off $\xi$, as well as the average convection zone velocity $\angles{u}$ are reported.
+We take these time averages over the final 1000 freefall times of the simulation.
+For short simulations $(t_{\rm{sim}} < 1000)$, we average over most of the simulation run time, but not early dynamical transients.
 }                                                          	

### 2021-07-19 manuscript/ms.tex
some changes to abstract and intro; need more

@@
 Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
-Here we examine how convective motions mix entropy and in turn extend the size of the convection zone, a process referred to as convective penetration.
-We derive a ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
-Following \citet{roxburgh1989} and \citet{zahn1991}, we construct a model of penetration based on an energy balance, and find that the extent of penetration is controlled by $\mP$.
-We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
+Here we examine how convective motions efficiently mix entropy in the radiative zone.
+We present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
+To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
+We conduct 3D simulations with Dedalus using a simplified Boussinesq model of stellar convection including a radiative flux, and we find good agreement between simulations and the derived theory.
 We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
-We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
-We further discuss prospects for extending these results to more realistic stellar contexts.
+We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
+We discuss prospects for extending these results to more realistic stellar contexts.
 \end{abstract}
@@
 Studies which more closely model the conditions inside of stars have presented confusing results.
-Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+Many studies have exhibited hints of penetrative convection -- that is, the mixing of the entropy towards an adiabatic profile beyond the convective boundary.
+Some of these studies exhibit dynamical or flux-based hints of penetration (the convective flux is negative and the radiative flux carries more than the total flux going through the simulation), but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}
+Others report a change of the entropy gradient towards the adiabatic beyond the convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, rogers_etal_2006, kitiashvili_etal_2016}
+Some simulations show little evidence of true penetration \citep[see e.g., the superadiabaticity profiles of][]{higl_etal_2021}.
 These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
@@
 We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
-This work was supported by NASA HTMS grant 80NSSC20K1280.
+This work was supported by NASA HTMS grant 80NSSC20K1280 and NASA SSW grant 80NSSC19K0026.
 Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.

### 2021-07-19 manuscript/ms.tex
Update ms.tex
Abstract

@@
 Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
-Here we examine how convective motions efficiently mix entropy in the radiative zone.
-We present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
+Here we present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
 To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
 Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
-We conduct 3D simulations with Dedalus using a simplified Boussinesq model of stellar convection including a radiative flux, and we find good agreement between simulations and the derived theory.
-We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
+We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
+Although it can take thousands of overturn times to develop, in all cases we find significant convective penetration.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.

### 2021-07-19 manuscript/ms.tex
updates to MESA fig with new model and to intro lit-recap

@@
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
-We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
+We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$50\% of a pressure scale height.
 We discuss prospects for extending these results to more realistic stellar contexts.
@@
 
-Studies which more closely model the conditions inside of stars have presented confusing results.
-Many studies have exhibited hints of penetrative convection -- that is, the mixing of the entropy towards an adiabatic profile beyond the convective boundary.
-Some of these studies exhibit dynamical or flux-based hints of penetration (the convective flux is negative and the radiative flux carries more than the total flux going through the simulation), but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}
-Others report a change of the entropy gradient towards the adiabatic beyond the convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, rogers_etal_2006, kitiashvili_etal_2016}
-Some simulations show little evidence of true penetration \citep[see e.g., the superadiabaticity profiles of][]{higl_etal_2021}.
-These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
-Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
-This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
+Many studies in both Cartesian and spherical geometries have exhibited hints of penetrative convection.
+Some authors report clear mixing of the entropy gradient beyond the nominal convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, rogers_etal_2006, kitiashvili_etal_2016}, but it is often unclear how much mixing is due to changes in the location of the Schwarzschild boundary (entrainment) and how much is pure penetration.
+Other authors present simulations with dynamical or flux-based hints of penetration such as a negative convective flux or a radiative flux which exceeds the total system flux, but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}.
+Still other simulations show negligible penetration \citep[e.g.,][]{higl_etal_2021}.
+Even detailed studies which sought a relationship between penetration depth and stiffness $\mS$ have presented contradictory results.
+Early work by e.g., \citet{hurlburt_etal_1994, singh_etal_1995} hinted at a link between $\mS$ and penetration length, at least for low values of $\mS$.
+Subsequent simulations by \citet{brummell_etal_2002} exhibit a weak scaling of penetration depth with $\mS$; the authors interpret this scaling as a sign of pure overshoot and claim their simulations do not achieve adiabatic convective penetration.
+Still later simulations by \citet{rogers_glatzmaier_2005} demonstrate a negligible scaling of the penetration depth against $\mS$ at moderate values of $\mS$.
+Prior simulations thus consistently show hints of penetration at low $\mS$ \citep[where results may not be relevant for stars,][]{couston_etal_2017}, but present confusing and contradictory results at moderate-to-high $\mS$.
 
@@
 (bottom) The difference in the sound speed in the MESA model with a PZ that is presented in the top panel compared to a model run at identical parameters but without a PZ.
-We see that the addition of a PZ increases the sound speed by $\mathcal{O}$(1-2\%) below the convection zone.
+We see that the addition of a PZ increases the sound speed by $\mathcal{O}$(2\%) below the convection zone.
 \label{fig:mesa_profiles}
@@
 We compare the sound speed profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
-We see that the inclusion of a PZ leads to an $\mathcal{O}$(1-2\%) increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
-
-At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.030R_\odot$, such that this PZ extends $\sim 36$\% of a scale height below the convection zone.
+We see that the inclusion of a PZ leads to an $\mathcal{O}$(2\%) increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
+
+At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot$, such that this PZ extends $\sim 50$\% of a scale height below the convection zone.
 Helioseismic studies have suggested that a PZ depth should be constrained to 5-10\% of $H_P$ \citep{basu_etal_1994, basu2016}; these constraints are significantly smaller than our crude model.

### 2021-07-20 dedalus_code/erf_step_3D.py
adds specifiable prediction width; cleans up config scripts

@@ -47,6 +47,7 @@ Options:
 
     --adiabatic_IC             If flagged, set the background profile as a pure adiabat (not thermal equilibrium in RZ)
     --predictive=<delta>       A guess for delta_P the penetration depth. The initial state grad(T) will be an erf from grad(T_ad) to grad(T_rad) centered at L_cz + delta_P
+    --predictive_width=<w>     Erf width for predictive ICs [default: 0.05]
     --plot_model               If flagged, create and plt.show() some plots of the 1D atmospheric structure.
 
     --T_iters=<N>              Number of times to iterate background profile before pure timestepping [default: 100]
@@ -495,7 +496,8 @@ def run_cartesian_instability(args):
             z_p = L_cz + float(args['--predictive'])
             logger.info('using predictive 1D ICs with zp: {:.2f}'.format(z_p))
 
-            T_z = -grad_ad + (T_rad_z0['g'] + grad_ad)*zero_to_one(z_de, z_p, width=0.05)
+            width = float(args['--predictive_width'])
+            T_z = -grad_ad + (T_rad_z0['g'] + grad_ad)*zero_to_one(z_de, z_p, width=width)
             T1_z['g'] = T_z - T0_z['g']
             T1_z.antidifferentiate('z', ('right', 0), out=T1)
 

### 2021-07-20 dedalus_code/damping_erf_step_3D.py
cleans up pleiades job scripts

@@ -1,789 +1,0 @@
-"""
-Dedalus script for a two-layer, Boussinesq simulation.
-The bottom of the domain is at z = 0.
-The lower part of the domain is stable; the domain is Schwarzschild stable above z >~ 1.
-
-There are 6 control parameters:
-    Re      - The approximate reynolds number = (u / diffusivity) of the evolved flows
-    Pr      - The Prandtl number = (viscous diffusivity / thermal diffusivity)
-    P       - The penetration parameter; When P >> 1 there is lots of convective penetration (of order P); when P -> 0 there is none.
-    S       - The stiffness: the characteristic ratio of N^2 (above the penetration region) compared to the square convective frequency.
-    zeta    - The fraction of the convective flux carried by the adiabatic gradient at z = 0 (below the heating layer)
-    Lz      - The height of the box
-    aspect  - The aspect ratio (Lx = aspect * Lz)
-
-Usage:
-    damping_erf_step_3D.py [options] 
-    damping_erf_step_3D.py <config> [options] 
-
-Options:
-    --Re=<Reynolds>            Freefall reynolds number [default: 1e2]
-    --Pr=<Prandtl>             Prandtl number = nu/kappa [default: 0.5]
-    --P=<penetration>          ratio of CZ convective flux / RZ convective flux [default: 1]
-    --S=<stiffness>            The stiffness [default: 1e2]
-    --zeta=<frac>              Fbot = zeta * F_conv [default: 1e-3]
-    --Lz=<L>                   Depth of domain [default: 2]
-    --aspect=<aspect>          Aspect ratio of domain [default: 2]
-    --L_cz=<L>                 Height of cz-rz erf step [default: 1]
-
-    --nz=<nz>                  Vertical resolution   [default: 256]
-    --nx=<nx>                  Horizontal (x) resolution [default: 32]
-    --ny=<ny>                  Horizontal (y) resolution (sets to nx by default)
-    --RK222                    Use RK222 timestepper (default: RK443)
-    --SBDF2                    Use SBDF2 timestepper (default: RK443)
-    --safety=<s>               CFL safety factor [default: 0.75]
-    --mesh=<m>                 Processor distribution mesh (e.g., "4,4")
-
[…]

### 2021-07-20 manuscript/ms.tex
Added MESA details

--- 2021-07-19 manuscript/ms.tex
@@
 \begin{abstract}
-Most stars host convection zones in which heat is transported directly by fluid motion.
+Most stars host convection zones, in which heat is transported directly by fluid motion.
 Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
-Here we present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
-To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
-Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
-We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
-Although it can take thousands of overturn times to develop, in all cases we find significant convective penetration.
+Here we examine how convective motions mix entropy and in turn extend the size of the convection zone, a process referred to as convective penetration.
+We derive a ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we construct a model of penetration based on an energy balance, and find that the extent of penetration is controlled by $\mP$.
+We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
-We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
-We discuss prospects for extending these results to more realistic stellar contexts.
+We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
+We further discuss prospects for extending these results to more realistic stellar contexts.
 \end{abstract}
@@
 \label{sec:introduction}
-
-\subsection{Context}
 Convection is a crucial mechanism for transporting heat in stars~\citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
@@
 
-The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes \citep{zahn1991, brummell_etal_2002, korre_etal_2019}.
-The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
-The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
-Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
-The primary focus of this work is convective penetration.
+The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
+The first class is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
+The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
+We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
+We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
+We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.
 
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
-\caption{
-Vertical slice through a simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
-The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
-The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
-(Left) Vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly at the top of the penetration zone where $\justgrad$ departs from $\gradad$.
-(Right) Temperature fluctuations, normalized by their average magnitude at each height to clearly display all dynamical features.
-%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
-\label{fig:vertical_dynamics_panels}
-}
-\end{figure*}
-
-Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
+Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+Experiments exhibiting extensive convective penetration have a long history \citep[dating back to e.g.,][]{musman1968, deardorff_etal_1969, moore_weiss_1973}.
+Modern experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
 The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
-Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
-Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
-While a link between stiffness and entrainment and overshoot processes has seemingly emerged in previous work, a mechanism for penetration remains elusive.
-
-Studies which more closely model the conditions inside of stars have presented confusing results.
-Many studies have exhibited hints of penetrative convection -- that is, the mixing of the entropy towards an adiabatic profile beyond the convective boundary.
-Some of these studies exhibit dynamical or flux-based hints of penetration (the convective flux is negative and the radiative flux carries more than the total flux going through the simulation), but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}
-Others report a change of the entropy gradient towards the adiabatic beyond the convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, rogers_etal_2006, kitiashvili_etal_2016}
-Some simulations show little evidence of true penetration \citep[see e.g., the superadiabaticity profiles of][]{higl_etal_2021}.
-These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
-Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
-This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
+Some recent studies in simplified Boussinesq setups suggest that the penetration depth is highly dependent on the stiffness \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
+Many studies of density-stratified convective atmospheres find significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, dietrich_wicht_2018}.
+However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
+Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
+This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but the precise results of past studies are often contradictory and no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.
 
 There are hints in the literature that convective penetration may be dependent upon energy fluxes.
-\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
+\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
 \citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
 Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
-Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
+Indeed, some simulations have tested this idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
 Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
@@
 
-\subsection{Convective penetration \& this study's findings}
-
-Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
-\begin{quote}
-\emph{
-In this paper, we present simulations which exhibit convective penetration.
-}
-\end{quote}
-This process is phenomenologically described in Sec.~\ref{sec:central_results}.
-
-In order to understand this phenomenon, we derive theoretical predictions for the size of the penetrative zone based on the ideas of \citet{roxburgh1989} and \citet{zahn1991}.
-%We design and carry out numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+In this work, we design two numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
+We use a modified incompressible, Boussinesq model to study the simplest possible system, and derive theoretical predictions for the size of the penetrative zone.
+We test this theory using 3D numerical simulations.
 \begin{quote}
@@
 \end{quote}
-Thus, the penetration length can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
+Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
 
 We present these findings as follows.
-In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
-In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
+In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and derive predictions for our two experimental designs from that theory.
 In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
-In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
+In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
 In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
-Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.
-
-\section{Central Result: Convective Penetration}
-\label{sec:central_results}
-
-In Fig.~\ref{fig:vertical_dynamics_panels}, we display a snapshot of dynamics in an evolved simulation which exhibits convective penetration.
-The simulation domain is a 3D Cartesian box, and this figure shows a vertical slice through the center of the domain.
-In the left panel, we display the vertical velocity.
-We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
-These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the temperature gradient departs from adiabatic towards the radiative gradient.
-In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
-We see that warm upwellings in the Schwarzschild-unstable convection zone (below the dashed line) become cold upwellings in the penetration zone (above the dashed line), and these motions excite gravity waves in the stable radiative zone (above the solid line).
-
-We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
-The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
-The radiative gradient $\gradrad$ is shown in orange.
-The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
-Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
-However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
-Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
-
-Our goals in this paper are to understand how these PZs form, and to parameterize this effect so that it can be included in 1D stellar evolution calculations.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth]{grad_profiles.pdf}
-\caption{
-Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
-We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
-\label{fig:grad_profiles}
-}
-\end{figure}
+Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.
 
@@
 \label{sec:theory}
-In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the convection and penetration zones.
-In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
-In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
-We find that excess KE in the convection zone can cause a penetration zone to form.
-By balancing the excess KE in the convection zone with a buoyancy-braking work term in the PZ, we are able to derive the size of the PZ.
-We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
 
@@
 \label{sec:theory_equations}
-Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
+Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
 \begin{align}
@@
 Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
 We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
@@
 
-Assuming convection reaches a time-stationary state, the heat fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
+Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
 \begin{equation}
@@
 where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
-The mean temperature profile $\overline{T}$ carries the radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
+We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
 We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
-We define the temperature gradient and radiative temperature gradient 
+We define the gradient and radiative gradient 
 \begin{equation}
@@
 We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions and intuition.
-Marginal stability is achieved when $\justgrad = \gradad$, which we take to be a constant.
+Marginal stability is achieved when $\justgrad = \gradad$, a constant.
 We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.
@@
 In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
-Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but in this incompressible model where there is no density stratification to break the symmetry of upflows and downflows precisely the same arguments can be applied to the inverted problem.
+Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but the same logic applies to the inverted problem.
 
@@
 \label{sec:theory_energy}
-
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
-\includegraphics[width=\columnwidth]{theory_profiles.pdf}
+\includegraphics[width=\textwidth]{theory_profiles.pdf}
 \caption{
-Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
-The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
-(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
-(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
-The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
+(left) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in a simulation. 
+$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
+Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
+Here, we have neglected the viscous portion of the fluxes; this contributes negligibly in the bulk, and is zero by construction at $z = [0, 2]$.
+(middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
+(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
 \label{fig:theory_profiles}
 }
-\end{figure}
+\end{figure*}
 
-Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
+Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
 \begin{equation}
@@
 \end{equation}
-Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panel}.
-As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
-In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous terms which are only nonzero near the bottom boundary.
-We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
-In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.
-
-At the boundaries of the convecting region, $\bar{\mathcal{F}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
-We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
+It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
+We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
 \begin{equation}
@@
 
-We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
-The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
+We now find it instructive to break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
+We note that the buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
 Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
@@
 \end{equation}
-Eqn.~\ref{eqn:constraint_cz_pz_split} is arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
-If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
-This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
-We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
-We now parameterize the fraction of the buoyant engine consumed by CZ dissipation,
+Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
+We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
+We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
 \begin{equation}
@@
 \begin{equation}
-\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
-+ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
-= (1 - f).
+\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
++ \frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+= 1 - f,
 \label{eqn:first_pz_parameterization}
 \end{equation}
-We will measure and report the values of $f$ achieved in our simulations in this work.
-Eqn.~\ref{eqn:first_pz_parameterization} provides two limits on a hypothetical PZ:
+and we can immediately read off limits on a hypothetical PZ according to $f$,
 \begin{enumerate}
-\item In the limit that $f \rightarrow 0$, viscous dissipation is inefficient.
-Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
+\item Viscous dissipation is inefficient in the limit that $f \rightarrow 0$.
+Reasonably also assuming that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
@@
 \end{enumerate}
-In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured from simulations.
-Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).
-Our simulations produce typical values of $f \sim 0.7$.
+In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
+Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).
 
-Assuming that a PZ of height $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
+Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
 \begin{equation}
@@
 \end{equation}
-Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation rate in the CZ and $\xi$ is a measurable parameter in ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
+Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a measurable parameter bounded by ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
 In words, we assume that $\bar{\Phi}(z = L_s) \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and that $\bar{\Phi}$ decreases with height in the PZ.
@@
 \end{equation}
-The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
-This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary.
-A parameterization like Eqn.~\ref{eqn:theory_fraction} can be implemented in stellar structure codes and used to find the extent of penetration zones under the specification of $f$ and $\xi$.
-The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
-In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
-
-In order to derive a specific prediction for the PZ height, one must specify the vertical shape of $\overline{\Fconv}$.
+In order to derive a specific prediction for the PZ depth, one must specify the vertical shape of $\overline{\Fconv}$.
 We will study two cases in this work, laid out below.
-In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux slightly above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
+In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
 \begin{equation}
-%\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
-\mP \equiv -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
+\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
+= -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
 \label{eqn:theory_P_defn}
@@
 Here, $\Fcz$ is a constant value of flux carried in the convection zone and $\mP_D$ is the penetration parameter (subscript D for discontinuous case).
-Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the CZ over a depth $L_{\rm{CZ}}$ below $L_s$ and the PZ over a height $\delp$ above $L_s$, we predict
+Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the CZ over a depth $L_{\rm{CZ}}$ below $L_s$ and the PZ over a depth $\delp$ above $L_s$, we predict
 \begin{equation}
@@
 \end{equation}
-Assuming that $f$ and $\xi$ are weak functions of $\mP_D$, we see that, for small $\mP_D$, the size of the penetration region is linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation.
+Assuming that $f$ is a weak function of $\mP_D$, we see that the size of the penetration region is roughly linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation at large $\mP_D$.
 Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
@@
 where $\zeta \equiv (\xi f/2)\sqrt{\mP_L/(1-f)}$.
-We expect the penetration height to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
+So we expect the penetration depth to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
 
@@
 \section{Simulation Details}
-We will now describe a set of simulations that test the predictions in Sec.~\ref{sec:theory}.
-While many simulations of convection interacting with radiative zones have been performed by previous authors, ours differ in two crucial ways.
-First, we construct our experiments so that $\mP$ and $\mS$ can be varied separately.
-$\mP$ is the ``Penetration Parameter,'' defined in Eqn.~\ref{eqn:theory_P_defn}, which compares the magnitude of the convective flux in the CZ and PZ; $\mS$ is the ``stiffness,'' defined in Eqn.~\ref{eqn:stiffness}, and compares the buoyancy frequency in the stable radiative zone to the convective frequency.
-We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
-Second, as we will show in Sec.~\ref{sec:results}, the development of penetrative zones is a slow process and many prior studies did not evolve simulations for long enough to see these regions grow and saturate.
-
 We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
@@
 Q = \begin{cases}
-0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \Delta_H,\\
-Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \Delta_H
+0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
+Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \delta_H
 \end{cases}.
@@
 \end{equation}
-The integrated flux through the system from heating is $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\Delta_H$.
-Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\Delta_H = 0.2$ so $F_H = 0.2$.
+The integrated value of the flux through the system from the heating is therefore $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
+Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
 We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
-Furthermore, since the conductivity is not zero at the bottom boundary, the adiabatic temperature gradient there carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
+We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
 
-The average convective velocity depends on the magnitude of the heating, $\angles{\vec{|u|}} \approx Q_{\rm{mag}}^{1/3} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{|u|}} / L_s \approx 1$.
+We expect the average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
 The stiffness is defined,
@@
 \mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
-\label{eqn:stiffness}
 \end{equation}
@@
 In our nondimensionalization, $N^2 = \gradad - \gradrad$.
-We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\gradrad$, which in turn sets the value of $k$ in the radiative zone.
+We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\justgrad$, which in turn sets the value of $k$ in the radiative zone.
 
-Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
-The value of $\mR$ roughly corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
+The crucial place in which our model differs from that of prior work is that we define the ``Penetration Parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
+We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
+We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$, and therefore found negligible penetration for moderate to high stiffness.
+
+Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the degree of turbulence.
+The value of $\mR$ roughly corresponds to the value of the peak Reynolds number $\rm{Re} = \mR |\vec{u}|$ measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
 Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
@@
 \begin{split}
-&k_{\rm{RZ}} = \frac{\Delta_H}{\mS\mP_D},\\
+&k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
 &k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \mu + \mP_D^{-1}},\\
@@
 \subsection{Case II: Piecewise linear flux}
-We also study simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
+We additionally study a select few simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
 We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
@@
 \begin{equation}
-\partial_z k_0 = \frac{\Delta_H}{L_s \mS \psi},\qquad
-k_b = \frac{\Delta_H\mu}{\mS\psi},\qquad
+\partial_z k_0 = \frac{\delta_H}{L_s \mS \psi},\qquad
+k_b = \frac{\delta_H\mu}{\mS\psi},\qquad
 \gradad = Q \mS \psi,
@@
 We use a domain aspect ratio of two so that $x \in [0, L_x]$ and $y \in [0, L_y]$ with $L_x = L_y = 2 L_z$.
-To avoid aliasing errors, we use the 3/2-dealiasing rule in all directions.
 To start our simulations, we add random noise temperature perturbations with a magnitude of $10^{-3}$ to a background temperature profile $\overline{T}$; we discuss the choice of $\overline{T}$ in appendix \ref{app:accelerated_evolution}.
@@
 \begin{equation}
-H(z; z_0, d_w) = \frac{1}{2}\left(1 + \mathrm{erf}\left[\frac{z - z_0}{d_w}\right]\right).
+H(z; z_0, d_w) = \frac{1}{2}\left(1 + \rm{erf}\left[\frac{z - z_0}{d_w}\right]\right).
 \label{eqn:heaviside}
@@
 In the limit that $d_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
-For Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $d_w = 0.02$; while for Eqn.~\ref{eqn:sim_discontinuous_k} we use $d_w = 0.075$.
+While constructing Eqn.~\ref{eqn:sim_Q} and Eqn.~\ref{eqn:sim_linear_k}, we use $d_w = 0.02$; while constructing Eqn.~\ref{eqn:sim_discontinuous_k} we use $d_w = 0.075$.
 In all other cases, we use $d_w = 0.05$.
@@
 We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
-All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [TODO CITE].
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [CITE].
+
+\subsection{Penetration depth measurements}
+In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
+In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
+We define the difference between the adiabatic and radiative gradient,
+\begin{equation}
+\Delta\justgrad \equiv \gradad(z) - \gradrad(z).
+\end{equation}
+We measure penetration and overshoot depths in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
+Specifically,
+\begin{equation}
+L_s + \delta_{h} = \rm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta\justgrad).
+\label{eqn:delta_p_measures}
+\end{equation}
+In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
+Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ roughly represents the width of the ``thermal adjustment layer.''
+We will simply refer to these as three different measures of the top of the PZ.
+We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
 
@@
 \caption{
-(left top panel) The PZ height $\delta_{0.5}$ vs.~time.
+(left top panel) Shown is a trace of the PZ depth $\delta_{0.5}$ vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units (defined using the background $k$ in the radiative zone) on the upper x-axis.
 We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
@@
 (right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
-The line color denotes the time, following the time traces in the left panels.
+The line color denotes the time, according to the time traces in the left panels.
 The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
@@
 
-\subsection{Penetration height measurements}
-In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
-In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
-We define the difference between the adiabatic and radiative gradient,
-\begin{equation}
-\Delta \equiv \gradad(z) - \gradrad(z).
-\end{equation}
-We measure penetration and overshoot heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
-Specifically,
-\begin{equation}
-L_s + \delta_{h} = \mathrm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta).
-\label{eqn:delta_p_measures}
-\end{equation}
-In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
-We will simply refer to these as three different measures of the top of the PZ.
-We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
+\section{Results}
+\label{sec:results}
 
+\subsection{Qualitative description of simulation evolution}
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
+\caption{
+Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
+In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
+(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
+(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
+Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
+\label{fig:vertical_dynamics_panels}
+}
+\end{figure*}
+
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
+In the top left panel, we display the measured extent of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
+We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution of the bulk of the simulations in this work (see Appendix \ref{app:accelerated_evolution} for details).
+
+The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
+We plot the rolling mean, averaged over 200 freefall time units. 
+We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full depth.
+We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
+The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.
+
+In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
+$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
+We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.
+
+In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
+We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
+Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
+On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
+These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
+
+\subsection{Dependence on $\mP$}
 \begin{figure*}[t]
@@
 Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
-The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
-The Case I penetration heights (upper left) vary linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
-The Case II penetration heights (upper right) vary like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
-In the middle panels, we measure $f$ according to Eqn.~\ref{eqn:f_defn}.
-We find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
-In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
+The top panels show the measured penetration depths according to Eqn.~\ref{eqn:delta_p_measures}.
+The Case I penetration depths (upper left) vary roughly linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
+The Case II penetration depths (upper right) vary roughly like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
+In the middle panels, we measure the evolved value of $f$ according to Eqn.~\ref{eqn:f_defn}.
+We generally find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration depths.
+In the bottom panels, we measure the evolved values of $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
 We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
@@
 
-\section{Results}
-\label{sec:results}
+We find that the depth of the penetration zone is strongly dependent on $\mP$.
+In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot measured values of the penetration depth ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
+The fixed values of $\mR$ and $\mS$ are shown above these panels.
+We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
+At small values of $\mP$ we see somewhat weaker scalings than these predictions; this is a numerical artifact caused by the fact that the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
+At large values of $\mP$, penetration depths begin to fall off of these predicted scaling laws, which makes sense: in this regime, dissipation dominates over buoyancy in the PZ and PZ depths saturate.
 
-We will now present on the results of the 3D dynamical simulations described in the previous section.
-Dynamics in these simulations resemble those previously shown in Fig.~\ref{fig:vertical_dynamics_panels}.
-To quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory}, we will present time- and volume-averaged scalar quantities, as well as some select horizontally-averaged vertical profiles.
+The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that it is reasonable but imprecise to assume that $f$ and $\xi$ are constant as a function of $\mP$.
+We find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
+We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
+We note a weak trend where $f$ increases as $\mP$ decreases.
+Most of the trend of $f$ increasing as $\mP$ decreases can be explained by slight increases in the CZ velocities and corresponding increases in the dissipation.
+We speculate that, as $\mP$ decreases, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) more efficiently deflects convective velocities sideways before they have a chance to buoyantly break, thereby slightly increasing bulk-CZ velocities.
+A similar trend of $\xi$ increasing as $\mP$ decreases can be seen.
+This makes sense: $\xi$ is a measure of how different dissipative dynamics are in the CZ and the PZ.
+As the size of the PZ shrinks, dynamics do not have the space to change appreciably from their bulk-CZ properties, and so $\xi$ is closer to one.
 
-\subsection{Qualitative description of simulation evolution}
+\subsection{Dependence on $\mS$}
 
-%\begin{figure*}[t]
-%\centering
-%\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
-%\caption{
-%Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
-%In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
-%(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
-%(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
-%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
-%\label{fig:vertical_dynamics_panels}
-%}
-%\end{figure*}
+We find that the depth of the penetration zone is weakly dependent on $\mS$.
+In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration depth of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
+We find that the mean penetration depth $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary somewhat strongly.
+In other words, the smooth transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
+To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
+We find that the width of this region roughly varies according to a $\mS^{-1/2}$ scaling law, which is reminiscent of the pure-overshoot laws described by \citet{korre_etal_2019}.
+This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose temperature profile has $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
-In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of convective overturn (freefall) times.
-The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
-We plot their rolling mean, averaged over 200 freefall time units. 
-We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full height.
-We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
-The evolved value of $f$ indicates that roughly 2/3 of the buoyancy driving is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
-The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.
+We note briefly that if the enstrophy, $\omega^2$ in the convection zone exceeded the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
+As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our turbulent cases.
 
-In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
-$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
-The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
-We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
-The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
-%This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.
-
-This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
-It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
-To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
-We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
-Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
-While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
-In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
-For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
-
-%In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
-%We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
-%Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
-%On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
-%These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
-
-\begin{figure*}[t]
+\begin{figure*}[t!]
 \centering
@@
 \caption{
-(Left panel) Penetration heights are shown as a function of stiffness for simulations with a discontinuous conductivity.
-While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
+(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
+While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
 (Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
@@
 
-\subsection{Dependence on $\mP$}
-We find that the height of the penetration zone is strongly dependent on $\mP$.
-In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot the penetration height ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
-The fixed values of $\mR$ and $\mS$ are shown above these panels.
-We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
-At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
-At large values of $\mP$, penetration height falls off of these predicted scaling laws.
-In this regime, dissipation dominates over buoyancy in the PZ and PZ heights saturate.
-
-The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that that $f$ and $\xi$ are to leading order constant with $\mP$.
-However, we find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
-We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
-We note a weak trend where $f$ decreases as $\mP$ increases.
-As $\mP$ incraeses, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
-When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
-As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
-A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
-Recall that smaller values of $\xi$ indicate the dissipative dynamics are rather different in the PZ and CZ.
-As the size of the PZ grows, the dynamical structures of the PZ shift from what is found in the CZ, and so $\xi$ shrinks.
-
-\subsection{Dependence on $\mS$}
-
-We find that the height of the penetration zone is weakly dependent on $\mS$.
-In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
-We find that the mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
-In other words, the transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
-To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
-We find that the width of this region varies according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
-%This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
-
-Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
-As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
-
 \subsection{Dependence on $\mR$}
 
-We find that the height of the penetration zone is weakly dependent on $\mR$.
-In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration height with the Reynolds number.
-In order to understand how this could happen at fixed $\mP$, we also plot the output values of $f$ (upper middle) and $\xi$ (upper right).
+We find that the depth of the penetration zone is weakly dependent on $\mR$.
+In the upper left panel of Fig.~\ref{fig:parameters_vs_re}, we find a logarithmic decrease in the penetration depth with the Reynolds number.
+In order to understand how this could happen at fixed $\mP$, we plot the output values of our parameterized values $f$ (upper middle) and $\xi$ (upper right).
 We find that $f$ increases with increasing $\mR$, but is perhaps leveling off as $\mR$ becomes large.
 We find that $\xi$ does not increase strongly with $\mR$ except for in the case of laminar simulations with $\mR < 200$.
-Eqn.~\ref{eqn:discontinuous_prediction} predicts that $\delp$ should change at fixed $\mP$ and $\xi$ if $f$ is changing.
-In the bottom left panel, we show that the change in $\delp$ is due to this change in $f$.
+Indeed, the variation of $\delp$ with $\mR$ can be seen as a variation of $\delp$ with $f$ in the bottom left panel.
 We find that this is true both for simulations with stress-free dynamical boundary conditions (open symbols, SF) and for no-slip conditions (closed symbols, NS).
 
-\begin{figure*}[t]
+In order to understand this better, we note that the dissipation profile can reasonably be approximated as a constant value in the CZ and zero in the bottom viscous boundary layer.
+We have visualized a NS dissipation profile in the right panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
+We can model the dissipation in the $f$ definition (Eqn.~\ref{eqn:f_defn}) as
+\begin{equation}
+\int_{\rm{CZ}} \bar{\Phi}\,dz \approx C ( L_s - \delta_\nu ),
+\end{equation}
+where $C$ is a constant dissipation value in the CZ and $\delta_\nu$ is the boundary layer depth.
+In this model, we expect the dissipation and therefore $f$ to vary linearly with the viscous boundary layer depth.
+We measure the viscous boundary layer depth by finding the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary.
+In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that $f \propto \delta_\nu$ is a decent description for the SF simulations (NS simulations show an increase at small $\delta_\nu$, but also have maximized dissipation in the bounary layer).
+In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
+If you assume the Nusselt Number dependence on the Rayleigh number is Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
+The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.} \citep{ahlers_etal_2009, goluskin2016}.
+Combining these trends, we expect $f \propto \mR^{-2/3}$, and so expect the changes in $f$ and $\delp$ to level off as $\mR$ increases to high values in the astrophysical regime.
+
+Unfortunately, we are limited by the long evolutionary timescales of these simulations (see Fig.~\ref{fig:time_evolution}), so we cannot extend our study to more turbulent simulations and higher values of $\mR$ than the ones shown here.
+We are only able to run the NS simulation at $\mR = 6.4 \times 10^3$ for a few hundred freefall times, and so cannot investigate the nature of these trends further.
+However, the link between $\delp$ and $f$ and the link between $f$ and $\delta_\nu$ --- both of which are effects we largely understand --- suggest that PZ depths should saturate at high $\mR$.
+
+\begin{figure*}[t!]
 \centering
-\includegraphics[width=\textwidth]{parameters_vs_re.pdf}
+\includegraphics{parameters_vs_re.pdf}
 \caption{
-(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
+(Upper left panel) Penetration depths are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
 We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
 In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
-(Upper middle panel) $f$ also increases with $\mR$.
-(Upper right panel) $\xi$ does not change appreciably with $\mR$ for turbulent simulations with $\mR \geq 200$.
-(Lower left panel) There is a strong correlation between $\delta_{0.5}$ and $f$, agreeing with our theoretical model of Eqn.~\ref{eqn:discontinuous_prediction}.
-(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
-(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\delta_{\nu} \rightarrow 0$.
+(Upper middle panel) We similarly see increases in the value of $f$ with $\mR$, although perhaps this measurement is leveling off at high values of $\mR$.
+(Upper right panel) We do not see large changes in the value of $\xi$ as $\mR$ increases, suggesting that the nature of dissipation in the PZ is not appreciably changing.
+(Lower left panel) In summary, we see a strong correlation between $\delta_{0.5}$ and $f$.
+(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\delta_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
+This makes sense, as more of the convective domain is available for the convective flows to dissipate energy.
+(Lower right panel) The viscous boundary layer follows a classical scaling laws seen in Rayleigh-B\'{e}nard convection, and so we anticipate that the trend in $\delta_{0.5}$ vs $\mR$ should saturate as $\delta_{\nu} \rightarrow 0$ and $f$ saturates.
 \label{fig:parameters_vs_re}
@@
 
-We now examine why $f$ increases as $\mR$ increasesIn the SF simulations, within the CZ, we can reasonably approximate $\bar{\Phi}$ as a constant $\Phi_{\rm{CZ}}$ in the bulk and zero within the viscous boundary layer,
-\begin{equation}
-\bar{\Phi}(z) = 
-\begin{cases}
-\Phi_{\rm{CZ}} 	& z > \ell_\nu \\
-0				& z \leq \ell_\nu
-\end{cases},
-\label{eqn:cz_dissipation_model}
-\end{equation}
-where $\ell_\nu$ is the viscous boundary layer depth.
-We have visualized a NS dissipation profile in the bottom panel of Fig.~\ref{fig:theory_profiles}; SF simulations look similar in the bulk, but drop towards zero at the bottom boundary rather than reaching a maximum.
-Then, we have
-\begin{equation}
-\int_{\rm{CZ}} \bar{\Phi}\,dz \approx \Phi_{\rm{CZ}} \left( L_s - \ell_\nu \right),
-\end{equation}
-and so per Eqn.~\ref{eqn:f_defn},
-\begin{equation}
-f = f_\infty\left(1 - \frac{\ell_\nu}{L_s}\right),
-\label{eqn:f_infty}
-\end{equation}
-where $f_\infty$ is the expected value of $f$ at $\mR = \infty$ when $\ell_\nu = 0$.
-So we see that the CZ dissipation and therefore $f$ vary linearly with $\ell_\nu$.
-
-In the bottom middle panel of Fig.~\ref{fig:parameters_vs_re}, we find that Eqn.~\ref{eqn:f_infty} with $f_\infty = 0.755$ captures the high-$\mR$ behavior.
-To measure $\ell_\nu$, we first measure the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary, and take $\ell_\nu$ to be the twice that height.
-We find that Eqn.~\ref{eqn:f_defn} is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore Eqn.~\ref{eqn:cz_dissipation_model} is a poor model for $z \leq \ell_\nu$.
-In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
-If you assume the Nusselt Number dependence on the Rayleigh number is throttled by the boundaries, Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
-The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.
-} \citep{ahlers_etal_2009, goluskin2016}.
-Combining these trends, we expect 
-\begin{equation}
-f = f_\infty(1 - C \mR^{-2/3})
-\end{equation}
-for a constant $C$.
-Thus as $\mR \rightarrow \infty$, $f \rightarrow f_\infty$.
-
-We use the fitted function of $f$ from the bottom middle panel, along with Eqn.~\ref{eqn:discontinuous_prediction}, to estimate $\delta_{0.5}$ in the bottom left panel.
-We need to multiply this equation by a factor of 0.9, which accounts for some differences between the simulations and the idealized ``discontinuous flux'' theoretical model.
-First, due to internal heating and the finite width of the conductivity transition around the Schwarzschild boundary, the convective flux is not truly constant through the full depth of the CZ.
-Thus, we expect $L_{\rm{CZ}}$  in Eqn.~\ref{eqn:discontinuous_prediction} to be smaller than 1.
-Furthermore, the theory is derived in the limit of an instantaneous transition from $\gradad$ to $\gradrad$ where $\delta_{0.1} = \delta_{0.5} = \delta_{0.9}$; our simulations have a finite transition width.
-Despite these subtle differences, we find good agreement.
-
-Using $f_\infty = 0.755$ we estimate that $\delta_{0.5} \approx 0.31$ for $\mR \rightarrow \infty$ and plot this as a horizontal orange line on the upper left panel of Fig.~\ref{fig:parameters_vs_re}.
-This value is coincidentally very near the value of $\delta_{0.5}$ achieved in our highest-$\mR$ simulations.
-Unfortunately, we cannot probe more turbulent simulations.
-We can only run the $\mR = 6.4 \times 10^{3}$ simulation for a few hundred freefall times.
-Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of the simulation (see Fig.~\ref{fig:time_evolution}).
-Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ heights of this simulation are converged to within a few percent.
-Future work should aim to better understand the trend of PZ height with turbulence.
-However, the displayed relationships between $\delp$ and $f$, $f$ and $\ell_\nu$, and $\ell_\nu$ and $\mR$ --- all of which are effects we largely understand --- suggest that PZ heights should saturate at high $\mR$.
-
-In summary, we find that $\delp$ decreases as $\mR$ increases.
-We find that these changes are caused by increases in $f$.
-In our simulations, these increases in $f$ seem to be caused by changes in the size of the viscous boundary layer $\ell_\nu$.
-By measuring $f$ and $\ell_\nu$ in a simulation, the value of $f_\infty$ can be found from Eqn.~\ref{eqn:f_infty}.
-Stellar convection zones are not adjacent to hard walls and so should be represented by the $\ell_\nu \rightarrow 0$ limited.
-Core convection zones geometrically have no lower boundary, and convective shells should be bounded both above and below by penetrative regions.
-
-While we have examine a Case I simulation with $\mP = 4$ here, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
-In this simulation, we measure $\xi \approx 0.6$, $f \approx 0.785$, $\ell_\nu \approx 0.08$, and $L_s = 1$.
-We therefore estimate that
-\begin{equation}
-f_\infty = 0.86\qquad\rm{and}\qquad
-\xi = 0.6
-\label{eqn:f_xi_estimates}
-\end{equation}
-are good first estimates for $f$ and $\xi$ when applying our theory of penetrative convection to stellar models.
-
 \section{A modified solar model}
 \label{sec:solar_model}
+Our simulation results present a strong case for the validity of a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
+In general, out of the simulations presented in this work, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
+In this simulation, we found $f \approx 0.8$ and $\xi \approx 0.6$; the results of Fig.~\ref{fig:parameters_vs_re} suggest that $f$ could increase by $\sim 0.1$ as $\mR$ increases into the stellar regime but $\xi$ probably doesn't change much.
+As such, we take $f \approx 0.9$ and $\xi \approx 0.6$ as first-guess values for our theory of convective penetration in stellar regimes.
+These values should of course be confirmed and tuned in more realistic stellar settings which include spherical geometry and realistic density stratifications.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth]{mesa_profiles.pdf}
-\caption{
-(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a MESA solar model with a penetration zone.
-(bottom) The difference in the sound speed in the MESA model with a PZ that is presented in the top panel compared to a model run at identical parameters but without a PZ.
-We see that the addition of a PZ increases the sound speed by $\mathcal{O}$(1-2\%) below the convection zone.
-\label{fig:mesa_profiles}
-}
-\end{figure}
-
-Our simulation results present a strong case for a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
-In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
-To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
+In spherical geometry, if the horizontal averages of Eqn.~\ref{eqn:integral_constraint} are replaced with integrals over latitude and longitude, the relevant integral constraint for convective penetration can be described in terms of the convective luminosity,
 \begin{equation}
@@
 \int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
-\label{eqn:sphere_xi_defn}
 \end{equation}
 where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
-Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
-Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
+This is the generalized version of Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
+A first-guess at the equivalent of Eqn.~\ref{eqn:theory_fraction} in stellar contexts is
 \begin{equation}
@@
 
-We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to determine an estimate of how the convective overshoot parameterization presented in this work might adjust a familiar stellar model.
-We note that the simulations that we have presented here do not include many of the complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.9$ and $\xi = 1$ to determine an extremely rough first-estimate of how the dissipative treatment presented in this work might adjust a familiar stellar model.
+We chose a value of $\xi = 1$ as it is the most conservative choice and should generally result in smaller penetration zones, and because it is unclear how our plane-parallel intuition for $\xi$ in this study maps into spherical geometry.
+We of course note that the work that we presented here is done under the incompressible approximation and does not include the many complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
 We present this model as a proof of concept and to inspire further work.
 
-In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from a 1 $M_\odot$ MESA model which has been evolved to an age of 4.56 Gyr and which includes convective penetration.
-Note that $\justgrad$ (green) remains close to $\gradad$ (purple) below the Schwarzschild convective boundary ($\gradad = \gradrad$) in a penetration zone.
-After some depth $\justgrad \rightarrow \gradrad$ (orange) in the star's interior.
-We additionally evolved a standard solar MESA model to a 4.56 Gyr age without the inclusion of a PZ.
-We compare the sound speed profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
-We see that the inclusion of a PZ leads to an $\mathcal{O}$(1-2\%) increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
+In Fig.~\ref{} we display the profile of X quantity at the base of a solar model using a penetrative zone (as described above) and using X classical prescription.
+Note the differences in this thing and that thing.
 
-At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.030R_\odot$, such that this PZ extends $\sim 36$\% of a scale height below the convection zone.
-Helioseismic studies have suggested that a PZ depth should be constrained to 5-10\% of $H_P$ \citep{basu_etal_1994, basu2016}; these constraints are significantly smaller than our crude model.
-Some recent simulations \citep{kapyla2019} have suggested that solar convection could exhibit penetration depths of $0.2 H_P$, which are closer to these models but still smaller than what we measure.
-Despite these discrepancies, Fig.~\ref{fig:mesa_profiles} shows the promise of a convective penetration parameterization such as the one presented here.
-Pathways for improving our parameterization will be discussed in the following section.
+TODO: Implement this in MESA, and make a simple figure comparing some solar profiles near the base of the CZ!
+
+We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
+Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
+However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
+We hope to improve this model and stuff in future work, please hang out with us and make it better.
 
@@
 \label{sec:discussion}
-In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild boundary.
-To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
-In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
-We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
+In this work, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
+We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the depth of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
-We briefly examined what the impliciations of this theory could be for a simple solar model.
+We furthermore examined briefly what the impliciations of this theory could be for a simple solar model.
 
-Our simulation results suggest that stellar convection zones should be bounded by sizeable penetration zones.
-In extreme simulations, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
+Our simulation results suggest that stellar convection zones should be bounded by appreciably large penetration zones.
+In extreme cases, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
 
-The simulations we presented in this work use a simplified setup to test the basic tenets of our theory.
-In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together determine the height of the penetration zone.
+The simulations we presented in this work were the simplest possible simulations to try to test the basic tenets of our theory.
+In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together fully determine the depth of the penetration zone.
 The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} here.
@@
 Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
-Future work should aim to understand whether $f$ and/or $\xi$ depend strongly on $\Pran$ in the turbulent regime.
+Future work should aim to understand whether $f$ and $\xi$ depend strongly on $\Pran$ in the turbulent regime.
 
@@
 
-Our work here assumes a uniform composition through the convective and radiative region.
-Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
-Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
+Finally, we note that our work here assumes a uniform composition through the convective and radiative region.
+Frequently within stars, convective boundaries coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
+Future work should also aim to determine if stabilizing composition gradients can prevent the formation of penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
 
@@
 \begin{acknowledgments}
-We thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
+We'd like to thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
+TODO thank Nordita program.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
-We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
-This work was supported by NASA HTMS grant 80NSSC20K1280 and NASA SSW grant 80NSSC19K0026.
 Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
-The Flatiron Institute is supported by the Simons Foundation.
 \end{acknowledgments}
@@
 This can be done because the convective dynamics converge rapidly even if the thermal profile converges slowly.
-This same separation of scales is observed in the penetrative dynamics in this work, and so similar techniques should be applicable.
+This same separation of scales is observed in the left panels of Fig.~\ref{fig:time_evolution} in this work, and so similar techniques should be applicable.
 
-To more quickly determine the final size of the evolved penetration zones we use the following algorithm.
+In this work, we accelerate the evolution of of our simulations in order to more quickly determine the final size of the evolved penetration zones according to the following algorithm.
 \begin{enumerate}
@@
 \end{itemize}
-\item Return to step 1.
+\item We restart from step 1.
 \end{enumerate}
@@
 However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/8$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
-AE simulations with orange lines start with PZ heights which are much larger than the final height, while green line solution start with initial PZ heights which are smaller than the expected height.
+AE simulations with orange lines start with PZ depths which are much larger than the final depth, while green line solution start with initial PZ depths which are smaller than the expected depth.
 Regardless of our choice of initial condition, we find that this AE procedure quickly evolves our simulations to within a few percent of the final value.
-After converging to within a few percent of the proper penetration zone height, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
+After converging to within a few percent of the proper penetration zone depth, this AE procedure continues to iteratively ``jitter'' around the right answer until the convergence criterion we described above are met.
 These jitters can be seen in the top panels of Fig.~\ref{fig:AE_time_figure}, where the solution jumps away from the proper answer in one AE iteration before jumping back towards it in the next iteration.
-If the PZ height continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the changes of $\delp$ have diminished.
+If the PZ depth continues to noticeably vary on timescales of a few hundred freefall times, we continue to timestep the simulations until the evolution of $\delp$ vs.~time has flattened.
 
-\begin{figure*}[t]
+\begin{figure*}[t!]
 \centering
@@
 \label{fig:AE_time_figure}
-(top row) Time traces of $\delta_{0.5}$ for simulations using standard timestepping (black lines), accelerated evolution with large initial values of $\delp$ (orange lines), and accelerated evolution with small initial values of $\delp$ (green lines).
+(top row) Time traces of $\delta_{0.1}$ and $\delta_{0.9}$ for simulations which are computed using (black lines) standard timestepping, (orange lines) accelerated evolution with large initial values of $\delp$, and (green lines) accelerated evolution with small initial values of $\delp$.
 The thin horizontal lines represent the final converged values from the standard timestepping simulations.
-Accelerated evolution timesteps can be seen as jumps in the $\delp$ trace.
+Accelerated evolution timesteps can be seen as discontinuities in the $\delp$ trace.
 Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.
@@
 All accelerated evolution simulations were run for $t_{\rm{sim}} = 3000$ freefall times.
-The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), and $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
-The vertical green-and-yellow bars show the total simulation time of the accelerated simulation in terms of the direct simulation time; i.e., the accelerated simulation converged in only $\sim$ 5\% of the simulation time of the direct simulation for $\mP = 4$.
-(Bottom row) Rolling average of $f$ over 200 freefall times, plotted in the same way as $\delta_{0.5}$.
+The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), or $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
+The vertical green-and-yellow bars show the total length of the accelerated simulation in terms of the classic simulation; so the vertical lines in the upper right panel show that the accelerated simulation was converged after $\sim$ 5\% of the classic simulation.
+(Bottom row) Same as top row, but where a rolling average of $f$ over 200 freefall times is shown.
 }
@@
 \label{app:mesa}
-Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
-We note that this impelementation is likely not universal or robust enough to be used in any stellar model, but it is robust enough to timestep stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
+
+Our 1D stellar evolution calculations were performed using the Modules for Experiments in Stellar Astrophysics software instrument\citep[MESA]{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
+
+\subsection{Input Physics}
+
+The MESA EOS is a blend of the OPAL \citep{Rogers2002}, SCVH
+\citep{Saumon1995}, FreeEOS \citep{Irwin2004}, HELM \citep{Timmes2000},
+and PC \citep{Potekhin2010} EOSes.
+
+Radiative opacities are primarily from OPAL \citep{Iglesias1993,
+Iglesias1996}, with low-temperature data from \citet{Ferguson2005}
+and the high-temperature, Compton-scattering dominated regime by
+\citet{Buchler1976}.  Electron conduction opacities are from
+\citet{Cassisi2007}.
+
+Nuclear reaction rates are from JINA REACLIB \citep{Cyburt2010} plus
+additional tabulated weak reaction rates \citet{Fuller1985, Oda1994,
+Langanke2000}.  (For MESA versions before 11701): Screening is
+included via the prescriptions of \citet{Salpeter1954, Dewitt1973,
+Alastuey1978, Itoh1979}.
+
+\subsection{Penetration Implementation}
+
+Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA.
+We note that this impelementation is likely not universal or robust enough to be used in most complex stellar models, but it is robust enough to time-step stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
 Future work should improve upon this model.
 
-To find the extent of the penetrative region, we override MESA's TODO routine for writing $\justgrad$ and instead have the solver follow these steps:
-\begin{enumerate}
-\item At each timestep, we find the location of the Schwarzschild convective boundary, $r_s$.
-We measure the value of the mixing length $\lambda$ there, and choose a convection zone length scale $\ell_{\rm{CZ}} = \text{min}(\lambda, L_{\rm{CZ}})$, where $L_{\rm{CZ}}$ is the full depth of the Schwarzschild-unstable convective region.
-We take the ``CZ'' integrals in Eqn.~\ref{eqn:mesa_eqn} to span radially from the Schwarzschild boundary to a depth $\ell_{\rm{CZ}}$ within the convection zone.
-\item We calculate the buoyancy integral $\int_{\rm{CZ}} L_{\rm{conv}} dr$ and the convection zone volume $V_{\rm{CZ}}$.
-\item Starting at the Schwarzschild boundary, we iteratively expand the size of the PZ until Eqn.~\ref{eqn:mesa_eqn} is satisfied.
-For each radial bin $i$ below the convection zone, we calculate $\int_{\rm{PZ},i}L_{\rm{conv}} dr$ and $V_{\rm{PZ},i}$.
-We evaluate the LHS of Eqn.~\ref{eqn:mesa_eqn} using those values.
-If LHS $\geq$ RHS, we assume that the radial coordinate of bin $i$ is the boundary of the penetrative region.
-\item We enforce $\justgrad \approx \gradad$ in the PZ by doing TODO.
-\item We ensure that the transition from the PZ to the RZ is smooth.
-Outside of the PZ, we model $\justgrad$ as TODO.
-\end{enumerate}
+To find the extent of the penetrative region we write Eqn.~\eqref{eq:mesa_eqn} as
+\begin{align}
+	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \xi f L_{\rm conv,avg,CZ} + L_{\rm conv} dr,
+	\label{eq:rwt}
+\end{align}
+where $L_{\rm conv,avg,CZ}$ is the average of $L_{\rm conv}$ in the convection zone and $L_{\rm conv}$ in the penetrative region is given by
+\begin{align}
+	L_{\rm conv} = \frac{L_{\rm rad}}{\nabla_r}(\nabla_a - \nabla_r),
+\end{align}
+which is the excess luminosity carried if the temperature gradient in the radiative zone is adiabatic.
 
-Using this procedure with $f = 0.8$ and $\xi = 1$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.
+We first integrate the left-hand side of Eqn.~\eqref{eq:rwt} over the convection zone and further use that to evaluate $L_{\rm conv,avg,CZ}$.
+Next we integrate the right-hand side of the same away from the convective boundary into the radiative zone until the equation is satisfied.
+The point where this integration stops is the edge of the penetrative region.
 
-\newpage
+We then implement convective penetration in stellar evolution with two modifications.
+First, we add an extra chemical mixing term in the penetration zone with a scale of $D \approx H_p (L/4\pi r^2 \rho)^{1/3}$, which is roughly the scale of the convective diffusivity.
+The precise choice of diffusivity here does not matter, as any plausible scale will be enough to eliminate any composition gradient on evolutionary time-scales.
+Secondly, we override the default routine in MESA for determining $\nabla$ and instead have the solver reduce $\nabla_a-\nabla$ by 90 per~cent in the penetrative zone.
+
+Using this procedure with $f = 0.86$ and $\xi = 0.6$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.
+
+\subsection{Models}
+
+Models were constructed to reasonably reproduce the present-day Sun and based on the 2019 MESA summer school lab by~\citet{pm}.
+Inlists and the \texttt{run\_star\_extras} source code are available at CITE.
+
 \section{Table of simulation parameters}
 \label{app:simulation_table}
-Input parameters and summary statistics of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.
 
@@
 \tabletypesize{\footnotesize}
-\caption{Table of simulation information.
+\caption{Table of simulation information
 \label{table:simulation_info}
@@
 \tablecomments{                                            	
-Simulation type is specified as ``D'' for discontinuous/Case I or ``L'' for linear/Case II.
-``D/SF'' simulations have stress-free boundary conditions.
-Input control parameters are listed for each simulation: the penetration parameter $\mP$, stiffness $\mS$, and freefall Reynolds number $\mR$.
-We also note the coefficient resolution (Chebyshev coefficients $nz$ and Fourier coeficients $nx$, $ny$).
-We report the number of freefall time units each simulation was run for $t_{\rm{sim}}$.
-Time-averaged values of the departure heights ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$), the dissipation fraction $f$, and the dissipation fall-off $\xi$, as well as the average convection zone velocity $\angles{u}$ are reported.
-We take these time averages over the final 1000 freefall times of the simulation.
-For short simulations $(t_{\rm{sim}} < 1000)$, we average over most of the simulation run time, but not early dynamical transients.
 }                                                          	

### 2021-07-20 mesa_model/work_sun_overshoot_files/src/run_star_extras.f90
Added MESA source

@@ -1,0 +1,580 @@
+! ***********************************************************************
+!
+!   Copyright (C) 2010-2019  Bill Paxton & The MESA Team
+!
+!   this file is part of mesa.
+!
+!   mesa is free software; you can redistribute it and/or modify
+!   it under the terms of the gnu general library public license as published
+!   by the free software foundation; either version 2 of the license, or
+!   (at your option) any later version.
+!
+!   mesa is distributed in the hope that it will be useful, 
+!   but without any warranty; without even the implied warranty of
+!   merchantability or fitness for a particular purpose.  see the
+!   gnu library general public license for more details.
+!
+!   you should have received a copy of the gnu library general public license
+!   along with this software; if not, write to the free software
+!   foundation, inc., 59 temple place, suite 330, boston, ma 02111-1307 usa
+!
+! ***********************************************************************
+ 
+      module run_star_extras
+
+      use star_lib
+      use star_def
+      use const_def
+      use math_lib
+      
+      implicit none
+
+
+      integer, parameter :: max_nz = 10000
+      real(dp) :: penetration_fraction(max_nz)
+
+      ! these routines are called by the standard run_star check_model
+      contains
+      
+
+      subroutine extras_controls(id, ierr)
+         integer, intent(in) :: id
+         integer, intent(out) :: ierr
+         type (star_info), pointer :: s
+         ierr = 0
+         call star_ptr(id, s, ierr)
+         if (ierr /= 0) return
+         
+         ! this is the place to set any procedure pointers you want to change
+         ! e.g., other_wind, other_mixing, other_energy  (see star_data.inc)
+
+
+         ! the extras functions in this file will not be called
+         ! unless you set their function pointers as done below.
+         ! otherwise we use a null_ version which does nothing (except warn).
+
+         s% extras_startup => extras_startup
+         s% extras_start_step => extras_start_step
+         s% extras_check_model => extras_check_model
[…]

### 2021-07-20 manuscript/ms.tex

--- 2021-07-19 manuscript/ms.tex
@@
 \label{app:mesa}
-Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
-We note that this impelementation is likely not universal or robust enough to be used in any stellar model, but it is robust enough to timestep stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
+
+Our 1D stellar evolution calculations were performed using the Modules for Experiments in Stellar Astrophysics software instrument\citep[MESA]{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
+
+\subsection{Input Physics}
+
+The MESA EOS is a blend of the OPAL \citep{Rogers2002}, SCVH
+\citep{Saumon1995}, FreeEOS \citep{Irwin2004}, HELM \citep{Timmes2000},
+and PC \citep{Potekhin2010} EOSes.
+
+Radiative opacities are primarily from OPAL \citep{Iglesias1993,
+Iglesias1996}, with low-temperature data from \citet{Ferguson2005}
+and the high-temperature, Compton-scattering dominated regime by
+\citet{Buchler1976}.  Electron conduction opacities are from
+\citet{Cassisi2007}.
+
+Nuclear reaction rates are from JINA REACLIB \citep{Cyburt2010} plus
+additional tabulated weak reaction rates \citet{Fuller1985, Oda1994,
+Langanke2000}.  (For MESA versions before 11701): Screening is
+included via the prescriptions of \citet{Salpeter1954, Dewitt1973,
+Alastuey1978, Itoh1979}.
+
+\subsection{Penetration Implementation}
+
+Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA.
+We note that this impelementation is likely not universal or robust enough to be used in most complex stellar models, but it is robust enough to time-step stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
 Future work should improve upon this model.
 
-To find the extent of the penetrative region, we override MESA's TODO routine for writing $\justgrad$ and instead have the solver follow these steps:
-\begin{enumerate}
-\item At each timestep, we find the location of the Schwarzschild convective boundary, $r_s$.
-We measure the value of the mixing length $\lambda$ there, and choose a convection zone length scale $\ell_{\rm{CZ}} = \text{min}(\lambda, L_{\rm{CZ}})$, where $L_{\rm{CZ}}$ is the full depth of the Schwarzschild-unstable convective region.
-We take the ``CZ'' integrals in Eqn.~\ref{eqn:mesa_eqn} to span radially from the Schwarzschild boundary to a depth $\ell_{\rm{CZ}}$ within the convection zone.
-\item We calculate the buoyancy integral $\int_{\rm{CZ}} L_{\rm{conv}} dr$ and the convection zone volume $V_{\rm{CZ}}$.
-\item Starting at the Schwarzschild boundary, we iteratively expand the size of the PZ until Eqn.~\ref{eqn:mesa_eqn} is satisfied.
-For each radial bin $i$ below the convection zone, we calculate $\int_{\rm{PZ},i}L_{\rm{conv}} dr$ and $V_{\rm{PZ},i}$.
-We evaluate the LHS of Eqn.~\ref{eqn:mesa_eqn} using those values.
-If LHS $\geq$ RHS, we assume that the radial coordinate of bin $i$ is the boundary of the penetrative region.
-\item We enforce $\justgrad \approx \gradad$ in the PZ by doing TODO.
-\item We ensure that the transition from the PZ to the RZ is smooth.
-Outside of the PZ, we model $\justgrad$ as TODO.
-\end{enumerate}
-
-Using this procedure with $f = 0.8$ and $\xi = 1$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.
+To find the extent of the penetrative region we write Eqn.~\eqref{eq:mesa_eqn} as
+\begin{align}
+	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \xi f L_{\rm conv,avg,CZ} + L_{\rm conv} dr,
+	\label{eq:rwt}
+\end{align}
+where $L_{\rm conv,avg,CZ}$ is the average of $L_{\rm conv}$ in the convection zone and $L_{\rm conv}$ in the penetrative region is given by
+\begin{align}
+	L_{\rm conv} = \frac{L_{\rm rad}}{\nabla_r}(\nabla_a - \nabla_r),
+\end{align}
+which is the excess luminosity carried if the temperature gradient in the radiative zone is adiabatic.
+
+We first integrate the left-hand side of Eqn.~\eqref{eq:rwt} over the convection zone and further use that to evaluate $L_{\rm conv,avg,CZ}$.
+Next we integrate the right-hand side of the same away from the convective boundary into the radiative zone until the equation is satisfied.
+The point where this integration stops is the edge of the penetrative region.
+
+We then implement convective penetration in stellar evolution with two modifications.
+First, we add an extra chemical mixing term in the penetration zone with a scale of $D \approx H_p (L/4\pi r^2 \rho)^{1/3}$, which is roughly the scale of the convective diffusivity.
+The precise choice of diffusivity here does not matter, as any plausible scale will be enough to eliminate any composition gradient on evolutionary time-scales.
+Secondly, we override the default routine in MESA for determining $\nabla$ and instead have the solver reduce $\nabla_a-\nabla$ by 90 per~cent in the penetrative zone.
+
+Using this procedure with $f = 0.86$ and $\xi = 0.6$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.
+
+\subsection{Models}
+
+Models were constructed to reasonably reproduce the present-day Sun and based on the 2019 MESA summer school lab by~\citet{pm}.
+Inlists and the \texttt{run\_star\_extras} source code are available at CITE.
 

### 2021-07-20 manuscript/ms.tex
some revs per notes from Adam

--- 2021-07-19 manuscript/ms.tex
@@
 While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are prohibitively expensive to perform at every timestep in a stellar evolution simulation.
-In order to resolve discrepancies between stellar evolution models and observations, a more complete and \emph{parameterizeable} understanding of convective overshoot is required.
+To resolve discrepancies between stellar evolution models and observations, a more complete and \emph{parameterizeable} understanding of convective overshoot is required.
 
@@
 \label{sec:theory}
-In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the convection and penetration zones.
+In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the Schwarzschild-unstable convection zone (CZ) and penetration zone (PZ).
 In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
 In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
-We find that excess KE in the convection zone can cause a penetration zone to form.
-By balancing the excess KE in the convection zone with a buoyancy-braking work term in the PZ, we are able to derive the size of the PZ.
-We find that a description of the size of a theoretical penetration zone does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
+We find that imbalances in KE source terms within the CZ determine the extent of the PZ.
+%We find that excess KE in the convection zone can cause a penetration zone to form.
+By balancing the excess KE generation in the CZ with buoyancy-braking and dissipation work terms in the PZ, we are able to derive the size of the PZ.
+We find that a description of the size of a theoretical PZ does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
 
@@
 We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
-We now parameterize the fraction of the buoyant engine consumed by CZ dissipation,
-\begin{equation}
-f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
+We now define
+\begin{equation}
+f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz},
 \label{eqn:f_defn}
 \end{equation}
-Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
+the measurable fraction of the buoyant engine consumed by CZ dissipation.
+Eqn.~\ref{eqn:constraint_cz_pz_split} can then be rewritten as
 \begin{equation}

### 2021-07-20 manuscript/ms.tex
incorporates comments from Adam in sct 6

@@
 \int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
+\label{eqn:mesa_integral_constraint}
 \end{equation}
@@
 
-At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot$, such that this PZ extends $\sim 50$\% of a scale height below the convection zone.
-Helioseismic studies have suggested that a PZ depth should be constrained to 5-10\% of $H_P$ \citep{basu_etal_1994, basu2016}; these constraints are significantly smaller than our crude model.
-Some recent simulations \citep{kapyla2019} have suggested that solar convection could exhibit penetration depths of $0.2 H_P$, which are closer to these models but still smaller than what we measure.
-Despite these discrepancies, Fig.~\ref{fig:mesa_profiles} shows the promise of a convective penetration parameterization such as the one presented here.
-Pathways for improving our parameterization will be discussed in the following section.
+When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).
+Helioseismic studies have argued that that the solar PZ depth cannot be larger than $\mathcal{O}$(0.05 $H_p$), because larger PZs would result in larger glitches than are detected  \citep[see Sct.~7.2.1 of][for a nice review]{basu2016}.
+However, some recent 3D convective simulations by \citet{kapyla2019} suggest that the solar PZ depth could be as large as $\mathcal{O}(0.2 H_p)$.
+In the model shown in Fig.~\ref{fig:mesa_profiles}, we find $H_p \approx 0.082R_\odot$ at the Schwarzschild CZ boundary, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot \sim 0.5 H_p$.
+This over-estimates fully compressible simulations by a factor of a few, and observations by an order of magnitude.
+However, it is unsurprising that our Boussinesq-based model only qualitatively matches observational constraints for the solar CZ.
+The solar convection zone is highly stratified ($\sim$14 density scale heights), and we neglected density stratification in this work.
+Fig.~\ref{fig:mesa_profiles} shows that our parameterization can produce penetration zones in 1D models with measurable acoustic glitches.
+In a future paper, we will produce more realistic models by building upon our parameterization to include the crucial effects of density stratification.
 
@@
 
-To find the extent of the penetrative region we write Eqn.~\eqref{eq:mesa_eqn} as
+To find the extent of the penetrative region we write Eqn.~\eqref{eqn:mesa_eqn} as
 \begin{align}
-	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \xi f L_{\rm conv,avg,CZ} + L_{\rm conv} dr,
+	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \left(\xi f L_{\rm conv,avg,CZ} + L_{\rm conv}\right) dr,
 	\label{eq:rwt}
@@
 
-\newpage
 \section{Table of simulation parameters}
@@
 
+\newpage
+\,
+\newpage
 \bibliographystyle{aasjournal}

### 2021-07-22 manuscript/ms.tex
some careful edits of scts 1-4

@@
 We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
-Although it can take thousands of overturn times to develop, in all cases we find significant convective penetration.
+In all cases we find significant convective penetration, although it can take thousands of overturn times to develop.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
@@
 Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
-Modern numerical experiments often examine the importance of the ``stiffness'' of a radiative-convective interface.
-The stiffness measures the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
+Modern numerical experiments often examine the importance of the ``stiffness'' $\mS$ of a radiative-convective interface.
+$\mS$ compares the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
 Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
 Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
-While a link between stiffness and entrainment and overshoot processes has seemingly emerged in previous work, a mechanism for penetration remains elusive.
+A link between $\mS$ and the processes of entrainment and overshoot has seemingly emerged, but a mechanism for penetration remains elusive.
 
@@
 Even detailed studies which sought a relationship between penetration depth and stiffness $\mS$ have presented contradictory results.
-Early work by e.g., \citet{hurlburt_etal_1994, singh_etal_1995} hinted at a link between $\mS$ and penetration length, at least for low values of $\mS$.
+Early work by e.g., \citet{hurlburt_etal_1994} and \citet{singh_etal_1995} hinted at a link between $\mS$ and penetration length, at least for low values of $\mS$.
 Subsequent simulations by \citet{brummell_etal_2002} exhibit a weak scaling of penetration depth with $\mS$; the authors interpret this scaling as a sign of pure overshoot and claim their simulations do not achieve adiabatic convective penetration.
@@
 We see that convective motions extend beyond the Schwarzschild boundary of the convection zone, which is denoted by a horizontal dashed grey line.
-These motions come to a halt at the top of a penetration zone, denoted by a solid horizontal line, where the temperature gradient departs from adiabatic towards the radiative gradient.
+These motions stop at the top of a penetration zone, denoted by a solid horizontal line, where the temperature gradient departs from adiabatic towards the radiative gradient.
 In the right panel, we display temperature perturbations away from the time-evolving mean temperature profile.
@@
 
-We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the thermodynamic gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
-The adiabatic gradient $\gradad$ is shown in purple and is a constant value in the simulation.
-The radiative gradient $\gradrad$ is shown in orange.
+We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the temperature gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
+The adiabatic gradient $\gradad$ (purple) has a constant value in the simulation.
+Also shown is the radiative gradient $\gradrad$ (orange).
 The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
 Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
-However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from roughly $1.04 \leq z \leq 1.4$.
-Above this point, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
-
-Our goals in this paper are to understand how these PZs form, and to parameterize this effect so that it can be included in 1D stellar evolution calculations.
+However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from $1.04 \lesssim z \lesssim 1.4$.
+Above the PZ, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
+
+Our goals in this paper are to understand how these PZs form and to parameterize this effect so that it can be included in 1D stellar evolution calculations.
 
@@
 \end{align}
-Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
+Here, the density is decomposed into a uniform, constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
 We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
@@
 In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
-Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but in this incompressible model where there is no density stratification to break the symmetry of upflows and downflows precisely the same arguments can be applied to the inverted problem.
+Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but in this incompressible model where there is no density stratification to break the symmetry of upflows and downflows, precisely the same arguments can be applied to the inverted problem.
 
@@
 \end{equation}
-Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panel}.
+Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panels}.
 As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
-In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous terms which are only nonzero near the bottom boundary.
+In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous flux term which is only nonzero in a small region above the bottom boundary.
 We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
@@
 
-We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
-The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
-Thus, in the PZ where $\gradad > \gradrad$ (see Fig.~\ref{fig:theory_profiles}, middle panel), we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
+We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and an extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
+The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$, and is positive in the CZ and negative in the PZ (see Fig.~\ref{fig:theory_profiles}, bottom panel).
 Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
@@
 \item In the limit that $f \rightarrow 0$, viscous dissipation is inefficient.
-Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the excess positive buoyant work of the CZ.
+Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be so large that its negative buoyant work is equal in magnitude to the positive buoyant work of the CZ.
 This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
@@
 The shape of $\bar{\Phi}$ determines $\xi$; a linear falloff gives $\xi = 1/2$, a quadratic falloff gives $\xi = 2/3$, and $\xi = 1$ assumes no falloff.
-With this parameterization, and $\bar{\mathcal{B}} \propto \bar{\Fconv}$, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
+With this parameterization, and $\bar{\mathcal{B}} \propto \bar{\Fconv}$, we rewrite Eqn.~\ref{eqn:first_pz_parameterization},
 \begin{equation}
@@
 \label{sec:linear_theory}
-We next assume that $\overline{\Fconv}(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be,
+We next examine a model where the derivative of $\overline{\Fconv}(z)$ may be discontinuous at the CZ-PZ boundary,
 \begin{equation}
@@
 \end{cases},
+\label{eqn:linear_flux_theory}
 \end{equation}
 where $(\partial \Frad / \partial z)|_{\rm{CZ}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
-When $\mP_L = 1$, $\bar{\Fconv}$ is just a linear profile that crosses through zero at $z = L_s$.
-Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux and integrating over $L_{\rm{CZ}}$ in the CZ and $\delp$ in the PZ, we retrieve a quadratic equation.
+When $\mP_L = 1$, $\bar{\Fconv}$ is a linear profile that crosses through zero at $z = L_s$.
+Solving Eqn.~\ref{eqn:theory_fraction} with Eqn.~\ref{eqn:linear_flux_theory} and integrating over $L_{\rm{CZ}}$ in the CZ and $\delp$ in the PZ, we retrieve a quadratic equation.
 This equation has two solution branches, only one of which corresponds to a positive value of $\delp$.
@@
 where $\zeta \equiv (\xi f/2)\sqrt{\mP_L/(1-f)}$.
-We expect the penetration height to be roughly proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
-
-In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
+We expect the penetration height to be proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
+
+In this work, we will test Eqn.~\ref{eqn:theory_fraction} through the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
 Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the values of $f$ and $\xi$.
@@
 
-The average convective velocity depends on the magnitude of the heating, $\angles{\vec{|u|}} \approx Q_{\rm{mag}}^{1/3} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{|u|}} / L_s \approx 1$.
+The average convective velocity depends on the magnitude of the convective flux, $\angles{\vec{|u|}} \approx F_H^{1/3} = (Q_{\rm{mag}}\Delta_H)^{1/3}$.
+The characteristic convective frequency is ${f_{\rm{conv}} = \angles{\vec{|u|}} / L_s}$.
+Empirically we find that for our choice of parameters, $\angles{\vec{|u|}} \approx 1$, and so going forward we define ${u_{\rm{ff}} \approx 1}$ and $f_{\rm{conv}} \approx 1$.
 The stiffness is defined,
@@
 In our nondimensionalization, $N^2 = \gradad - \gradrad$.
-We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\gradrad$, which in turn sets the value of $k$ in the radiative zone.
+We use $\mS$ as a control parameter.
 
@@
 where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
-Leaving $\mS$ and $\mP_D$ as free parameters and requiring that $\gradad$ carries $\Fbot$ at $z = 0$ and that $\gradrad$ carries $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
+Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
+We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqn.~\ref{eqn:discontinuous_constants}
+In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
+},
 \begin{equation}
 \begin{split}
-&k_{\rm{RZ}} = \frac{\Delta_H}{\mS\mP_D},\\
-&k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \mu + \mP_D^{-1}},\\
-&\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \mu + \mP_D^{-1}),\\
-&\gradrad = \gradad - Q_{\rm{mag}}\mS.
+&k_{\rm{RZ}} = \frac{F_H}{f_{\rm{conv}}^2\mS\mP_D},\\
+&k_{\rm{CZ}} = k_{\rm{RZ}}\frac{\mu}{1 + \mu + \mP_D^{-1}},\\
+&\gradad = f_{\rm{conv}}^{2}\mS\mP_D(1 + \mu + \mP_D^{-1}),\\
+&\gradrad = \gradad - f_{\rm{conv}}^{2}\mS.
+\label{eqn:discontinuous_constants}
 \end{split}
@@
 
-We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper in which we hold two of these parameters constant and vary the other.
+We study a sweep through each of the ($\mP_D$, $\mS$, $\mR$) parameter spaces while holding all other parameters constant.
 We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
-%We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
 According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
@@
 \end{equation}
-Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
-By this choice, we require
-\begin{equation}
-\partial_z k_0 = \frac{\Delta_H}{L_s \mS \psi},\qquad
-k_b = \frac{\Delta_H\mu}{\mS\psi},\qquad
-\gradad = Q \mS \psi,
+Since $k$ varies with height, formally the values of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
+By this choice\footnote{
+We solve the system of equations where ${k_{\rm{bot}}\gradad = F_{\rm{bot}}}$, ${k_{\rm{ad}}\gradad = F_{\rm{bot}} + F_H}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
+}, we require
+\begin{equation}
+\partial_z k_0 = \frac{F_{H}}{f_{\rm{conv}}^2L_s \mS \psi},\,\,
+k_b = \frac{F_H \mu}{f_{\rm{conv}}^2\mS\psi},\,\,
+\gradad = f_{\rm{conv}}^2 \mS \psi,
 \end{equation}
 where $\psi \equiv 1 + \mP_L(1 + \mu)$.
-%In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
 We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$.
@@
 In order to approximate discontinuous functions such as Eqns.~\ref{eqn:sim_Q}, \ref{eqn:sim_discontinuous_k}, and \ref{eqn:sim_linear_k}, we must use smooth transitions.
-To create these smooth transitions, we define an approximate Heaviside step function using the error function,
+We therefore define a smooth Heaviside step function,
 \begin{equation}
@@
 \end{equation}
+where erf is the error function.
 In the limit that $d_w \rightarrow 0$, this function behaves identically to the classical Heaviside function centered at $z_0$.
@@
 \subsection{Penetration height measurements}
-In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
-In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
+In our evolved simulations, the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
+To characterize the height of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
 We define the difference between the adiabatic and radiative gradient,
 \begin{equation}
-\Delta \equiv \gradad(z) - \gradrad(z).
-\end{equation}
-We measure penetration and overshoot heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
+\Delta \equiv \gradad - \gradrad(z).
+\end{equation}
+We measure penetration heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$ of $\Delta$.
 Specifically,
@@
 Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
-We will simply refer to these as three different measures of the top of the PZ.
-We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
+We find that these measurements based on the (slowly-evolving) thermodynamic profile provide a robust and straightforward measurement of penetration height \citep[for a discussion of alternate measurement choices, see][]{pratt_etal_2017}.
 
@@
 
-We will now present on the results of the 3D dynamical simulations described in the previous section.
+We now describe the results of the 3D dynamical simulations described in the previous section.
 Dynamics in these simulations resemble those previously shown in Fig.~\ref{fig:vertical_dynamics_panels}.

### 2021-07-23 manuscript/ms.tex
updates paper after final comb-through

@@
 \caption{
-Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
+Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in an evolved simulation.
 The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
@@
 The characteristic convective frequency is ${f_{\rm{conv}} = \angles{\vec{|u|}} / L_s}$.
-Empirically we find that for our choice of parameters, $\angles{\vec{|u|}} \approx 1$, and so going forward we define ${u_{\rm{ff}} \approx 1}$ and $f_{\rm{conv}} \approx 1$.
+Empirically we find that for our choice of parameters, $\angles{\vec{|u|}} \approx 1$, so going forward we define $f_{\rm{conv}} = 1$.
 The stiffness is defined,
 \begin{equation}
-\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
+\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} = N^2,
 \label{eqn:stiffness}
@@
 Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
-The value of $\mR$ roughly corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
-Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
+The value of $\mR$ corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we will vary $\mR$.
+Astrophysical convection exists in the limit of $\Pran \ll 1$ \citep{garaud2021}; in this work we choose a modest value of $\Pran = 0.5$ which slightly separates the thermal and viscous scales while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.
 
@@
 Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
-We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqn.~\ref{eqn:discontinuous_constants}
-In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
+We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqns.~\ref{eqn:discontinuous_constants}.
+%In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
 },
@@
 By this choice\footnote{
-We solve the system of equations where ${k_{\rm{bot}}\gradad = F_{\rm{bot}}}$, ${k_{\rm{ad}}\gradad = F_{\rm{bot}} + F_H}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
+We solve the system of equations where ${F_{\rm{bot}} = k_{\rm{bot}}\gradad}$, ${F_{\rm{bot}} + F_H = k_{\rm{ad}}\gradad}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
 }, we require
@@
 The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
-The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
+The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line.
 The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
@@
 In the middle panels, we measure $f$ according to Eqn.~\ref{eqn:f_defn}.
-We find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
+We find values of $f \in [0.6, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
 In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
@@
 We now describe the results of the 3D dynamical simulations described in the previous section.
-Dynamics in these simulations resemble those previously shown in Fig.~\ref{fig:vertical_dynamics_panels}.
-To quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory}, we will present time- and volume-averaged scalar quantities, as well as some select horizontally-averaged vertical profiles.
+Fig.~\ref{fig:vertical_dynamics_panels} displays the dynamics in one of these simulations.
+In this section, we quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory} using temporally averaged measures.
 
@@
 
-%\begin{figure*}[t]
-%\centering
-%\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
-%\caption{
-%Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
-%In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
-%(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
-%(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
-%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
-%\label{fig:vertical_dynamics_panels}
-%}
-%\end{figure*}
-
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose temperature profile has $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial temperature profile sets $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
 In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
-This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of convective overturn (freefall) times.
+This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of freefall times.
 The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
-We plot their rolling mean, averaged over 200 freefall time units. 
+We plot the rolling mean, averaged over 200 freefall time units. 
 We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full height.
-We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
+We quantify this fast evolution by plotting vertical lines in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its equilibrated value.
+The equilibrated value is averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line.
 The evolved value of $f$ indicates that roughly 2/3 of the buoyancy driving is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
@@
 $\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
-The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line.
 We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
-The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are overplotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
 We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
-%This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.
-
-This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
+
+This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 20 days on 1024 cores for a total of $\sim$500,000 cpu-hours.
 It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
@@
 
-%In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
-%We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
-%Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
-%On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
-%These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.
-
 \begin{figure*}[t]
@@
 \caption{
-(Left panel) Penetration heights are shown as a function of stiffness for simulations with a discontinuous conductivity.
+(Left panel) Penetration heights are shown as a function of stiffness for Case I simulations with a discontinuous conductivity.
 While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
@@
 We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
-At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
-At large values of $\mP$, penetration height falls off of these predicted scaling laws.
-In this regime, dissipation dominates over buoyancy in the PZ and PZ heights saturate.
+At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Figs.~\ref{fig:grad_profiles} \& \ref{fig:time_evolution} and Sec.~\ref{sct:numerics}).
+At large values of $\mP$, the penetration height falls off of these predicted scaling laws.
+In this regime, dissipation dominates over buoyancy in the PZ, so the PZ height saturates.
 
@@
 We note a weak trend where $f$ decreases as $\mP$ increases.
-As $\mP$ incraeses, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
+As $\mP$ increases, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
 When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
@@
 We find that the height of the penetration zone is weakly dependent on $\mS$.
-In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
-We find that the mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
-In other words, the transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
+In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few Case I simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
+The mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
+The thermal adjustment layer in which $\justgrad$ changes from $\gradad$ in the PZ to $\gradrad$ in the RZ therefore becomes narrower as $\mS$ increases.
 To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
-We find that the width of this region varies according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
+We find that the width of this region varies roughly according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
 %This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
 
-Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
-As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
+Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ become nonlinear.
+We therefore restrict the simulations in this study to relatively large\footnote{These values are modest compared to astrophysical values, but large for nonlinear simulations.} values of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
 
@@
 \caption{
-(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for simulations with a discontinuous conductivity.
+(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations with a discontinuous conductivity.
 We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
@@
 (Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
-(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\delta_{\nu} \rightarrow 0$.
+(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
 \label{fig:parameters_vs_re}
@@
 
-We now examine why $f$ increases as $\mR$ increasesIn the SF simulations, within the CZ, we can reasonably approximate $\bar{\Phi}$ as a constant $\Phi_{\rm{CZ}}$ in the bulk and zero within the viscous boundary layer,
+We now examine why $f$ increases as $\mR$ increases.
+In the SF simulations, within the CZ, we can reasonably approximate $\bar{\Phi}$ as a constant $\Phi_{\rm{CZ}}$ in the bulk and zero within the viscous boundary layer,
 \begin{equation}
@@
 To measure $\ell_\nu$, we first measure the height of the extremum of the viscous portion of the kinetic energy flux $\bar{\mathcal{F}}$ near the boundary, and take $\ell_\nu$ to be the twice that height.
-We find that Eqn.~\ref{eqn:f_defn} is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the bounary layer, and therefore Eqn.~\ref{eqn:cz_dissipation_model} is a poor model for $z \leq \ell_\nu$.
+We find that Eqn.~\ref{eqn:f_infty} is a slightly better description for the SF simulations than the NS simulations; NS simulations have maximized dissipation in the boundary layer, and therefore Eqn.~\ref{eqn:cz_dissipation_model} is a poor model for $z \leq \ell_\nu$.
 In the bottom right panel of Fig.~\ref{fig:parameters_vs_re}, we demonstrate that the depth of the viscous boundary layer follows classical scaling laws from Rayleigh-B\'{e}nard convection\footnote{
 If you assume the Nusselt Number dependence on the Rayleigh number is throttled by the boundaries, Nu $\propto$ Ra$^{1/3}$ (as is frequently measured), and the Reynolds number is Re $\propto$ Ra$^{1/2}$, you retrieve Nu $\propto$ Re$^{2/3}$.
-The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\delta^{-1}$, and so we expect $\delta_{\nu} \propto \mR^{-2/3}$.
+The Nusselt number generally varies like the inverse of the boundary layer depth, Nu $\propto$ $\ell^{-1}$, and so we expect $\ell_{\nu} \propto \mR^{-2/3}$.
 } \citep{ahlers_etal_2009, goluskin2016}.
@@
 We find that these changes are caused by increases in $f$.
-In our simulations, these increases in $f$ seem to be caused by changes in the size of the viscous boundary layer $\ell_\nu$.
+In our simulations, $f$ seems to have a linear relationship with the size of the viscous boundary layer $\ell_\nu$.
 By measuring $f$ and $\ell_\nu$ in a simulation, the value of $f_\infty$ can be found from Eqn.~\ref{eqn:f_infty}.
-Stellar convection zones are not adjacent to hard walls and so should be represented by the $\ell_\nu \rightarrow 0$ limited.
-Core convection zones geometrically have no lower boundary, and convective shells should be bounded both above and below by penetrative regions.
+Stellar convection zones are not adjacent to hard walls\footnote{
+Core convection zones have no lower boundary due to geometry; flows pass through the singular point at $r = 0$.
+Convective shells in should be bounded both above and below by penetrative regions.
+}, so $f_\infty$ and the limit $\ell_\nu \rightarrow 0$ applies to stellar convection.
 
@@
 In this simulation, we measure $\xi \approx 0.6$, $f \approx 0.785$, $\ell_\nu \approx 0.08$, and $L_s = 1$.
-We therefore estimate that
+Using Eqn.~\ref{eqn:f_infty}, we estimate that
 \begin{equation}
@@
 (top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a MESA solar model with a penetration zone.
-(bottom) The difference in the sound speed in the MESA model with a PZ that is presented in the top panel compared to a model run at identical parameters but without a PZ.
-We see that the addition of a PZ increases the sound speed by $\mathcal{O}$(2\%) below the convection zone.
+(bottom) Sound speed differences between the model shown in the top panel and a standard (std) model run at identical parameters but without a PZ.
+The addition of a PZ creates an acoustic glitch, raising the sound speed by $\mathcal{O}$(2\%) below the convection zone.
 \label{fig:mesa_profiles}
@@
 As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
+In other words, the combined effects of penetration and entrainment should be considered.
 Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
@@
 \begin{acknowledgments}
-We thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
+We thank Keaton Burns, Matt Browning, Matteo Cantiello, Geoff Vasil, and Kyle Augustson for useful discussions and/or questions which improved the content of this manuscript.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
@@
 \begin{equation}
-\partial_z \overline{T} = -\gradad - H(z; \delta_{\rm{0.5,\rm{new}}}, d_w) \Delta\justgrad,
+\justgrad = \gradad + H(z; \delta_{\rm{0.5,\rm{new}}}, d_w) \Delta\justgrad,
 \label{eqn:initial_grad}
@@
 
-In Fig.~\ref{fig:AE_time_figure}, we display the time evolution of $\delp$ and $f$ in Case I simulations with $\mS = 10^3$, $\mR = 400$, and $\mP_D = [1,2,4]$ simulations using black lines.
+In Fig.~\ref{fig:AE_time_figure}, we plot in black the time evolution of $\delp$ and $f$ in Case I simulations with $\mS = 10^3$, $\mR = 400$, and $\mP_D = [1,2,4]$.
 We overplot the evolution of simulations which use this accelerated evolution (AE) procedure using orange and green lines.
@@
 
-Our 1D stellar evolution calculations were performed using the Modules for Experiments in Stellar Astrophysics software instrument\citep[MESA]{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
+Our 1D stellar evolution calculations were performed using the Modules for Experiments in Stellar Astrophysics software instrument \citep[MESA]{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
 

### 2021-07-23 data/plot_results_vs_re.py

@@ -47,7 +47,8 @@ for i, d in enumerate(dirs):
         fconv_cz = f['fconv_cz'][()]
         Ls = np.mean(f['Ls'][()])
         tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
+        time_window = np.min((500, tot_time-50))
+        time_window = np.min((500, tot_time-50))
         good_times = times > (times[-1] - time_window)
         mean_L_d01 = np.mean(L_d01s[good_times])
         mean_L_d05 = np.mean(L_d05s[good_times])
@@ -133,9 +134,9 @@ ax1.scatter(Re[good], (L_d09 - Ls)[good], facecolor=(1,1,1,0.5), color='k', mark
 ax1.scatter(Re[good], (L_d05 - Ls)[good], facecolor=(1,1,1,0.5), color='k', marker='o', label='SF')
 ax1.scatter(Re[good], (L_d01 - Ls)[good], facecolor=(1,1,1,0.5), color='k', marker='^')
 good = sf == 0
-ax1.scatter(Re[good], (L_d09 - Ls)[good], color='k', marker='v', alpha=0.8)
-ax1.scatter(Re[good], (L_d05 - Ls)[good], color='k', marker='o', label='NS', alpha=0.8)
-ax1.scatter(Re[good], (L_d01 - Ls)[good], color='k', marker='^', alpha=0.8)
+ax1.scatter(Re[good], (L_d09 - Ls)[good], color='k', marker='v', alpha=0.8, s=15)
+ax1.scatter(Re[good], (L_d05 - Ls)[good], color='k', marker='o', label='NS', alpha=0.8, s=15)
+ax1.scatter(Re[good], (L_d01 - Ls)[good], color='k', marker='^', alpha=0.8, s=15)
 ax1.set_xscale('log')
 ax1.legend(frameon=True, fontsize=8, framealpha=0.6)
 ax1.set_xlabel(r'$\mathcal{R}$')
@@ -146,7 +147,7 @@ ax1.set_xlim(2e1, 7e3)
 good = sf == 1
 ax2.scatter(Re[good], theory_f[good], facecolor=(1,1,1,0.5), color='k', marker='o')
 good = sf == 0
[…]

### 2021-07-23 data/create_scalar_table.sh
creates pipeline for scalar output file

@@ -1,0 +1,1 @@
+python3 output_simulation_details.py noslip_erf_*/erf*/ stressfree_erf_Re_cut/erf*/ noslip_linear_P_cut/linear_3D_Re8e2_P*/ erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart3 erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart5

### 2021-07-23 data/output_simulation_details.py

@@ -20,12 +20,28 @@ args = docopt(__doc__)
 
 dirs = args['<dirs>']
 
+fields = dict()
+fields['t_sim'] = 'times'
+fields['d_01'] = 'L_d01s'
+fields['d_05'] = 'L_d05s'
+fields['d_09'] = 'L_d09s'
+fields['f']  = 'modern_f'
+fields['xi'] = 'modern_xi'
+fields['Ls']    = 'Ls'
+fields['volavg_enstrophy_Ls']    = 'enstrophy_Ls'
+fields['volavg_enstrophy_CZ+PZ'] = 'enstrophy_cz'
+fields['volavg_fconv_Ls']        = 'fconv_Ls'
+fields['volavg_velocity_Ls'] = 'vel_Ls'
+
 data_chunks = []
-for d in dirs:
+for dnum, d in enumerate(dirs):
+    data = dict()
     S = float(d.split('_S')[-1].split('_')[0])
     P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
     Re = float(d.split('_Re')[-1].split('_')[0])
     Lz = float(d.split('_Lz')[-1].split('_')[0])
+    resolution = d.split('Titer')[-1].split('_')[1].split('/')[0]
+
 
     if '3D' in d:
         threeD = True
@@ -35,23 +51,44 @@ for d in dirs:
         erf = True
     else:
         erf = False
+    if 'stressfree' in d:
+        sf = True
+    else:
+        sf = False
+    if 'schwarzschild' in d:
+        ae = False
+    else:
+        ae = True
+
+
+    data['S'] = S
+    data['P'] = P
+    data['R'] = Re
+    data['Lz'] = Lz
+    data['3D'] = threeD
+    data['erf'] = erf
+    data['sf']  = sf
+    data['ae'] = ae
+    data['resolution'] = resolution
 
     with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        Ls = f['Ls'][()]
-        L_d09s = f['L_d09s'][()]
-        enstrophy_Ls = f['enstrophy_Ls'][()]
-        enstrophy_cz = f['enstrophy_cz'][()]
-        fconv_Ls = f['fconv_Ls'][()]
-        vel_Ls = f['vel_Ls'][()]
-
[…]

### 2021-07-23 data/table_creator.py
auto-generate latex table

@@ -1,0 +1,67 @@
+import numpy as np
+
+def exponent_parser(s):
+    outstr = '$'
+    pieces = s.split('e')
+    if float(pieces[0]) != 1:
+        outstr += pieces[0]
+    if int(pieces[1][1:]) != 0:
+        if outstr == '$':
+            outstr += ' 10^{'
+        else:
+            outstr += ' \\cdot 10^{'
+        if pieces[1][0] == "-":
+            outstr += '-'
+        outstr += '{}'.format(int(pieces[1][1:]))
+        outstr += '}'
+    if outstr == '$':
+        outstr += '1.0'
+    outstr += '$'
+    return outstr
+    
+        
+
+datachunk = np.genfromtxt('scalar_table_data.csv', skip_header=1, delimiter=',', dtype=np.unicode_)
+
+for i in range(datachunk.shape[0]):
+    this_str = ''
+
+    #figure out the type
+    erf = datachunk[i,5]
+    sf  = datachunk[i,6]
+    if 'False' in erf and 'False' in sf:
+        this_str += 'L & '
+    elif 'True' in erf and 'False' in sf:
+        this_str += 'D & '
+    elif 'True' in erf and 'True' in sf:
+        this_str += 'D/SF & '
+
+    #add the P, S, R
+    for j in [1, 0, 2]:
+        this_str += exponent_parser(datachunk[i,j]) + ' & '
+    
+    #add resolution
+    this_str += datachunk[i,8] + ' & '
+
+    #add tsim
+    this_str += '$' + datachunk[i,9] + '$ & '
+
+    #add deltas
+    this_str += '('
+    for j in [10, 11, 12]:  
+        this_str += datachunk[i,j][1:]
+        if j != 12:
+            this_str += ', '
+    this_str += ') & '
+
+    #add f
+    this_str += datachunk[i,13] + ' & '
+    
+    #add xi
+    this_str += datachunk[i,14] + ' & '
+
+    #add vel
+    this_str += datachunk[i,-1] + ' \\\\ '
+
+    print(this_str)
+

### 2021-07-23 data/plot_results_vs_p.py
all parameter space plots now plot out of .csv files

@@ -4,63 +4,50 @@ import matplotlib.pyplot as plt
 plt.style.use('apj')
 import h5py
 
-from matplotlib.patches import ConnectionPatch
-
 col_width = 3.25
 page_width = 6.5
 golden_ratio = 1.61803398875
 
-dirs = glob.glob('noslip_linear_P_cut/linear*')
-dirs += glob.glob('noslip_erf_P_cut/erf*')
 
-data = []
-for d in dirs:
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        modern_f = f['modern_f'][()]
-        modern_xi = f['modern_xi'][()]
-        fconv_Ls = f['fconv_Ls'][()]
-        vel_rms = f['vel_cz'][()]
-        Ls = np.mean(f['Ls'][()])
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_f  = np.mean(modern_f[good_times])
-        mean_xi = np.mean(modern_xi[good_times])
-        mean_fconv_Ls = np.mean(fconv_Ls[good_times])
-        mean_vel_rms = np.mean(vel_rms[good_times])
-    if 'erf' in d:
-        erf = True
-    else:
-        erf = False
-
[…]

### 2021-07-23 data/plot_results_vs_re.py

@@ -5,120 +5,102 @@ import matplotlib.pyplot as plt
 plt.style.use('apj')
 import h5py
 
-import dedalus.public as de
-from scipy.interpolate import interp1d
-from scipy.optimize import brentq
-
 col_width = 3.25
 page_width = 6.5
 golden_ratio = 1.61803398875
 
-dirs = glob.glob('noslip_erf_Re_cut/erf*/')
-dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
-dirs += glob.glob('stressfree_erf_Re_cut/erf*/')
-dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
+calculate_BLs = False
 
-#nz = 1024
-#Lz = 2
-#z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
-#domain = de.Domain([z_basis], grid_dtype=np.float64)
-#ke_rhs = domain.new_field()
-#ke_flux = domain.new_field()
-#domain_z = domain.grid(-1)
+if calculate_BLs:
 
-cmap = "viridis_r"
-norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
-sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+    dirs = glob.glob('noslip_erf_Re_cut/erf*/')
+    dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
+    dirs += glob.glob('stressfree_erf_Re_cut/erf*/')
+    dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
 
-data = []
-for i, d in enumerate(dirs):
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
[…]

### 2021-07-23 data/plot_results_vs_s.py

@@ -4,72 +4,59 @@ import matplotlib.pyplot as plt
 plt.style.use('apj')
 import h5py
 
-from matplotlib.patches import ConnectionPatch
-
 col_width = 3.25
 page_width = 6.5
 golden_ratio = 1.61803398875
 
-dirs = glob.glob('noslip_erf_S_cut/erf*')
-dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
 
-data = []
-for d in dirs:
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        modern_f = f['modern_f'][()]
-        modern_xi = f['modern_xi'][()]
-        fconv_Ls = f['fconv_Ls'][()]
-        Ls = np.mean(f['Ls'][()])
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_f  = np.mean(modern_f[good_times])
-        mean_xi = np.mean(modern_xi[good_times])
-        mean_fconv_Ls = np.mean(fconv_Ls[good_times])
-    if 'erf' in d:
-        erf = True
-    else:
-        erf = False
-
-    data.append((S, P, Re, Ls, Lz, erf, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, mean_xi, mean_fconv_Ls))
-data = np.array(data)
-
-S = data[:,0]
-P = data[:,1]
[…]

### 2021-07-23 data/vertical_dynamics_panels.py
small data file for vertical dynamics panel added.

@@ -7,28 +7,48 @@ import h5py
 import dedalus.public as de
 plt.style.use('apj')
 
+read_raw_files = False
+plot_ind = -3
 
-# Get data from files
-dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s9.h5'
-profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s9.h5'
-#dynamics_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/slices/slices_s5.h5'
-#profile_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/profiles/profiles_s5.h5'
+if read_raw_files:
+    # Get data from files
+    dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s9.h5'
+    profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s9.h5'
 
-with h5py.File(profile_file, 'r') as f:
-    z = f['scales/z/1.0'][()].squeeze()
-    mean_T1 = np.mean(f['tasks/T1'][()][:,:].squeeze(), axis=0)
-    T1_fluc = np.mean(f['tasks/T1_fluc'][()][:,:].squeeze(), axis=0)
-    grad = -np.mean(f['tasks/T_z'][()][:,:].squeeze(), axis=0)
-    grad_ad = -np.mean(f['tasks/T_ad_z'][()][:,:].squeeze(), axis=0)
-    grad_rad = -np.mean(f['tasks/T_rad_z'][()][:,:].squeeze(), axis=0)
+    with h5py.File(profile_file, 'r') as f:
[…]

### 2021-07-23 manuscript/ms.tex
auto-generate latex table
cleans up all the figs and data

@@
 
-This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 20 days on 1024 cores for a total of $\sim$500,000 cpu-hours.
+This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 24 days on 1024 cores for a total of $\sim$600,000 cpu-hours.
 It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
@@
 Time units on the x-axis are normalized in terms of the total simulation run time in order to more thoroughly demonstrate the evolutionary differences between standard timestepping and AE.
-However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/8$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
+However, the AE simulations are much shorter: the vertical green-and-yellow lines demonstrate how long the AE simulation ran compared to the standard timestepping simulation (so for $\mP_D = 1$, the AE simulations only took $\sim 1/4$ as long; for $\mP_D = 2$, they took $\sim 1/10$ as long; for $\mP_D = 4$, they took $\sim 1/20$ as long).
 AE simulations with orange lines start with PZ heights which are much larger than the final height, while green line solution start with initial PZ heights which are smaller than the expected height.
@@
 \tablehead{
-\colhead{Type} 	& \colhead{$\mP$}	& \colhead{$\mS$}	& \colhead{$\mR$}	& \colhead{$nz \times (nx \times ny)$}	&	\colhead{$t_{\rm{sim}}$}	&	\colhead{$(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$}	& \colhead{$f$}	& \colhead{$\xi$}	& \colhead{$\angles{u}$}
+\colhead{Type} 	& \colhead{$\mP$}	& \colhead{$\mS$}	& \colhead{$\mR$}	& \colhead{$nx \times ny \times nz$}	&	\colhead{$t_{\rm{sim}}$}	&	\colhead{$(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$}	& \colhead{$f$}	& \colhead{$\xi$}	& \colhead{$\angles{u}$}
 }
@@
 \multicolumn{3}{l}{\textbf{``Standard timestepping'' simulations}}\\
-D	& 1	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 12347	& ($0.078, 0.112, 0.136$)	& 0.81	& 0.70	& 0.61 \\
-D	& 2	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 22593	& ($0.191, 0.220, 0.242$)	& 0.75	& 0.62	& 0.62 \\
-D	& 4	& $10^3$	& $4 \times 10^2$	& 256$\times$64$^2$	& 57170	& ($0.434, 0.461, 0.483$)	& 0.67	& 0.58	& 0.62 \\
+D & $1.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 12347$ & (0.078, 0.112, 0.136) &  0.810 &  0.682 &  0.618 \\
+D & $ 2.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 32057$ & (0.200, 0.230, 0.254) &  0.749 &  0.601 &  0.639 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 66557$ & (0.445, 0.472, 0.496) &  0.668 &  0.562 &  0.619 \\
 \hline
 \multicolumn{3}{l}{\textbf{``Accelerated Evolution'' simulations}}\\
-D		& 0.1,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4561 	& ($0.017, 0.042, 0.069$)	&  0.83	&  0.77	& 0.59 \\
-D		& 0.3,  & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 4681 	& ($0.030, 0.064, 0.092$)	&  0.81	&  0.80	& 0.62 \\
-D		& 1,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 3000 	& ($0.082, 0.116, 0.140$)	&  0.80	&  0.69	& 0.62 \\
-D		& 2,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.199, 0.228, 0.252$)	&  0.75	&  0.60	& 0.64 \\
-D		& 4,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 5000 	& ($0.452, 0.480, 0.505$)	&  0.67	&  0.55	& 0.62 \\
-D		& 6,    & $10^3$    & $4 \times 10^2$   & 256$\times$64$^2$	 	& 6000 	& ($0.620, 0.647, 0.667$)	&  0.64	&  0.53	& 0.60 \\
-D		& 8,    & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4357 	& ($0.731, 0.757, 0.778$)	&  0.64	&  0.48	& 0.59 \\
-D		& 10,   & $10^3$    & $4 \times 10^2$   & 512$\times$128$^2$	& 4226 	& ($0.857, 0.884, 0.903$)	&  0.63	&  0.45	& 0.59 \\
-D   	& 4		& $10^3$			& 25				& 256$\times$16$^2$ 	& 3000	& (0.321, 0.379, 0.437)	& 0.77	& 0.27	& 0.34 \\
-D   	& 4		& $10^3$			& 50				& 256$\times$32$^2$ 	& 3000	& (0.398, 0.442, 0.487)	& 0.73	& 0.36	& 0.42 \\
-D   	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 3000	& (0.469, 0.503, 0.534)	& 0.67	& 0.46	& 0.48 \\
-D   	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$64$^2$ 	& 3000	& (0.485, 0.515, 0.542)	& 0.65	& 0.55	& 0.55 \\
-D   	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 3000	& (0.407, 0.434, 0.455)	& 0.69	& 0.57	& 0.68 \\
-D   	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 3000	& (0.366, 0.397, 0.419)	& 0.71	& 0.57	& 0.72 \\
-D   	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2469	& (0.313, 0.350, 0.372)	& 0.73	& 0.60	& 0.75 \\
-D   	& 4		& $10^3$			& $6.4 \times 10^3$	& 384$^3$				& 414 	& (0.277, 0.314, 0.335)	& 0.74	& 0.62	& 0.76 \\
-D/SF	& 4		& $10^3$			& 50				& 256$\times$16$^2$ 	& 5000	& (0.435, 0.477, 0.516)	& 0.68	& 0.42	& 0.50 \\
-D/SF	& 4		& $10^3$			& $1 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.482, 0.516, 0.547)	& 0.64	& 0.54	& 0.57 \\
-D/SF	& 4		& $10^3$			& $2 \times 10^2$	& 256$\times$32$^2$ 	& 5000	& (0.490, 0.520, 0.547)	& 0.63	& 0.59	& 0.64 \\
-D/SF	& 4		& $10^3$			& $4 \times 10^2$	& 256$\times$64$^2$ 	& 8000	& (0.474, 0.502, 0.531)	& 0.65	& 0.59	& 0.69 \\
-D/SF	& 4		& $10^3$			& $8 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.410, 0.437, 0.461)	& 0.68	& 0.59	& 0.73 \\
-D/SF	& 4		& $10^3$			& $1.6 \times 10^3$	& 256$\times$128$^2$	& 5710	& (0.368, 0.400, 0.426)	& 0.70	& 0.59	& 0.76 \\
-D/SF	& 4		& $10^3$			& $3.2 \times 10^3$	& 256$^3$				& 2933	& (0.315, 0.352, 0.381)	& 0.73	& 0.59	& 0.77 \\
-D		& 4		& $10^2$			& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.377, 0.505, 0.581)	& 0.65	& 0.53	& 0.62 \\
-D		& 4		& $3\times 10^2$	& $4 \times 10^2$	& 256$\times$128$^2$	& 5000	& (0.420, 0.477, 0.514)	& 0.66	& 0.55	& 0.62 \\
-D		& 4		& $3\times 10^3$	& $4 \times 10^2$	& 256$\times$128$^2$	& 1170	& (0.455, 0.472, 0.487)	& 0.66	& 0.58	& 0.62 \\
-L		& 0.01	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1139	& (0.017, 0.030, 0.052)	& 0.87	& 0.79	& 0.45 \\
-L		& 0.03	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 929 	& (0.021, 0.045, 0.070)	& 0.86	& 0.79	& 0.45 \\
-L		& 0.1	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1142	& (0.084, 0.076, 0.102)	& 0.85	& 0.72	& 0.45 \\
-L		& 0.3	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 1109	& (0.077, 0.130, 0.158)	& 0.82	& 0.66	& 0.45 \\
-L		& 1		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.182, 0.225, 0.251)	& 0.79	& 0.60	& 0.44 \\
-L		& 2		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 3000	& (0.278, 0.315, 0.340)	& 0.76	& 0.57	& 0.44 \\
-L		& 4		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.396, 0.427, 0.449)	& 0.73	& 0.53	& 0.43 \\
-L		& 8		& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 5000	& (0.519, 0.545, 0.562)	& 0.72	& 0.48	& 0.42 \\
-L		& 16	& $10^3$			& $8 \times 10^2$   & 256$\times$128$^2$	& 8000	& (0.687, 0.709, 0.723)	& 0.70	& 0.44	& 0.42 \\
+D & $ 4.0$ & $ 10^{2}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.377, 0.505, 0.581) &  0.654 &  0.526 &  0.617 \\
+D & $ 4.0$ & $3.0 \cdot 10^{2}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.420, 0.477, 0.514) &  0.663 &  0.551 &  0.618 \\
+D & $ 10^{-1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 4561 $ & (0.017, 0.042, 0.069) &  0.831 &  0.769 &  0.588 \\
+D & $ 3.0 \cdot 10^{-1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 4681 $ & (0.030, 0.064, 0.092) &  0.814 &  0.804 &  0.620 \\
+D & $1.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 3000 $ & (0.082, 0.116, 0.140) &  0.804 &  0.690 &  0.624 \\
+D & $ 2.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.199, 0.228, 0.252) &  0.750 &  0.597 &  0.638 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 2.5 \cdot 10^{1}$ &  16x16x256   & $ 3000 $ & (0.321, 0.379, 0.437) &  0.772 &  0.274 &  0.343 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 5.0 \cdot 10^{1}$ &  32x32x256   & $ 3000 $ & (0.398, 0.442, 0.487) &  0.732 &  0.358 &  0.423 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 10^{2}$ &  32x32x256   & $ 3000 $ & (0.469, 0.503, 0.534) &  0.672 &  0.464 &  0.484 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 2.0 \cdot 10^{2}$ &  64x64x256   & $ 3000 $ & (0.485, 0.515, 0.542) &  0.648 &  0.546 &  0.548 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.452, 0.480, 0.505) &  0.667 &  0.553 &  0.617 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.407, 0.434, 0.455) &  0.689 &  0.566 &  0.678 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 1.6 \cdot 10^{3}$ &  128x128x256 & $ 3000 $ & (0.366, 0.397, 0.419) &  0.709 &  0.574 &  0.720 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 3.2 \cdot 10^{3}$ &  256x256x256 & $ 3235 $ & (0.321, 0.358, 0.381) &  0.723 &  0.605 &  0.746 \\
+D & $ 4.0$ & $ 10^{3}$ & $ 6.4 \cdot 10^{3}$ &  384x384x384 & $ 414  $ & (0.277, 0.315, 0.335) &  0.744 &  0.605 &  0.757 \\
+D & $ 6.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 6000 $ & (0.620, 0.647, 0.667) &  0.635 &  0.532 &  0.597 \\
+D & $ 8.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  128x128x512 & $ 4357 $ & (0.732, 0.759, 0.779) &  0.640 &  0.481 &  0.592 \\
+D & $ 10^{1}$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  128x128x512 & $ 4226 $ & (0.858, 0.885, 0.904) &  0.630 &  0.453 &  0.587 \\
+D & $ 4.0$ & $3.0 \cdot 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x512   & $ 1170 $ & (0.437, 0.454, 0.469) &  0.672 &  0.581 &  0.619 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 5.0 \cdot 10^{1}$ &  32x32x256   & $ 5000 $ & (0.435, 0.477, 0.516) &  0.680 &  0.418 &  0.505 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 10^{2}$ &  32x32x256   & $ 5000 $ & (0.482, 0.516, 0.547) &  0.638 &  0.543 &  0.573 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 2.0 \cdot 10^{2}$ &  64x64x256   & $ 5000 $ & (0.490, 0.520, 0.547) &  0.634 &  0.589 &  0.640 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 4.0 \cdot 10^{2}$ &  64x64x256   & $ 8000 $ & (0.474, 0.502, 0.531) &  0.651 &  0.588 &  0.693 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 5000 $ & (0.410, 0.437, 0.461) &  0.683 &  0.587 &  0.732 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 1.6 \cdot 10^{3}$ &  128x128x256 & $ 5710 $ & (0.368, 0.400, 0.426) &  0.703 &  0.590 &  0.758 \\
+D/SF & $ 4.0$ & $ 10^{3}$ & $ 3.2 \cdot 10^{3}$ &  256x256x256 & $ 3917 $ & (0.320, 0.357, 0.388) &  0.725 &  0.595 &  0.772 \\
+L & $ 10^{-2}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1139 $ & (0.017, 0.030, 0.051) &  0.873 &  0.783 &  0.445 \\
+L & $ 3.0 \cdot 10^{-2}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 929  $ & (0.020, 0.044, 0.070) &  0.863 &  0.782 &  0.448 \\
+L & $ 10^{-1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1142 $ & (0.081, 0.076, 0.102) &  0.848 &  0.725 &  0.450 \\
+L & $ 3.0 \cdot 10^{-1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 1109 $ & (0.076, 0.129, 0.157) &  0.825 &  0.655 &  0.451 \\
+L & $1.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.182, 0.225, 0.251) &  0.787 &  0.599 &  0.442 \\
+L & $ 2.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 3000 $ & (0.278, 0.315, 0.340) &  0.759 &  0.570 &  0.436 \\
+L & $ 4.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 10000$ & (0.399, 0.431, 0.455) &  0.737 &  0.518 &  0.428 \\
+L & $ 8.0$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 5000 $ & (0.519, 0.545, 0.562) &  0.718 &  0.484 &  0.421 \\
+L & $ 1.6 \cdot 10^{1}$ & $ 10^{3}$ & $ 8.0 \cdot 10^{2}$ &  128x128x256 & $ 8000 $ & (0.687, 0.709, 0.723) &  0.700 &  0.442 &  0.417 \\
 \enddata                                                   	

### 2021-07-23 data/check_turbulence_hypothesis.py

@@ -1,0 +1,222 @@
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+from scipy.optimize import brentq
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('new_erf_Re*/erf*') 
+dirs += ["new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/"]
+dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
+
+nz = 1024
+Lz = 2
+z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
+domain = de.Domain([z_basis], grid_dtype=np.float64)
+ke_rhs = domain.new_field()
+ke_flux = domain.new_field()
+domain_z = domain.grid(-1)
+
+fig = plt.figure()
+
+ax1 = fig.add_subplot(1,2,1)
+ax2 = fig.add_subplot(1,2,2)
+
+fig2 = plt.figure()
+ax3 = fig2.add_subplot(1,1,1)
+
+fig3 = plt.figure()
+ax4 = fig3.add_subplot(1,1,1)
+
+fig4 = plt.figure()
+ax5 = fig4.add_subplot(1,1,1)
+
+
+fig5 = plt.figure()
+ax6 = fig5.add_subplot(1,1,1)
+
+fig6 = plt.figure()
+ax7 = fig6.add_subplot(1,1,1)
+
+
+cmap = "viridis_r"
+norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
+sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+
+
+
+
+data = []
+for i, d in enumerate(dirs):
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        theory_f = f['f_theory_cz'][()]
+        Ls = f['Ls'][()]
+        tot_time = times[-1] - times[0]
[…]

### 2021-07-23 data/consolidate_time_data.py

@@ -1,0 +1,173 @@
+from collections import OrderedDict
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+from scipy.interpolate import interp1d
+import pandas as pd
+
+
+dirs_p1 = ["erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild/",
+           "erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart/"]
+
+dirs_p1_down = ['noslip_erf_P_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0/']
+dirs_p1_up   = ['erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.3']
+
+dirs_p2 = ["erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild/",
+           "erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart/",
+           "erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart2/",
+           "erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart3/"]
+
[…]

### 2021-07-23 data/create_scalar_table.sh

@@ -1,1 +1,2 @@
-python3 output_simulation_details.py noslip_erf_*/erf*/ stressfree_erf_Re_cut/erf*/ noslip_linear_P_cut/linear_3D_Re8e2_P*/ erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart3 erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart5
+python3 output_simulation_details.py noslip_erf_*/erf*/ stressfree_erf_Re_cut/erf*/ noslip_linear_P_cut/linear_3D_Re8e2_P*/ erf_AE_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart erf_AE_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart3 erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart6
+python3 table_creator.py

### 2021-07-23 data/daniel_proposal_fig.py

@@ -1,0 +1,223 @@
+import matplotlib
+from collections import OrderedDict
+import numpy as np
+import matplotlib.pyplot as plt
+import h5py
+
+import glob
+
+import dedalus.public as de
+plt.style.use('apj')
+
+
+# Get data from files
+dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s8.h5'
+profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s8.h5'
+#dynamics_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/slices/slices_s5.h5'
+#profile_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/profiles/profiles_s5.h5'
+
+with h5py.File(profile_file, 'r') as f:
+    z = f['scales/z/1.0'][()].squeeze()
+    mean_T1 = np.mean(f['tasks/T1'][()][:,:].squeeze(), axis=0)
+    T1_fluc = np.mean(f['tasks/T1_fluc'][()][:,:].squeeze(), axis=0)
+    grad = -np.mean(f['tasks/T_z'][()][:,:].squeeze(), axis=0)
+    grad_ad = -np.mean(f['tasks/T_ad_z'][()][:,:].squeeze(), axis=0)
+    grad_rad = -np.mean(f['tasks/T_rad_z'][()][:,:].squeeze(), axis=0)
+
+    departure_frac = 0.5
+    departed_points = (z > 1)*(grad > grad_ad - departure_frac * (grad_ad - grad_rad))
+    departure_point = z[departed_points][-1]
+
+
+#    plt.plot(z, grad_ad)
+#    plt.plot(z, grad_rad)
+#    plt.plot(z, grad)
+#    plt.show()
+
+
+# Set up figure subplots
+fig = plt.figure(figsize=(6.5, 1.5))
+cax_specs = [( 0,   0.8,   0.27,   0.08),
+             ]
+ax_specs = [
[…]

### 2021-07-23 data/plot_AE_fig.py

@@ -10,12 +10,21 @@ import pandas as pd
 col_width = 3.25
 golden_ratio = 1.61803398875
 
-dirs = glob.glob('erf_AE_cut/erf*/')
-dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0/']
-dirs += ['noslip_erf_P_cut/not_in_use/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.1/']
-#dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
-dirs += ['noslip_erf_P_cut/not_in_use/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/']
-#dirs += ['noslip_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256/']
+S = 1e3
+Re = 400
+Lz = 2
+
+p1      = ('p1_long', 'temporal_data/erf_re4e2_p1e0_s1e3_longevolution.h5')
+p1_down = ('p1_down', 'temporal_data/erf_re4e2_p1e0_s1e3_pertDown.h5')
+p1_up   = ('p1_up'  , 'temporal_data/erf_re4e2_p1e0_s1e3_pertUp.h5')
+p2      = ('p2_long', 'temporal_data/erf_re4e2_p2e0_s1e3_longevolution.h5')
+p2_down = ('p2_down', 'temporal_data/erf_re4e2_p2e0_s1e3_pertDown.h5')
+p2_up   = ('p2_up'  , 'temporal_data/erf_re4e2_p2e0_s1e3_pertUp.h5')
+p4      = ('p4_long', 'temporal_data/erf_re4e2_p4e0_s1e3_longevolution.h5')
+p4_down = ('p4_down', 'temporal_data/erf_re4e2_p4e0_s1e3_pertDown.h5')
[…]

### 2021-07-23 data/plot_erf_delta_p.py

@@ -14,13 +14,18 @@ dirs = glob.glob('new_erf*/erf*')
 
 data = []
 for d in dirs:
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
     with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
         times = f['times'][()]
         L_d01s = f['L_d01s'][()]
         L_d05s = f['L_d05s'][()]
         L_d09s = f['L_d09s'][()]
         theory_f = f['f_theory_cz'][()]
-        Ls = f['Ls'][()]
+        z2 = f['z2'][()]
+        Ls = np.mean(f['Ls'][()])
         tot_time = times[-1] - times[0]
         time_window = np.min((500, tot_time/2))
         good_times = times > (times[-1] - time_window)
@@ -28,10 +33,9 @@ for d in dirs:
         mean_L_d05 = np.mean(L_d05s[good_times])
         mean_L_d09 = np.mean(L_d09s[good_times])
         mean_f = np.mean(theory_f[good_times])
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
+        mean_z2 = np.mean(z2[good_times])
+        if Re == 6.4e3:
+            print(mean_L_d01 - Ls, mean_L_d05 - Ls, mean_L_d09 - Ls)
     if '3D' in d:
         threeD = True
     else:
@@ -45,7 +49,7 @@ for d in dirs:
     else:
         ae = False
 
-    data.append((S, P, Re, threeD, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, Ls, Lz, erf, ae))
+    data.append((S, P, Re, threeD, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, Ls, Lz, erf, ae, mean_z2))
[…]

### 2021-07-23 data/plot_erf_dissipation_vs_p.py

@@ -1,0 +1,211 @@
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+from matplotlib.patches import ConnectionPatch
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('new_erf*/erf*')
+
+data = []
+for d in dirs:
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        theory_f = f['f_theory_cz'][()]
+        enstrophy = f['enstrophy_Ls'][()]
+        fconv = f['fconv_cz'][()]
+        vel_Ls = f['vel_Ls'][()]
+        z2 = f['z2'][()]
+        Ls = np.mean(f['Ls'][()])
+        tot_time = times[-1] - times[0]
+        time_window = np.min((500, tot_time/2))
+        good_times = times > (times[-1] - time_window)
+        mean_L_d01 = np.mean(L_d01s[good_times])
+        mean_L_d05 = np.mean(L_d05s[good_times])
+        mean_L_d09 = np.mean(L_d09s[good_times])
+        mean_f = np.mean(theory_f[good_times])
+        mean_dissipation = np.mean(enstrophy[good_times])/Re
+        mean_z2 = np.mean(z2[good_times])
+        mean_vel = np.mean(vel_Ls[good_times])
+        mean_fconv = np.mean(fconv[good_times])
+        if Re == 6.4e3:
+            print(mean_L_d01 - Ls, mean_L_d05 - Ls, mean_L_d09 - Ls)
+    if '3D' in d:
+        threeD = True
+    else:
+        threeD = False
[…]

### 2021-07-23 data/plot_mesa_profiles.py

@@ -19,8 +19,8 @@ brewer_green  = np.array(( 27,158,119, 255))/255
 brewer_orange = np.array((217, 95,  2, 255))/255
 brewer_purple = np.array((117,112,179, 255))/255
 
-penetration_run_file = 'MESA/PZ.data'#mesa_penetration_profile67.data'
-standard_run_file = 'MESA/no_pz.data'#mesa_penetration_profile67.data'
+penetration_run_file = 'MESA/PZ.data'
+standard_run_file = 'MESA/no_pz.data'
 pf = mr.MesaData(penetration_run_file)
 sf = mr.MesaData(standard_run_file)
 
@@ -29,14 +29,14 @@ fig_mesa = plt.figure(figsize=(col_width, 1.5*col_width/golden_ratio))
 ax_grad   = fig_mesa.add_axes([0.00, 0.50, 1, 0.5])
 ax_cs = fig_mesa.add_axes([0.00, 0.00, 1, 0.5])
 
-pz_mass = pf.mass[::-1] * constants.M_sun
-pz_radius = pf.radius[::-1] * constants.R_sun
+pz_mass = pf.mass[::-1] * constants.M_sun.cgs
+pz_radius = pf.radius[::-1] * constants.R_sun.cgs
 pz_rho    = 10**(pf.logRho[::-1]) * (u.g/u.cm**3)
 pz_P      = 10**(pf.logP[::-1]) * (u.g / u.cm / u.s**2)
-gravity   = constants.G.cgs*pz_mass/pz_radius**2
-gradP     = pz_rho*gravity
-grad_ln_P = gradP/pz_P
-HP        = 1/grad_ln_P
+gravity   = constants.G.cgs*pz_mass.cgs/pz_radius.cgs**2
+gradP     = pz_rho.cgs*gravity.cgs
+grad_ln_P = gradP.cgs/pz_P.cgs
+HP        = 1/grad_ln_P.cgs
 penetration = pf.penetration_fraction[::-1]
 
 good_pz = (penetration == 1)*(pz_radius.cgs/constants.R_sun.cgs < 0.85)
@@ -70,7 +70,7 @@ ax_grad.plot(r, grad_rad, c=brewer_orange, label=r'$\nabla_{\rm{rad}}$', lw=1.5)
[…]

### 2021-07-23 data/plot_theory_profiles.py

@@ -17,24 +17,11 @@ brewer_green  = np.array(( 27,158,119, 255))/255
 brewer_orange = np.array((217, 95,  2, 255))/255
 brewer_purple = np.array((117,112,179, 255))/255
 
-#d = directory = 'erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart4/'
-#d = directory = 'new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/'
-d = directory = 'noslip_erf_Re_cut/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/'
-filename = directory + '/avg_profs/averaged_avg_profs.h5'
-
-S = float(d.split('_S')[-1].split('_')[0])
-P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-Re = float(d.split('_Re')[-1].split('_')[0])
-Lz = float(d.split('_Lz')[-1].split('_')[0])
-
-fig_grad = plt.figure(figsize=(col_width, col_width/golden_ratio))
-fig_theory = plt.figure(figsize=(col_width, 1.5*col_width/golden_ratio))
-
-ax_grad = fig_grad.add_subplot(1,1,1)
-
-ax_flux   = fig_theory.add_axes([0.00, 0.50, 1, 0.5])
-ax_source = fig_theory.add_axes([0.00, 0.00, 1, 0.5])
-
+Re = 6.4e3
+P = 4
+S = 1e3
+Lz = 2
+filename = 'turbulent_profiles/re6.4e3_p4e0_s1e3_avg_profiles.h5'
 with h5py.File(filename, 'r') as f:
     enstrophy_profiles = f['enstrophy'][()]
     fconv_profiles = f['F_conv'][()]
@@ -52,6 +39,16 @@ ke_eqn_rhs  = fconv - dissipation
 grad     = grad_profiles[N,:]
 grad_ad  = grad_ad_profiles[N,:]
 grad_rad = grad_rad_profiles[N,:]
+
+
[…]

### 2021-07-23 data/plot_time_fig.py

@@ -13,13 +13,27 @@ import pandas as pd
 col_width = 3.25
 golden_ratio = 1.61803398875
 
-dirs = ["erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild/",
-        "erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart",
-        "erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart2",
-        "erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart3",
-        "erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart4",
-        "erf_AE_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart5",
-        ]
+with h5py.File('temporal_data/erf_re4e2_p4e0_s1e3_longevolution.h5', 'r') as in_f:
+    d01s = in_f['scalars/d01'][100:] 
+    d05s = in_f['scalars/d05'][100:] 
+    d09s = in_f['scalars/d09'][100:] 
+    times = in_f['scalars/times'][100:]
+    f = in_f['scalars/f'][100:]
+    xi = in_f['scalars/xi'][100:]  
+    Ls = in_f['scalars/Ls'][()]
+    z    = in_f['profiles/z'][()]
+    grad = in_f['profiles/grad'][()]  
+    prof_times = in_f['profiles/times'][()] 
+    grad_ad = in_f['profiles/grad_ad'][()] 
+    grad_rad = in_f['profiles/grad_rad'][()] 
+
+S = 1e3
+P = 4
+Re = 4e2
+Lz = 2
+
+k_rz = 0.2 / (S * P)
+t_diff = 1/k_rz
 
[…]

### 2021-07-23 data/print_linear_ell_nu.py

@@ -1,0 +1,121 @@
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+from scipy.optimize import brentq
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('noslip_linear_P_cut/*P1e0*/')
+dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
+
+#nz = 1024
+#Lz = 2
+#z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
+#domain = de.Domain([z_basis], grid_dtype=np.float64)
+#ke_rhs = domain.new_field()
+#ke_flux = domain.new_field()
+#domain_z = domain.grid(-1)
+
+cmap = "viridis_r"
+norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
+sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+
+data = []
+for i, d in enumerate(dirs):
+    S = float(d.split('_S')[-1].split('_')[0])
+    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
+    Re = float(d.split('_Re')[-1].split('_')[0])
+    Lz = float(d.split('_Lz')[-1].split('_')[0])
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        modern_f = f['modern_f'][()]
+        modern_xi = f['modern_xi'][()]
+        fconv_Ls = f['fconv_Ls'][()]
+        fconv_cz = f['fconv_cz'][()]
+        Ls = np.mean(f['Ls'][()])
+        tot_time = times[-1] - times[0]
+        time_window = np.min((500, tot_time/2))
+        good_times = times > (times[-1] - time_window)
+        mean_L_d01 = np.mean(L_d01s[good_times])
+        mean_L_d05 = np.mean(L_d05s[good_times])
+        mean_L_d09 = np.mean(L_d09s[good_times])
[…]

### 2021-07-23 data/top_bottom_dissipation.py

@@ -1,0 +1,237 @@
+import glob
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+import dedalus.public as de
+from scipy.interpolate import interp1d
+from scipy.optimize import brentq
+
+col_width = 3.25
+page_width = 6.5
+golden_ratio = 1.61803398875
+
+dirs = glob.glob('new_erf_Re*/erf*') 
+dirs += ["new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/"]
+dirs += glob.glob('stressfree_erf/erf*/')
+dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
+
+nz = 1024
+Lz = 2
+z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
+domain = de.Domain([z_basis], grid_dtype=np.float64)
+ke_rhs = domain.new_field()
+ke_flux = domain.new_field()
+domain_z = domain.grid(-1)
+
+fig = plt.figure()
+
+ax1 = fig.add_subplot(2,2,1)
+ax2 = fig.add_subplot(2,2,2)
+ax3 = fig.add_subplot(2,2,3)
+ax4 = fig.add_subplot(2,2,4)
+
+fig2 = plt.figure(figsize=(8, 3))
+
+ax_f1 = fig2.add_subplot(1,2,1)
+ax_f2 = fig2.add_subplot(1,2,2)
+
+cmap = "viridis_r"
+norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
+sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
+
+
+
+
+data = []
+for i, d in enumerate(dirs):
+    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
+        times = f['times'][()]
+        L_d01s = f['L_d01s'][()]
+        L_d05s = f['L_d05s'][()]
+        L_d09s = f['L_d09s'][()]
+        theory_f = f['f_theory_cz'][()]
+        Ls = f['Ls'][()]
+        tot_time = times[-1] - times[0]
+        time_window = np.min((500, tot_time/2))
+        good_times = times > (times[-1] - time_window)
[…]

### 2021-07-23 manuscript/ms.tex
drops in Zenodo citation

@@
 We produce the figures in this paper using matplotlib \citep{hunter2007, mpl3.3.4}.
-All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository, found at [TODO CITE].
+All of the Python scripts used to run the simulations in this paper and to create the figures in this paper are publicly available in a git repository\footnote{\url{https://github.com/evanhanders/convective_penetration_paper}}, and in a Zenodo repository \citep{supp}.
 
@@
 Models were constructed to reasonably reproduce the present-day Sun and based on the 2019 MESA summer school lab by~\citet{pm}.
-Inlists and the \texttt{run\_star\_extras} source code are available at CITE.
+Inlists and the \texttt{run\_star\_extras} source code are available in a Zenodo repository \citep{supp}.
 

### 2021-07-23 data/check_turbulence_hypothesis.py
deletes some unecessary data files

@@ -1,222 +1,0 @@
-import glob
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-import dedalus.public as de
-from scipy.interpolate import interp1d
-from scipy.optimize import brentq
-
-col_width = 3.25
-page_width = 6.5
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('new_erf_Re*/erf*') 
-dirs += ["new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/"]
-dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
-
-nz = 1024
-Lz = 2
-z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
-domain = de.Domain([z_basis], grid_dtype=np.float64)
-ke_rhs = domain.new_field()
-ke_flux = domain.new_field()
-domain_z = domain.grid(-1)
-
-fig = plt.figure()
-
-ax1 = fig.add_subplot(1,2,1)
-ax2 = fig.add_subplot(1,2,2)
-
-fig2 = plt.figure()
-ax3 = fig2.add_subplot(1,1,1)
-
-fig3 = plt.figure()
-ax4 = fig3.add_subplot(1,1,1)
-
-fig4 = plt.figure()
-ax5 = fig4.add_subplot(1,1,1)
-
-
-fig5 = plt.figure()
-ax6 = fig5.add_subplot(1,1,1)
-
-fig6 = plt.figure()
-ax7 = fig6.add_subplot(1,1,1)
-
-
-cmap = "viridis_r"
-norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
-sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
-
-
-
-
-data = []
-for i, d in enumerate(dirs):
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        theory_f = f['f_theory_cz'][()]
-        Ls = f['Ls'][()]
-        tot_time = times[-1] - times[0]
[…]

### 2021-07-23 data/compare_time_traces.py

@@ -1,54 +1,0 @@
-"""
-Script for plotting movies of 1D profile movies showing the top of the CZ vs time.
-
-Usage:
-    compare_top_cz_traces.py <dirs>... [options]
-
-Options:
-    --dpi=<dpi>                         Image pixel density [default: 200]
-
-"""
-from collections import OrderedDict
-import h5py
-from mpi4py import MPI
-from docopt import docopt
-args = docopt(__doc__)
-from plotpal.file_reader import SingleFiletypePlotter as SFP
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.ticker as mtick
-import scipy.optimize as sop
-from scipy.interpolate import interp1d
-import logging
-logger = logging.getLogger(__name__)
-
-dirs = args['<dirs>']
-
-fig = plt.figure(figsize=(8, 5))
-ax1 = fig.add_subplot(2,1,1)
-ax2 = fig.add_subplot(2,1,2)
-
-colors = ['k', 'b', 'g', 'r']
-
-for i, d in enumerate(dirs):
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        f_theory_cz = f['f_theory_cz'][()]
-
-    if 'predictive' in d:
-        label = d.split('predictive')[-1].split('/')[0]
-    else:
-        label = "?"
-    ax1.plot(times, L_d01s, c=colors[i], label=label)
-    ax1.plot(times, L_d05s, c=colors[i])
-    ax1.plot(times, L_d09s, c=colors[i])
-
-    ax2.plot(times, f_theory_cz, c=colors[i])
-ax2.set_ylim(0.4, 1)
-ax1.legend()
-
-for d in dirs:
-    plt.savefig('{:s}/comparison_top_cz_trace.png'.format(d), dpi=int(args['--dpi']), bbox_inches='tight')

### 2021-07-23 data/daniel_proposal_fig.py

@@ -1,223 +1,0 @@
-import matplotlib
-from collections import OrderedDict
-import numpy as np
-import matplotlib.pyplot as plt
-import h5py
-
-import glob
-
-import dedalus.public as de
-plt.style.use('apj')
-
-
-# Get data from files
-dynamics_file = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/slices_s8.h5'
-profile_file  = 'turbulence_slices/erf_step_3D_Re6.4e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_384x384x384/profiles_s8.h5'
-#dynamics_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/slices/slices_s5.h5'
-#profile_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/profiles/profiles_s5.h5'
-
-with h5py.File(profile_file, 'r') as f:
-    z = f['scales/z/1.0'][()].squeeze()
-    mean_T1 = np.mean(f['tasks/T1'][()][:,:].squeeze(), axis=0)
-    T1_fluc = np.mean(f['tasks/T1_fluc'][()][:,:].squeeze(), axis=0)
-    grad = -np.mean(f['tasks/T_z'][()][:,:].squeeze(), axis=0)
-    grad_ad = -np.mean(f['tasks/T_ad_z'][()][:,:].squeeze(), axis=0)
-    grad_rad = -np.mean(f['tasks/T_rad_z'][()][:,:].squeeze(), axis=0)
-
-    departure_frac = 0.5
-    departed_points = (z > 1)*(grad > grad_ad - departure_frac * (grad_ad - grad_rad))
-    departure_point = z[departed_points][-1]
-
-
-#    plt.plot(z, grad_ad)
-#    plt.plot(z, grad_rad)
-#    plt.plot(z, grad)
-#    plt.show()
-
-
-# Set up figure subplots
-fig = plt.figure(figsize=(6.5, 1.5))
-cax_specs = [( 0,   0.8,   0.27,   0.08),
-             ]
-ax_specs = [
[…]

### 2021-07-23 data/dynamics_panels.py

@@ -1,117 +1,0 @@
-import matplotlib
-from collections import OrderedDict
-import numpy as np
-import matplotlib.pyplot as plt
-import h5py
-
-import dedalus.public as de
-plt.style.use('apj')
-
-
-# Get data from files
-dynamics_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/slices/slices_s5.h5'
-profile_file = 'turbulence_slices/erf_step_3D_Re3.2e3_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer200_256x256x256_predictive0.46/profiles/profiles_s5.h5'
-
-with h5py.File(profile_file, 'r') as f:
-    z = f['scales/z/1.0'][()].squeeze()
-    mean_T1 = np.mean(f['tasks/T1'][()][:,:].squeeze(), axis=0)
-    grad = -np.mean(f['tasks/T_z'][()][:,:].squeeze(), axis=0)
-    grad_ad = -np.mean(f['tasks/T_ad_z'][()][:,:].squeeze(), axis=0)
-    grad_rad = -np.mean(f['tasks/T_rad_z'][()][:,:].squeeze(), axis=0)
-
-    departure_frac = 0.5
-    departed_points = (z > 1)*(grad > grad_ad - departure_frac * (grad_ad - grad_rad))
-    departure_point = z[departed_points][-1]
-#    plt.plot(z, grad_ad)
-#    plt.plot(z, grad_rad)
-#    plt.plot(z, grad)
-#    plt.show()
-
-
-# Set up figure subplots
-fig = plt.figure(figsize=(3.5, 6.5))
-cax_specs = [( 0,   0.95,   0.47,   0.04),
-             ( 0.53, 0.95,   0.47,   0.04)]
-ax_specs = [( 0,   0.78,    0.47,   0.12),
-            ( 0,   0.52,    0.47,   0.25),
-            ( 0,   0.26,    0.47,   0.25),
-            ( 0,   0,       0.47,   0.25),
-            ( 0.53, 0.78,   0.47,   0.12),
-            ( 0.53, 0.52,   0.47,   0.25),
-            ( 0.53, 0.26,   0.47,   0.25),
-            ( 0.53, 0,      0.47,   0.25),
-            ]
[…]

### 2021-07-23 data/plot_erf_delta_p.py

@@ -1,186 +1,0 @@
-import glob
-import numpy as np
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-from matplotlib.patches import ConnectionPatch
-
-col_width = 3.25
-page_width = 6.5
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('new_erf*/erf*')
-
-data = []
-for d in dirs:
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        theory_f = f['f_theory_cz'][()]
-        z2 = f['z2'][()]
-        Ls = np.mean(f['Ls'][()])
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_f = np.mean(theory_f[good_times])
-        mean_z2 = np.mean(z2[good_times])
-        if Re == 6.4e3:
-            print(mean_L_d01 - Ls, mean_L_d05 - Ls, mean_L_d09 - Ls)
-    if '3D' in d:
-        threeD = True
-    else:
-        threeD = False
-    if 'erf' in d:
-        erf = True
-    else:
-        erf = False
-    if 'AE' in d:
-        ae = True
-    else:
-        ae = False
-
-    data.append((S, P, Re, threeD, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, Ls, Lz, erf, ae, mean_z2))
-#    print(d)
[…]

### 2021-07-23 data/plot_erf_dissipation_vs_p.py

@@ -1,211 +1,0 @@
-import glob
-import numpy as np
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-from matplotlib.patches import ConnectionPatch
-
-col_width = 3.25
-page_width = 6.5
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('new_erf*/erf*')
-
-data = []
-for d in dirs:
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        theory_f = f['f_theory_cz'][()]
-        enstrophy = f['enstrophy_Ls'][()]
-        fconv = f['fconv_cz'][()]
-        vel_Ls = f['vel_Ls'][()]
-        z2 = f['z2'][()]
-        Ls = np.mean(f['Ls'][()])
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_f = np.mean(theory_f[good_times])
-        mean_dissipation = np.mean(enstrophy[good_times])/Re
-        mean_z2 = np.mean(z2[good_times])
-        mean_vel = np.mean(vel_Ls[good_times])
-        mean_fconv = np.mean(fconv[good_times])
-        if Re == 6.4e3:
-            print(mean_L_d01 - Ls, mean_L_d05 - Ls, mean_L_d09 - Ls)
-    if '3D' in d:
-        threeD = True
-    else:
-        threeD = False
[…]

### 2021-07-23 data/plot_linear_delta_p.py

@@ -1,95 +1,0 @@
-import glob
-import numpy as np
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-col_width = 3.25
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('linear*/lin*/')
-dirs += glob.glob('new_linear*/lin*/')
-
-data = []
-for d in dirs:
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        enstrophy_f = f['f_theory_enstrophy'][()]
-        Ls = f['Ls'][()]
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_enstrophy_f = np.mean(enstrophy_f[good_times])
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    if 'new_linear' not in d and P >= 1:
-        continue
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    if '3D' in d:
-        threeD = True
-    else:
-        threeD = False
-    if 'erf' in d:
-        erf = True
-    else:
-        erf = False
-    if 'AE' in d:
-        ae = True
-    else:
-        ae = False
-
-    data.append((S, P, Re, threeD, mean_L_d01, mean_L_d05, mean_L_d09, mean_enstrophy_f, Ls, Lz, erf, ae))
-    print(d)
-    print("                 ",S, P, Re, mean_L_d01, mean_L_d05, mean_L_d09, mean_enstrophy_f)
-data = np.array(data)
-
-S = data[:,0]
-P = data[:,1]
-Re = data[:,2]
-threeD = data[:,3]
-L_d01 = data[:,4]
[…]

### 2021-07-23 data/plot_turbulence_velocities.py

@@ -1,53 +1,0 @@
-import glob
-import numpy as np
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-col_width = 3.25
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('erf_Re_cut*/erf*/') + glob.glob('erf_P_cut*/erf*/')
-
-data = []
-for d in dirs:
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        cz_vel = f['cz_velocities'][()]
-        tot_time = times[-1] - times[0]
-        good_times = times > times[0] + tot_time/2
-        mean_vel = np.mean(cz_vel[good_times])
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    if '3D' in d:
-        threeD = True
-    else:
-        threeD = False
-    if 'erf' in d:
-        erf = True
-    else:
-        erf = False
-
-    data.append((S, P, Re, threeD, mean_vel, Lz, erf))
-data = np.array(data)
-
-S = data[:,0]
-P = data[:,1]
-Re = data[:,2]
-threeD = data[:,3]
-vel = data[:,4]
-Lz = data[:,5]
-erf = data[:,6]
-
-plt.figure(figsize=(col_width, col_width/golden_ratio))
-good = (erf == 1) * (P == 4)
-plt.scatter(Re[good], vel[good], c='k')
-plt.xscale('log')
-#plt.yscale('log')
-
-plt.show()
-
-#plt.savefig('linear_3D_penetration_depths.png', dpi=300, bbox_inches='tight')
-#plt.savefig('../manuscript/linear_3D_penetration_depths.pdf', dpi=300, bbox_inches='tight')

### 2021-07-23 data/print_linear_ell_nu.py

@@ -1,121 +1,0 @@
-import glob
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-import dedalus.public as de
-from scipy.interpolate import interp1d
-from scipy.optimize import brentq
-
-col_width = 3.25
-page_width = 6.5
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('noslip_linear_P_cut/*P1e0*/')
-dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
-
-#nz = 1024
-#Lz = 2
-#z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
-#domain = de.Domain([z_basis], grid_dtype=np.float64)
-#ke_rhs = domain.new_field()
-#ke_flux = domain.new_field()
-#domain_z = domain.grid(-1)
-
-cmap = "viridis_r"
-norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
-sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
-
-data = []
-for i, d in enumerate(dirs):
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        modern_f = f['modern_f'][()]
-        modern_xi = f['modern_xi'][()]
-        fconv_Ls = f['fconv_Ls'][()]
-        fconv_cz = f['fconv_cz'][()]
-        Ls = np.mean(f['Ls'][()])
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
[…]

### 2021-07-23 data/print_scalars.py

@@ -1,51 +1,0 @@
-import glob
-import numpy as np
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-col_width = 3.25
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('new_linear*/lin*/') + glob.glob('new_erf*/erf*/')
-
-data = []
-print('{:5s}, {:5s}, {:5s}, {:10s}, {:10s}, {:10s}'.format('P', 'R', 'S', 'type', 'f', 'Lcz'))
-for d in dirs:
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        theory_f = f['f_theory_cz'][()]
-        Ls = f['Ls'][()]
-        z2 = f['z2'][()]
-        L_cz = Ls - z2
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
-        mean_L_d01 = np.mean(L_d01s[good_times])
-        mean_L_d05 = np.mean(L_d05s[good_times])
-        mean_L_d09 = np.mean(L_d09s[good_times])
-        mean_f = np.mean(theory_f[good_times])
-        mean_L_cz = np.mean(L_cz[good_times])
-    S = float(d.split('_S')[-1].split('_')[0])
-    P = float(d.split('_Pr')[0].split('_P')[-1].split('_')[0])
-    Re = float(d.split('_Re')[-1].split('_')[0])
-    Lz = float(d.split('_Lz')[-1].split('_')[0])
-    if '3D' in d:
-        threeD = True
-    else:
-        threeD = False
-    if 'erf' in d:
-        dirtype = 'erf'
-    else:
-        dirtype = 'linear' 
-    if 'AE' in d:
-        ae = True
-    else:
-        ae = False
-
-    data.append((S, P, Re, threeD, mean_L_d01, mean_L_d05, mean_L_d09, mean_f, Ls, Lz, dirtype, ae))
-    print('{:5.0f}, {:5.0f}, {:5.0f}, {:10s}, {:10f}, {:10f}'.format(P, Re, S, dirtype, mean_f, mean_L_cz))
-

### 2021-07-23 data/pull.sh

@@ -1,135 +1,0 @@
-PLEIADESROOT=/nobackup/eanders/convective_penetration_paper/dedalus_code/
-
-# linear P runs
-PLEIADESBASE=$PLEIADESROOT/paper_linear_P_cut/
-LOCALBASE=linear_P_cut/
-declare -a StringArray=(\
-"linear_3D_Re8e2_P1e-2_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.023"
-"linear_3D_Re8e2_P3e-2_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.04"
-"linear_3D_Re8e2_P1e-1_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.073"
-"linear_3D_Re8e2_P3e-1_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.126"
-"linear_3D_Re8e2_P1e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.23"
-"linear_3D_Re8e2_P2e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.325"
-"linear_3D_Re8e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.46"
-"linear_3D_Re8e2_P8e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.65"
-"linear_3D_Re8e2_P1.6e1_zeta1e-3_S1e3_Lz2.25_Lcz1_Pr0.5_a2_Titer0_64x64x256_predictive0.92"
-)
-for d in ${StringArray[@]}
-do
-	echo $d
-	LOCALDIR=$LOCALBASE/$d
-	PLEIADESDIR=$PLEIADESBASE/$d
-	mkdir $LOCALDIR/
-	scp pfe:$PLEIADESDIR/top_cz/cz_velocities.png ./$LOCALDIR/
-	scp pfe:$PLEIADESDIR/top_cz/trace_top_cz.png ./$LOCALDIR/
[…]

### 2021-07-23 data/top_bottom_dissipation.py

@@ -1,237 +1,0 @@
-import glob
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-plt.style.use('apj')
-import h5py
-
-import dedalus.public as de
-from scipy.interpolate import interp1d
-from scipy.optimize import brentq
-
-col_width = 3.25
-page_width = 6.5
-golden_ratio = 1.61803398875
-
-dirs = glob.glob('new_erf_Re*/erf*') 
-dirs += ["new_erf_P_cut/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer100_64x64x256_predictive0.4/"]
-dirs += glob.glob('stressfree_erf/erf*/')
-dirs.sort(key = lambda x: float(x.split('_Re')[-1].split('_')[0]))
-
-nz = 1024
-Lz = 2
-z_basis = de.Chebyshev('z', nz, interval=[0, Lz], dealias=1)
-domain = de.Domain([z_basis], grid_dtype=np.float64)
-ke_rhs = domain.new_field()
-ke_flux = domain.new_field()
-domain_z = domain.grid(-1)
-
-fig = plt.figure()
-
-ax1 = fig.add_subplot(2,2,1)
-ax2 = fig.add_subplot(2,2,2)
-ax3 = fig.add_subplot(2,2,3)
-ax4 = fig.add_subplot(2,2,4)
-
-fig2 = plt.figure(figsize=(8, 3))
-
-ax_f1 = fig2.add_subplot(1,2,1)
-ax_f2 = fig2.add_subplot(1,2,2)
-
-cmap = "viridis_r"
-norm = mpl.colors.Normalize(vmin=np.log10(50), vmax=3.5)
-sm = mpl.cm.ScalarMappable(norm=norm, cmap=cmap)
-
-
-
-
-data = []
-for i, d in enumerate(dirs):
-    with h5py.File('{:s}/data_top_cz.h5'.format(d), 'r') as f:
-        times = f['times'][()]
-        L_d01s = f['L_d01s'][()]
-        L_d05s = f['L_d05s'][()]
-        L_d09s = f['L_d09s'][()]
-        theory_f = f['f_theory_cz'][()]
-        Ls = f['Ls'][()]
-        tot_time = times[-1] - times[0]
-        time_window = np.min((500, tot_time/2))
-        good_times = times > (times[-1] - time_window)
[…]

### 2021-07-26 manuscript/ms.tex
starts implementing changes from Ben, including parameter space fig

@@
 %%%% Title and Abstract
-\title{Convective penetration probably parameterizes convective overshoot}
+\title{Convective penetration: It exists and we found it}
 \author[0000-0002-3433-4733]{Evan H. Anders}
@@
 To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
-Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
-We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
-In all cases we find significant convective penetration, although it can take thousands of overturn times to develop.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based theoretical model in which the extent of penetration is controlled by $\mP$.
+We test this theory using 3D numerical simulations which employ a simplified Boussinesq model of stellar convection.
+We find significant convective penetration in all simulations.
+Our simple theory describes the simulations well.
+Penetration zones can take thousands of overturn times to develop, so long simulations or accelerated evolutionary techniques are required.
 In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
-We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$50\% of a pressure scale height.
+We present a MESA stellar model of the Sun which employs our parameterization of convective penetration as a proof of concept.
 We discuss prospects for extending these results to more realistic stellar contexts.
@@
 The broad category of ``convective overshoot'' in the stellar literature is an umbrella term for a few hydrodynamical processes \citep{zahn1991, brummell_etal_2002, korre_etal_2019}.
-The first process is confusingly also called ``\emph{convective overshoot}'' in the fluid dynamics literature, and refers to motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles.
-The second process is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
-Many studies have also examined \emph{entrainment}, the process by which convection zones expand by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
+Motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles belong to a process called ``\emph{convective overshoot}'' in the fluid dynamics literature.
+A second process called ``\emph{entrainment}'' includes motions which expand convection zones by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
+Convective motions which extend the adiabatically-mixed convective region beyond the convective boundary belong to a third process called ``\emph{convective penetration}.''
 The primary focus of this work is convective penetration.
@@
 \subsection{Case I: Discontinuous flux}
+\label{sec:numerics_case1}
 Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
@@
 
-We study a sweep through each of the ($\mP_D$, $\mS$, $\mR$) parameter spaces while holding all other parameters constant.
+We study a sweep through each of the ($\mP_D$, $\mS$, $\mR$) parameter spaces while holding all other parameters constant (see Fig.~\ref{fig:parameter_space}).
 We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth]{parameter_space.pdf}
+\caption{
+Each point corresponds to a simulations conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
+Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty markers are simulations with stress-free boundary conditions while filled-in markers are simulations with no-slip boundary conditions.
+We additionally conduct simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
+\label{fig:parameter_space}
+}
+\end{figure}
+
 \subsection{Case II: Piecewise linear flux}
+\label{sec:numerics_case2}
+
 We also study simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
@@
 where $\psi \equiv 1 + \mP_L(1 + \mu)$.
-We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$.
+We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$ (see Fig.~\ref{fig:parameter_space}).
 According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.
@@
 \caption{
+Time evolution of the $\mR = 400$, $\mP = 4$, $\mS = 10^3$ Case I simulation.
 (left top panel) The PZ height $\delta_{0.5}$ vs.~time.
@@
 \caption{
-Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
+Results from the cuts through $\mP$ parameter space for the Case I (left panels; see solid purple circles in Fig.~\ref{fig:parameter_space}) and Case II (right panels; solid orange diamonds in Fig.~\ref{fig:parameter_space}) simulations.
 The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
@@
 \caption{
-(Left panel) Penetration heights are shown as a function of stiffness for Case I simulations with a discontinuous conductivity.
+Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
+(Left panel) Penetration heights are shown vs.~$\mS$.
 While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
@@
 \caption{
-(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations with a discontinuous conductivity.
+(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations (see vertical cut in Fig.~\ref{fig:parameter_space}).
 We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
@@
 We can only run the $\mR = 6.4 \times 10^{3}$ simulation for a few hundred freefall times.
-Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of the simulation (see Fig.~\ref{fig:time_evolution}).
+Our accuracy in measuring results from this simulation is limited by the long evolutionary timescales of the simulation (see Fig.~\ref{fig:time_evolution} for similar evolution in a less turbulent, $\mR = 400$ case).
 Even accounting for our accelerated evolutionary procedure, we can only be confident that the PZ heights of this simulation are converged to within a few percent.
@@
 
-While we have examine a Case I simulation with $\mP = 4$ here, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
+While we have examined a Case I simulation with $\mP = 4$ here, we expect the simulation with $\mP_L = 1$ (a linear radiative conductivity profile) to be the most representative of conditions near a stellar convective boundary.
 In this simulation, we measure $\xi \approx 0.6$, $f \approx 0.785$, $\ell_\nu \approx 0.08$, and $L_s = 1$.
@@
 
-\section{A modified solar model}
+\section{Testing our parameterization in a simple stellar model of the Sun}
 \label{sec:solar_model}
@@
 Our simulation results present a strong case for a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
+In this section, we discuss a simple stellar model of the Sun which we have created by implementing our parameterization into MESA (see Appendix~\ref{app:mesa}).
+We of course note that the theory and 3D simulations in this work do not include many of the complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
+We present this model as a proof of concept and to inspire further work.
+
 In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
@@
 
-We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and computed a standard solar model with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to determine an estimate of how the convective overshoot parameterization presented in this work might adjust a familiar stellar model.
-We note that the simulations that we have presented here do not include many of the complications of stellar convection like density stratification, sphericity, rotation, magnetism, etc.
-We present this model as a proof of concept and to inspire further work.
-
-In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from a 1 $M_\odot$ MESA model which has been evolved to an age of 4.56 Gyr and which includes convective penetration.
+We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and evolved a $1 M_\odot$ model to an age of 4.56 Gyr with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to qualitatively understand how our penetration parameterization modifies a stellar model.
+In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from the model which includes convective penetration.
 Note that $\justgrad$ (green) remains close to $\gradad$ (purple) below the Schwarzschild convective boundary ($\gradad = \gradrad$) in a penetration zone.
 After some depth $\justgrad \rightarrow \gradrad$ (orange) in the star's interior.
-We additionally evolved a standard solar MESA model to a 4.56 Gyr age without the inclusion of a PZ.
-We compare the sound speed profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
-We see that the inclusion of a PZ leads to an $\mathcal{O}$(2\%) increase in the sound speed profile near the base of the solar convection zone, similar to what is observed between helioseismic observations and standard models \citep{bergemann_serenelli_2014}.
-
+We additionally evolved a standard 1 $M_\odot$ MESA model to a 4.56 Gyr age without the inclusion of a PZ.
+We compare the sound speed $c$ profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
 When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).
+
 Helioseismic studies have argued that that the solar PZ depth cannot be larger than $\mathcal{O}$(0.05 $H_p$), because larger PZs would result in larger glitches than are detected  \citep[see Sct.~7.2.1 of][for a nice review]{basu2016}.
-However, some recent 3D convective simulations by \citet{kapyla2019} suggest that the solar PZ depth could be as large as $\mathcal{O}(0.2 H_p)$.
 In the model shown in Fig.~\ref{fig:mesa_profiles}, we find $H_p \approx 0.082R_\odot$ at the Schwarzschild CZ boundary, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot \sim 0.5 H_p$.
-This over-estimates fully compressible simulations by a factor of a few, and observations by an order of magnitude.
-However, it is unsurprising that our Boussinesq-based model only qualitatively matches observational constraints for the solar CZ.
+The inclusion of this PZ leads to an $\mathcal{O}$(2\%) increase in $c$ near the base of the solar convection zone.
+This change in $c$ has the same sign as is necessary to create better agreement between stellar models and helioseismic obserations, but is too large.
+Observations suggest that the change in $c$ should be $\mathcal{O}(1\%)$ \citep{bergemann_serenelli_2014} or that the change in $c^2$ should be $\mathcal{O}(0.4\%)$ \citep{christensen-dalsgaard_etal_2011}.
+While the PZ in Fig.~\ref{fig:mesa_profiles} is larger than helioseismic measures of $c$ suggest is possible, we note that the width of the PZ in this model aligns with the inferred width of the tachocline of $(0.039 \pm 0.013)R_\odot$ \citep{charbonneau_etal_1999}.
+
+It is unsurprising that our Boussinesq-based model only qualitatively matches observational constraints for the solar CZ.
 The solar convection zone is highly stratified ($\sim$14 density scale heights), and we neglected density stratification in this work.
-Fig.~\ref{fig:mesa_profiles} shows that our parameterization can produce penetration zones in 1D models with measurable acoustic glitches.
+Furthermore, the solar model used here is essentially a ``stock'' MESA model and has some obvious disagreement with the solar model S (e.g., the Schwarzschild base of the CZ should be closer to $r/R_\odot = 0.7$ than it is).
+Despite the limitations of this minimal proof of concept, Fig.~\ref{fig:mesa_profiles} shows that our parameterization can produce penetration zones in 1D models with measurable acoustic glitches.
 In a future paper, we will produce more realistic models by building upon our parameterization to include the crucial effects of density stratification.
@@
 We thank Keaton Burns, Matt Browning, Matteo Cantiello, Geoff Vasil, and Kyle Augustson for useful discussions and/or questions which improved the content of this manuscript.
+Ben Brown thanks Jeffrey Oishi for many years of discussions about overshooting convection.
 EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 

### 2021-07-26 data/plot_parameter_space.py

@@ -1,0 +1,74 @@
+from collections import OrderedDict
+import glob
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use('apj')
+import h5py
+
+from scipy.optimize import brentq
+from scipy.interpolate import interp1d
+
+import pandas as pd
+
+col_width = 3.25
+golden_ratio = 1.61803398875
+
+brewer_green  = np.array(( 27,158,119, 255))/255
+brewer_orange = np.array((217, 95,  2, 255))/255
+brewer_purple = np.array((117,112,179, 255))/255
+
+data = np.genfromtxt('scalar_table_data.csv', skip_header=1, delimiter=',', dtype=np.unicode_)
+S  = np.array(data[:,0], dtype=np.float64)
+P  = np.array(data[:,1], dtype=np.float64)
+Re = np.array(data[:,2], dtype=np.float64)
+erf = data[:,5]
+sf  = data[:,6]
+ae  = data[:,7]
+tmp = np.zeros_like(erf, dtype=bool)
+for i in range(erf.shape[0]):
+    if 'False' in erf[i]:
+        tmp[i] = 0
+    elif 'True' in erf[i]:
+        tmp[i] = 1
+erf = np.copy(tmp)
+
+tmp = np.zeros_like(sf, dtype=bool)
+for i in range(sf.shape[0]):
+    if 'False' in sf[i]:
+        tmp[i] = 0
+    elif 'True' in sf[i]:
+        tmp[i] = 1
+sf = np.copy(tmp)
+
+tmp = np.zeros_like(ae, dtype=bool)
+for i in range(ae.shape[0]):
+    if 'False' in ae[i]:
+        tmp[i] = 0
+    elif 'True' in ae[i]:
+        tmp[i] = 1
+ae = np.copy(tmp)
+
+fig = plt.figure(figsize=(col_width, col_width/golden_ratio))
+
+ax = fig.add_subplot(1,1,1)
+
+cut1 = (ae == True)*(sf == False)*(erf == True)*(S == 1e3)
+cut2 = (ae == True)*(sf == True)*(erf == True)*(S == 1e3)
+cut3 = (ae == True)*(sf == False)*(erf == False)*(S == 1e3)
+case2 = ax.scatter(P[cut3], Re[cut3], marker='d', c=brewer_orange, s=20, label='Case II')
[…]

### 2021-07-27 manuscript/ms.tex
updates figures and manuscript with comments from Ben; need a final pass-through

@@
 
+We will now describe the setup of the two types of simulations conducted in this work (Case I and Case II).
+As a visual aid, we provide Fig.~\ref{fig:parameter_space} to guide the eye to the portion of parameter space that we have studied in each of these cases.
+We denote two ``landmark cases'' using a purple box (Case I landmark) and an orange box (Case II landmark), and throughout this work we will call out data from these cases with a similar box to guide the eye.
+
 \subsection{Case I: Discontinuous flux}
@@
 We additionally conduct simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
+The two ``landmark'' simulations are denoted by boxes.
+The landmark Case I simulation has $\mR = 400$ and $\mP_D = 4$.
+The landmark Case II simulation has $\mR = 800$ and $\mP_L = 4$.
+Both landmark simulations have $\mS = 10^3$ and no-slip boundary conditions.
 \label{fig:parameter_space}
@@
 
+\subsection{Penetration height measurements}
+In our evolved simulations, the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
+To characterize the height of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
+We define the difference between the adiabatic and radiative gradient,
+\begin{equation}
+\Delta \equiv \gradad - \gradrad(z).
+\end{equation}
+We measure penetration heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$ of $\Delta$.
+Specifically,
+\begin{equation}
+L_s + \delta_{h} = \mathrm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta).
+\label{eqn:delta_p_measures}
+\end{equation}
+In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
+Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
+We find that these measurements based on the (slowly-evolving) thermodynamic profile provide a robust and straightforward measurement of penetration height \citep[for a discussion of alternate measurement choices, see][]{pratt_etal_2017}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth]{lessturb_dynamics_panels.pdf}
+\caption{
+Shown are temperature anomalies in the landmark simulations.
+(top) Case I landmark ($\mR = 400$, $\mP_D = 4$, $\mS = 10^3$) and (bottom) Case II landmark ($\mR = 800$, $\mP_L = 4$, $\mS = 10^3$).
+The temporally- and volume- averaged Reynolds number in the convection zone is $\sim 250$ in the top panel and $\sim 350$ in the bottom panel.
+As in Fig.~\ref{fig:vertical_dynamics_panels}, the boundary between the penetrative and radiative zones is shown as a solid horizontal line.
+The boundary between the penetrative zone and bulk convection zone is shown as a dashed horizontal line.
+In the bottom panel, there is an additional dashed horizontal line near the bottom of the domain; the linearly increasing conductivity creates a second PZ there where $\justgrad \approx \gradad > \gradrad$ below internal heating layer.
+We see that temperature anomalies have different signs in the bulk CZ and PZ, as in Fig.~\ref{fig:vertical_dynamics_panels}.
+\label{fig:lessturb_dynamics_panels}
+}
+\end{figure}
+
 \begin{figure*}[t]
@@
 \caption{
-Time evolution of the $\mR = 400$, $\mP = 4$, $\mS = 10^3$ Case I simulation.
+Time evolution of the landmark Case I simulation ($\mR = 400$, $\mP_D = 4$, $\mS = 10^3$).
 (left top panel) The PZ height $\delta_{0.5}$ vs.~time.
@@
 
-\subsection{Penetration height measurements}
-In our evolved simulations, the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
-To characterize the height of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
-We define the difference between the adiabatic and radiative gradient,
-\begin{equation}
-\Delta \equiv \gradad - \gradrad(z).
-\end{equation}
-We measure penetration heights in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$ of $\Delta$.
-Specifically,
-\begin{equation}
-L_s + \delta_{h} = \mathrm{max}(z) \,\,\mid\,\, \justgrad > (\gradad - h\,\Delta).
-\label{eqn:delta_p_measures}
-\end{equation}
-In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
-We find that these measurements based on the (slowly-evolving) thermodynamic profile provide a robust and straightforward measurement of penetration height \citep[for a discussion of alternate measurement choices, see][]{pratt_etal_2017}.
+\section{Results}
+\label{sec:results}
+
+We now describe the results of the 3D dynamical simulations described in the previous section.
+Fig.~\ref{fig:vertical_dynamics_panels} displays the dynamics in one of these simulations.
+While we will briefly examine dynamics here, our primary goal in this section is to quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory} using temporally averaged measures.
+
+\subsection{Dynamics}
+In Fig.~\ref{fig:lessturb_dynamics_panels} we display snapshots of the temperature anomalies in the two ``landmark'' simulations denoted by boxes in Fig.~\ref{fig:parameter_space}.
+We display the temperature anomaly in the top panel of the Case I simulation with $\mR = 400$, $\mP_D = 4$, and $\mS = 10^3$; this simulation is included in all three of our parameter space sweeps and represents the point where our ($\mR, \mP, \mS$) cuts converge  in Fig.~\ref{fig:parameter_space}.
+We display the temperature anomaly in the bottom panel of the Case II simulation with $\mR = 800$, $\mP_L = 4$, and $\mS = 10^3$.
+The bulk reynolds number in the convection zones of these simulations are (top) $\sim 250$ and (bottom) $\sim 350$.
+Thus, these simulations are less turbulent than the simulation in Fig.~\ref{fig:vertical_dynamics_panels} (bulk Re $\sim$ 5000).
+Aside from the degree of turbulence, the dynamics are very similar in Figs.~\ref{fig:vertical_dynamics_panels} \& \ref{fig:lessturb_dynamics_panels}.
+In particular, we observe that hot plumes in the CZ turn into cold plumes in the PZ (as they cross the dashed horizontal lines), and hot downflows in the PZ turn into cold downflows in the CZ.
+Convective plumes extend through the penetrative region and impact the stable radiative zone (above the solid horizontal line).
+The interface with the radiative zone is stiff, and so convective motions excite waves at a shallow angle above the radiative-convective boundary.
+We note that the Case II simulation has an additional temperature inversion at the base of the simulation.
+Case II simulations have a linearly increasing conductivity $k$ in the convection zone, so there is formally a small penetrative region where $\justgrad \approx \gradad > \gradrad$ at the base of the domain below the internal heating layer.
+
+While the landmark simulations in Fig.~\ref{fig:lessturb_dynamics_panels} are not as turbulent as the dynamics in Fig.~\ref{fig:vertical_dynamics_panels}, they are sufficiently nonlinear to be interesting.
+Importantly, these simulations develop large penetration zones, and can be evolved for tens of thousands of convective overturn times.
+As we will demonstrate in the next section, the formation timescale of penetrative zones can take tens of thousands of convective overturn times.
 
@@
 Results from the cuts through $\mP$ parameter space for the Case I (left panels; see solid purple circles in Fig.~\ref{fig:parameter_space}) and Case II (right panels; solid orange diamonds in Fig.~\ref{fig:parameter_space}) simulations.
+Boxed data points show the location of landmark simulations from Fig.~\ref{fig:parameter_space}.
 The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
@@
 
-\section{Results}
-\label{sec:results}
-
-We now describe the results of the 3D dynamical simulations described in the previous section.
-Fig.~\ref{fig:vertical_dynamics_panels} displays the dynamics in one of these simulations.
-In this section, we quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory} using temporally averaged measures.
-
 \subsection{Qualitative description of simulation evolution}
 
-In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial temperature profile sets $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
+In Fig.~\ref{fig:time_evolution}, we show the time evolution of the landmark Case I simulation ($\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$) whose initial temperature profile sets $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
 In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
@@
 Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
+Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
 (Left panel) Penetration heights are shown vs.~$\mS$.
@@
 (Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
+Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
 \label{fig:parameters_vs_re}
@@
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
-We briefly examined what the impliciations of this theory could be for a simple solar model.
-
-Our simulation results suggest that stellar convection zones should be bounded by sizeable penetration zones.
+We briefly examined what the impliciations of this theory could be for a simple stellatellarr model.
+
+Our simulation results suggest that stellar convection zones could be bounded by sizeable penetration zones.
 In extreme simulations, we observe penetration zones which are as large as the convection zones they accompany; however, for realistic stellar values ($\mP \approx 1$), we find that they may be as large as 20-30\% of the convective zone length scale ($\sim$the mixing length).
@@
 In particular, they demonstrate that the shape of the flux near the convective boundary and the viscous dissipation together determine the height of the penetration zone.
-The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} here.
-Future work should aim to understand how these parameters and the theory presented in e.g., Eqn.~\ref{eqn:mesa_eqn} change when these realistic effects are taken into account.
+The precise values of the parameters $f$ and $\xi$ achieved in natural, turbulent, fully compressible, spherical stellar convection may be different from those presented in e.g., Fig.~\ref{fig:parameters_vs_p} and Eqn.~\ref{eqn:f_xi_estimates} here.
+Future work should aim to understand how these parameters and the theory presented in e.g., Eqn.~\ref{eqn:mesa_eqn} change when more realistic effects are taken into account.
 

### 2021-07-27 data/plot_nonturb_dynamics.py

@@ -1,0 +1,139 @@
+import matplotlib
+from collections import OrderedDict
+import numpy as np
+import matplotlib.pyplot as plt
+import h5py
+
+import dedalus.public as de
+plt.style.use('apj')
+
+read_raw_files = False
+if read_raw_files:
+    erf_plot_ind = 12 
+    linear_plot_ind = 16
+    # Get data from files
+    linear_dynamics_file = 'turbulence_slices/linear_3D_Re8e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_128x128x256/slices_s49.h5'
+    linear_profile_file  = 'turbulence_slices/linear_3D_Re8e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_128x128x256/profiles_s49.h5'
+    erf_dynamics_file    = 'turbulence_slices/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart6/slices_s234.h5'
+    erf_profile_file     = 'turbulence_slices/erf_step_3D_Re4e2_P4e0_zeta1e-3_S1e3_Lz2_Lcz1_Pr0.5_a2_Titer0_64x64x256_schwarzschild_restart6/profiles_s234.h5'
+
+    with h5py.File(linear_profile_file, 'r') as f:
+        linear_z = f['scales/z/1.0'][()].squeeze()
+        linear_mean_T1 = np.mean(f['tasks/T1'][()][:,:].squeeze(), axis=0)
+        linear_T1_fluc = np.mean(f['tasks/T1_fluc'][()][:,:].squeeze(), axis=0)
+        grad = -np.mean(f['tasks/T_z'][()][:,:].squeeze(), axis=0)
+        grad_ad = -np.mean(f['tasks/T_ad_z'][()][:,:].squeeze(), axis=0)
+        grad_rad = -np.mean(f['tasks/T_rad_z'][()][:,:].squeeze(), axis=0)
+
+        departure_frac = 0.5
+        departed_points = (linear_z > 1)*(grad > grad_ad - departure_frac * (grad_ad - grad_rad))
+        linear_departure_point = linear_z[departed_points][-1]
+
+    with h5py.File(erf_profile_file, 'r') as f:
+        erf_z = f['scales/z/1.0'][()].squeeze()
[…]

### 2021-07-27 data/plot_parameter_space.py

@@ -62,9 +62,15 @@ case1 = ax.scatter(P[cut1], Re[cut1], marker='o', c=brewer_purple, s=10, label='
 hh=[case1, case1sf, case2]
 ax.legend(hh,[H.get_label() for H in hh], fontsize=9)
 
-ax.scatter(4, 400, marker='x', c=brewer_green)
+
+ax.scatter(4, 400, marker='s', s=80, edgecolor=brewer_purple, facecolor=(1,1,1,0))
+ax.scatter(4, 800, marker='s', s=80, edgecolor=brewer_orange, facecolor=(1,1,1,0))
+
+ax.scatter(4, 400, marker='x', s=60, c=brewer_green)
 ax.set_xlabel(r'$\mathcal{P}$')
 ax.set_ylabel(r'$\mathcal{R}$')
+
+
 
 
 ax.set_xscale('log')

### 2021-07-27 data/plot_results_vs_p.py

@@ -9,6 +9,11 @@ page_width = 6.5
 golden_ratio = 1.61803398875
 
 
+brewer_green  = np.array(( 27,158,119, 255))/255
+brewer_orange = np.array((217, 95,  2, 255))/255
+brewer_purple = np.array((117,112,179, 255))/255
+
+
 data = np.genfromtxt('scalar_table_data.csv', skip_header=1, delimiter=',', dtype=np.unicode_)
 S  = np.array(data[:,0], dtype=np.float64)
 P  = np.array(data[:,1], dtype=np.float64)
@@ -65,6 +70,10 @@ ax1.scatter(P[good], d05[good], c='k', label=r"$\delta_{0.5}$", zorder=1, marker
 ax1.scatter(P[good], d01[good], c='k', label=r"$\delta_{0.1}$", zorder=1, marker='^')
 ax1_1.scatter(P[good], f[good], c='k')
 ax1_2.scatter(P[good], xi[good], c='k')
+
+ax1.scatter(P[good*(P==4)], d05[good*(P==4)], marker='s',  s=150, edgecolor=brewer_purple, facecolor=(1,1,1,0))
+ax1_1.scatter(P[good*(P==4)], f[good*(P==4)], marker='s',  s=100, edgecolor=brewer_purple, facecolor=(1,1,1,0))
+ax1_2.scatter(P[good*(P==4)], xi[good*(P==4)], marker='s', s=100, edgecolor=brewer_purple, facecolor=(1,1,1,0))
 leg1 = ax1.legend(frameon=True, fontsize=10, framealpha=0.6, loc='lower right')
 
 line_P = np.linspace(0, 21, 100)
@@ -92,6 +101,10 @@ ax2.scatter(P[good], d05[good], c='k', zorder=1, marker='o')
 ax2.scatter(P[good], d01[good], c='k', zorder=1, marker='^')
 ax2_1.scatter(P[good], f[good], c='k')
 ax2_2.scatter(P[good], xi[good], c='k')
+
+ax2.scatter(P[good*(P==4)], d05[good*(P==4)], marker='s',  s=150, edgecolor=brewer_orange, facecolor=(1,1,1,0))
+ax2_1.scatter(P[good*(P==4)], f[good*(P==4)], marker='s',  s=100, edgecolor=brewer_orange, facecolor=(1,1,1,0))
[…]

### 2021-07-27 data/plot_results_vs_re.py

@@ -9,6 +9,10 @@ col_width = 3.25
 page_width = 6.5
 golden_ratio = 1.61803398875
 
+brewer_green  = np.array(( 27,158,119, 255))/255
+brewer_orange = np.array((217, 95,  2, 255))/255
+brewer_purple = np.array((117,112,179, 255))/255
+
 calculate_BLs = False
 
 if calculate_BLs:
@@ -125,6 +129,7 @@ ax1.legend(frameon=True, fontsize=8, framealpha=0.6)
 ax1.set_xlabel(r'$\mathcal{R}$')
 ax1.set_ylabel(r'$\delta_{0.5}$')
 ax1.set_xlim(2e1, 7e3)
+ax1.scatter(Re[good_ns*(Re==400)], d05[good_ns*(Re==400)], marker='s',  s=350, edgecolor=brewer_purple, facecolor=(1,1,1,0))
 
 
 ax2.scatter(Re[good_sf], f[good_sf], facecolor=(1,1,1,0.5), color='k', marker='o')
@@ -133,6 +138,7 @@ ax2.set_xscale('log')
 ax2.set_xlabel(r'$\mathcal{R}$')
 ax2.set_ylabel(r'$f$')
 ax2.set_xlim(2e1, 7e3)
+ax2.scatter(Re[good_ns*(Re==400)], f[good_ns*(Re==400)], marker='s',  s=150, edgecolor=brewer_purple, facecolor=(1,1,1,0))
 
 ax3.scatter(Re[good_sf], xi[good_sf], facecolor=(1,1,1,0.5), color='k', marker='o')
 ax3.scatter(Re[good_ns], xi[good_ns], color='k', marker='o', alpha=0.8, s=15)
@@ -140,6 +146,7 @@ ax3.set_xscale('log')
 ax3.set_ylabel(r'$\xi$')
 ax3.set_xlabel(r'$\mathcal{R}$')
 ax3.set_xlim(2e1, 7e3)
+ax3.scatter(Re[good_ns*(Re==400)], xi[good_ns*(Re==400)], marker='s',  s=150, edgecolor=brewer_purple, facecolor=(1,1,1,0))
 
 good_sf *= (Re >= 200)
 good_ns *= (Re >= 200)
@@ -150,6 +157,7 @@ ax4.set_xlabel(r'$f$')
 ax4.set_ylabel(r'$\delta_{0.5}$')
[…]

### 2021-07-27 data/plot_results_vs_s.py

@@ -8,6 +8,10 @@ col_width = 3.25
 page_width = 6.5
 golden_ratio = 1.61803398875
 
+brewer_green  = np.array(( 27,158,119, 255))/255
+brewer_orange = np.array((217, 95,  2, 255))/255
+brewer_purple = np.array((117,112,179, 255))/255
+
 
 data = np.genfromtxt('scalar_table_data.csv', skip_header=1, delimiter=',', dtype=np.unicode_)
 S  = np.array(data[:,0], dtype=np.float64)
@@ -59,6 +63,10 @@ ax1.scatter(S[good], d05[good], c='k', label=r"$\delta_{0.5}$", zorder=1, marker
 ax1.scatter(S[good], d01[good], c='k', label=r"$\delta_{0.1}$", zorder=1, marker='^')
 leg1 = ax1.legend(frameon=True, fontsize=8, framealpha=0.6, loc='upper right')
 ax1.set_xscale('log')
+
+
+ax1.scatter(S[good*(S==1e3)], d05[good*(S==1e3)], marker='s',  s=1200, edgecolor=brewer_purple, facecolor=(1,1,1,0))
+ax2.scatter(S[good*(S==1e3)], (d09-d01)[good*(S==1e3)], marker='s',  s=150, edgecolor=brewer_purple, facecolor=(1,1,1,0))
 
 ax1.set_xlabel(r'$\mathcal{S}$')
 ax1.set_ylabel(r'$\delta_{\rm{p}}$')

### 2021-07-27 manuscript/ms.tex
some small edits

@@
 Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
 Modern numerical experiments often examine the importance of the ``stiffness'' $\mS$ of a radiative-convective interface.
 $\mS$ compares the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
-Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
 Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
@@
 
-There are hints in the literature that convective penetration may be dependent upon energy fluxes.
+There are hints in the literature that convective penetration may depend on energy fluxes.
 \citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
@@
 
+$\,$
 \subsection{Convective penetration \& this study's findings}
@@
 In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
-In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
-Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.
+In Sec.~\ref{sec:solar_model}, we create and discuss a stellar model in MESA which has convective penetration.
+Finally, we discuss pathways for future work in Sec.~\ref{sec:discussion}.
 
@@
 
-We study a sweep through each of the ($\mP_D$, $\mS$, $\mR$) parameter spaces while holding all other parameters constant (see Fig.~\ref{fig:parameter_space}).
-We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
-According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
-
 \begin{figure}[t]
@@
 \caption{
-Each point corresponds to a simulations conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
+Each marker corresponds to a simulation conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
 Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty markers are simulations with stress-free boundary conditions while filled-in markers are simulations with no-slip boundary conditions.
-We additionally conduct simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
+We additionally conduct Case I simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
 The two ``landmark'' simulations are denoted by boxes.
@@
 \end{figure}
+
+We study a sweep through each of the ($\mP_D$, $\mS$, $\mR$) parameter spaces while holding all other parameters constant (see Fig.~\ref{fig:parameter_space}).
+We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
+According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
 
@@
 Convective plumes extend through the penetrative region and impact the stable radiative zone (above the solid horizontal line).
-The interface with the radiative zone is stiff, and so convective motions excite waves at a shallow angle above the radiative-convective boundary.
+The convective motions excite waves at a shallow angle above the stiff radiative-convective boundary.
 We note that the Case II simulation has an additional temperature inversion at the base of the simulation.
@@
 Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
-Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
+Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
 (Left panel) Penetration heights are shown vs.~$\mS$.
@@
 (Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
-Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
+Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
 \label{fig:parameters_vs_re}
@@
 \caption{
-(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a MESA solar model with a penetration zone.
+(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a 1 $M_\odot$ MESA stellar model with a penetration zone.
 (bottom) Sound speed differences between the model shown in the top panel and a standard (std) model run at identical parameters but without a PZ.
@@
 \end{equation}
-where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
+where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the PZ and CZ respectively.
 Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
@@
 We additionally evolved a standard 1 $M_\odot$ MESA model to a 4.56 Gyr age without the inclusion of a PZ.
-We compare the sound speed $c$ profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
+We compare the sound speed ($c$) profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
 When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).
@@
 \label{sec:discussion}
-In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild boundary.
+In this work, we presented dynamical simulations of convective penetration, in which convection mixes ${\justgrad \rightarrow \gradad}$ beyond the Schwarzschild boundary.
 To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
@@
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
-We briefly examined what the impliciations of this theory could be for a simple stellatellarr model.
+We briefly examined what the impliciations of this theory could be for a simple stellar model.
 
@@
 
-Furthermore, it is important to note that stellar opacities, and thus stellar conductivities, are functions of thermodynamic variables rather than radial location.
-As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
-In other words, the combined effects of penetration and entrainment should be considered.
-Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
-
-An additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
+Stellar opacities, and thus stellar radiative conductivities, are functions of thermodynamic variables rather than radial location.
+The formation of a penetration zone will therefore affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
+In other words, convective penetration and entrainment \emph{both} occur in realistic settings, and their combined effects should be studied.
+Future work should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.
+
+Our work here assumes a uniform composition through the convective and radiative region.
+Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
+Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here.
+
+Furthermore, stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
 Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$ and $\xi$.
@@
 
-Our work here assumes a uniform composition through the convective and radiative region.
-Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
-Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).
-
 In summary, we have unified \citet{roxburgh1989}'s integral constraint with \citet{zahn1991}'s theory of flux-dependent penetration into a parameterized theory of convective penetration.
 We tested this theory with simulations and found good agreement between the theory and our simulations.
-In future work, we will aim to more robustly implement this theory into MESA and use simulations to test some of the complicating factors we discussed here.
+In future work, we will use simulations to test some of the complicating factors we discussed here and aim to more robustly implement convective penetration into MESA.
 

### 2021-07-28 manuscript/ms.tex
careful figure caption edits

@@
 A second process called ``\emph{entrainment}'' includes motions which expand convection zones by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
-Convective motions which extend the adiabatically-mixed convective region beyond the convective boundary belong to a third process called ``\emph{convective penetration}.''
-The primary focus of this work is convective penetration.
+The primary focus of this work is a third process called ``\emph{convective penetration}''.
+Convective penetration occurs when motions extend the adiabatically-mixed convective region beyond the Schwarzschild-stable convective boundary.
 
@@
 Vertical slice through a simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ (see Sec.~\ref{sec:simulation_details}).
-The Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line.
+The dashed horizontal line denotes the Schwarzschild convective boundary where $\gradad = \gradrad$.
 The top of the penetrative zone ($\delta_{0.1}$, see Sec.~\ref{sec:simulation_details}) is shown by a solid horizontal line.
@@
 
-Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
+Convective overshoot, entrainment, and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
 Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
@@
 \caption{
-Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in an evolved simulation.
-The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
+Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
+The vertical dashed line denotes the Schwarzschild CZ boundary, and the vertical solid line corresponds to the top of the PZ.
 (upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
@@
 
-We will now describe the setup of the two types of simulations conducted in this work (Case I and Case II).
-As a visual aid, we provide Fig.~\ref{fig:parameter_space} to guide the eye to the portion of parameter space that we have studied in each of these cases.
-We denote two ``landmark cases'' using a purple box (Case I landmark) and an orange box (Case II landmark), and throughout this work we will call out data from these cases with a similar box to guide the eye.
+We now describe the two types of simulations conducted in this work (Case I and Case II).
+We provide Fig.~\ref{fig:parameter_space} to visualize the portion of the parameter space that we have studied.
+We denote two ``landmark cases'' using a purple box (Case I landmark) and an orange box (Case II landmark).
+These landmark cases will be mentioned throughout this work.
 
@@
 \caption{
-Each marker corresponds to a simulation conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
-Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty markers are simulations with stress-free boundary conditions while filled-in markers are simulations with no-slip boundary conditions.
-We additionally conduct Case I simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
-The two ``landmark'' simulations are denoted by boxes.
+Each marker denotes a simulation conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
+Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty circular markers have stress-free (SF) boundary conditions and all other simulations have no-slip boundaries.
+The green ``x'' at $\mP = 4$ and $\mR = 400$ denotes the location in $\mR-\mP$ parameter space where we vary $\mS$ in select Case I simulations.
+Boxes denote the two ``landmark'' simulations.
 The landmark Case I simulation has $\mR = 400$ and $\mP_D = 4$.
@@
 \caption{
-Shown are temperature anomalies in the landmark simulations.
+Temperature anomalies in vertical slices through the landmark simulations.
 (top) Case I landmark ($\mR = 400$, $\mP_D = 4$, $\mS = 10^3$) and (bottom) Case II landmark ($\mR = 800$, $\mP_L = 4$, $\mS = 10^3$).
-The temporally- and volume- averaged Reynolds number in the convection zone is $\sim 250$ in the top panel and $\sim 350$ in the bottom panel.
-As in Fig.~\ref{fig:vertical_dynamics_panels}, the boundary between the penetrative and radiative zones is shown as a solid horizontal line.
-The boundary between the penetrative zone and bulk convection zone is shown as a dashed horizontal line.
-In the bottom panel, there is an additional dashed horizontal line near the bottom of the domain; the linearly increasing conductivity creates a second PZ there where $\justgrad \approx \gradad > \gradrad$ below internal heating layer.
-We see that temperature anomalies have different signs in the bulk CZ and PZ, as in Fig.~\ref{fig:vertical_dynamics_panels}.
+The temporally- and volume- averaged Reynolds number in the CZ is $\sim 250$ in the top panel and $\sim 350$ in the bottom panel.
+A dashed horizontal line denotes the Schwarzschild convective boundary.
+A solid line denotes the boundary between the penetrative and radiative zones.
+The Case II simulation has an additional Schwarzschild boundary near the bottom of the domain due to the conductivity linearly increasing below the internal heating layer.
+As in Fig.~\ref{fig:vertical_dynamics_panels}, temperature anomalies have different signs in the bulk CZ and PZ.
 \label{fig:lessturb_dynamics_panels}
@@
 Time evolution of the landmark Case I simulation ($\mR = 400$, $\mP_D = 4$, $\mS = 10^3$).
-(left top panel) The PZ height $\delta_{0.5}$ vs.~time.
-We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
-The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
+In the top left panel, we plot the PZ height $\delta_{0.5}$ vs.~time.
+Also shown are the time evolution of $f$ (middle left panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (bototm left panel, defined in Eqn.~\ref{eqn:xi_defn}).
+Thin horizontal lines denote the equilibrium values of each trace.
+Vertical lines denote when each trace first converges to within 1\% of its equilibrium value.
 (right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
 The line color denotes the time, following the time traces in the left panels.
-The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
+A horizontal dashed grey line denotes the constant value of $\gradad$.
+The solid grey curve denotes the profile of $\gradrad$.
 The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line.
-The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
+The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as a black line).
 \label{fig:time_evolution}
@@
 \caption{
-Results from the cuts through $\mP$ parameter space for the Case I (left panels; see solid purple circles in Fig.~\ref{fig:parameter_space}) and Case II (right panels; solid orange diamonds in Fig.~\ref{fig:parameter_space}) simulations.
-Boxed data points show the location of landmark simulations from Fig.~\ref{fig:parameter_space}.
+Simulation results vs.~$\mP$ for both Case I (left panels; solid purple circles in Fig.~\ref{fig:parameter_space}) and Case II (right panels; solid orange diamonds in Fig.~\ref{fig:parameter_space}).
+Boxed data points denote landmark simulations from Fig.~\ref{fig:parameter_space}.
 The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
@@
 In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
-We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
+We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi \approx 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
 \label{fig:parameters_vs_p}
@@
 \caption{
-Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
-Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
-(Left panel) Penetration heights are shown vs.~$\mS$.
-While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
-(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
-We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
+Case I simulations results vs.~$\mS$ at $\mR = 400$, $\mP = 4$.
+Boxed data points denote the landmark simulation from Fig.~\ref{fig:parameter_space}.
+(Left panel) Penetration heights vs.~$\mS$.
+While $\delta_{0.1}$ and $\delta_{0.9}$ show some variation, the mean penetration height ($\delta_{0.5}$) is roughly constant.
+(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) vs.~$\mS$.
+We roughly observe a $\mS^{-1/2}$ scaling.
 \label{fig:parameters_vs_s}
@@
 \caption{
-(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations (see vertical cut in Fig.~\ref{fig:parameter_space}).
-We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
-In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
-(Upper middle panel) $f$ also increases with $\mR$.
+(Upper left panel) Penetration heights vs.~$\mR$ for Case I simulations (vertical cuts in Fig.~\ref{fig:parameter_space}).
+Empty markers denote stress-free boundaries (SF) and filled markers denote no-slip boundaries (NS).
+In both cases, we see a roughly logarithmic decrease of $\delp$ vs.~$\mR$.
+(Upper middle panel) $f$ increases with $\mR$.
 (Upper right panel) $\xi$ does not change appreciably with $\mR$ for turbulent simulations with $\mR \geq 200$.
 (Lower left panel) There is a strong correlation between $\delta_{0.5}$ and $f$, agreeing with our theoretical model of Eqn.~\ref{eqn:discontinuous_prediction}.
-(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
-(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
-Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
+(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain.
+(Lower right panel) $\ell_\nu$ follows a well-known convective scaling law, so $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
+Boxed data points denote the landmark simulation from Fig.~\ref{fig:parameter_space}.
 \label{fig:parameters_vs_re}
@@
 \label{fig:AE_time_figure}
-(top row) Time traces of $\delta_{0.5}$ for simulations using standard timestepping (black lines), accelerated evolution with large initial values of $\delp$ (orange lines), and accelerated evolution with small initial values of $\delp$ (green lines).
-The thin horizontal lines represent the final converged values from the standard timestepping simulations.
+(top row) Time traces of $\delta_{0.5}$ for simulations using standard timestepping (black lines), accelerated simulations with large initial values of $\delp$ (orange lines), and accelerated simulations with small initial values of $\delp$ (green lines).
+Thin horizontal lines denote the equilibrated value of $\delta_{0.5}$.
 Accelerated evolution timesteps can be seen as jumps in the $\delp$ trace.
-Once the procedure gets to within a few percent of the appropriate value, any large steps away from the ``correct'' solution are quickly reversed.
+After converging to within a few percent, the accelerated evolution procedure ``jitters'' around the equilibrated value.
 Time units are normalized by the total run time of the simulation.
-All accelerated evolution simulations were run for $t_{\rm{sim}} = 3000$ freefall times.
-The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 2.2 \times 10^4$ ($\mP_D = 2$), and $t_{\rm{sim}} = 5.7 \times 10^4$ ($\mP_D = 4$) freefall times.
-The vertical green-and-yellow bars show the total simulation time of the accelerated simulation in terms of the direct simulation time; i.e., the accelerated simulation converged in only $\sim$ 5\% of the simulation time of the direct simulation for $\mP = 4$.
+Accelerated simulations were run for $t_{\rm{sim}} = 3000$ freefall times.
+The standard timestepping (black line) simulations were run for $t_{\rm{sim}} = 1.2 \times 10^4$ ($\mP_D = 1$), $t_{\rm{sim}} = 3.2 \times 10^4$ ($\mP_D = 2$), and $t_{\rm{sim}} = 6.7 \times 10^4$ ($\mP_D = 4$) freefall times.
+The vertical green-and-yellow lines show the total simulation time of the accelerated simulation in terms of the direct simulation time; i.e., the accelerated simulation converged in only $\sim$ 5\% of the simulation time of the direct simulation for $\mP = 4$.
 (Bottom row) Rolling average of $f$ over 200 freefall times, plotted in the same way as $\delta_{0.5}$.

### 2021-07-28 manuscript/ms.tex
ms ready for shipping

@@
 Motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles belong to a process called ``\emph{convective overshoot}'' in the fluid dynamics literature.
-A second process called ``\emph{entrainment}'' includes motions which expand convection zones by eroding composition gradients or modifying the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
+Convection zones can expand through a second process called ``\emph{entrainment},'' through which motions erode composition gradients or modify the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
 The primary focus of this work is a third process called ``\emph{convective penetration}''.
-Convective penetration occurs when motions extend the adiabatically-mixed convective region beyond the Schwarzschild-stable convective boundary.
+Convective penetration occurs when motions mix the entropy gradient towards the adiabatic in a region that is stable by the Schwarzschild criterion.
 
@@
 (top) Case I landmark ($\mR = 400$, $\mP_D = 4$, $\mS = 10^3$) and (bottom) Case II landmark ($\mR = 800$, $\mP_L = 4$, $\mS = 10^3$).
-The temporally- and volume- averaged Reynolds number in the CZ is $\sim 250$ in the top panel and $\sim 350$ in the bottom panel.
+The temporally- and volume- averaged Reynolds number in the CZ is $\rm{Re} \sim 250$ in the top panel and $\rm{Re} \sim 350$ in the bottom panel.
 A dashed horizontal line denotes the Schwarzschild convective boundary.
@@
 We display the temperature anomaly in the bottom panel of the Case II simulation with $\mR = 800$, $\mP_L = 4$, and $\mS = 10^3$.
-The bulk reynolds number in the convection zones of these simulations are (top) $\sim 250$ and (bottom) $\sim 350$.
+The bulk Reynolds number in the convection zones of these simulations are (top) $\rm{Re} \sim 250$ and (bottom) $\rm{Re} \sim 350$.
 Thus, these simulations are less turbulent than the simulation in Fig.~\ref{fig:vertical_dynamics_panels} (bulk Re $\sim$ 5000).
@@
 We note that the Case II simulation has an additional temperature inversion at the base of the simulation.
-Case II simulations have a linearly increasing conductivity $k$ in the convection zone, so there is formally a small penetrative region where $\justgrad \approx \gradad > \gradrad$ at the base of the domain below the internal heating layer.
+Case II simulations have a linearly increasing conductivity $k$ in the convection zone, so there is formally a small penetrative region where $\justgrad \approx \gradad > \gradrad$ at the base of the domain below the internal heating layer (lower dotted line in bottom panel of Fig.~\ref{fig:lessturb_dynamics_panels}).
 
@@
 We additionally evolved a standard 1 $M_\odot$ MESA model to a 4.56 Gyr age without the inclusion of a PZ.
-We compare the sound speed ($c$) profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
-When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).
-
-Helioseismic studies have argued that that the solar PZ depth cannot be larger than $\mathcal{O}$(0.05 $H_p$), because larger PZs would result in larger glitches than are detected  \citep[see Sct.~7.2.1 of][for a nice review]{basu2016}.
+We compare the sound speed $c$ profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
+When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile.
+
 In the model shown in Fig.~\ref{fig:mesa_profiles}, we find $H_p \approx 0.082R_\odot$ at the Schwarzschild CZ boundary, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot \sim 0.5 H_p$.
 The inclusion of this PZ leads to an $\mathcal{O}$(2\%) increase in $c$ near the base of the solar convection zone.
-This change in $c$ has the same sign as is necessary to create better agreement between stellar models and helioseismic obserations, but is too large.
-Observations suggest that the change in $c$ should be $\mathcal{O}(1\%)$ \citep{bergemann_serenelli_2014} or that the change in $c^2$ should be $\mathcal{O}(0.4\%)$ \citep{christensen-dalsgaard_etal_2011}.
-While the PZ in Fig.~\ref{fig:mesa_profiles} is larger than helioseismic measures of $c$ suggest is possible, we note that the width of the PZ in this model aligns with the inferred width of the tachocline of $(0.039 \pm 0.013)R_\odot$ \citep{charbonneau_etal_1999}.
+Helioseismic observations suggest a similar increase below the base of the solar convection zone \citep[e.g.,][their Fig. 17]{christensen-dalsgaard_etal_2011}.
+The difference $\Delta c = c_{\rm{PZ}} - c_{\rm{std}}$ that we see in this stellar model of the Sun (Fig.~\ref{fig:mesa_profiles}) has the same sign and roughly the same shape.
+However, the magnitude of the change in $c$ is larger than is observed; literature values include $\Delta c / c \approx \mathcal{O}(1\%)$ \citep{bergemann_serenelli_2014} and $\Delta c^2 / c^2 \approx \mathcal{O}(0.4\%)$ \citep{christensen-dalsgaard_etal_2011}, and our sound speed bump is located at a different radius than the observed bump.
+Other helioseismic studies have argued that that the solar PZ depth cannot be larger than $\mathcal{O}$(0.05 $H_p$), because larger PZs would result in larger glitches than are detected  \citep[see Sct.~7.2.1 of][for a nice review]{basu2016}.
+It is interesting, however, that the width of the PZ in Fig.~\ref{fig:mesa_profiles} is strikingly similar to the inferred width of the tachocline $(0.039 \pm 0.013)R_\odot$ that is reported by \citet{charbonneau_etal_1999}.
 
@@
 The solar convection zone is highly stratified ($\sim$14 density scale heights), and we neglected density stratification in this work.
-Furthermore, the solar model used here is essentially a ``stock'' MESA model and has some obvious disagreement with the solar model S (e.g., the Schwarzschild base of the CZ should be closer to $r/R_\odot = 0.7$ than it is).
+Furthermore, the solar model used here is essentially a ``stock'' MESA model and has obvious disagreements with the solar model~S \citep[see Fig.~1 in][where the Schwarzschild base of the CZ is $r/R_\odot \approx 0.712$, whereas the one in Fig.~\ref{fig:mesa_profiles} is at $r/R_{\odot} \approx 0.75$]{christensen-dalsgaard_etal_2011}.
 Despite the limitations of this minimal proof of concept, Fig.~\ref{fig:mesa_profiles} shows that our parameterization can produce penetration zones in 1D models with measurable acoustic glitches.
@@
 In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
-We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
+We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region $\delp$ should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
@@
 
-Stellar opacities, and thus stellar radiative conductivities, are functions of thermodynamic variables rather than radial location.
+Stellar opacities and thus stellar radiative conductivities are functions of thermodynamic variables rather than radial location.
 The formation of a penetration zone will therefore affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
@@
 Time-averaged values of the departure heights ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$), the dissipation fraction $f$, and the dissipation fall-off $\xi$, as well as the average convection zone velocity $\angles{u}$ are reported.
-We take these time averages over the final 1000 freefall times of the simulation.
-For short simulations $(t_{\rm{sim}} < 1000)$, we average over most of the simulation run time, but not early dynamical transients.
+We take these time averages over the final 1000 freefall times or half of the simulation, whichever is shorter.
 }                                                          	

### 2021-10-06 manuscript/ms.tex
adds line numbers per apj request
rough draft of response to referee report 1

@@
 % Preamble
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 \usepackage{natbib}
@@
 \usepackage{hyperref}
+\usepackage{xcolor}
 
@@
 
+\newcommand{\editone}[1]{\textcolor{orange}{#1}}
+
 %%%% Journal preamble
@@
 %%%% Title and Abstract
-\title{Convective penetration: It exists and we found it}
+\title{\editone{Stellar convective penetration: parameterized theory and dynamical simulations}}
 \author[0000-0002-3433-4733]{Evan H. Anders}
@@
 This process is phenomenologically described in Sec.~\ref{sec:central_results}.
+\editone{
+    In this work, the convection zone lies beneath an adjacent stable layer and convection penetrates upwards; our results equally apply to the reversed problem.
+}
 
@@
 Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
-However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from $1.04 \lesssim z \lesssim 1.4$.
-Above the PZ, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).
+However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from $1.04 \lesssim z \lesssim 1.3$.
+\editone{
+    At the top of the PZ, between $1.3 \lesssim z \lesssim 1.4$, there is a ``thermal adjustment layer'' where convective motions give way to conductive transport and $\justgrad$ adjusts from $\gradad$ to $\gradrad$.
+    Above $z \gtrsim 1.4$, $\justgrad \approx \gradrad$ in a classical stable radiative zone (RZ).
+}
 
@@
 We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
+    \editone{
+        The dashed vertical line denotes the Schwarzschild boundary of the convection zone (CZ), the greyed region denotes the thermal adjustment layer, and the solid vertical line denotes the bottom of the radiative zone (RZ).
+    }
 \label{fig:grad_profiles}
@@
 %We find that excess KE in the convection zone can cause a penetration zone to form.
-By balancing the excess KE generation in the CZ with buoyancy-braking and dissipation work terms in the PZ, we are able to derive the size of the PZ.
+By balancing the excess KE generation in the CZ with \editone{buoyant deceleration} and dissipation work terms in the PZ, we are able to derive the size of the PZ.
 We find that a description of the size of a theoretical PZ does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.
@@
 Here, the density is decomposed into a uniform, constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We define the velocity vector $\vec{u}$, \editone{the pressure $p$,} the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
 We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
@@
 The vertical dashed line denotes the Schwarzschild CZ boundary, and the vertical solid line corresponds to the top of the PZ.
-(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
-(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
+(upper) Kinetic energy fluxes $\bar{\mathcal{F}_{\editone{z}}}$, which go to zero at the bottom boundary and the top of the PZ.
+    (bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}_{\editone{z}}}$ in the upper panel is similarly normalized).
 The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
@@
 \frac{\partial \mathcal{K}}{\partial t}
-+ \grad\dot\mathcal{F}
+    + \grad\dot\editone{\vec{\mathcal{F}}}
 = \mathcal{B} - \Phi,
@@
 \end{equation}
-where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
+where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\editone{\vec{\mathcal{F}}} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
 We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
@@
 \begin{equation}
-\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
+    \frac{d\bar{\mathcal{F}_{\editone{z}}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi},
 \label{eqn:kinetic_energy_1D}
 \end{equation}
+\editone{where $\mathcal{F}_z$ is the z-component of $\vec{\mathcal{F}}$.}
 Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panels}.
 As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
-In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous flux term which is only nonzero in a small region above the bottom boundary.
-We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
+In the top panel, we display $\bar{\mathcal{F}_{\editone{z}}}$, neglecting the viscous flux term which is only nonzero in a small region above the bottom boundary.
+We see that $\bar{\mathcal{F}_{\editone{z}}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
 In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.
 
-At the boundaries of the convecting region, $\bar{\mathcal{F}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
+At the boundaries of the convecting region, $\bar{\mathcal{F}_{\editone{z}}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
 We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
@@
 This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
-We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
+We see that the viscous dissipation and \editone{buoyant deceleration} felt by flows in the PZ determine its size.
 We now define
@@
 A parameterization like Eqn.~\ref{eqn:theory_fraction} can be implemented in stellar structure codes and used to find the extent of penetration zones under the specification of $f$ and $\xi$.
+\editone{
+    We note that an implementation of Eqn.~\ref{eqn:theory_fraction} likely requires an \emph{iterative} solve, as the penetration zone depth ($\delp$) and thus the PZ integral of the flux, are not known \emph{a-priori}.
+}
 The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
@@
 When $\mP \sim 1$, both terms matter.
+\editone{
+    In this work, we have assumed that $\mP$ and $\xi$ are fully independent parameters.
+    We make this choice because $\mP$ can be determined directly from a known conductivity profile or stratification, whereas $\xi$ is a measurable of evolved nonlinear convective dynamics.
+    However, it is possible that there is an implicit relationship between these parameters (as $\mP$ increases, so too does the extent of the PZ, which likely in turn modifies the value of $\xi$).
+}
 
@@
 Assuming that $f$ and $\xi$ are weak functions of $\mP_D$, we see that, for small $\mP_D$, the size of the penetration region is linearly proportional to $\mP_D$, but saturates as $\mP_D \rightarrow \infty$ due to dissipation.
-Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
+Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the \editone{deceleration caused by} buoyancy in the PZ shrink, resulting in larger penetrative regions (but this growth cannot extend indefinitely).
 
@@
 where $\zeta \equiv (\xi f/2)\sqrt{\mP_L/(1-f)}$.
-We expect the penetration height to be proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$.
+We expect the penetration height to be proportional to $\sqrt{\mP_L}$ for small values of $\mP_L$, and to again saturate at large values of $\mP_L$ \editone{(as $\mP_L \rightarrow \infty$, so too $\zeta \rightarrow \infty$, and $(\sqrt{\zeta^2 + 1} - \zeta) \rightarrow 0$).}
 
@@
 While many simulations of convection interacting with radiative zones have been performed by previous authors, ours differ in two crucial ways.
-First, we construct our experiments so that $\mP$ and $\mS$ can be varied separately.
+First, we construct our experiments so that $\mP$ and $\mS$ can be varied separately \editone{by driving convection with internal heating, thus avoiding strongly superadiabatic boundary layers where $\justgrad \rightarrow \gradrad$}.
 $\mP$ is the ``Penetration Parameter,'' defined in Eqn.~\ref{eqn:theory_P_defn}, which compares the magnitude of the convective flux in the CZ and PZ; $\mS$ is the ``stiffness,'' defined in Eqn.~\ref{eqn:stiffness}, and compares the buoyancy frequency in the stable radiative zone to the convective frequency.
-We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness.
+We suspect that some past experiments have implicitly set $\mP \approx \mS^{-1}$, which would result in negligible penetration for high stiffness \editone{(see discussion following Eqn.~\ref{eqn:stiffness})}.
 Second, as we will show in Sec.~\ref{sec:results}, the development of penetrative zones is a slow process and many prior studies did not evolve simulations for long enough to see these regions grow and saturate.
+
+\editone{
+    In Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, there are nine fundamental input parameters: $\rho_0$, $\alpha$, $g$, $\nu$, $\chi$, $Q$, $\gradad$, $k_{\rm{CZ}}$, and $k_{\rm{RZ}}$.
+    There are four fundamental dimensions (mass, length, time, and temperature), and so we are left with five independent prognostic parameters in setting up our system.
+    For two of these parameters, we will choose the freefall Reynolds number and the Prandtl number, which are analagous to the Rayleigh and Prandtl numbers in Rayleigh-B\'{e}nard convection.
+    The remaining three parameters are $\mS$, $\mP$, and an additional parameter ``$\eta$,'' which we will hold constant and which sets the value of the flux entering the bottom boundary.
+}
 
@@
 
+\editone{
+    Throughout this paper, we assume that the convection zone is roughly adiabatically stratified.
+    We therefore define a dynamical measure of the stiffness, rather than one based on e.g., the superadiabaticity of $\gradrad$ in the convection zone.
+}
 The average convective velocity depends on the magnitude of the convective flux, $\angles{\vec{|u|}} \approx F_H^{1/3} = (Q_{\rm{mag}}\Delta_H)^{1/3}$.
@@
 where $N^2$ is the \brunt$\,$frequency in the radiative zone.
-In our nondimensionalization, $N^2 = \gradad - \gradrad$.
+In our nondimensionalization, $N^2 = \gradad - \gradrad$ in the radiative zone.
 We use $\mS$ as a control parameter.
+
+\editone{
+    In many prior studies, the stiffness has been set by the ratio of the subadiabaticity of $\gradrad$ in the RZ to the superadiabaticity of $\gradrad$ in the CZ,
+    \begin{equation}
+        \mS_{\rm{alt}} = \frac{|\gradrad - \gradad|_{\rm{RZ}}}{|\gradrad - \gradad|_{\rm{CZ}}} = \frac{N^2}{|\gradrad - \gradad|_{\rm{CZ}}}.
+    \end{equation}
+    In those studies, $\mS_{\rm{alt}}$ primarily describes the stratification of the initial state, but it also describes the stratification near superadiabatic boundary layers which drive convection.
+    This differs from the case studied here, in that we use an internal heating function which is offset from the boundary to hold the stratification to adiabatic in the CZ once convection develops.
+    Previous work has not defined $\mP$, but its definition in our current study should apply to previous studies,
+    \begin{equation}
+        \mP = -\frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}}(\gradrad - \gradad)_{\rm{RZ}}}.
+        %= \frac{k_{\rm{CZ}}}{k_{\rm{RZ}} \mS_{\rm{alt}}} = \frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}} \mS}.
+    \end{equation}
+    We note that $\mP$ can be related to $\mS$ and $\mS_{\rm{alt}}$, $\mP = (k_{\rm{CZ}}/k_{\rm{RZ}}) \mS_{\rm{alt}}^{-1} = (k_{\rm{CZ}}/k_{\rm{RZ}}) (\gradrad - \gradad)_{\rm{CZ}} \mS^{-1}$.
+    Our use of internal heating to decouple convective perturbations from $\gradrad$ in the CZ allows us to separately specify these nondimensional parameters.
+}
 
@@
 Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
-We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqns.~\ref{eqn:discontinuous_constants}.
+We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP_D = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqns.~\ref{eqn:discontinuous_constants}.
 %In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
@@
 In the top left panel, we plot the PZ height $\delta_{0.5}$ vs.~time.
-Also shown are the time evolution of $f$ (middle left panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (bototm left panel, defined in Eqn.~\ref{eqn:xi_defn}).
+Also shown are the time evolution of $f$ (middle left panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (bottom left panel, defined in Eqn.~\ref{eqn:xi_defn}).
 Thin horizontal lines denote the equilibrium values of each trace.
@@
 Aside from the degree of turbulence, the dynamics are very similar in Figs.~\ref{fig:vertical_dynamics_panels} \& \ref{fig:lessturb_dynamics_panels}.
-In particular, we observe that hot plumes in the CZ turn into cold plumes in the PZ (as they cross the dashed horizontal lines), and hot downflows in the PZ turn into cold downflows in the CZ.
+In particular, we observe that \editone{relatively} hot plumes in the CZ turn into \editone{relatively} cold plumes in the PZ (as they cross the dashed horizontal lines), and \editone{relatively hot regions in the PZ lie above relatively cold regions in the CZ}.
 Convective plumes extend through the penetrative region and impact the stable radiative zone (above the solid horizontal line).
@@
 
-In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
-$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
-The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line.
-We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
-The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are overplotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
-We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
-
-This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 24 days on 1024 cores for a total of $\sim$600,000 cpu-hours.
-It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
-To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
-We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
-Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
-While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
-In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
-For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
-
 \begin{figure*}[t]
@@
 
+In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
+$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
+The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line.
+We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
+The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are overplotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
+We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
+
+This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 24 days on 1024 cores for a total of $\sim$600,000 cpu-hours.
+It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
+To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
+We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
+Using these values, we take a large ``time step'' forward \editone{to evolve $\delp$.}
+While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
+In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
+For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.
+
 \subsection{Dependence on $\mP$}
@@
 The fixed values of $\mR$ and $\mS$ are shown above these panels.
-We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
+We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data \editone{well at intermediate values of $\mP$} (orange lines).
 At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Figs.~\ref{fig:grad_profiles} \& \ref{fig:time_evolution} and Sec.~\ref{sct:numerics}).
@@
 When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
-As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
+As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly \editone{decelerate} before deflection, resulting in slightly lower bulk velocities.
 A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
@@
 In a future paper, we will produce more realistic models by building upon our parameterization to include the crucial effects of density stratification.
+\editone{
+    We note briefly that the integral formulation of the equations in e.g., Eqn.~\ref{eqn:mesa_eqn} is not aware of the topology of convective perturbations, which depends upon the density stratification across the convective domain.
+    We suspect that relaxing the Boussinesq approximation and accounting for stratification changes the theory by adding explicit stratification terms into the integral constraint, but this derivation is beyond the scope of this work.
+}
 

### 2021-10-06 data/plot_results_vs_re.py

@@ -119,13 +119,13 @@ good_sf = (erf == 1) * (ae == 1) * (sf == 1) * (S == 1e3) * (P == 4)
 good_ns = (erf == 1) * (ae == 1) * (sf == 0) * (S == 1e3) * (P == 4) 
 
 ax1.scatter(Re[good_sf], d09[good_sf], facecolor=(1,1,1,0.5), color='k', marker='v')
-ax1.scatter(Re[good_sf], d05[good_sf], facecolor=(1,1,1,0.5), color='k', marker='o', label='SF')
+ax1.scatter(Re[good_sf], d05[good_sf], facecolor=(1,1,1,0.5), color='k', marker='o', label=r'$\rm{SF}$')
 ax1.scatter(Re[good_sf], d01[good_sf], facecolor=(1,1,1,0.5), color='k', marker='^')
 ax1.scatter(Re[good_ns], d09[good_ns], color='k', marker='v', alpha=0.8, s=15)
-ax1.scatter(Re[good_ns], d05[good_ns], color='k', marker='o', label='NS', alpha=0.8, s=15)
+ax1.scatter(Re[good_ns], d05[good_ns], color='k', marker='o', label=r'$\rm{NS}$', alpha=0.8, s=15)
 ax1.scatter(Re[good_ns], d01[good_ns], color='k', marker='^', alpha=0.8, s=15)
 ax1.set_xscale('log')
-ax1.legend(frameon=True, fontsize=8, framealpha=0.6)
+ax1.legend(frameon=True, fontsize=8, framealpha=0.9)
 ax1.set_xlabel(r'$\mathcal{R}$')
 ax1.set_ylabel(r'$\delta_{0.5}$')
 ax1.set_xlim(2e1, 7e3)

### 2021-10-06 data/plot_theory_profiles.py

@@ -52,6 +52,7 @@ ax_source = fig_theory.add_axes([0.00, 0.00, 1, 0.5])
 
 ax_grad.axvline(1.044, c='k', lw=0.5, ls='--')
 ax_grad.axvline(1.39, c='k', lw=0.5)
+ax_grad.fill_between((1.3, 1.39), 0, 2, facecolor='grey', alpha=0.5, rasterized=True)
 ax_grad.axhline(1, c=brewer_purple, lw=1.5, label=r'$\nabla_{\rm{ad}}$')
 ax_grad.plot(z, grad_rad/grad_ad, c=brewer_orange, label=r'$\nabla_{\rm{rad}}$', lw=1.5)
 ax_grad.plot(z, grad/grad_ad, c=brewer_green, label=r'$\nabla$', lw=2)
@@ -59,7 +60,7 @@ ax_grad.legend(fontsize=10, loc='lower left')
 ax_grad.set_ylim(0.75, 1.2)
 ax_grad.set_ylabel(r'$\nabla/\nabla_{\rm{ad}}$')
 ax_grad.text(0.5, 1.1, 'CZ', ha='center', va='center')
-ax_grad.text(1.044 + (0.39-0.044)/2, 1.1, 'PZ', ha='center', va='center')
+ax_grad.text(1.044 + (0.3-0.044)/2, 1.1, 'PZ', ha='center', va='center')
 ax_grad.text(1.39 + 0.305, 1.1, 'RZ', ha='center', va='center')
 
 
@@ -79,7 +80,7 @@ ax_flux.axhline(0, c='k', lw=0.5)
 ax_flux.plot(z, f_ke_p/0.2, c=brewer_green, lw=2)
 #ax_flux.axvline(brentq(interp1d(z, f_ke_p), 0.05, 0.9), c='k', ls='--')
 #ax_flux.axvline(1.42, c='k')
-ax_flux.set_ylabel(r'$\overline{\mathcal{F}}$')
+ax_flux.set_ylabel(r'$\overline{\mathcal{F}_z}$')
 ax_flux.axvline(1.044, c='k', lw=0.5, ls='--')
 ax_flux.axvline(1.39, c='k', lw=0.5)
 

### 2021-10-07 manuscript/ms.tex
incorporates feedback from adam and daniel

@@
 \editone{
-    At the top of the PZ, between $1.3 \lesssim z \lesssim 1.4$, there is a ``thermal adjustment layer'' where convective motions give way to conductive transport and $\justgrad$ adjusts from $\gradad$ to $\gradrad$.
     Above $z \gtrsim 1.4$, $\justgrad \approx \gradrad$ in a classical stable radiative zone (RZ).
+    Between $1.3 \lesssim z \lesssim 1.4$, there is a PZ-RZ boundary layer (referred to as the ``thermal adjustment layer'' in some prior studies) where convective motions give way to conductive transport and $\justgrad$ adjusts from $\gradad$ to $\gradrad$.
 }
@@
     \editone{
-        The dashed vertical line denotes the Schwarzschild boundary of the convection zone (CZ), the greyed region denotes the thermal adjustment layer, and the solid vertical line denotes the bottom of the radiative zone (RZ).
+        The dashed vertical line denotes the Schwarzschild boundary of the convection zone (CZ), the solid vertical line denotes the bottom of the radiative zone (RZ), and the greyed region denotes the PZ-RZ boundary layer.
     }
@@
 \editone{
-    In Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, there are nine fundamental input parameters: $\rho_0$, $\alpha$, $g$, $\nu$, $\chi$, $Q$, $\gradad$, $k_{\rm{CZ}}$, and $k_{\rm{RZ}}$.
+    Appealing to the Buckingham $\pi$ theorem \citep{buckingham_1914}, we count nine fundamental input parameters in Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}: $\rho_0$, $\alpha g$, $L_s$, $\nu$, $\chi$, $Q$, $\gradad$, $k_{\rm{CZ}}$, and $k_{\rm{RZ}}$.
     There are four fundamental dimensions (mass, length, time, and temperature), and so we are left with five independent prognostic parameters in setting up our system.
     For two of these parameters, we will choose the freefall Reynolds number and the Prandtl number, which are analagous to the Rayleigh and Prandtl numbers in Rayleigh-B\'{e}nard convection.
-    The remaining three parameters are $\mS$, $\mP$, and an additional parameter ``$\eta$,'' which we will hold constant and which sets the value of the flux entering the bottom boundary.
-}
-
-We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
+    The remaining three parameters are $\mS$, $\mP$, and an additional parameter $\eta$, which we will hold constant and which sets the ratio between $\gradrad$ and $\gradad$ in the convection zone (see discussion following Eqn.~\ref{eqn:sim_Q}).
+}
+
+We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$; \editone{mass is nondimensionalized so that the freefall ram pressure $\rho_0(L_s/\tau_{ff})^2$ is one,}
 \begin{equation}
@@
     \begin{equation}
-        \mS_{\rm{alt}} = \frac{|\gradrad - \gradad|_{\rm{RZ}}}{|\gradrad - \gradad|_{\rm{CZ}}} = \frac{N^2}{|\gradrad - \gradad|_{\rm{CZ}}}.
-    \end{equation}
-    In those studies, $\mS_{\rm{alt}}$ primarily describes the stratification of the initial state, but it also describes the stratification near superadiabatic boundary layers which drive convection.
+        \tilde{\mS} = \frac{|\gradrad - \gradad|_{\rm{RZ}}}{|\gradrad - \gradad|_{\rm{CZ}}} = \frac{N^2}{|\gradrad - \gradad|_{\rm{CZ}}}.
+    \end{equation}
+    In those studies, $\tilde{\mS}$ primarily describes the stratification of the initial state, but it also describes the stratification in superadiabatic boundary layers which drive convection.
     This differs from the case studied here, in that we use an internal heating function which is offset from the boundary to hold the stratification to adiabatic in the CZ once convection develops.
@@
         \mP = -\frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}}(\gradrad - \gradad)_{\rm{RZ}}}.
-        %= \frac{k_{\rm{CZ}}}{k_{\rm{RZ}} \mS_{\rm{alt}}} = \frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}} \mS}.
-    \end{equation}
-    We note that $\mP$ can be related to $\mS$ and $\mS_{\rm{alt}}$, $\mP = (k_{\rm{CZ}}/k_{\rm{RZ}}) \mS_{\rm{alt}}^{-1} = (k_{\rm{CZ}}/k_{\rm{RZ}}) (\gradrad - \gradad)_{\rm{CZ}} \mS^{-1}$.
+    \end{equation}
+    We note that $\mP$ can be related to $\mS$ and $\tilde{\mS}$, $\mP = (k_{\rm{CZ}}/k_{\rm{RZ}}) \tilde{\mS}^{-1} = (k_{\rm{CZ}}/k_{\rm{RZ}}) (\gradrad - \gradad)_{\rm{CZ}} \mS^{-1}$.
     Our use of internal heating to decouple convective perturbations from $\gradrad$ in the CZ allows us to separately specify these nondimensional parameters.
-}
-
-Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
+    The distinction between $\mS$ and $\mP$ is perhaps clearer in the language of stellar evolution, where $\mS$ is roughly the inverse Mach number of the convection while $\mP$ is set by the ratio of $\gradrad$ and $\gradad$.
+}
+
+Aside from $\mS$, $\mP$, and $\eta$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
 The value of $\mR$ corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we will vary $\mR$.
@@
 In this work, we measure the 10\% ($\delta_{0.1}$, $h=0.1$), 50\% ($\delta_{0.5}$, $h=0.5$), and 90\% ($\delta_{0.9}$, $h=0.9$) departure points.
-Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the ``thermal adjustment layer.''
+Using \citet{zahn1991}'s terminology, $\delta_{0.5}$ is the mean value of the top of the PZ while $\delta_{0.9} - \delta_{0.1}$ represents the width of the \editone{PZ-RZ boundary layer}. 
 We find that these measurements based on the (slowly-evolving) thermodynamic profile provide a robust and straightforward measurement of penetration height \citep[for a discussion of alternate measurement choices, see][]{pratt_etal_2017}.
@@
 The mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
-The thermal adjustment layer in which $\justgrad$ changes from $\gradad$ in the PZ to $\gradrad$ in the RZ therefore becomes narrower as $\mS$ increases.
+The \editone{PZ-RZ boundary layer} in which $\justgrad$ changes from $\gradad$ to $\gradrad$ becomes narrower as $\mS$ increases.
 To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
@@
 Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ become nonlinear.
-We therefore restrict the simulations in this study to relatively large\footnote{These values are modest compared to astrophysical values, but large for nonlinear simulations.} values of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
+We therefore restrict the simulations in this study to relatively large\footnote{These values are large for nonlinear simulations, but modest compared to astrophysical values.
+\editone{While there is observational uncertainty about the magnitude of deep convective velocities in the Sun, in the MESA model presented in Sct.~\ref{sec:solar_model}, $f_{\rm{conv}} \approx 10^{-6}$ s$^{-1}$ and $N \approx 10^{-3}$ s$^{-1}$, so $\mS \approx 10^6$.}} values of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.
 
@@
 \editone{
-    We note briefly that the integral formulation of the equations in e.g., Eqn.~\ref{eqn:mesa_eqn} is not aware of the topology of convective perturbations, which depends upon the density stratification across the convective domain.
-    We suspect that relaxing the Boussinesq approximation and accounting for stratification changes the theory by adding explicit stratification terms into the integral constraint, but this derivation is beyond the scope of this work.
+    We note briefly that the theory in e.g., Eqn.~\ref{eqn:mesa_eqn} only knows about integral quantities of the convection and does not therefore know about quantities like the filling factor of upflows and downflows which stratification would modify.
+    We suspect that dynamical differences that arise from including stratification would manifest as changes in $f$ and $\xi$, but a detailed exploration is beyond the scope of this work.
 }
@@
 We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
+\editone{
+    These simulations differ from past studies because we separately specify $\mP$ and the stiffness $\mS$, and we allow the simulations to evolve for a very long time or use numerical techniques for rapid evolution.
+}
 We briefly examined what the impliciations of this theory could be for a simple stellar model.
@@
 If $|\Delta \delta_p| > 0.05$, we limit its value to 0.05.
-We calculate the width of the thermal adjustment layer $d_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
+We calculate the width of the \editone{PZ-RZ boundary layer} $d_w$ as the minimum of $\angles{\delta_{0.9} - \delta_{0.5}}_t$ and $\angles{\delta_{0.5} - \delta_{0.1}}_t$.
 We adjust the mean temperature gradient to

### 2021-10-08 manuscript/ms.tex
some small clarifications per advice from daniel; eta -> mu

@@
     For two of these parameters, we will choose the freefall Reynolds number and the Prandtl number, which are analagous to the Rayleigh and Prandtl numbers in Rayleigh-B\'{e}nard convection.
-    The remaining three parameters are $\mS$, $\mP$, and an additional parameter $\eta$, which we will hold constant and which sets the ratio between $\gradrad$ and $\gradad$ in the convection zone (see discussion following Eqn.~\ref{eqn:sim_Q}).
-}
-
-We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$; \editone{mass is nondimensionalized so that the freefall ram pressure $\rho_0(L_s/\tau_{ff})^2$ is one,}
+    The remaining three parameters are $\mS$, $\mP$, and an additional parameter $\mu$, which we will hold constant and which sets the ratio between $\gradrad$ and $\gradad$ in the convection zone.
+}
+
+We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone
+
+\begin{equation}
+    \editone{
+    \tau_{\rm{ff}} = \left(\frac{L_s}{|\alpha| g Q_0}\right)^{1/3},
+}
+\end{equation}
+and the temperature scale of the internal heating over that freefall time $\Delta T$; \editone{mass is nondimensionalized so that the freefall ram pressure $\rho_0(L_s/\tau_{\rm{ff}})^2 = 1$,}
 \begin{equation}
@@
 \\
-&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\,\,\,\,\,
-\grad^* = L_s^{-1} \grad,
+&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t,\,\,\,\,\,
+\grad^* = L_s^{-1} \grad,\,\,\,\,\,
+p^* = \rho_0 u_{\rm{ff}}^2\varpi,
 \\
-&\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
-p^* = \rho_0 u_{\rm{ff}}^2\varpi,
+    &\vec{u}^* = u_{\rm{ff}}\vec{u} = \frac{L_s}{\tau_{\rm{ff}}} \vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
 \\
@@
 We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
-Furthermore, since the conductivity is not zero at the bottom boundary, the adiabatic temperature gradient there carries some flux, $\Fbot = \mu F_H$ and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
+Furthermore, since the conductivity is not zero at the bottom boundary, the adiabatic temperature gradient there carries some flux.
+\editone{
+We specify the flux using
+\begin{equation}
+    \mu \equiv \frac{\Fbot}{F_H}
+    \label{eqn:mu_defn}
+\end{equation}
+}
+and we choose $\mu = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.
 
@@
 
-Aside from $\mS$, $\mP$, and $\eta$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
+Aside from $\mS$, $\mP$, and $\mu$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
 The value of $\mR$ corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we will vary $\mR$.

### 2021-10-08 manuscript/ms.tex
small edits per adam/daniel

@@
 \\
-&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t,\,\,\,\,\,
+&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t,\qquad\qquad\qquad\,\,\,
 \grad^* = L_s^{-1} \grad,\,\,\,\,\,
+\\
+    &\vec{u}^* = u_{\rm{ff}}\vec{u} = \frac{L_s}{\tau_{\rm{ff}}} \vec{u}, \qquad\qquad
 p^* = \rho_0 u_{\rm{ff}}^2\varpi,
-\\
-    &\vec{u}^* = u_{\rm{ff}}\vec{u} = \frac{L_s}{\tau_{\rm{ff}}} \vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
 \\
@@
     In those studies, $\tilde{\mS}$ primarily describes the stratification of the initial state, but it also describes the stratification in superadiabatic boundary layers which drive convection.
-    This differs from the case studied here, in that we use an internal heating function which is offset from the boundary to hold the stratification to adiabatic in the CZ once convection develops.
+    In this work, we maintain a nearly adiabatic convection zone without strongly superadiabatic regions by driving convection with an internal heating function which is offset from the lower boundary.
+}
+
+\editone{
     Previous work has not defined $\mP$, but its definition in our current study should apply to previous studies,
@@
     Our use of internal heating to decouple convective perturbations from $\gradrad$ in the CZ allows us to separately specify these nondimensional parameters.
-    The distinction between $\mS$ and $\mP$ is perhaps clearer in the language of stellar evolution, where $\mS$ is roughly the inverse Mach number of the convection while $\mP$ is set by the ratio of $\gradrad$ and $\gradad$.
+    The distinction between $\mS$ and $\mP$ is perhaps clearer in the language of stellar evolution, where $\mS$ is roughly the inverse square Mach number of the convection while $\mP$ is set by the ratio of $\gradrad$ and $\gradad$.
 }

### 2021-11-30 manuscript/ms.tex
orange->black text for arxiv; adds dates
edits after referee report 2

@@
 \documentclass[twocolumn, linenumbers]{aastex631}
+%\documentclass[twocolumn]{aastex631}
 \usepackage{natbib}
@@
 
+%\newcommand{\editone}[1]{#1}
 \newcommand{\editone}[1]{\textcolor{orange}{#1}}
+\newcommand{\edittwo}[1]{\textcolor{blue}{#1}}
 
 %%%% Journal preamble
-\received{}
-\revised{}
+\received{July 28, 2021}
+\revised{October 19, 2021}
 \accepted{}
@@
 We test this theory using 3D numerical simulations which employ a simplified Boussinesq model of stellar convection.
-We find significant convective penetration in all simulations.
+\edittwo{
+    We drive convection with internal heating and a height-dependent radiative conductivity rather than in diffusively-dominated boundary layers; this choice allows us to separately specify $\mP$ and the stiffness $\mS$ of the radiative-convective boundary.
+}We find significant convective penetration in all simulations.
 Our simple theory describes the simulations well.
@@
 Motions which extend beyond the convective boundary but do not adjust the thermodynamic profiles belong to a process called ``\emph{convective overshoot}'' in the fluid dynamics literature.
-Convection zones can expand through a second process called ``\emph{entrainment},'' through which motions erode composition gradients or modify the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
+Convection zones can expand through a second process called ``\emph{entrainment},'' through which motions erode composition gradients or modify the radiative gradient \citep[][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, jones_etal_2017, fuentes_cumming_2020, horst_etal_2021}.
 The primary focus of this work is a third process called ``\emph{convective penetration}''.
@@
 Other authors present simulations with dynamical or flux-based hints of penetration such as a negative convective flux or a radiative flux which exceeds the total system flux, but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}.
-Still other simulations show negligible penetration \citep[e.g.,][]{higl_etal_2021}.
+Still other simulations show negligible penetration \citep[e.g.,][]{cai2020, higl_etal_2021}.
 Even detailed studies which sought a relationship between penetration depth and stiffness $\mS$ have presented contradictory results.
@@
 Thus, the penetration length can be calculated using the radiative conductivity (or opacity) \emph{profile} near the convective boundary.
+\edittwo{
+    We present simulations of internally heated convection in which both the Schwarzschild boundary location and the extent of convective penetration depend primarily on the depth-dependent radiative conductivity.
+}
 
@@
 Here, the density is decomposed into a uniform, constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
-We define the velocity vector $\vec{u}$, \editone{the pressure $p$,} the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
+We define the velocity vector $\vec{u}$, \editone{the pressure $p$,} the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity\footnote{
+    \edittwo{
+        In a star, $\chi \equiv k$.
+        We separate these values out of practicality, because simulations are well-resolved and numerically stable when $k \ll \chi$.
+        The maximum vertical wavenumber of the $\bar{T}$ expansion is set by the stiffness (see Eqn.~\ref{eqn:stiffness}), not the radiative diffusivity $k$, so $k$ can be small.
+        On the other hand, an expansion of the turbulent fluctuations $T'$ must include the cutoff wavenumber of the turbulent cascade, which is set by $\chi$.
+        We separate $k$ and $\chi$ in order to explore simulations with a wider range of penetrative behaviors (per Eqn.~\ref{eqn:theory_P_defn}), as the theory presented here depends only on $k$.
+        Note that as we increase the turbulence (the Reynolds number) in our simulations, we decrease $\chi$, and $\chi \rightarrow k$.
+    }
+} $k$.
 We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
@@
 where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
-Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
-We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP_D = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqns.~\ref{eqn:discontinuous_constants}.
-%In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
-},
+Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system,
 \begin{equation}
@@
 \end{equation}
+\edittwo{
+     Eqns.~\ref{eqn:discontinuous_constants} are found by solving the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP_D = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$.
+}
 
@@
 Since $k$ varies with height, formally the values of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
-By this choice\footnote{
-We solve the system of equations where ${F_{\rm{bot}} = k_{\rm{bot}}\gradad}$, ${F_{\rm{bot}} + F_H = k_{\rm{ad}}\gradad}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
-}, we require
+By this choice, we require
 \begin{equation}
@@
 \gradad = f_{\rm{conv}}^2 \mS \psi,
+    \label{eqns:linear_constants}
 \end{equation}
@@
 According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.
+\edittwo{
+    We arrive at Eqns.~\ref{eqns:linear_constants} by solving the system of equations where ${F_{\rm{bot}} = k_{\rm{bot}}\gradad}$, ${F_{\rm{bot}} + F_H = k_{\rm{ad}}\gradad}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
+}
 
@@
 
+\edittwo{
+    Our simulation setup (in which convection is driven by internal heating and stopped by a radiative flux divergence) most closely imitates core convection in massive stars.
+    Other shell or envelope convection zones in stars are driven entirely by divergences in the radiative flux.
+    These divergences act as radiative heating (at the base of the convection zone) and radiative cooling (at the top of the convection zone).
+    We suspect that our simulation setup (and separate specification of $\mP$ and $\mS$) could straightforwardly be implemented in a model where the total flux is constant with height and convection is driven entirely by changes in $k$ with height.
+    Future work should test this by examining three-layer experiments where a CZ sits between two RZs, and the convection is driven at the base by a decrease in $k$ and then stopped by an increase in $k$ at the top.
+    These experiments would help constrain how penetration zone depths change when \emph{two} PZs (one above, one below) must be accounted for in the integral constraint.
+}
+
 Our work here assumes a uniform composition through the convective and radiative region.
@@
 Ben Brown thanks Jeffrey Oishi for many years of discussions about overshooting convection.
-EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
+    \edittwo{
+        We thank the anonymous referee for carefully reading our manuscript, engaging with our science, and helping identify places where our descriptions of our simulations were confusing.
+}EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
 We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.

### 2021-12-02 manuscript/ms.tex
editone text orange -> black per comment from ben
abstract wordsmithing

@@
 
-%\newcommand{\editone}[1]{#1}
-\newcommand{\editone}[1]{\textcolor{orange}{#1}}
+\newcommand{\editone}[1]{#1}
+%\newcommand{\editone}[1]{\textcolor{orange}{#1}}
 \newcommand{\edittwo}[1]{\textcolor{blue}{#1}}
@@
 \begin{abstract}
-Most stars host convection zones in which heat is transported directly by fluid motion.
-Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
+Most stars host convection zones in which heat is transported directly by fluid motion, but the behavior of convective boundaries is not well understood.
 Here we present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
 To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
-Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based theoretical model in which the extent of penetration is controlled by $\mP$.
+Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based theoretical model in which $\mP$ controls the extent of penetration.
 We test this theory using 3D numerical simulations which employ a simplified Boussinesq model of stellar convection.
 \edittwo{
-    We drive convection with internal heating and a height-dependent radiative conductivity rather than in diffusively-dominated boundary layers; this choice allows us to separately specify $\mP$ and the stiffness $\mS$ of the radiative-convective boundary.
+    The convection is driven by internal heating and we use a height-dependent radiative conductivity; this allows us to separately specify $\mP$ and the stiffness $\mS$ of the radiative-convective boundary.
 }We find significant convective penetration in all simulations.
@@
 Penetration zones can take thousands of overturn times to develop, so long simulations or accelerated evolutionary techniques are required.
-In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
+In stars, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
 We present a MESA stellar model of the Sun which employs our parameterization of convective penetration as a proof of concept.
